### 2023-11-14 README.qmd
Parse the IADB dataset into several branches for parallel processing

---
format: gfm
knitr:
  opts_chunk:
    echo: false
    comments: "|"
---

```{r init}

pkgs <- c("targets", "magrittr")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

```

# Source of data

The data is obtained from [IADB](https://iadb.nl/) with a restricted access. After obtaining the access, you may read the following [documentation](https://apodat.iadb.nl/voorbeelden/iadb_vars.html) describing standard IADB variables.

# Getting started

Most of the works in this repository, especially the `R` scripts, should be directly reproducible. You'll need [`git`](https://git-scm.com/downloads), [`R`](https://www.r-project.org/), [`quarto`](https://quarto.org/docs/download/), and more conveniently [RStudio IDE](https://posit.co/downloads/) installed and running well in your system. You simply need to fork/clone this repository using RStudio by following [this tutorial, start right away from `Step 2`](https://book.cds101.com/using-rstudio-server-to-clone-a-github-repo-as-a-new-project.html#step---2). Using terminal in linux/MacOS, you can issue the following command:

```
quarto tools install tinytex
```

This command will install `tinytex` in your path, which is required to compile quarto documents as latex/pdf.  Afterwards, in your RStudio command line, you can copy paste the following code to setup your working directory:

```
install.packages("renv") # Only need to run this step if `renv` is not installed
```

This step will install `renv` package, which will help you set up the `R` environment. Please note that `renv` helps tracking, versioning, and updating packages I used throughout the analysis.

```
renv::restore()
```

This step will read `renv.lock` file and install required packages to your local machine. When all packages loaded properly (make sure there's no error at all), you *have to* restart your R session. Then, you should be able to proceed with:

```
targets::tar_make()
```

This step will read `_targets.R` file, where I systematically draft all of the analysis steps. Once it's done running, you will find the rendered document (either in `html` or `pdf`) inside the `draft` directory.

# What's this all about?

This is the analysis pipeline for conducting analysis in an umbrella review. The complete flow can be viewed in the following `mermaid` diagram:

```{r, results = "asis"}

cat("```mermaid", tar_mermaid(), "```", sep = "\n")

```

### 2023-11-14 _targets.R

@@ -1,0 +1,39 @@
+# Load packages
+pkgs <- c("magrittr", "targets", "tarchetypes", "crew")
+pkgs_load <- sapply(pkgs, library, character.only = TRUE)
+
+# Source user-defined functions
+funs <- list.files("src/R", pattern = "*.R", full.name = TRUE) %>%
+  lapply(source)
+
+# Set options for targets
+tar_option_set(
+  controller = crew_controller_local(workers = 4), # Enable parallel processing
+  storage    = "worker",
+  retrieval  = "worker",
+  memory     = "transient", # Free up superfluous data
+  garbage_collection = TRUE
+)
+
+# Set paths for the raw data
+iadb <- lsData(pattern = "iadb")
+
+# Set the analysis pipeline
+list(
+
+  # Read the dataset then group by date
+  tar_target(tbl_iadb, readIADB(iadb[[2]]), format = "fst_tbl"),
+  tar_group_select(tbl_iadb_by_date, tbl_iadb, by = c("month", "year")),
+
+  # Split ATC in each grouped data frame
+  tar_target(
+    tbl_iadb_split_atc,
+    iterby(tbl_iadb_by_date, "startdat", splitAtc, "atcs"),
+    pattern   = map(tbl_iadb_by_date),
+    iteration = "vector"
+  ),
+
+  # Generate documentation
+  tar_quarto(readme, "README.qmd", priority = 0)
+
+)

### 2023-11-14 src/R/parse.R

@@ -1,0 +1,130 @@
+# Functions to parse the dataset
+
+lsData <- function(path = "data/raw", ...) {
+  #' List Data
+  #'
+  #' List all data file within `path` directory
+  #'
+  #' @param path A path of raw data directory, set to "data/raw" by default
+  #' @return A list of complete relative path of each dataset
+  filepath <- list.files(path, full.name = TRUE, recursive = TRUE, ...) %>%
+    set_names(gsub(x = ., ".*_|\\.\\w*", ""))
+
+  return(filepath)
+}
+
+readIADB <- function(filepath, ...) {
+  #' Read IADB
+  #'
+  #' Read IADB dataset as a tibble using vroom
+  #'
+  #' @param filepath The complete path of the data
+  #' @inheritDotParams vroom::vroom
+  #' @return An indexed tibble data frame
+  tbl <- vroom::vroom(filepath, delim = ";", ...) %>%
+    tibble::add_column(
+      "month" = format(.$startdat, "%m"),
+      "year"  = format(.$startdat, "%y")
+    )
+  
+  return(tbl)
+}
+
+groupAtc <- function(atc_list) {
+  #' Categorize ATC Code
+  #'
+  #' Categorize the ATC code based on WHOCC aggregation groups. For
+  #' ATCs in N group, the second level of aggregation is used. For other
+  #' medications, the first level of aggregation is used.
+  #'
+  #' @param atc_list List of multiple ATC entries for a subject for each
+  #' recorded date
+  #' @return extended list of ATC including its corresponding grouping variable
+  atc_group <- atc_list$label %>%
+    {dplyr::case_when(
+      grepl(x = ., "^A")    ~ "Alimentary and metabolism",
+      grepl(x = ., "^B")    ~ "Blood",
+      grepl(x = ., "^C")    ~ "Cardiovascular",
+      grepl(x = ., "^D")    ~ "Dermatologicals",
+      grepl(x = ., "^G")    ~ "Genitourinary",
+      grepl(x = ., "^H")    ~ "Systemic hormonal",
+      grepl(x = ., "^J")    ~ "Systemic anti-infectives",
+      grepl(x = ., "^L")    ~ "Antineoplastics",
+      grepl(x = ., "^M")    ~ "Musculoskeletal",
+      grepl(x = ., "^N01")  ~ "Anesthetic",
+      grepl(x = ., "^N02")  ~ "Analgesics",
[…]

### 2023-11-15 src/R/network.R
Transform the split ATC into a graph object

@@ -1,0 +1,106 @@
+# Functions to prepare for a graph object
+
+pairByRow <- function(atc_tbl, all = FALSE) {
+  #' Make Pairwise Row Combination
+  #'
+  #' Create a pairwise combination for each row of the input data frame.
+  #' Pairwise combination is created by indexing each row number. Indexed row
+  #' entries are then paired to generate a `from` and `to` field combinations.
+  #' This combination will is useful for generating a graph object (see
+  #' `igraphs::graph.data.frame`).
+  #'
+  #' @param atc_tbl A data frame containing split ATC
+  #' @param all Boolean indicating whether to return a complete list of
+  #' weight or not
+  #' @return A data frame for generating graph object, containing number of
+  #' edges and its weight
+
+  # Set weight
+  atc_tbl %<>% inset2("weight", value = ifelse(.$dose != 0, .$n / .$dose, .$n))
+
+  # Get the combination index
+  id   <- RcppAlgos::comboGeneral(nrow(atc_tbl), 2, nThreads = 2)
+  from <- id[, 1]
+  to   <- id[, 2]
+
+  tbl_from <- atc_tbl[from, ] %>% set_names(paste(names(.), "from", sep = "_"))
+  tbl_to   <- atc_tbl[to, ]   %>% set_names(paste(names(.), "to",   sep = "_"))
+
+  # Combine the column based on the index
+  tbl_pair <- cbind(tbl_from, tbl_to) %>%
+    inset2("weight", value = mean(c(.$weight_from, .$weight_to)))
+  return(tbl_pair)
+
+  # Aggregate the metrics
+  if (all) {
+
+    tbl_agg <- tbl_pair %>% {
+      list(
+        aggregate(n_from ~ group_from + group_to, data = ., sum),
+        aggregate(N_from ~ group_from + group_to, data = ., mean),
+        aggregate(weight ~ group_from + group_to, data = ., sum)
+      )
+    } %>%
+      {Reduce(\(x, y) merge(x, y), .)} %>%
+      set_names(c("from", "to", "n", "N", "weight")) %>%
+      inset2("reg_n", value = .$n / .$N)
+
+  } else {
+
+    tbl_agg <- aggregate(weight ~ group_from + group_to, data = tbl_pair, sum) %>%
+      set_names(c("from", "to", "weight"))
+
+  }
+
+  return(tbl_agg)
+}
+
+mkGraph <- function(atc_tbl) {
+  #' Generate Graph Object
+  #'
[…]

### 2023-11-15 _targets.R
Cancel graph transformation due to resource constraint

@@ -8,6 +8,7 @@ funs <- list.files("src/R", pattern = "*.R", full.name = TRUE) %>%
 
 # Set options for targets
 tar_option_set(
+  error      = "continue",
   controller = crew_controller_local(workers = 4), # Enable parallel processing
   storage    = "worker",
   retrieval  = "worker",
@@ -16,13 +17,17 @@ tar_option_set(
 )
 
 # Set paths for the raw data
-iadb <- lsData(pattern = "iadb")
+iadb_raw <- lsData(pattern = "iadb")
+
+# Switcher for testing or production
+is_test <- FALSE
+iadb    <- ifelse(is_test, iadb_raw[[1]], iadb_raw[[2]])
 
 # Set the analysis pipeline
 list(
 
   # Read the dataset then group by date
-  tar_target(tbl_iadb, readIADB(iadb[[2]]), format = "fst_tbl"),
+  tar_target(tbl_iadb, readIADB(iadb), format = "fst_tbl"),
   tar_group_select(tbl_iadb_by_date, tbl_iadb, by = c("month", "year")),
 
   # Split ATC in each grouped data frame
@@ -32,6 +37,24 @@ list(
     pattern   = map(tbl_iadb_by_date),
     iteration = "vector"
   ),
+
+  ## Generate graph objects from the split ATC data frame
+  #tar_target(
+  #  iadb_graph,
+  #  lapply(tbl_iadb_split_atc, mkGraph),
+  #  pattern   = map(tbl_iadb_split_atc),
+  #  iteration = "list",
+  #  priority  = 0
+  #),
+
+  ## Calculate metrics for the graph objects
+  #tar_target(
+  #  iadb_metrics,
+  #  lapply(iadb_graph, function(branch) {
+  #    lapply(branch, getMetrics) %>% combineMetrics()
+  #  }) %>%
+  #    {do.call(rbind, .)}
+  #),
 
   # Generate documentation
   tar_quarto(readme, "README.qmd", priority = 0)

### 2023-11-15 src/R/parse.R

@@ -87,21 +87,30 @@ splitAtc <- function(tbl, atcs) {
   #' @param tbl IADB data frame
   #' @param atcs A character vector indicating the ATC variable name
   #' @return A tibble containing multiple ATC entries for each recorded date
-  atc_tbls <- tbl[[atcs]] %>% lapply(
-    function(atc) {
-      atc   %<>% as.character() %>% strsplit(split = ",") %>% unlist()
-      label  <-  gsub(x = atc, ";.*", "")
-      dose   <-  atc %>%
-        {gsub(x = ., ".*;|\\s.+", "")} %>%
-        as.numeric()
 
-      tbl <- tibble::tibble(label, dose, "n" = 1) %>%
-        groupAtc() %>%
-        subset(!.$label == "")
+  # Calculate unique patients within the dataset
+  N <- unique(tbl$anopat) %>% length()
 
-      return(tbl)
-    }
-  )
+  # Iterate through a vector of combined ATCs
+  atc_tbls <- apply(tbl, 1, function(entry) {
+    anopat   <- entry[1]
+    startdat <- entry[2]
+    atc      <- entry[4]
+
+    atc   %<>% as.character() %>% strsplit(split = ",") %>% unlist()
+    label  <- gsub(x = atc, ";.*", "")
+    dose   <- atc %>%
+      {gsub(x = ., ".*;|\\s.+", "")} %>%
+      as.numeric()
+
+    tbl <- tibble::tibble(
+      label, dose, "n" = 1, "N" = N, "id" = anopat, "date" = startdat
+    ) %>%
+      groupAtc() %>%
+      subset(.$label != "")
+
+    return(tbl)
+  })
 
   atc_tbl <- do.call(rbind, atc_tbls)
   

### 2023-11-15 src/R/parse.R
Set the column types verbosely

@@ -21,7 +21,8 @@ readIADB <- function(filepath, ...) {
   #' @param filepath The complete path of the data
   #' @inheritDotParams vroom::vroom
   #' @return An indexed tibble data frame
-  tbl <- vroom::vroom(filepath, delim = ";", ...) %>%
+  coltype = "cDDci"
+  tbl <- vroom::vroom(filepath, delim = ";", col_types = coltype, ...) %>%
     tibble::add_column(
       "month" = format(.$startdat, "%m"),
       "year"  = format(.$startdat, "%y")

### 2023-11-15 src/R/network.R
Optimize graph-object generating functions

@@ -1,6 +1,44 @@
 # Functions to prepare for a graph object
 
-pairByRow <- function(atc_tbl, all = FALSE) {
+genLabel <- function() {
+  #' Generate Matrix Label
+  #'
+  #' Generate label for matrix dimension, the label is set to ATC group name by
+  #' default
+  #'
+  #' @return A vector of character object
+  label <- c(
+      "Alimentary and metabolism",
+      "Blood",
+      "Cardiovascular",
+      "Dermatologicals",
+      "Genitourinary",
+      "Systemic hormonal",
+      "Systemic anti-infectives",
+      "Antineoplastics",
+      "Musculoskeletal",
+      "Anesthetic",
+      "Analgesics",
+      "Antiepileptics",
+      "Antiparkinson",
+      "Antipsychotics",
+      "Anxiolytics",
+      "Hypnotics and sedatives",
+      "Antidepressants",
+      "Psychostimulants",
+      "Psycholeptics + psychoanaleptics",
+      "Antidementia",
+      "Other nervous system drugs",
+      "Antiparasitics",
+      "Respiratory",
+      "Sensory",
+      "Others"
+  )
+
+  return(label)
+}
+
+pairByRow <- function(atc_tbl, ..., weight = "weight") {
   #' Make Pairwise Row Combination
   #'
   #' Create a pairwise combination for each row of the input data frame.
@@ -10,8 +48,8 @@ pairByRow <- function(atc_tbl, all = FALSE) {
   #' `igraphs::graph.data.frame`).
   #'
   #' @param atc_tbl A data frame containing split ATC
-  #' @param all Boolean indicating whether to return a complete list of
-  #' weight or not
+  #' @param weight Method to weight, either `n` or `weight`
+  #' @inheritDotParams base::aggregate
   #' @return A data frame for generating graph object, containing number of
   #' edges and its weight
 
@@ -19,40 +57,73 @@ pairByRow <- function(atc_tbl, all = FALSE) {
   atc_tbl %<>% inset2("weight", value = ifelse(.$dose != 0, .$n / .$dose, .$n))
 
   # Get the combination index
-  id   <- RcppAlgos::comboGeneral(nrow(atc_tbl), 2, nThreads = 2)
-  from <- id[, 1]
-  to   <- id[, 2]
[…]

### 2023-11-27 src/R/visualize.R
Set the function to subset or facet based on medication group

@@ -1,6 +1,6 @@
 # Functions to visualize the data
 
-vizDot <- function(tbl, y, ...) {
+vizDot <- function(tbl, y, groupname = NULL, ...) {
   #' Visualize the Dot Plot
   #'
   #' Visualizing the data frame content as a dot plot
@@ -8,22 +8,32 @@ vizDot <- function(tbl, y, ...) {
   #' @param tbl Time-series data frame containing metrics and statistics of
   #' daily medication claims
   #' @param y The time-varying variable to plot
+  #' @param groupname A character object specifying the medication group name.
+  #' If not provided (`null` by default), all groups are shown as a faceted
+  #' plot.
   #' @inheritDotParams ggplot2::facet_wrap
   #' @return A GGPlot object
   require("ggplot2")
 
   labelname <- dplyr::case_when(
     y == "n_claim" ~ "The number of medication claims",
-    y == "n_patient" ~ "The number of patients prescribed for the medication",
+    y == "n_patient" ~ "The number of patients prescribed for a medication",
     y == "claim2patient" ~ "Medication claim to patient ratio",
     y == "eigen" ~ "Eigenvector centrality",
     y == "pagerank" ~ "Page rank centrality"
   )
 
+  if (!is.null(groupname)) {
+    tbl %<>% subset(.$group == groupname)
+  }
+
   plt <- ggplot(tbl, aes(x = date, y = get(y))) +
     geom_point(alpha = 0.4, size = 0.6) +
-    facet_wrap(~group, scales = "free_y", ...) +
     labs(x = "Year", y = labelname)
+
+  if (is.null(groupname)) {
+    plt <- plt + facet_wrap(~group, scales = "free_y", ...)
+  }
 
   return(plt)
 }

### 2023-11-27 src/R/clean.R
Call aggregateTS from mergeTS

@@ -56,7 +56,7 @@ getNeuroMeds <- function() {
   return(res)
 }
 
-mergeTS <- function(tbl_metrics, tbl_stats) {
+mergeTS <- function(tbl_metrics, tbl_stats, ...) {
   #' Merge Time Series Data
   #'
   #' Get the time-series data frame by combining graph-object centrality
@@ -68,6 +68,7 @@ mergeTS <- function(tbl_metrics, tbl_stats) {
   #' @param tbl_metrics A data frame containing node names and its metrics
   #' @param tbl_stats An aggregate data frame summarizing the number of daily
   #' claims for each medication group
+  #' @param ... Parameters to pass on to `aggregateTS`
   #' @return A tidy time-series data frame combining graph's metrics and the
   #' field summary
   tbl <- merge(tbl_metrics, tbl_stats, all.x = TRUE) %>%
@@ -89,9 +90,58 @@ mergeTS <- function(tbl_metrics, tbl_stats) {
       .$date  >= "2018-01-01" &
       .$date  <= "2022-12-31"
     )
+
+  if (hasArg("type")) {
+    ts <- tbl_clean %>% aggregateTS(...)
+    return(ts)
+  }
   
   # Return as a time series
   ts <- tbl_clean %>% tsibble::as_tsibble(key = group, index = date)
 
   return(ts)
 }
+
+aggregateTS <- function(ts, type = "week", ...) {
+  #' Aggregate Time Series
+  #'
+  #' Aggregate time-series data into week, month, or quarter
+  #'
+  #' @param ts A tidy time-series data frame, usually the returned value of
+  #' `mergeTS`. Could also be a data frame containing `index` (and optionally
+  #' `key`) to generate a `tsibble`.
+  #' @param type Type of aggregation, supporting either `week`, `month`, or
+  #' `quarter`
+  #' @return A tidy time-series data with aggregated metrics
+
+  if (type == "week") {
+    ts %<>% inset2("date", value = tsibble::yearweek(.$date))
+  } else if (type == "month") {
+    ts %<>% inset2("date", value = tsibble::yearmonth(.$date))
+  } else if (type == "quarter") {
+    ts %<>% inset2("date", value = tsibble::yearquarter(.$date))
+  } else {
+    warning("Returning time-series of daily records")
+    ts %<>% tsibble::as_tsibble(key = group, index = date)
[…]

### 2023-11-27 src/R/visualize.R
Generate autocorrelation plot

@@ -1,5 +1,63 @@
 # Functions to visualize the data
 
+genColor <- function() {
+  #' Generate Color Palette
+  #'
+  #' Generate the color palette to use when plotting
+  #'
+  #' @return A named list of color palette
+  col_palette <- list(
+    "black"  = "#2E3440",
+    "white"  = "#ECEFF4",
+    "red"    = "#BF616A",
+    "blue"   = "#5E81AC",
+    "green"  = "#8FBCBB",
+    "yellow" = "#EBCB8B",
+    "orange" = "#D08770"
+  )
+
+  return(col_palette)
+}
+
+getLabel <- function(metric) {
+  #' Get Label Name
+  #'
+  #' Get the label name based on the metric names
+  #'
+  #' @param metric A metric name from the time-series data
+  #' @return A character vector signifying the label name
+
+  labelname <- dplyr::case_when(
+    metric == "n_claim" ~ "The number of medication claims",
+    metric == "n_patient" ~ "The number of patients prescribed for a medication",
+    metric == "claim2patient" ~ "Medication claim to patient ratio",
+    metric == "eigen" ~ "Eigenvector centrality",
+    metric == "pagerank" ~ "Page rank centrality"
+  )
+
+  return(labelname)
+}
+
+setStripColor <- function(group) {
+  #' Set Strip Color
+  #'
+  #' Set strip color in a faceted GGPlot2 object
+  #'
+  #' @param group A character vector of medication group, usually containing 25
+  #' groups enlisted in the `setGroupFactor` function
+  #' @return Themed strip as a `ggh4x` object
+  require("ggh4x")
+
+  colors    <- genColor()
+  strip_col <- ggh4x::strip_themed(
+    background_x = ggh4x::elem_list_rect(
+      fill = ifelse(unique(group) %in% getNeuroMeds(), colors$green, "grey90")
+    )
+  )
+
+  return(strip_col)
+}
+
 vizDot <- function(tbl, y, groupname = NULL, ...) {
   #' Visualize the Dot Plot
   #'
@@ -7,33 +65,110 @@ vizDot <- function(tbl, y, groupname = NULL, ...) {
   #'
   #' @param tbl Time-series data frame containing metrics and statistics of
   #' daily medication claims
-  #' @param y The time-varying variable to plot
[…]

### 2023-11-27 docs/methods.qmd
Draft the initial report

# Methods

- Determine confidence interval in ACF: https://stats.stackexchange.com/questions/211628/how-is-the-confidence-interval-calculated-for-the-acf-function

### 2023-11-27 docs/results.qmd
Draft the initial report

---
knitr:
  opts_chunk:
    fig.width: 12
    fig.height: 8
---

```{r init}

pkgs <- c("targets", "magrittr")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

```

# Results

## Descriptive analysis

In this section,

{{< pagebreak >}}

\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

### Time-series on a daily interval

```{r, fig.width = 14}

tar_read(plt_dot_day)[[1]]
tar_read(plt_dot_day)[[2]]
tar_read(plt_dot_day)[[3]]
tar_read(plt_dot_day)[[4]]

```

{{< pagebreak >}}

### Time-series on a weekly interval

```{r, fig.width = 14}

tar_read(plt_dot_week)[[1]]
tar_read(plt_dot_week)[[2]]
tar_read(plt_dot_week)[[3]]
tar_read(plt_dot_week)[[4]]

```

{{< pagebreak >}}

### Time-series on a monthly interval

```{r, fig.width = 14}

tar_read(plt_dot_month)[[1]]
tar_read(plt_dot_month)[[2]]
tar_read(plt_dot_month)[[3]]
tar_read(plt_dot_month)[[4]]

```

{{< pagebreak >}}

### Exploring seasonality within the number of medication claims (day) {#sec-nclaim-day}

```{r}

tar_read(plt_acf_day)[[1]]
tar_read(plt_pacf_day)[[1]]

```

### Exploring seasonality within the number of patients (day) {#sec-npat-day}

```{r}

tar_read(plt_acf_day)[[2]]
tar_read(plt_pacf_day)[[2]]

```

### Exploring seasonality within the claim-to-patient ratio (day) {#sec-ratio-day}

```{r}

tar_read(plt_acf_day)[[3]]
tar_read(plt_pacf_day)[[3]]

```

### Exploring seasonality within the eigenvector centrality (day) {#sec-eigen-day}

```{r}

tar_read(plt_acf_day)[[4]]
tar_read(plt_pacf_day)[[4]]

```

### Exploring seasonality within the number of medication claims (week) {#sec-nclaim-week}

```{r}

tar_read(plt_acf_week)[[1]]
tar_read(plt_pacf_week)[[1]]

```

### Exploring seasonality within the number of patients (week) {#sec-npat-week}

```{r}

tar_read(plt_acf_week)[[2]]
tar_read(plt_pacf_week)[[2]]

```

### Exploring seasonality within the claim-to-patient ratio (week) {#sec-ratio-week}

```{r}

tar_read(plt_acf_week)[[3]]
tar_read(plt_pacf_week)[[3]]

```

### Exploring seasonality within the eigenvector centrality (week) {#sec-eigen-week}

```{r}

tar_read(plt_acf_week)[[4]]
tar_read(plt_pacf_week)[[4]]

```

### Exploring seasonality within the number of medication claims (month) {#sec-nclaim-month}

```{r}

tar_read(plt_acf_month)[[1]]
tar_read(plt_pacf_month)[[1]]

```

### Exploring seasonality within the number of patients (month) {#sec-npat-month}

```{r}

tar_read(plt_acf_month)[[2]]
tar_read(plt_pacf_month)[[2]]

```

### Exploring seasonality within the claim-to-patient ratio (month) {#sec-ratio-month}

```{r}

tar_read(plt_acf_month)[[3]]
tar_read(plt_pacf_month)[[3]]

```

### Exploring seasonality within the eigenvector centrality (month) {#sec-eigen-month}

```{r}

tar_read(plt_acf_month)[[4]]
tar_read(plt_pacf_month)[[4]]

```

### 2023-11-27 _targets.R

@@ -62,36 +62,55 @@ list(
   ),
 
   # Merge graph metrics and descriptive statistics as a time-series data
-  tar_target(iadb_ts, mergeTS(iadb_metrics, iadb_stats)),
+  tar_target(vizDotParams, data.frame(
+    "metrics" = c("n_claim", "n_patient", "claim2patient", "eigen", "pagerank"),
+    "scales"  = c("free_y", "free_y", "fixed", "fixed", "fixed")
+  )),
 
-  # Visualize the data for initial exploration
   tar_map(
     unlist = FALSE,
-    values = tibble::tibble(
-      "y" = c("n_claim", "n_patient", "claim2patient", "eigen", "pagerank")
-    ),
-    tar_target(plt_dot, vizDot(iadb_ts, y = y, nrow = 4))
-  ),
-
-  # Perform time-series decomposition per group of medications
-  tar_target(groupname, unique(iadb_ts$group) %>% as.character()),
-
-  tar_map(
-    unlist = TRUE,
-    values = tidyr::expand_grid(
-      "period" = c(paste(1:3, "week"), paste(1:2, "month")),
-      "method" = c("classic", "loess"),
-      "tvar"   = c("eigen", "pagerank", "claim2patient")
+    values = data.frame("type" = c("day", "week", "month", "quarter")),
+    tar_target(ts, mergeTS(iadb_metrics, iadb_stats, type = type)),
+    tar_target(
+      plt_dot,
+      vizDot(ts, y = vizDotParams$metrics, scales = vizDotParams$scales, nrow = 4),
+      pattern = map(vizDotParams),
+      iteration = "list"
     ),
     tar_target(
-      iadb_decom,
-      timeDecomp(iadb_ts, varname = tvar, group = groupname, period = period, method = method),
-      pattern = map(groupname),
+      plt_acf,
+      vizAutocor(ts, y = vizDotParams$metrics, type = "ACF", lag_max = 12),
+      pattern = map(vizDotParams),
+      iteration = "list"
+    ),
+    tar_target(
+      plt_pacf,
+      vizAutocor(ts, y = vizDotParams$metrics, type = "PACF", lag_max = 12),
+      pattern = map(vizDotParams),
       iteration = "list"
     )
   ),
 
+  ## Perform time-series decomposition per group of medications
+  #tar_target(groupname, unique(ts$group) %>% as.character()),
+
+  #tar_map(
+  #  unlist = TRUE,
[…]

### 2023-11-27 src/R/analyze.R

@@ -61,3 +61,4 @@ timeDecomp <- function(ts, varname, groupname, period, method, ...) {
 
   return(decomp)
 }
+

### 2023-11-28 _targets.R
Export figure as pdf for future use

@@ -71,23 +71,68 @@ list(
     unlist = FALSE,
     values = data.frame("type" = c("day", "week", "month", "quarter")),
     tar_target(ts, mergeTS(iadb_metrics, iadb_stats, type = type)),
+
+    # Visualize the dot plot
     tar_target(
       plt_dot,
       vizDot(ts, y = vizDotParams$metrics, scales = vizDotParams$scales, nrow = 4),
       pattern = map(vizDotParams),
       iteration = "list"
     ),
+
+    # Visualize ACF and PACF
     tar_target(
       plt_acf,
       vizAutocor(ts, y = vizDotParams$metrics, type = "ACF", lag_max = 12),
       pattern = map(vizDotParams),
       iteration = "list"
     ),
+
     tar_target(
       plt_pacf,
       vizAutocor(ts, y = vizDotParams$metrics, type = "PACF", lag_max = 12),
       pattern = map(vizDotParams),
       iteration = "list"
+    ),
+
+    # Write generated plots into the specified dir
+    tar_target(
+      fig_dot,
+      saveFig(
+        plt_dot,
+        path   = "docs/_fig",
+        args   = c("plt_dot", type, vizDotParams$metrics),
+        width  = 14,
+        height = 8
+      ),
+      pattern = map(plt_dot, vizDotParams),
+      format = "file"
+    ),
+
+    tar_target(
+      fig_acf,
+      saveFig(
+        plt_acf,
+        path   = "docs/_fig",
+        args   = c("plt_acf", type, vizDotParams$metrics),
+        width  = 12,
+        height = 8
+      ),
+      pattern = map(plt_acf, vizDotParams),
+      format = "file"
+    ),
+
+    tar_target(
+      fig_pacf,
+      saveFig(
+        plt_pacf,
+        path   = "docs/_fig",
+        args   = c("plt_pacf", type, vizDotParams$metrics),
+        width  = 12,
+        height = 8
+      ),
+      pattern = map(plt_pacf, vizDotParams),
+      format = "file"
     )
   ),
 

### 2023-11-28 src/R/visualize.R

@@ -172,3 +172,19 @@ vizAutocor <- function(ts, y, type = "ACF", ...) {
 
   return(plt)
 }
+
+saveFig <- function(plt, path, args, ...) {
+  #' Save Generated Figure
+  #'
+  #' Save the generated plot as a figure document written the specified path
+  #'
+  #' @param plt A GGPlot2 object
+  #' @param path A specified path to write the figure
+  #' @param args A character vector of arguments to construct the filename
+  #' @inheritDotParams ggplot2::ggsave
+  #' @return This function does not return anything *except* writing the figure
+  #' into the specified path
+  fname <- sprintf("%s.pdf", paste(args, collapse = "_"))
+  fpath <- sprintf("%s/%s", path, fname)
+  ggplot2::ggsave(fpath, plot = plt, device = "pdf", ...)
+}

### 2023-11-30 src/R/report.R
Add functions to report findings

@@ -1,0 +1,58 @@
+# Functions to report results
+
+describe <- function(ts, type, ...) {
+  #' Describe the Time Series
+  #'
+  #' A wrapper function to perform descriptive statistics in a time-series data
+  #'
+  #' @param ts A tidy time-series data frame, usually the output of `mergeTS`
+  #' function
+  #' @param type Type of descriptive analysis to perform
+  #' @param ... Parameters to pass on to `describeMean` or `vizPairs`
+  #' @return A data frame or GGPlot2 object containing the statistical summary
+
+  if (type == "mean") {
+    res <- describeMean(ts, ...)
+  } else if (type == "pair") {
+    res <- vizPair(ts, ...)
+  }
+
+  return(res)
+}
+
+describeMean <- function(ts) {
+  #' Describe the Mean Difference
+  #'
+  #' Describe the mean difference beyond certain time point in a time-series
+  #' data
+  #'
+  #' @param ts A tidy time-series data frame, usually the output of `mergeTS`
+  #' function
+  #' @return A data frame containing the statistical summary
+
+  # Transform the time series into a long-format tibble
+  tbl <- ts %>%
+    tibble::tibble() %>%
+    subset(select = -c(date, neuro_med)) %>%
+    tidyr::pivot_longer(eigen:claim2patient)
+
+  # Calculate the mean difference for all metrics before and after 2019
+  res <- tbl %>%
+    tidyr::nest(data = c(event, value)) %>%
+    dplyr::mutate(
+      "diff" = purrr::map(data, ~ t.test(value ~ event, data = .x)),
+      "tidy_diff" = purrr::map(diff, broom::tidy)
+    ) %>%
+    tidyr::unnest(tidy_diff) %>%
+    subset(select = c(name, group, estimate1, estimate2, estimate, p.value)) %>%
+    dplyr::rename(
+      p = p.value,
+      diff = estimate,
+      metric = name,
+      covid  = estimate1,
+      pre_covid = estimate2
+    ) %>%
+    dplyr::arrange(metric, group)
+
+  return(res)
+}

### 2023-11-30 src/R/visualize.R
Generate a pair plot

@@ -58,6 +58,22 @@ setStripColor <- function(group) {
   return(strip_col)
 }
 
+saveFig <- function(plt, path, args, ...) {
+  #' Save Generated Figure
+  #'
+  #' Save the generated plot as a figure document written the specified path
+  #'
+  #' @param plt A GGPlot2 object
+  #' @param path A specified path to write the figure
+  #' @param args A character vector of arguments to construct the filename
+  #' @inheritDotParams ggplot2::ggsave
+  #' @return This function does not return anything *except* writing the figure
+  #' into the specified path
+  fname <- sprintf("%s.pdf", paste(args, collapse = "_"))
+  fpath <- sprintf("%s/%s", path, fname)
+  ggplot2::ggsave(fpath, plot = plt, device = "pdf", ...)
+}
+
 vizDot <- function(tbl, y, groupname = NULL, ...) {
   #' Visualize the Dot Plot
   #'
@@ -158,7 +174,7 @@ vizAutocor <- function(ts, y, type = "ACF", ...) {
     geom_segment(aes(x = lag, xend = lag, y = 0, yend = ac), alpha = 0.6, lwd = ts_ac$size, color = ts_ac$color) +
     geom_point(alpha = 0.6, size = ts_ac$size, color = ts_ac$color) +
     ggh4x::facet_wrap2(~group, nrow = 4, strip = strip_col) +
-    scale_x_continuous(n.breaks = max(ts_ac$lag) %>% as.numeric()) +
+    scale_x_continuous(n.breaks = max(ts_ac$lag) %>% as.numeric() %>% divide_by(2) %>% round()) +
     labs(
       x = sprintf("Lag (%s)", tsibble:::format.interval(feasts:::interval_pull.cf_lag(ts_ac))),
       y = sprintf("%s of %s", type, labelname),
@@ -173,18 +189,23 @@ vizAutocor <- function(ts, y, type = "ACF", ...) {
   return(plt)
 }
 
-saveFig <- function(plt, path, args, ...) {
-  #' Save Generated Figure
+vizPair <- function(ts, groupname) {
+  #' Generate a Pair Plot
   #'
-  #' Save the generated plot as a figure document written the specified path
+  #' Generate a pair plot to describe the time series
   #'
-  #' @param plt A GGPlot2 object
-  #' @param path A specified path to write the figure
-  #' @param args A character vector of arguments to construct the filename
-  #' @inheritDotParams ggplot2::ggsave
[…]

### 2023-11-30 docs/results.qmd
Export figure as pdf for future use
Perform time-series decomposition, specified for the daily, weekly, and monthly data

@@
 
+options(digits = 2)
+
 ```
@@
 
-## Descriptive analysis
+## Descriptive analysis of the raw data
 
 In this section,
+
+```{r}
+#| tbl-cap: Mean difference of all metrics before and during COVID-19
+
+tar_read(desc_ts) %>% knitr::kable()
+
+```
 
@@
 \recalctypearea
+
+### Paired plot of all metrics for each medication group
+
+```{r}
+
+tar_read(plt_pair)
+
+```
 
@@
 ```
+
+## Descriptive analysis of the deseasonalized data
+
+### Time-series on a daily interval
+
+```{r}
+
+tar_read(plt_decom_ts_day_1.week_classic_n_claim)
+tar_read(plt_decom_ts_day_1.week_classic_claim2patient)
+tar_read(plt_decom_ts_day_1.week_classic_eigen)
+
+```
+
+### Time-series on a weekly interval
+
+```{r}
+
+tar_read(plt_decom_ts_week_1.month_classic_n_claim)
+tar_read(plt_decom_ts_week_1.month_classic_claim2patient)
+tar_read(plt_decom_ts_week_1.month_classic_eigen)
+
+```
+
+### Time-series on a monthly interval
+
+```{r}
+
+tar_read(plt_decom_ts_month_1.year_classic_n_claim)
+tar_read(plt_decom_ts_month_1.year_classic_claim2patient)
+tar_read(plt_decom_ts_month_1.year_classic_eigen)
+
+```

### 2023-11-30 _targets.R

@@ -70,6 +70,8 @@ list(
   tar_map(
     unlist = FALSE,
     values = data.frame("type" = c("day", "week", "month", "quarter")),
+
+    # Merge time-series and calculate the descriptive stat
     tar_target(ts, mergeTS(iadb_metrics, iadb_stats, type = type)),
 
     # Visualize the dot plot
@@ -80,17 +82,17 @@ list(
       iteration = "list"
     ),
 
-    # Visualize ACF and PACF
+    # Visualize the pair plot, ACF, and PACF
     tar_target(
       plt_acf,
-      vizAutocor(ts, y = vizDotParams$metrics, type = "ACF", lag_max = 12),
+      vizAutocor(ts, y = vizDotParams$metrics, type = "ACF", lag_max = 24),
       pattern = map(vizDotParams),
       iteration = "list"
     ),
 
     tar_target(
       plt_pacf,
-      vizAutocor(ts, y = vizDotParams$metrics, type = "PACF", lag_max = 12),
+      vizAutocor(ts, y = vizDotParams$metrics, type = "PACF", lag_max = 24),
       pattern = map(vizDotParams),
       iteration = "list"
     ),
@@ -136,23 +138,38 @@ list(
     )
   ),
 
-  ## Perform time-series decomposition per group of medications
-  #tar_target(groupname, unique(ts$group) %>% as.character()),
+  # Set medication groups for iteration
+  tar_target(med_groups, unique(ts_quarter$group)),
 
-  #tar_map(
-  #  unlist = TRUE,
-  #  values = tidyr::expand_grid(
-  #    "period" = c(paste(1:3, "week"), paste(1:3, "month")),
-  #    "method" = c("classic", "loess"),
-  #    "tvar"   = c("eigen", "pagerank", "claim2patient", "n_claim")
-  #  ),
-  #  tar_target(
-  #    iadb_decom,
-  #    timeDecomp(ts, varname = tvar, group = groupname, period = period, method = method),
-  #    pattern = map(groupname),
-  #    iteration = "list"
-  #  )
-  #),
+  # Descriptive statistics on the time-series data
+  tar_target(desc_ts, describe(ts_day, type = "mean")),
+  tar_target(
+    plt_pair,
+    describe(ts_day, type = "pair", groupname = med_groups),
+    pattern = map(med_groups),
+    iteration = "list"
+  ),
+
+  # Perform time-series decomposition per metrics
+  tar_map(
+    unlist = TRUE,
[…]

### 2023-11-30 src/R/analyze.R

@@ -21,7 +21,7 @@ fieldSummary <- function(tbl) {
   return(res)
 }
 
-timeDecomp <- function(ts, varname, groupname, period, method, ...) {
+timeDecomp <- function(ts, varname, period, method, ...) {
   #' Time Series Decomposition
   #'
   #' An extended wrapper for `stats::decompose` and `stats::stl`, conveniently
@@ -30,7 +30,6 @@ timeDecomp <- function(ts, varname, groupname, period, method, ...) {
   #'
   #' @param ts A time series data, usually resulting form the `mergeTS` function
   #' @param varname A variable name indicating the time series to decompose
-  #' @param groupname The grouping variable to subset data
   #' @param period Period of time when calculating the moving average or LOESS
   #' @param method Method of decomposition, only accepts `classic` (moving
   #' average) and `loess` (LOESS)
@@ -39,11 +38,10 @@ timeDecomp <- function(ts, varname, groupname, period, method, ...) {
   require("feasts")
 
   form <- sprintf("%s ~ season(period = '%s')", varname, period) %>% as.formula()
-  sub_ts <- ts %>% subset(.$group == groupname)
 
   if (method == "classic") {
 
-    decomp <- sub_ts %>%
+    decomp <- ts %>%
       fabletools::model(feasts::classical_decomposition(
         form, ...
       )) %>%
@@ -51,7 +49,7 @@ timeDecomp <- function(ts, varname, groupname, period, method, ...) {
 
   } else if (method == "loess") {
 
-    decomp <- sub_ts %>%
+    decomp <- ts %>%
       fabletools::model(feasts::STL(
         form, iteration = 10
       )) %>%

### 2023-11-30 src/R/clean.R

@@ -78,6 +78,9 @@ mergeTS <- function(tbl_metrics, tbl_stats, ...) {
   tbl_clean <- tbl %>%
     inset2("group", value = setGroupFactor(.$group)) %>% # Set factor
     inset2("neuro_med", value = .$group %in% getNeuroMeds()) %>% # Neuro meds
+    inset2("event", value = { # Pre/during COVID-19
+      ifelse(.$date < "2020-01-30", "Pre-COVID-19", "COVID-19")
+    }) %>%
     inset( # Replace `NA` with 0
       c("n_claim", "claim2patient"),
       value = list(
@@ -137,7 +140,8 @@ aggregateTS <- function(ts, type = "week", ...) {
       "n_claim"       = sum(n_claim, na.rm = TRUE),
       "n_patient"     = sum(n_patient, na.rm = TRUE),
       "claim2patient" = sum(n_claim, na.rm = TRUE) / sum(n_patient, na.rm = TRUE),
-      "neur_med"      = all(neuro_med)
+      "neuro_med"     = all(neuro_med),
+      "event"         = table(event) |> sort() |> names() |> tail(1)
     ) %>%
     dplyr::ungroup() %>%
     tsibble::as_tsibble(key = group, index = date)

### 2023-12-07 docs/methods.qmd
Fit exploratory ARIMA models

@@
 
+- Transform time-series data as a series of graph objects
+- Calculate centrality from each graph, insert it to the original time-series data
+- Smoothen the time-series by aggregating to weekly, monthly, and quarterly interval
+- Evaluate autocorrelation using ACF and PACF plots
 - Determine confidence interval in ACF: https://stats.stackexchange.com/questions/211628/how-is-the-confidence-interval-calculated-for-the-acf-function
+- Perform first-order differencing and time-series decomposition:
+  - Time-series decomposition only applicable to medication claim data in a daily interval, where it shows repeating autocorrelation every seven days
+  - Data in other intervals does not present with seasonality
+  - Choice: Use deseasonalized time-series in a daily interval OR use weekly aggregated data
+  - Decision: Use weekly data because the seasonal pattern in a daily interval only implies administrative patterns (e.g.
+more patients claiming medication during start of the week or weekend, but not mid week)
+- Exploratory ARIMA modelling following the Hyndman-Khandakar algorithm

### 2023-12-07 docs/results/arima.qmd
Fit exploratory ARIMA models

---
knitr:
  opts_chunk:
    fig.width: 12
    fig.height: 7
---

```{r init}

pkgs <- c("targets", "magrittr")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

options(digits = 2)

reportMod <- function(mods) {
  require("kableExtra")
  tar_load(med_groups)
  spec  <- lapply(mods, forecast::arimaorder) %>% sapply(paste, collapse = ", ")
  label <- sprintf("%s (%s)", med_groups, spec)
  res   <- mods %>%
    set_names(label) %>%
    lapply(function(mod) {
      mod %>% lmtest::coeftest() %>% broom::tidy() %>% data.frame()
    }) %>%
    {do.call(rbind, .)} %>%
    tibble::add_column("Model" = gsub(x = rownames(.), "\\..*", ""), .before = 1) %>%
    set_rownames(c()) %>%
    kable(longtable = TRUE, booktabs = TRUE) %>%
    kable_styling(font_size = 10, latex_options = c("repeat_header"))

  return(res)
}

reportLB <- function(mod_evals) {
  require("kableExtra")
  tar_load(med_groups)
  res <- mod_evals %>%
    set_names(med_groups) %>%
    {do.call(rbind, .)} %>%
    set_colnames(c("Ljung-Box", "p")) %>%
    kable(longtable = TRUE, booktabs = TRUE) %>%
    kable_styling(latex_options = c("repeat_header"))

  return(res)
}

```

# Results

## Model evaluation

### Number of claim

#### Model fit

```{r}

tar_read(mod_arima_n_claim) %>% reportMod()

```

#### Portmanteau test

```{r}

tar_read(mod_arima_eval_n_claim) %>% reportLB()

```

### Claim-to-patient ratio

#### Model fit

```{r}

tar_read(mod_arima_claim2patient) %>% reportMod()

```

#### Portmanteau test

```{r}

tar_read(mod_arima_eval_claim2patient) %>% reportLB()

```

### Eigenvector centrality

#### Model fit

```{r}

tar_read(mod_arima_eigen) %>% reportMod()

```

#### Portmanteau test

```{r}

tar_read(mod_arima_eval_eigen) %>% reportLB()

```

{{< pagebreak >}}
\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

## Forecast evaluation

### Number of claim

```{r}

tar_read(plt_arima_forecast_n_claim)

```

{{< pagebreak >}}

### Claim-to-patient ratio

```{r}

tar_read(plt_arima_forecast_claim2patient)

```

{{< pagebreak >}}

### Eigenvector centrality

```{r}

tar_read(plt_arima_forecast_eigen)

```

### 2023-12-07 _targets.R

@@ -71,8 +71,9 @@ list(
     unlist = FALSE,
     values = data.frame("type" = c("day", "week", "month", "quarter")),
 
-    # Merge time-series and calculate the descriptive stat
+    # Merge time-series and calculate the first-degree diff
     tar_target(ts, mergeTS(iadb_metrics, iadb_stats, type = type)),
+    tar_target(ts_diff, timeDiff(ts)),
 
     # Visualize the dot plot
     tar_target(
@@ -171,8 +172,39 @@ list(
     )
   ),
 
+  # Automatically fit an ARIMA model for each medication and metrics
+  tar_map(
+    unlist = FALSE,
+    values = list("y" = c("n_claim", "claim2patient", "eigen")),
+    tar_target(
+      mod_arima,
+      fitModel(ts_week, groupname = med_groups, y = y, type = "arima"),
+      pattern = map(med_groups),
+      iteration = "list"
+    ),
+    tar_target(
+      mod_arima_eval,
+      feasts::ljung_box(mod_arima %>% extract2("residuals")),
+      pattern = map(mod_arima),
+      iteration = "list"
+    ),
+    tar_target(
+      mod_arima_forecast,
+      forecast::forecast(mod_arima),
+      pattern = map(mod_arima),
+      iteration = "list"
+    ),
+    tar_target(
+      plt_arima_forecast,
+      vizArima(mod_arima_forecast, y = y, groupname = med_groups),
+      pattern = map(mod_arima_forecast, med_groups),
+      iteration = "list"
+    )
+  ),
+
   # Generate documentation
-  tar_quarto(report, "docs", profile = "report"),
+  tar_quarto(report_descriptive, "docs", profile = "descriptive"),
+  tar_quarto(report_arima, "docs", profile = "arima"),
   tar_quarto(readme, "README.qmd", priority = 0)
 
 )

### 2023-12-07 src/R/analyze.R

@@ -60,3 +60,49 @@ timeDecomp <- function(ts, varname, period, method, ...) {
   return(decomp)
 }
 
+timeDiff <- function(ts, n = 1, ...) {
+  #' Time-Series Differencing
+  #'
+  #' Perform n-order time-series differencing
+  #'
+  #' @param ts A tidy time series data frame, usually the output of `mergeTS`
+  #' @param n Order of differences
+  #' @inheritDotParams base::diff
+  #' @return A tidy time-series data frame
+  if (is.vector(ts)) {
+    pad     <- rep(NA, n)
+    ts_diff <- c(pad, diff(ts, differences = n, ...))
+  } else {
+    ts_diff <- ts %>%
+      dplyr::group_by(group) %>%
+      dplyr::mutate(
+        eigen         = timeDiff(eigen, n = n, ...),
+        pagerank      = timeDiff(pagerank, n = n, ...),
+        n_claim       = timeDiff(n_claim, n = n, ...),
+        n_patient     = timeDiff(n_patient, n = n, ...),
+        claim2patient = timeDiff(claim2patient, n = n, ...)
+      ) %>%
+      dplyr::ungroup()
+  }
+
+  return(ts_diff)
+}
+
+fitModel <- function(ts, groupname, y, type = "arima", ...) {
+  #' Fit Time-Series Model
+  #'
+  #' Fit a model to explain or forecast time-series data frame
+  #'
+  #' @param ts A tidy time-series data frame
+  #' @param groupname The name of medication group to subset the data
+  #' @param y Metrics to evaluate
+  #' @param type The type of model to fit
+  #' @param ... Parameters to specify the model
+  #' @return A model object
+  sub_ts <- ts %>% subset(.$group == groupname, select = y)
+  if (type == "arima") {
+    mod <- sub_ts %>% forecast::auto.arima(...)
+  }
+
+  return(mod)
+}

### 2023-12-07 src/R/visualize.R

@@ -118,8 +118,6 @@ vizDot <- function(tbl, y, groupname = NULL, ...) {
   return(plt)
 }
 
-vizDot(tar_read(ts_day), "n_claim")
-
 vizAutocor <- function(ts, y, type = "ACF", ...) {
   #' Visualize the Autocorrelation Plot
   #'
@@ -209,3 +207,21 @@ vizPair <- function(ts, groupname) {
   return(plt)
 }
 
+vizArima <- function(mod, y, groupname, ...) {
+  #' Visualize ARIMA forecast
+  #'
+  #' Visualize ARIMA forecast from the `forecast` package using its autoplot
+  #' function
+  #'
+  #' @param mod An ARIMA model, usually the output of `forecast::auto.arima`
+  #' @param y Metric names to set the y label
+  #' @param groupname Medication group name, set as the subtitle
+  #' @return A GGPlot2 object
+  require("ggplot2")
+
+  plt <- forecast::autoplot(mod) +
+    labs(y = getLabel(y), subtitle = groupname) +
+    ggpubr::theme_pubclean()
+
+  return(plt)
+}

### 2024-01-26 docs/index.qmd
Explore monthly seasonality

# Executive Summary {-}

::: {.content-visible when-profile="seasonality"}

Exploration on seasonality is done on monthly data with a first-order difference

:::

### 2024-01-26 docs/results/arima.qmd
Explore monthly seasonality

@@
     lapply(function(mod) {
-      mod %>% lmtest::coeftest() %>% broom::tidy() %>% data.frame()
+      tryCatch(
+        mod %>% lmtest::coeftest() %>% broom::tidy() %>% data.frame(),
+        error = function(e) { # In case error due to no AR nor MA component
+          data.frame(
+            "term" = NA,
+            "estimate" = NA,
+            "std.error" = NA,
+            "statistic" = NA,
+            "p.value" = NA
+          )
+        }
+      )
     }) %>%
+    subset(subset = !is.na(.)) %>%
     {do.call(rbind, .)} %>%

### 2024-01-26 docs/results/seasonality.qmd
Explore monthly seasonality

---
knitr:
  opts_chunk:
    fig.width: 12
    fig.height: 6
---

\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

```{r init}

pkgs <- c("magrittr", "targets")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

options(digits = 2)

```

# Results

## Dot plots

### Time-series on a weekly interval

```{r, fig.width = 14}

tar_read(plt_dot_diff_week)[[1]]
tar_read(plt_dot_diff_week)[[2]]
tar_read(plt_dot_diff_week)[[3]]
tar_read(plt_dot_diff_week)[[4]]

```

{{< pagebreak >}}

## Autocorrelation plots

### Exploring seasonality within the number of medication claims (month) {#sec-nclaim-month}

```{r}

tar_read(plt_acf_diff_month)[[1]]
tar_read(plt_pacf_diff_month)[[1]]

```

### Exploring seasonality within the claim-to-patient ratio (month) {#sec-ratio-month}

```{r}

tar_read(plt_acf_diff_month)[[3]]
tar_read(plt_pacf_diff_month)[[3]]

```

### Exploring seasonality within the eigenvector centrality (month) {#sec-eigen-month}

```{r}

tar_read(plt_acf_diff_month)[[4]]
tar_read(plt_pacf_diff_month)[[4]]

```

{{< pagebreak >}}

\KOMAoptions{paper=portrait,pagesize}
\recalctypearea

## Polar Plots

### Number of claim

```{r}

tar_read(plt_polar_n_claim)

```

{{< pagebreak >}}

### Claim-to-patient ratio

```{r}

tar_read(plt_polar_claim2patient)

```

{{< pagebreak >}}

### Eigenvector centrality

```{r}

tar_read(plt_polar_eigen)

```

### 2024-01-26 _targets.R

@@ -61,12 +61,13 @@ list(
     iadb_stats, lapply(tbl_iadb_split_atc, fieldSummary) %>% combineMetrics()
   ),
 
-  # Merge graph metrics and descriptive statistics as a time-series data
+  # Set iteration parameters of metrics and scales for visualization
   tar_target(vizDotParams, data.frame(
     "metrics" = c("n_claim", "n_patient", "claim2patient", "eigen", "pagerank"),
     "scales"  = c("free_y", "free_y", "fixed", "fixed", "fixed")
   )),
 
+  # Merge graph metrics and descriptive statistics as a time-series data
   tar_map(
     unlist = FALSE,
     values = data.frame("type" = c("day", "week", "month", "quarter")),
@@ -74,6 +75,12 @@ list(
     # Merge time-series and calculate the first-degree diff
     tar_target(ts, mergeTS(iadb_metrics, iadb_stats, type = type)),
     tar_target(ts_diff, timeDiff(ts)),
+    tar_target(ts_diff2, timeDiff(ts, n = 2)),
+
+    # Assess stationarity using the Augmented Dickey-Fuller test
+    tar_target(ts_uroot, evalUnitRoot(ts, y = vizDotParams$metrics), pattern = map(vizDotParams)),
+    tar_target(ts_diff_uroot, evalUnitRoot(ts_diff, y = vizDotParams$metrics), pattern = map(vizDotParams)),
+    tar_target(ts_diff2_uroot, evalUnitRoot(ts_diff2, y = vizDotParams$metrics), pattern = map(vizDotParams)),
 
     # Visualize the dot plot
     tar_target(
@@ -83,31 +90,38 @@ list(
       iteration = "list"
     ),
 
+    tar_target(
+      plt_dot_diff,
+      vizDot(ts_diff, y = vizDotParams$metrics, scales = vizDotParams$scales, nrow = 4),
+      pattern = map(vizDotParams),
+      iteration = "list"
+    ),
+
     # Visualize the pair plot, ACF, and PACF
     tar_target(
       plt_acf,
-      vizAutocor(ts, y = vizDotParams$metrics, type = "ACF", lag_max = 24),
+      vizAutocor(ts, y = vizDotParams$metrics, type = "ACF", lag_max = 52),
       pattern = map(vizDotParams),
       iteration = "list"
     ),
 
     tar_target(
       plt_acf_diff,
[…]

### 2024-01-26 src/R/analyze.R

@@ -88,6 +88,40 @@ timeDiff <- function(ts, n = 1, ...) {
   return(ts_diff)
 }
 
+evalUnitRoot <- function(ts, y, summarize = TRUE) {
+  #' Calculate the Augmented Dickey-Fuller Test
+  #'
+  #' Test for stationarity using the ADF test. Stationary time-series will have
+  #' a significant p-value.
+  #'
+  #' @param ts A time-series data
+  #' @param y Metrics to evaluate
+  #' @param summarize A boolean to return only the summary of time-series
+  #' presenting with non-stationarity
+  #' @return A tidy data frame containing the results of the ADF test
+
+  meds <- ts$group %>% unique() %>% set_names(., .)
+  res  <- lapply(meds, function(med) {
+    ts %>%
+      subset(.$group == med) %>%
+      extract2(y) %>%
+      na.omit() %>%
+      tseries::pp.test() %>% # Calculate the ADF test
+      broom::tidy() %>%
+      data.frame()
+  }) %>%
+    {do.call(rbind, .)} %>% # Combining all results
+    inset2("group", value = rownames(.)) %>%
+    inset2("metric", value = y) %>%
+    tibble::tibble()
+
+  if (summarize) {
+    res %<>% subset(.$p.value >= 0.05, select = c(group, metric))
+  }
+
+  return(res)
+}
+
 fitModel <- function(ts, groupname, y, type = "arima", ...) {
   #' Fit Time-Series Model
   #'

### 2024-01-30 _targets.R
Convert to undirected graph, collapse all weighted edges

@@ -63,7 +63,7 @@ list(
 
   # Set iteration parameters of metrics and scales for visualization
   tar_target(vizDotParams, data.frame(
-    "metrics" = c("n_claim", "n_patient", "claim2patient", "eigen", "pagerank"),
+    "metrics" = c("n_claim", "n_patient", "claim2patient", "eigen", "strength"),
     "scales"  = c("free_y", "free_y", "fixed", "fixed", "fixed")
   )),
 
@@ -184,7 +184,7 @@ list(
     unlist = TRUE,
     values = tidyr::expand_grid(
       "method" = c("classic", "loess"),
-      "tvar"   = c("eigen", "pagerank", "claim2patient", "n_claim")
+      "tvar"   = c("eigen", "strength", "claim2patient", "n_claim")
     ),
     tar_map(
       unlist = TRUE,

### 2024-01-30 src/R/clean.R

@@ -137,6 +137,8 @@ aggregateTS <- function(ts, type = "week", ...) {
       "date"          = min(date),
       "eigen"         = mean(eigen, na.rm = TRUE),
       "pagerank"      = mean(pagerank, na.rm = TRUE),
+      "degree"        = sum(degree, na.rm = TRUE),
+      "strength"      = sum(strength, na.rm = TRUE),
       "n_claim"       = sum(n_claim, na.rm = TRUE),
       "n_patient"     = sum(n_patient, na.rm = TRUE),
       "claim2patient" = sum(n_claim, na.rm = TRUE) / sum(n_patient, na.rm = TRUE),

### 2024-01-30 src/R/network.R

@@ -139,7 +139,8 @@ mkGraph <- function(atc_tbl) {
       mtx <- mkMatrix(atc_tbl, sum)
       igraph::graph_from_adjacency_matrix(
         mtx, weighted = TRUE, mode = "directed"
-      )
+      ) %>%
+        igraph::as.undirected(mode = "collapse")
     },
     error = \(e) NULL
   )
@@ -157,12 +158,14 @@ getMetrics <- function(graph) {
   is_graph <- igraph::is_igraph(graph)
 
   if (is_graph) {
+    degree   <- igraph::degree(graph)
+    strength <- igraph::strength(graph)
     pagerank <- igraph::page_rank(graph) %>% extract2("vector")
     eigen    <- igraph::eigen_centrality(graph) %>%
       extract2("vector") %>%
       divide_by(sum(.))
 
-    metrics <- data.frame(eigen, pagerank) %>%
+    metrics <- data.frame(eigen, pagerank, degree, strength) %>%
       tibble::add_column("group" = rownames(.), .before = 1)
 
     return(metrics)

### 2024-01-30 src/R/visualize.R

@@ -32,7 +32,9 @@ getLabel <- function(metric) {
     metric == "n_patient" ~ "The number of patients prescribed for a medication",
     metric == "claim2patient" ~ "Medication claim to patient ratio",
     metric == "eigen" ~ "Eigenvector centrality",
-    metric == "pagerank" ~ "Page rank centrality"
+    metric == "pagerank" ~ "Page rank centrality",
+    metric == "degree" ~ "Node degree",
+    metric == "strength" ~ "Weighted node degree"
   )
 
   return(labelname)

### 2024-01-31 src/R/visualize.R
Reformat the report

@@ -201,7 +201,7 @@ vizPair <- function(ts, groupname) {
   require("ggplot2")
 
   sub_ts <- ts %>%
-    subset(.$group == groupname, select = c(eigen:claim2patient, event))
+    subset(.$group == groupname, select = c(eigen, strength:claim2patient, event))
 
   plt <- GGally::ggpairs(sub_ts, aes(color = event, alpha = 0.6)) +
     labs(title = groupname)

### 2024-02-05 docs/results/seasonality.qmd
Reformat the report
Plot ACF/PACF and seasonal pattern of detrended data, closes #7, closes #8, CU-86cuhtqv9, CU-86cuhtqz6, CU-86cuhtqmg

@@
   opts_chunk:
-    fig.width: 12
-    fig.height: 6
+    fig.width: 14
+    fig.height: 8
 ---
 
+{{< pagebreak >}}
 \KOMAoptions{paper=landscape,pagesize}
@@
 
-### Time-series on a weekly interval
+### Differenced time-series on a daily interval
 
-```{r, fig.width = 14}
+```{r}
+
+tar_read(plt_dot_diff_day)[-5]
+
+```
+
+### Differenced time-series on a weekly interval
+
+```{r}
 
@@
 
+### Differenced time-series interval on a monthly interval
+
+```{r}
+
+tar_read(plt_dot_diff_month)[-5]
+
+```
+
 {{< pagebreak >}}
 
-## Autocorrelation plots
+## Autocorrelation periodic plots
+
+### Exploring seasonality within the number of medication claims (day) {#sec-nclaim-day}
+
+```{r}
+
+tar_read(plt_period_day)[[1]]
+tar_read(plt_acf_diff_day)[[1]]
+tar_read(plt_pacf_diff_day)[[1]]
+
+```
+
+### Exploring seasonality within the number of patients (day) {#sec-npat-day}
+
+```{r}
+
+tar_read(plt_period_day)[[2]]
+tar_read(plt_acf_diff_day)[[2]]
+tar_read(plt_pacf_diff_day)[[2]]
+
+```
+
+### Exploring seasonality within the claim-to-patient ratio (day) {#sec-ratio-day}
+
+```{r}
+
+tar_read(plt_period_day)[[3]]
+tar_read(plt_acf_diff_day)[[3]]
+tar_read(plt_pacf_diff_day)[[3]]
+
+```
+
+### Exploring seasonality within the eigenvector centrality (day) {#sec-eigen-day}
+
+```{r}
+
+tar_read(plt_period_day)[[4]]
+tar_read(plt_acf_diff_day)[[4]]
+tar_read(plt_pacf_diff_day)[[4]]
+
+```
+
+### Exploring seasonality within the number of medication claims (week) {#sec-nclaim-week}
+
+```{r}
+
+tar_read(plt_period_week)[[1]]
+tar_read(plt_acf_diff_week)[[1]]
+tar_read(plt_pacf_diff_week)[[1]]
+
+```
+
+### Exploring seasonality within the number of patients (week) {#sec-npat-week}
+
+```{r}
+
+tar_read(plt_period_week)[[2]]
+tar_read(plt_acf_diff_week)[[2]]
+tar_read(plt_pacf_diff_week)[[2]]
+
+```
+
+### Exploring seasonality within the claim-to-patient ratio (week) {#sec-ratio-week}
+
+```{r}
+
+tar_read(plt_period_week)[[3]]
+tar_read(plt_acf_diff_week)[[3]]
+tar_read(plt_pacf_diff_week)[[3]]
+
+```
+
+### Exploring seasonality within the eigenvector centrality (week) {#sec-eigen-week}
+
+```{r}
+
+tar_read(plt_period_week)[[4]]
+tar_read(plt_acf_diff_week)[[4]]
+tar_read(plt_pacf_diff_week)[[4]]
+
+```
 
@@
 
+tar_read(plt_period_month)[[1]]
 tar_read(plt_acf_diff_month)[[1]]
 tar_read(plt_pacf_diff_month)[[1]]
+
+```
+
+### Exploring seasonality within the number of patients (month) {#sec-npat-month}
+
+```{r}
+
+tar_read(plt_period_month)[[2]]
+tar_read(plt_acf_diff_month)[[2]]
+tar_read(plt_pacf_diff_month)[[2]]
 
@@
 
+tar_read(plt_period_month)[[3]]
 tar_read(plt_acf_diff_month)[[3]]
@@
 
+tar_read(plt_period_month)[[4]]
 tar_read(plt_acf_diff_month)[[4]]
@@
 ```
-
-{{< pagebreak >}}
-
-\KOMAoptions{paper=portrait,pagesize}
-\recalctypearea
-
-## Polar Plots
-
-### Number of claim
-
-```{r}
-
-tar_read(plt_polar_n_claim)
-
-```
-
-{{< pagebreak >}}
-
-### Claim-to-patient ratio
-
-```{r}
-
-tar_read(plt_polar_claim2patient)
-
-```
-
-{{< pagebreak >}}
-
-### Eigenvector centrality
-
-```{r}
-
-tar_read(plt_polar_eigen)
-
-```

### 2024-02-05 _targets.R

@@ -70,7 +70,7 @@ list(
   # Merge graph metrics and descriptive statistics as a time-series data
   tar_map(
     unlist = FALSE,
-    values = data.frame("type" = c("day", "week", "month", "quarter")),
+    values = data.frame("type" = c("day", "week", "month")),
 
     # Merge time-series and calculate the first-degree diff
     tar_target(ts, mergeTS(iadb_metrics, iadb_stats, type = type)),
@@ -126,6 +126,14 @@ list(
       iteration = "list"
     ),
 
+    # Visualize the periodic patterns
+    tar_target(
+      plt_period,
+      vizPeriod(ts, y = vizDotParams$metrics, period = type, nrow = 4, scales = "free"),
+      pattern = map(vizDotParams),
+      iteration = "list"
+    ),
+
     # Write generated plots into the specified dir
     tar_target(
       fig_dot,
@@ -168,7 +176,7 @@ list(
   ),
 
   # Set medication groups for iteration
-  tar_target(med_groups, unique(ts_quarter$group)),
+  tar_target(med_groups, unique(ts_month$group)),
 
   # Descriptive statistics on the time-series data
   tar_target(desc_ts, describe(ts_day, type = "mean")),

### 2024-02-05 src/R/visualize.R

@@ -87,7 +87,7 @@ vizDot <- function(tbl, y, groupname = NULL, ...) {
   #' @param groupname A character object specifying the medication group name.
   #' If not provided (`null` by default), all groups are shown as a faceted
   #' plot.
-  #' @inheritDotParams ggplot2::facet_wrap
+  #' @inheritDotParams ggh4x::facet_wrap2
   #' @return A GGPlot object
   require("ggplot2")
   require("tsibble")
@@ -224,6 +224,75 @@ vizArima <- function(mod, y, groupname, ...) {
   plt <- forecast::autoplot(mod) +
     labs(y = getLabel(y), subtitle = groupname) +
     ggpubr::theme_pubclean()
+
+  return(plt)
+}
+
+vizPeriod <- function(ts, y, period = "month", groupname = NULL, ...) {
+  #' Visualize Periodic Patterns
+  #'
+  #' Visualize patterns of a time-series data using the period as the x axis
+  #'
+  #' @param ts A time-series data frame, usually `ts_month` or its derivatives
+  #' @param y A metric names of the time-series data
+  #' @param period A period of time to observe the periodicity, currently
+  #' supporting `day`, `week`, and `month`
+  #' @param groupname A character object specifying the medication group name.
+  #' If not provided (`null` by default), all groups are shown as a faceted
+  #' plot.
+  #' @inheritDotParams ggh4x::facet_wrap2
+  #' @return A GGplot2 object
+  require("ggplot2")
+  require("tsibble")
+
+  # Create labels for the plot
+  if (!is.null(groupname)) {
+    ts      %<>% subset(.$group == groupname)
+    plt_lab  <-  labs(title = groupname, x = "", y = getLabel(y))
+  } else {
+    plt_lab  <- labs(x = "", y = getLabel(y))
+  }
+
+  # Prepare the table for plotting
+  ts %<>%
+    aggregateTS(type = period) %>%
+    timeDiff(n = 1) %>% # Dynamically detrending the time series
+    dplyr::mutate(
+      "year"  = lubridate::year(date) %>% ordered(),
+      "xtick" = switch(
+        period,
+        "day"   = lubridate::wday(date, label = TRUE),
+        "week"  = lubridate::week(date) %>% as.ordered(),
+        "month" = lubridate::month(date, label = TRUE)
+      ),
+      "color" = switch(
+        period,
+        "day"   = tsibble::yearweek(date) %>% as.ordered(),
[…]

### 2024-02-05 _targets.R
Explicitly use differenced time series CU-86cuhtqmg

@@ -129,7 +129,7 @@ list(
     # Visualize the periodic patterns
     tar_target(
       plt_period,
-      vizPeriod(ts, y = vizDotParams$metrics, period = type, nrow = 4, scales = "free"),
+      vizPeriod(ts_diff, y = vizDotParams$metrics, period = type, nrow = 4, scales = "free"),
       pattern = map(vizDotParams),
       iteration = "list"
     ),

### 2024-02-05 src/R/visualize.R

@@ -255,8 +255,6 @@ vizPeriod <- function(ts, y, period = "month", groupname = NULL, ...) {
 
   # Prepare the table for plotting
   ts %<>%
-    aggregateTS(type = period) %>%
-    timeDiff(n = 1) %>% # Dynamically detrending the time series
     dplyr::mutate(
       "year"  = lubridate::year(date) %>% ordered(),
       "xtick" = switch(

### 2024-02-05 docs/results/arima.qmd
Reformat the report
Extract and report seasonality orders CU-86cuh2ymc CU-86cuh2vn3

--- 2023-12-07 docs/results/arima.qmd
@@
 
+getArimaParam <- function(mod) {
+  orders <- mod$arma %>% {c(
+    "p" = .[1],
+    "q" = .[2],
+    "P" = .[3],
+    "Q" = .[4],
+    "d" = .[6],
+    "D" = .[7]
+  )}
+  res <- sprintf(
+    "(%s) (%s)",
+    paste(orders[c("p", "d", "q")], collapse = ", "),
+    paste(orders[c("P", "D", "Q")], collapse = ", ")
+  )
+  return(res)
+}
+
 reportMod <- function(mods) {
@@
   tar_load(med_groups)
-  spec  <- lapply(mods, forecast::arimaorder) %>% sapply(paste, collapse = ", ")
-  label <- sprintf("%s (%s)", med_groups, spec)
+  spec  <- lapply(mods, getArimaParam)
+  label <- sprintf("%s %s", med_groups, spec)
   res   <- mods %>%
@@
 
+{{< pagebreak >}}
+
 ### Claim-to-patient ratio
@@
 ```
+
+{{< pagebreak >}}
 

### 2024-02-05 _targets.R
Calculate difference for strength and degree metrics CU-86cuhtr9g CU-86cuhtr9t CU-86cuhtqmg

@@ -255,9 +255,9 @@ list(
   ),
 
   # Generate documentation
-  tar_quarto(report_descriptive, "docs", profile = "descriptive"),
-  tar_quarto(report_arima, "docs", profile = "arima"),
-  tar_quarto(report_seasonality, "docs", profile = "seasonality"),
+  tar_quarto(report_descriptive, "docs", profile = "descriptive", priority = 0),
+  tar_quarto(report_arima, "docs", profile = "arima", priority = 0),
+  tar_quarto(report_seasonality, "docs", profile = "seasonality", priority = 0),
   tar_quarto(readme, "README.qmd", priority = 0)
 
 )

### 2024-02-05 src/R/analyze.R

@@ -69,6 +69,8 @@ timeDiff <- function(ts, n = 1, ...) {
   #' @param n Order of differences
   #' @inheritDotParams base::diff
   #' @return A tidy time-series data frame
+  require("tsibble")
+
   if (is.vector(ts)) {
     pad     <- rep(NA, n)
     ts_diff <- c(pad, diff(ts, differences = n, ...))
@@ -78,6 +80,8 @@ timeDiff <- function(ts, n = 1, ...) {
       dplyr::mutate(
         eigen         = timeDiff(eigen, n = n, ...),
         pagerank      = timeDiff(pagerank, n = n, ...),
+        degree        = timeDiff(degree, n = n, ...),
+        strength      = timeDiff(strength, n = n, ...),
         n_claim       = timeDiff(n_claim, n = n, ...),
         n_patient     = timeDiff(n_patient, n = n, ...),
         claim2patient = timeDiff(claim2patient, n = n, ...)

### 2024-02-06 _targets.R
Fit in a singular spectrum model #9 #6 CU-86cuhtr9g CU-86cuhtqmg

@@ -200,7 +200,7 @@ list(
         "ts_dat" = rlang::syms(paste("ts", c("day", "week", "month"), sep = "_")),
         "period" = paste(1, c("week", "month", "year"))
       ),
-      tar_target(decom, timeDecomp(ts_dat, varname = tvar, period = period, method = method)),
+      tar_target(decom, timeDecom(ts_dat, varname = tvar, period = period, method = method)),
       tar_target(
         plt_decom,
         vizDot(decom, y = "season_adjust", nrow = 4) + labs(y = getLabel(tvar))
@@ -208,7 +208,7 @@ list(
     )
   ),
 
-  # Set variables to fit in an ARIMA model
+  # Set variables to iterate
   tar_map(
     unlist = FALSE,
     values = list("y" = c("n_claim", "claim2patient", "eigen")),
@@ -224,7 +224,7 @@ list(
     # Fit ARIMA models
     tar_target(
       mod_arima,
-      fitModel(ts_month, groupname = med_groups, y = y, type = "arima", test = "pp"),
+      fitModel(ts_week, groupname = med_groups, y = y, FUN = fitArima, test = "pp"),
       pattern = map(med_groups),
       iteration = "list"
     ),
@@ -249,6 +249,14 @@ list(
       plt_arima_forecast,
       vizArima(mod_arima_forecast, y = y, groupname = med_groups),
       pattern = map(mod_arima_forecast, med_groups),
+      iteration = "list"
+    ),
+
+    # Fit SSA models
+    tar_target(
+      mod_ssa,
+      fitModel(ts_week, groupname = med_groups, y = y, FUN = fitSsa, kind = "1d-ssa"),
+      pattern = map(med_groups),
       iteration = "list"
     )
 

### 2024-02-06 src/R/analyze.R

@@ -21,7 +21,7 @@ fieldSummary <- function(tbl) {
   return(res)
 }
 
-timeDecomp <- function(ts, varname, period, method, ...) {
+timeDecom <- function(ts, varname, period, method, ...) {
   #' Time Series Decomposition
   #'
   #' An extended wrapper for `stats::decompose` and `stats::stl`, conveniently
@@ -41,7 +41,7 @@ timeDecomp <- function(ts, varname, period, method, ...) {
 
   if (method == "classic") {
 
-    decomp <- ts %>%
+    decom <- ts %>%
       fabletools::model(feasts::classical_decomposition(
         form, ...
       )) %>%
@@ -49,7 +49,7 @@ timeDecomp <- function(ts, varname, period, method, ...) {
 
   } else if (method == "loess") {
 
-    decomp <- ts %>%
+    decom <- ts %>%
       fabletools::model(feasts::STL(
         form, iteration = 10
       )) %>%
@@ -57,7 +57,7 @@ timeDecomp <- function(ts, varname, period, method, ...) {
 
   }
 
-  return(decomp)
+  return(decom)
 }
 
 timeDiff <- function(ts, n = 1, ...) {
@@ -126,21 +126,3 @@ evalUnitRoot <- function(ts, y, summarize = TRUE) {
   return(res)
 }
 
-fitModel <- function(ts, groupname, y, type = "arima", ...) {
-  #' Fit Time-Series Model
-  #'
-  #' Fit a model to explain or forecast time-series data frame
-  #'
-  #' @param ts A tidy time-series data frame
-  #' @param groupname The name of medication group to subset the data
-  #' @param y Metrics to evaluate
-  #' @param type The type of model to fit
-  #' @param ... Parameters to specify the model
-  #' @return A model object
-  sub_ts <- ts %>% subset(.$group == groupname, select = y)
-  if (type == "arima") {
-    mod <- sub_ts %>% forecast::auto.arima(...)
-  }
-
-  return(mod)
-}

### 2024-02-06 src/R/model.R

@@ -1,0 +1,54 @@
+# Functions to perform modelling
+
+fitModel <- function(ts, groupname, y, FUN, ...) {
+  #' Fit Time-Series Model
+  #'
+  #' Fit a model to explain or forecast time-series data frame
+  #'
+  #' @param ts A tidy time-series data frame
+  #' @param groupname The name of medication group to subset the data
+  #' @param y Metrics to evaluate
+  #' @param FUN The function to fit in a model
+  #' @param ... Parameters to specify the model
+  #' @return A model object
+
+  sub_ts <- ts %>% subset(.$group == groupname, select = y)
+  mod    <- FUN(sub_ts, ...)
+  
+  base::attributes(mod)$group  <- groupname
+  base::attributes(mod)$metric <- y
+
+  return(mod)
+}
+
+fitArima <- function(ts, ...) {
+  #' Fit Auto-ARIMA Model
+  #'
+  #' Fit an auto-ARIMA model following Hyndman-Khandakar algorithm
+  #'
+  #' @param ts A tidy time-series data frame, should be a subset of a metric as
+  #' specified by `fitModel`
+  #' @inheritDotParams forecast::auto.arima
+  #' @return A model object
+  require("forecast")
+
+  mod <- ts %>% forecast::auto.arima(...)
+
+  return(mod)
+}
+
+fitSsa <- function(ts, ...) {
+  #' Fit Singular-Spectrum Model
+  #'
+  #' Fit a singular-spectrum analysis model using the `Rssa` package
+  #'
+  #' @param ts A tidy time-series data frame, should be a subset of a metric as
+  #' specified by `fitModel`
+  #' @inheritDotParams Rssa::ssa
+  #' @return A model object
+  require("Rssa")
+
+  mod <- ts %>% extract2(1) %>% Rssa::ssa(...)
+
+  return(mod)
+}

### 2024-02-06 src/R/spectral.R

@@ -1,0 +1,71 @@
+# Functions to perform spectral analysis, especially manipulate objects from `Rssa`
+
+reconSsa <- function(ssa, naive = TRUE, type = "cor", ...) {
+  #' Reconstruct SSA Decomposition
+  #'
+  #' Reconstruct the SSA model to obtain its constituting functions
+  #'
+  #' @param ssa An SSA model, usually obtained from `fitSsa`
+  #' @param naive A boolean to indicate extracting a naive reconstruction, i.e.
+  #' no prior assumption on groupings
+  #' @param type Type of SSA group to extract, support either `pgram`, `wcor`,
+  #' or `cor`. This argument is passed on to `getSsaGroup` when `naive` is
+  #' `FALSE`.
+  #' @inheritDotParams Rssa::reconstruct
+  require("Rssa")
+
+  args <- list(...)
+
+  if (naive) {
+    recon  <- Rssa::reconstruct(ssa, ...)
+  } else {
+    groups <- getSsaGroup(ssa, type = type)
+    recon  <- Rssa::reconstruct(ssa, groups = groups, ...)
+  }
+
+  ssa_attr <- base::attr(ssa, "group")
+
+  if (!is.null(ssa_attr)) {
+    base::attributes(recon)$group <- ssa_attr
+  }
+
+  return(recon)
+}
+
+getSsaGroup <- function(ssa, type = "cor", ...) {
+  #' Extract SSA Groupings
+  #'
+  #' Extract SSA groupings automatically based on periodogram or correlation
+  #' clusters
+  #'
+  #' @param ssa An SSA model, usually obtained from `fitSsa`
+  #' @param type Type of SSA group to extract, support either `pgram`, `wcor`,
+  #' or `cor`
+  #' @inheritDotParams Rssa::grouping.auto
+  require("Rssa")
+
+  if (type == "cor") {
+
+    naive  <- Rssa::reconstruct(ssa) # Avoid calling `reconSsa` to prevent cyclical call in targets
+    n_col  <- length(naive)
+    mtx    <- unlist(naive) %>% matrix(ncol = n_col) %>% cor(use = "complete.obs")
+    groups <- apply(mtx, 1, \(x) which(abs(x) > 0.5), simplify = FALSE) %>%
+      unique()
+
+  } else if (type == "wcor") {
+
+    groups <- Rssa::grouping.auto.wcor(ssa, ...)
+
[…]

### 2024-02-07 docs/results/spectral.qmd
Report the reconstructed time series, close #9 CU-86cuhtr9g[closed], update #6 CU-86cuhtqmg[in-progress]

---
knitr:
  opts_chunk:
    fig.width: 14
    fig.height: 8
---

\KOMAoptions{paper=landscape,pagesize}
\recalctypearea

```{r init}

pkgs <- c("magrittr", "targets")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)

options(digits = 2)

reportResid <- function(mod) {

  group <- attr(mod, "group")
  res   <- residuals(mod)

  normality <- shapiro.test(res) %>%
    broom::tidy()

  tbl   <- res %>%
    tseries::pp.test() %>%
    broom::tidy() %>%
    subset(select = c("statistic", "p.value", "method")) %>%
    set_colnames(c("stat", "p", "method")) %>%
    inset(c("stat2", "p2", "method2"), value = normality) %>%
    tibble::add_column("group" = group, .before = 1) %>%
    dplyr::mutate(
      "mean"   = mean(res),
      "median" = median(res),
      "sd"     = sd(res),
      "IQR"    = IQR(res)
    )

  return(tbl)
}

```

# Results

## Residuals analysis

### Number of medication claims

```{r}

tar_read(mod_ssa_n_claim) %>%
  lapply(reportResid) %>%
  {do.call(rbind, .)} %>%
  knitr::kable()

```

### Claim-to-patient ratio

```{r}

tar_read(mod_ssa_claim2patient) %>%
  lapply(reportResid) %>%
  {do.call(rbind, .)} %>%
  knitr::kable()

```

### Eigenvector centrality

```{r}

tar_read(mod_ssa_eigen) %>%
  lapply(reportResid) %>%
  {do.call(rbind, .)} %>%
  knitr::kable()

```

{{< pagebreak >}}

## Reconstructed plots

### Number of medication claim

```{r}

tar_read(plt_ssa_recon_n_claim)

```

### Medication claim to patient ratio

```{r}

tar_read(plt_ssa_recon_claim2patient)

```

### Eigenvector centrality

```{r}

tar_read(plt_ssa_recon_eigen)

```

### 2024-02-07 _targets.R

@@ -252,11 +252,26 @@ list(
       iteration = "list"
     ),
 
-    # Fit SSA models
+    # Fit SSA models to decompose the time series based on singular spectrum analysis
     tar_target(
       mod_ssa,
       fitModel(ts_week, groupname = med_groups, y = y, FUN = fitSsa, kind = "1d-ssa"),
       pattern = map(med_groups),
+      iteration = "list"
+    ),
+
+    # Reconstruct decomposed time-series obtained from the SSA models
+    tar_target(
+      mod_ssa_recon,
+      reconSsa(mod_ssa, naive = FALSE, type = "wcor"),
+      pattern = map(mod_ssa),
+      iteration = "list"
+    ),
+
+    tar_target(
+      plt_ssa_recon,
+      vizReconSsa(mod_ssa_recon),
+      pattern = map(mod_ssa_recon),
       iteration = "list"
     )
 
@@ -266,6 +281,7 @@ list(
   tar_quarto(report_descriptive, "docs", profile = "descriptive", priority = 0),
   tar_quarto(report_arima, "docs", profile = "arima", priority = 0),
   tar_quarto(report_seasonality, "docs", profile = "seasonality", priority = 0),
+  tar_quarto(report_spectral, "docs", profile = "spectral", priority = 0),
   tar_quarto(readme, "README.qmd", priority = 0)
 
 )

### 2024-02-07 src/R/analyze.R

@@ -110,7 +110,7 @@ evalUnitRoot <- function(ts, y, summarize = TRUE) {
       subset(.$group == med) %>%
       extract2(y) %>%
       na.omit() %>%
-      tseries::pp.test() %>% # Calculate the ADF test
+      tseries::pp.test() %>% # Calculate the Phillips-Perron test
       broom::tidy() %>%
       data.frame()
   }) %>%

### 2024-02-07 src/R/model.R

@@ -12,11 +12,12 @@ fitModel <- function(ts, groupname, y, FUN, ...) {
   #' @param ... Parameters to specify the model
   #' @return A model object
 
-  sub_ts <- ts %>% subset(.$group == groupname, select = y)
-  mod    <- FUN(sub_ts, ...)
+  sub_ts <- ts %>% subset(.$group == groupname, select = c(y, "date"))
+  mod    <- FUN(sub_ts[y], ...)
   
   base::attributes(mod)$group  <- groupname
   base::attributes(mod)$metric <- y
+  base::attributes(mod)$date   <- sub_ts$date
 
   return(mod)
 }

### 2024-02-07 src/R/spectral.R

@@ -1,6 +1,6 @@
 # Functions to perform spectral analysis, especially manipulate objects from `Rssa`
 
-reconSsa <- function(ssa, naive = TRUE, type = "cor", ...) {
+reconSsa <- function(ssa, naive = TRUE, type = "cor", as_tibble = TRUE, ...) {
   #' Reconstruct SSA Decomposition
   #'
   #' Reconstruct the SSA model to obtain its constituting functions
@@ -11,25 +11,74 @@ reconSsa <- function(ssa, naive = TRUE, type = "cor", ...) {
   #' @param type Type of SSA group to extract, support either `pgram`, `wcor`,
   #' or `cor`. This argument is passed on to `getSsaGroup` when `naive` is
   #' `FALSE`.
+  #' @param as_tibble A boolean to indicate return as a tibble
   #' @inheritDotParams Rssa::reconstruct
+  #' @return A reconstructed time-series data
   require("Rssa")
 
-  args <- list(...)
-
+  # Reconstruct the time-series
   if (naive) {
-    recon  <- Rssa::reconstruct(ssa, ...)
-  } else {
-    groups <- getSsaGroup(ssa, type = type)
+    recon  <- Rssa::reconstruct(ssa, ...) # Without groupings
+  } else { # With automatic groupings
+    groups <- getSsaGroup(ssa, type = type, ...)
     recon  <- Rssa::reconstruct(ssa, groups = groups, ...)
   }
 
-  ssa_attr <- base::attr(ssa, "group")
+  # Insert custom attributes
+  attributes(recon)$group  <- attr(ssa, "group")
+  attributes(recon)$date   <- attr(ssa, "date")
+  attributes(recon)$metric <- attr(ssa, "metric")
 
-  if (!is.null(ssa_attr)) {
-    base::attributes(recon)$group <- ssa_attr
+  # Return either tibble or the original reconstructed time-series
+  if (as_tibble) {
+    recon %<>% tidyReconSsa()
   }
 
   return(recon)
+}
+
+tidyReconSsa <- function(recon) {
+  #' Tidying Reconstructed Time-Series
+  #'
+  #' Create a tidy data frame for reconstructed time-series object obtained
+  #' from the SSA model
+  #'
+  #' @param recon
+  #' @return A tidy reconstructed time-series
+  require("tsibble")
+
+  # Get the total length of the recon object
+  n_col <- length(recon)
+
+  # Extract attributes
[…]

### 2024-02-07 src/R/visualize.R

@@ -350,3 +350,24 @@ vizPolar <- function(...) {
 
   return(plt_polar)
 }
+
+vizReconSsa <- function(tidy_recon, ...) {
+  #' Visualize Reconstructed Time-Series
+  #'
+  #' Visualize the reconstructed series obtained from SSA model
+  #'
+  #' @param tidy_recon A tidy data frame obtained from `tidyReconSsa`
+  #' @return A GGPlot2 object
+  require("ggplot2")
+  
+  med <- unique(tidy_recon$group)
+  lab <- unique(tidy_recon$metric) %>% getLabel()
+  
+  plt <- ggplot(tidy_recon, aes(x = date, y = value)) +
+    geom_line(alpha = 0.8) +
+    facet_wrap(~ component, scales = "free", ...) +
+    labs(title = med, y = lab, x = "") +
+    ggpubr::theme_pubclean()
+
+  return(plt)
+}

### 2024-02-07 src/R/visualize.R
Set strip color for original and residual facets, change SSA model to use daily time series

@@ -40,20 +40,25 @@ getLabel <- function(metric) {
   return(labelname)
 }
 
-setStripColor <- function(group) {
+setStripColor <- function(group, ref = NULL) {
   #' Set Strip Color
   #'
   #' Set strip color in a faceted GGPlot2 object
   #'
   #' @param group A character vector of medication group, usually containing 25
   #' groups enlisted in the `setGroupFactor` function
+  #' @param ref A reference group to use a different color
   #' @return Themed strip as a `ggh4x` object
   require("ggh4x")
+
+  if (is.null(ref)) {
+    ref <- getNeuroMeds()
+  }
 
   colors    <- genColor()
   strip_col <- ggh4x::strip_themed(
     background_x = ggh4x::elem_list_rect(
-      fill = ifelse(unique(group) %in% getNeuroMeds(), colors$green, "grey90")
+      fill = ifelse(unique(group) %in% ref, colors$green, "grey90")
     )
   )
 
@@ -362,10 +367,12 @@ vizReconSsa <- function(tidy_recon, ...) {
   
   med <- unique(tidy_recon$group)
   lab <- unique(tidy_recon$metric) %>% getLabel()
+
+  strip_col <- setStripColor(unique(tidy_recon$component), ref = c("Original", "Residuals"))
   
   plt <- ggplot(tidy_recon, aes(x = date, y = value)) +
     geom_line(alpha = 0.8) +
-    facet_wrap(~ component, scales = "free", ...) +
+    ggh4x::facet_wrap2(~component, scales = "free", strip = strip_col, ...) +
     labs(title = med, y = lab, x = "") +
     ggpubr::theme_pubclean()
 

### 2024-02-07 _targets.R
Fit sequential SSA models #6 CU-86cuhtqmg

@@ -255,7 +255,7 @@ list(
     # Fit SSA models to decompose the time series based on singular spectrum analysis
     tar_target(
       mod_ssa,
-      fitModel(ts_week, groupname = med_groups, y = y, FUN = fitSsa, kind = "1d-ssa"),
+      fitModel(ts_week, groupname = med_groups, y = y, FUN = fitSsa, method = "sequential", kind = "1d-ssa", L = 52),
       pattern = map(med_groups),
       iteration = "list"
     ),
@@ -263,18 +263,30 @@ list(
     # Reconstruct decomposed time-series obtained from the SSA models
     tar_target(
       mod_ssa_recon,
-      reconSsa(mod_ssa, naive = FALSE, type = "wcor"),
+      reconSsa(mod_ssa, naive = FALSE, type = "wcor", nclust = 2),
       pattern = map(mod_ssa),
       iteration = "list"
     ),
 
     tar_target(
       plt_ssa_recon,
-      vizReconSsa(mod_ssa_recon),
+      vizReconSsa(mod_ssa_recon, ncol = 1),
       pattern = map(mod_ssa_recon),
       iteration = "list"
     )
 
+  ),
+
+  # Combine SSA-based decomposition
+  tar_target(
+    decom_ssa,
+    bindReconSsa(
+      list(
+        mod_ssa_recon_n_claim,
+        mod_ssa_recon_claim2patient,
+        mod_ssa_recon_eigen
+      )
+    )
   ),
 
   # Generate documentation

### 2024-02-07 src/R/model.R

@@ -38,18 +38,48 @@ fitArima <- function(ts, ...) {
   return(mod)
 }
 
-fitSsa <- function(ts, ...) {
+fitSsa <- function(ts, method = NULL, ...) {
   #' Fit Singular-Spectrum Model
   #'
   #' Fit a singular-spectrum analysis model using the `Rssa` package
   #'
   #' @param ts A tidy time-series data frame, should be a subset of a metric as
   #' specified by `fitModel`
+  #' @param method Further method for fitting the model, currently supporting
+  #' sequential SSA modelling
   #' @inheritDotParams Rssa::ssa
   #' @return A model object
   require("Rssa")
 
   mod <- ts %>% extract2(1) %>% Rssa::ssa(...)
 
+  if (is.null(method)) { # Quick termination when method is NULL
+    return(mod)
+  }
+
+  # Continue model fitting based on the chosen method
+  if (method == "sequential") {
+
+    # Extract the reconstructed trend and residuals
+    recon <- reconSsa(mod, naive = TRUE, as_tibble = FALSE, groups = 1)
+    trend <- recon[[1]]
+    resid <- residuals(recon)
+
+    # Reconstruct other series from the residuals
+    mod_orig <- mod
+    mod      <- Rssa::ssa(resid)
+
+    # Insert attributes to the new model
+    attributes(mod)$trend  <- trend
+    attributes(mod)$series <- attr(recon, "series")
+
+  } else {
+
+    message("Method is not supported, returning the model")
+    return(mod)
+
+  }
+
   return(mod)
+
 }

### 2024-02-07 src/R/spectral.R

@@ -1,6 +1,6 @@
 # Functions to perform spectral analysis, especially manipulate objects from `Rssa`
 
-reconSsa <- function(ssa, naive = TRUE, type = "cor", as_tibble = TRUE, ...) {
+reconSsa <- function(ssa, naive = TRUE, type = "wcor", as_tibble = TRUE, ...) {
   #' Reconstruct SSA Decomposition
   #'
   #' Reconstruct the SSA model to obtain its constituting functions
@@ -29,6 +29,18 @@ reconSsa <- function(ssa, naive = TRUE, type = "cor", as_tibble = TRUE, ...) {
   attributes(recon)$date   <- attr(ssa, "date")
   attributes(recon)$metric <- attr(ssa, "metric")
 
+  # Inserting trend from a sequential model
+  trend  <- attr(ssa, "trend")
+  series <- attr(ssa, "series")
+
+  if (!is.null(trend)) {
+    attributes(recon)$trend <- trend
+  }
+
+  if (!is.null(series)) {
+    attributes(recon)$series <- series
+  }
+
   # Return either tibble or the original reconstructed time-series
   if (as_tibble) {
     recon %<>% tidyReconSsa()
@@ -45,7 +57,6 @@ tidyReconSsa <- function(recon) {
   #'
   #' @param recon
   #' @return A tidy reconstructed time-series
-  require("tsibble")
 
   # Get the total length of the recon object
   n_col <- length(recon)
@@ -54,6 +65,7 @@ tidyReconSsa <- function(recon) {
   ssa_group  <- attr(recon, "group")
   ssa_date   <- attr(recon, "date")
   ssa_metric <- attr(recon, "metric")
+  trend      <- attr(recon, "trend")
 
   # Create a tidy data frame
   tbl <- recon %>% unlist() %>%
@@ -62,23 +74,55 @@ tidyReconSsa <- function(recon) {
     tibble::tibble() %>%
     dplyr::rename_with(~ gsub("X", "F", .x)) %>%
     tibble::add_column("Original"  = attr(recon, "series"), .before = 1) %>%
-    tibble::add_column("Residuals" = attr(recon, "residuals"), .after = 1) %>%
-    tibble::add_column("group"     = ssa_group, .before = 1) %>%
-    tibble::add_column("date"      = as.Date(ssa_date), .after  = 1) %>%
-    tibble::add_column("metric"    = ssa_metric, .after = 2)
[…]

### 2024-02-07 src/R/visualize.R

@@ -368,11 +368,12 @@ vizReconSsa <- function(tidy_recon, ...) {
   med <- unique(tidy_recon$group)
   lab <- unique(tidy_recon$metric) %>% getLabel()
 
-  strip_col <- setStripColor(unique(tidy_recon$component), ref = c("Original", "Residuals"))
+  strip_col <- setStripColor(unique(tidy_recon$component), ref = c("Original", "Trend"))
   
   plt <- ggplot(tidy_recon, aes(x = date, y = value)) +
-    geom_line(alpha = 0.8) +
-    ggh4x::facet_wrap2(~component, scales = "free", strip = strip_col, ...) +
+    geom_point(alpha = 0.4, color = "grey40", size = 2) +
+    geom_line(alpha = 0.2, color = "grey40", linewidth = 1.5) +
+    ggh4x::facet_wrap2(~component, scales = "free_y", strip = strip_col, ...) +
     labs(title = med, y = lab, x = "") +
     ggpubr::theme_pubclean()
 

### 2024-02-08 _targets.R
Increase the number of clusters when grouping the oscillating functions #6 CU-86cuhtqmg

@@ -263,17 +263,12 @@ list(
     # Reconstruct decomposed time-series obtained from the SSA models
     tar_target(
       mod_ssa_recon,
-      reconSsa(mod_ssa, naive = FALSE, type = "wcor", nclust = 2),
+      reconSsa(mod_ssa, naive = FALSE, type = "wcor"),
       pattern = map(mod_ssa),
       iteration = "list"
     ),
 
-    tar_target(
-      plt_ssa_recon,
-      vizReconSsa(mod_ssa_recon, ncol = 1),
-      pattern = map(mod_ssa_recon),
-      iteration = "list"
-    )
+    tar_target(plt_ssa_recon, vizReconSsa(mod_ssa_recon), pattern = map(mod_ssa_recon), iteration = "list")
 
   ),
 

### 2024-02-08 src/R/model.R

@@ -53,21 +53,20 @@ fitSsa <- function(ts, method = NULL, ...) {
 
   mod <- ts %>% extract2(1) %>% Rssa::ssa(...)
 
-  if (is.null(method)) { # Quick termination when method is NULL
-    return(mod)
-  }
+  # Extract the reconstructed trend and residuals
+  recon <- reconSsa(mod, naive = TRUE, as_tibble = FALSE, groups = 1)
+  trend <- recon[[1]]
+  resid <- residuals(recon)
+
+  # Insert attributes to the new model
+  attributes(mod)$trend  <- trend
+  attributes(mod)$series <- attr(recon, "series")
 
   # Continue model fitting based on the chosen method
   if (method == "sequential") {
 
-    # Extract the reconstructed trend and residuals
-    recon <- reconSsa(mod, naive = TRUE, as_tibble = FALSE, groups = 1)
-    trend <- recon[[1]]
-    resid <- residuals(recon)
-
     # Reconstruct other series from the residuals
-    mod_orig <- mod
-    mod      <- Rssa::ssa(resid)
+    mod <- Rssa::ssa(resid)
 
     # Insert attributes to the new model
     attributes(mod)$trend  <- trend
@@ -76,7 +75,6 @@ fitSsa <- function(ts, method = NULL, ...) {
   } else {
 
     message("Method is not supported, returning the model")
-    return(mod)
 
   }
 

### 2024-02-08 src/R/spectral.R

@@ -57,6 +57,7 @@ tidyReconSsa <- function(recon) {
   #'
   #' @param recon
   #' @return A tidy reconstructed time-series
+  require("tsibble")
 
   # Get the total length of the recon object
   n_col <- length(recon)

### 2024-02-08 src/R/visualize.R

@@ -365,17 +365,75 @@ vizReconSsa <- function(tidy_recon, ...) {
   #' @return A GGPlot2 object
   require("ggplot2")
   
+  # Separate oscillating functions + noise from the rest
+  id      <- grepl(x = tidy_recon$component, "^F")
+  tbl_fun <- subset(tidy_recon, id)
+  resid   <- tidy_recon %>% subset(.$component == "Residuals")
+  tbl     <- tidy_recon %>%
+    subset(!{id | .$component == "Residuals"}) %>%
+    tidyr::pivot_wider(names_from = component, values_from = value)
+
+  # Set labels and colors
   med <- unique(tidy_recon$group)
   lab <- unique(tidy_recon$metric) %>% getLabel()
+  colors <- genColor()
+  plt_title <- sprintf("%s of %s", lab, med)
 
-  strip_col <- setStripColor(unique(tidy_recon$component), ref = c("Original", "Trend"))
-  
-  plt <- ggplot(tidy_recon, aes(x = date, y = value)) +
-    geom_point(alpha = 0.4, color = "grey40", size = 2) +
-    geom_line(alpha = 0.2, color = "grey40", linewidth = 1.5) +
-    ggh4x::facet_wrap2(~component, scales = "free_y", strip = strip_col, ...) +
-    labs(title = med, y = lab, x = "") +
-    ggpubr::theme_pubclean()
+  # Scale the date (x) axis
+  scale_date <- scale_x_date(
+    date_breaks = "1 month", date_labels = "%b %Y", expand = expansion(add = c(10, 30))
+  )
+
+  # Plot for original and trend
+  plt1 <- ggplot(tbl, aes(x = date)) +
+    geom_point(aes(y = Original, color = "Data"), alpha = 0.4, size = 2, shape = 18) +
+    geom_line(aes(y = Original, color = "Data"), alpha  = 0.2, linewidth = 1.2) +
+    geom_line(aes(y = Trend, color = "Trend"), alpha  = 0.8, linewidth = 2) +
+    labs(title = plt_title, x = "", y = "") +
+    scale_date +
+    scale_color_manual(
+      name = "",
+      values = c("Data" = colors$black, "Trend" = colors$green),
+      guide = guide_legend(override.aes = aes(fill = NA))
+    ) +
+    ggpubr::theme_pubclean() +
+    theme(
+      axis.ticks.y = element_blank(),
+      axis.text.x = element_text(angle = 45, vjust = 0.8, hjust = 1),
[…]

### 2024-02-09 docs/exec-summary/report.qmd
Draft the report and abstract, close #1 CU-86cuh2hq2[closed], #6 CU-86cuhtqmg

## Abstract

**Objectives:**
Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide. People with chronic diseases are at a higher risk of having mental health issues, which in turn potentially worsen their overall well-being. This investigation highlights the interrelatedness of mental health problems with other diagnoses, reflected as a relative importance score of psychopharmaca in a medication claim registry.

**Methods:**
Exploratory time-series analysis was performed using University of Groningen prescription database, IADB.nl. Data of patients with at least one prescription of psychopharmaca from 2018 to 2022 was extracted. A medication-claim network was constructed as an undirected graph to capture weighted co-prescription. Eigenvector centrality was computed as a measure of relative nodal importance. The number of medication claims, number of patients, claim-to-patient ratio, and eigenvector centrality were then extracted as a time-series data. Singular spectrum analysis was performed to decompose the data into its constituting trend, periodicity, and white noises.

**Results:**
Antidepressants (WHO/ATCC `N06A`), antipsychotics (`N05A`), anxiolytics (`N05B`), and hypnotics (`N05C`) are psychopharmaca with high relative importances. These classes of medication are likely to be co-prescribed alongside other medications, including medications for alimentary and metabolism (`A01-A16`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory (`R01-R07`). From four important psychopharmaca, only antidepressants and hypnotics have a positive trend for both importance and actual number of claims.

**Discussion:**
The data presented with complex periodicity and many underlying oscillating functions, which makes it challenging to extract the trend. Positive trends in both importance and claims suggest that increasing uses of antidepressants and hypnotics are related to co-prescription or its combination with other medications from the same class. Constructing a medication claim network enriches the exploratory analysis procedure on the population level. A thorough data cleaning procedure is paramount to ensure adequate separation between trend, periodicity, and noises.

{{< pagebreak >}}

## Highlighted findings

- @tbl-mean-diff and @sec-pair-plot describe difference in several measures before and during the COVID-19 pandemic
  - Further analysis is necessary and will be planned for later investigation
  - Interrupted time-series analysis should be conducted by considering:
    1. Counterfactual data using trend before COVID-19
    1. Counterfactual data using trend during COVID-19 given policy changes
    1. Calculate the mean percentage changes between counterfactual and actual data
- @sec-decom-classic-stl displays the data after classical and STL seasonal decomposition
  - The data still presents with other patterns, implying that seasonality does not completely explains the variance
  - Eigenvector centrality on daily, weekly, and monthly series suggests high importance of several psychopharmaca, including:
    1. Antidepressants
    1. Antipsychotics
    1. Anxiolytics
    1. Hypnotic and sedatives
  - Other medications considered important by eigenvector centrality:
    1. Alimentary and metabolism
    1. Cardiovascular
    1. Analgesics
    1. Respiratory
  - High eigenvector centrality implies that these eight medications are often co-prescribed
- @sec-seasonality demonstrates two repeating patterns in medication claims:
  - Increasing claims on Monday and decreasing claims on Saturday in the daily data, implying day-to-day differences
  - Increasing claims in March and December in the monthly data, this pattern is persistent for weekly data as well
  - Weekly data better captures repeating patterns and should be use for further analysis
- Model evaluation tables in @sec-arima consistently show high value of intercept
  - All models for medication claims have a relatively low effect size for AR, MA, or drift term
  - No model has fitted with a (P, D, Q) term, implying no detected seasonality for models maximizing AICc
  - Seasonality might be undetected due to the presence of noise and other underlying periodicity
- @tbl-trend shows differences between the actual and decomposed data
  - Trend is more visible in the decomposed data due to being free from noises and periodicity
  - The magnitude of detected trend is naturally larger, and still implies the same monotonicity with the original data
  - The number of claims in 11 medication classes are declining overtime
  - The relative importance in 14 medication classes are declining overtime
  - Changes in claim represents the actual change of the expected number of medication claim in the population. Changes in importance represents changes of how likely a medication being prescribed together. Differences between relative importance and number of medication claims are observed in:
    1. Genitourinary: decreasing claim, increasing importance
    1. Systemic hormonal: increasing claim, decreasing importance
    1. Antiparkinson: increasing claim, decreasing importance
    1. Antipsychotics: increasing claim, decreasing importance
    1. Antidementia: increasing claim, decreasing importance
    1. Other nervous system drugs: decreasing claim, increasing importance
    1. Antiparasitics: increasing claim, decreasing importance
- @tbl-resid-n-claim and @tbl-resid-eigen shows the residuals analysis of the decomposition model using singular spectrum analysis
  - All residuals are stationary, i.e. having a constant mean and variance
  - All residuals follow the normal distribution (see especially Shapiro-Wilk statistics, mean, and standard deviation)
  - These findings imply that the residuals of decomposition models are likely to be evenly and randomly distributed
- @sec-recon depicts complex periodicity within each time series
  - These go in line with findings from @sec-seasonality
  - Despite visible patterns of weekly and yearly seasonality, these patterns are obscured with other oscillating functions
  - The oscillating functions were ordered based on their contribution in explaining the variance in the data, e.g. `F1` has a higher contribution than `F2`, and so on

{{< pagebreak >}}

## Analytical procedures

### Source of data

The University of Groningen IADB.nl pharmacy prescription database is a growing database that contains prescription data for 31 years from 1994 till 2024 from approximately 120 community pharmacies and covers an estimated population of 1,120,000 patients. Registration in the database is irrespective of health care insurance and age, gender and prescription rates among the database population have been found to be representative of the Netherlands as a whole, and the database has been widely used for research. Each person is individually tracked throughout the database period and prescription records contain information on the date of dispensing, the quantity dispensed, the dose regimen, the number of days the prescription is valid, the prescribing physician and the Anatomical Therapeutic Chemical code (ATC code). Each patient has a unique anonymous identifier; date of birth and gender are known. Due to the high patient-pharmacy commitment in the Netherlands, the medication records for each patient are virtually complete, except for over the counter (OTC) drugs and medication dispensed during hospitalization.

#### Inclusion criteria

- Adult aged 18-65 years old at time of dispensing anxiolytic and/or antidepressant
- Prescribed for anxiolytics (`N05B`) or antidepressant (`N06A`) at any time in the time span from 2018 to 2022

#### Exclusion criteria

- (None)

### Data pre-processing

Daily medication claims can be represented as a square matrix, with rows and columns representing medication entities. N number of medications will then form an adjacency matrix describing the concurrent use of enlisted drugs. Therefore, the matrix diagonal represents using only one medication over the observation period. The matrix follows a knowledge graph construct with a subject-predicate-object (s, p, o) triples, i.e. `Medication1-PrescribedAlongside-Medication2`. The graph object is constructed from recorded prescription claims on a daily epoch. The edge (predicate) in this graph represents the number of concurrency, which will differ from one epoch to another depending on the number of patients claiming the prescription. To regularize the number of daily claims, it is essential to adjust the weight of the edge by dividing it by the defined daily dose (DDD). Regularization will allow direct comparison of one drug to another when calculating the graph metrics. Regularization based on DDD essentially transforms the dosage into a unit-free scale, which will be assigned as a weighted edge in the graph object.

### Measuring relative importance

The choice of graph metrics to use would be node centrality, which can be interpreted as node importance in a graph object. In our case, each node represents a single medication being claimed on that particular day. From various selection of centrality measures, we will focus on using eigenvector centrality, i.e. a prestige score. By calculating eigenvector centrality, each node will have a relative score. A high-scoring node implies that the node is highly connected with other high-scoring nodes. In a way, this shall reflect the score of importance when one drug is used alongside other drugs. Nodes with high eigenvector centrality can be further interpreted as strongly-connected nodes.

{{< include exec-summary/descriptive.qmd >}}

{{< include exec-summary/arima.qmd >}}

{{< include exec-summary/seasonality.qmd >}}

{{< include exec-summary/spectral.qmd >}}

### 2024-02-09 docs/exec-summary/seasonality.qmd
Draft the report and abstract, close #1 CU-86cuh2hq2[closed], #6 CU-86cuhtqmg

### Exploring seasonality in the dataset

Exploration on seasonality is done on monthly data with a first-order difference.

### 2024-02-09 docs/exec-summary/spectral.qmd
Draft the report and abstract, close #1 CU-86cuh2hq2[closed], #6 CU-86cuhtqmg

### Decomposition with singular spectrum analysis

### 2024-02-09 docs/index.qmd
Add templates for executive summaries
Draft the report and abstract, close #1 CU-86cuh2hq2[closed], #6 CU-86cuhtqmg

@@
 
+```{r init}
+
+options(scipen = 999)
+
+```
+
+::: {.content-visible when-meta="in.report"}
+{{< include exec-summary/report.qmd >}}
+:::
+
+::: {.content-visible when-profile="descriptive"}
+{{< include exec-summary/descriptive.qmd >}}
+:::
+
+::: {.content-visible when-profile="arima"}
+{{< include exec-summary/arima.qmd >}}
+:::
+
 ::: {.content-visible when-profile="seasonality"}
+{{< include exec-summary/seasonality.qmd >}}
+:::
 
-Exploration on seasonality is done on monthly data with a first-order difference
+::: {.content-visible when-profile="spectral"}
+{{< include exec-summary/spectral.qmd >}}
+:::
+
+::: {.content-visible when-meta="in.report"}
+
+## Contents
+
+- @sec-descriptive contains a descriptive explanation of the dataset
+- @sec-seasonality reports exploration of seasonality on detrended data
+- @sec-arima showcases results obtained from ARIMA models
+- @sec-spectral outlines the decomposed time series using singular-spectrum analysis
 

### 2024-02-09 docs/results/descriptive.qmd
Draft the report and abstract, close #1 CU-86cuh2hq2[closed], #6 CU-86cuhtqmg

--- 2023-11-27 docs/results.qmd
@@
 
+options(digits = 2, scipen = 999)
+
 ```
 
-# Results
+# Results on descriptive statistics {#sec-descriptive}
 
-## Descriptive analysis
+## Descriptive analysis of the raw data
 
-In this section,
+```{r tbl-mean-diff}
+#| tbl-cap: Mean difference of all metrics before and during COVID-19
 
-{{< pagebreak >}}
+tar_read(desc_ts) %>% knitr::kable()
 
-\KOMAoptions{paper=landscape,pagesize}
-\recalctypearea
+```
+
+\uselandscape
+
+:::: {.content-hidden when-meta="in.report"}
+
+### Paired plot of all metrics for each medication group {#sec-pair-plot}
+
+```{r}
+
+tar_read(plt_pair)
+
+```
 
@@
 
+::: {.content-visible when-profile="descriptive"}
+
 ### Exploring seasonality within the number of patients (day) {#sec-npat-day}
@@
 ```
+
+:::
 
@@
 
+::: {.content-visible when-profile="descriptive"}
+
 ### Exploring seasonality within the number of patients (week) {#sec-npat-week}
@@
 
+::: {.content-visible when-profile="descriptive"}
+
 ### Exploring seasonality within the number of patients (month) {#sec-npat-month}
@@
 
+:::
+
 ### Exploring seasonality within the eigenvector centrality (month) {#sec-eigen-month}
@@
 ```
+
+::::
+
+## Descriptive analysis of the decomposed data {#sec-decom-classic-stl}
+
+### Decomposed time-series on a daily interval
+
+```{r}
+
+tar_read(plt_decom_ts_day_1.week_classic_n_claim)
+tar_read(plt_decom_ts_day_1.week_classic_eigen)
+
+```
+
+### Decomposed time-series on a weekly interval
+
+```{r}
+
+tar_read(plt_decom_ts_week_1.month_classic_n_claim)
+tar_read(plt_decom_ts_week_1.month_classic_eigen)
+
+```
+
+### Decomposed time-series on a monthly interval
+
+```{r}
+
+tar_read(plt_decom_ts_month_1.year_classic_n_claim)
+tar_read(plt_decom_ts_month_1.year_classic_eigen)
+
+```
+
+\normalpapersize

### 2024-02-09 docs/results/spectral.qmd
Increase the number of clusters when grouping the oscillating functions #6 CU-86cuhtqmg
Draft the report and abstract, close #1 CU-86cuh2hq2[closed], #6 CU-86cuhtqmg

@@
   opts_chunk:
-    fig.width: 14
-    fig.height: 8
+    fig.width: 18
+    fig.height: 12
 ---
-
-\KOMAoptions{paper=landscape,pagesize}
-\recalctypearea
 
@@
 
-pkgs <- c("magrittr", "targets")
+pkgs <- c("magrittr", "targets", "kableExtra")
 pkgs_load <- sapply(pkgs, library, character.only = TRUE)
 
-options(digits = 2)
+options(digits = 2, scipen = 999)
+
+prettyRound <- function(x, ...) {
+  x %<>% round(...) %>% {ifelse(. == 0, "<0.001", as.character(.))}
+}
 
@@
     dplyr::mutate(
-      "mean"   = mean(res),
-      "median" = median(res),
-      "sd"     = sd(res),
+      "Unit Root" = sprintf("%s (p %s)", round(stat, 2), prettyRound(p, 3)),
+      "Normality" = sprintf("%s (p %s)", round(stat2, 2), prettyRound(p2, 3)),
+      "Mean"   = mean(res),
+      "SD"     = sd(res),
+      "Median" = median(res),
       "IQR"    = IQR(res)
-    )
+    ) %>%
+    subset(select = -c(stat:method2)) %>%
+    dplyr::rename("ATCC Group" = group)
 
@@
 
-# Results
+\normalpapersize
+
+# Results on singular spectrum analysis {#sec-spectral}
+
+## Trend evaluation
+
+```{r tbl-trend}
+#| tbl-cap: Trend of medication uses alongside its measure of relative importance
+
+fnote <- "The statistics were obtained from Mann-Kendall trend test, where positive result signifies a positive slope"
+
+tar_read(decom_ssa) %>%
+  subset(.$component %in% c("Original", "Trend") & .$metric != "claim2patient") %>%
+  tibble::tibble() %>%
+  dplyr::group_by(metric, group, component) %>%
+  dplyr::group_modify(~trend::mk.test(.x$value) %>% broom::tidy()) %>%
+  dplyr::ungroup() %>%
+  dplyr::mutate(
+    "Mann-Kendall" = sprintf(
+      "%s (p %s)", prettyRound(statistic, 2), prettyRound(p.value, 3)
+    )
+  ) %>%
+  subset(select = -c(statistic:alternative)) %>%
+  tidyr::pivot_wider(names_from = metric, values_from = `Mann-Kendall`) %>%
+  tidyr::pivot_wider(names_from = component, values_from = eigen:n_claim) %>%
+  set_colnames(c("ATCC Group", rep(c("Original", "Trend"), 2))) %>%
+  knitr::kable(longtable = TRUE, booktabs = TRUE) %>%
+  kableExtra::kable_styling(latex_options = "repeat_header") %>%
+  kableExtra::add_header_above(c(" " = 1, "Eigenvector Centrality" = 2, "Medication Claims" = 2)) %>%
+  kableExtra::add_footnote(fnote, notation = "none")
+
+```
+
+\uselandscape
 
@@
 
-```{r}
+```{r tbl-resid-n-claim}
+#| tbl-cap: Residuals analysis for unit-root and normality test for the decomposition model of number of claims
 
@@
   {do.call(rbind, .)} %>%
-  knitr::kable()
-
-```
-
-### Claim-to-patient ratio
-
-```{r}
-
-tar_read(mod_ssa_claim2patient) %>%
-  lapply(reportResid) %>%
-  {do.call(rbind, .)} %>%
-  knitr::kable()
+  knitr::kable(longtable = TRUE, booktabs = TRUE) %>%
+  kableExtra::kable_styling(latex_options = "repeat_header", font_size = 8)
 
@@
 
-```{r}
+```{r tbl-resid-eigen}
+#| tbl-cap: Residuals analysis for unit-root and normality test for the decomposition model of relative importance
 
@@
   {do.call(rbind, .)} %>%
-  knitr::kable()
+  knitr::kable(longtable = TRUE, booktabs = TRUE) %>%
+  kableExtra::kable_styling(latex_options = "repeat_header", font_size = 8)
 
@@
 
-## Reconstructed plots
+## Reconstructed plots {#sec-recon}
 
@@
 
-### Medication claim to patient ratio
+::: {.content-visible when-profile="spectral"}
+
+### Claim-to-patient ratio
 

### 2024-02-09 _targets.R

@@ -285,6 +285,8 @@ list(
   ),
 
   # Generate documentation
+  tar_quarto(report, "docs", profile = "report", priority = 0),
+  tar_quarto(summary, "docs", profile = "summary", priority = 0),
   tar_quarto(report_descriptive, "docs", profile = "descriptive", priority = 0),
   tar_quarto(report_arima, "docs", profile = "arima", priority = 0),
   tar_quarto(report_seasonality, "docs", profile = "seasonality", priority = 0),

### 2024-02-09 src/R/visualize.R

@@ -377,7 +377,7 @@ vizReconSsa <- function(tidy_recon, ...) {
   med <- unique(tidy_recon$group)
   lab <- unique(tidy_recon$metric) %>% getLabel()
   colors <- genColor()
-  plt_title <- sprintf("%s of %s", lab, med)
+  plt_title <- sprintf("%s of %s", lab, stringr::str_to_lower(med))
 
   # Scale the date (x) axis
   scale_date <- scale_x_date(
@@ -386,7 +386,7 @@ vizReconSsa <- function(tidy_recon, ...) {
 
   # Plot for original and trend
   plt1 <- ggplot(tbl, aes(x = date)) +
-    geom_point(aes(y = Original, color = "Data"), alpha = 0.4, size = 2, shape = 18) +
+    geom_point(aes(y = Original), color = colors$black, alpha = 0.4, size = 2, shape = 18) +
     geom_line(aes(y = Original, color = "Data"), alpha  = 0.2, linewidth = 1.2) +
     geom_line(aes(y = Trend, color = "Trend"), alpha  = 0.8, linewidth = 2) +
     labs(title = plt_title, x = "", y = "") +

### 2024-02-12 docs/exec-summary/seasonality.qmd
Explain the seasonality detection procedure, close #13, CU-86cujzpdx[closed]

@@
 
-Exploration on seasonality is done on monthly data with a first-order difference.
+Exploration on seasonality was done on detrended daily, weekly, and monthly data by generating seasonal plots and calculating the autocorrelation (ACF) and partial autocorrelation function (PACF).
+Seasonal plots were generated for weekly and yearly pattern by using daily and monthly data, respectively.
+To generate the seasonal plots, the data was first deconstructed based on its period.
+For daily data, the weekly period was used; while for monthly data, the yearly period was used.
+The weekly period was obtained by creating an ordered value formatted as year - week, e.g.
+`2018 - W01`.
+Similarly, monthly period was obtained by creating an ordered value formatted as year - month, e.g.
+`2018 - M01`.
+We then grouped the series by its deconstructed period and visually examine seasonality as overlapping pattern in most periods.
+To substantiate the findings, ACF and PACF plots were used to check on statistical significance of a given pattern.

### 2024-02-12 docs/exec-summary/spectral.qmd
Brief the SSA algorithm and procedure, closes #15, CU-86cujzqey[closed]

@@
 ### Decomposition with singular spectrum analysis
+
+Classical and STL-based decomposition technique may not sufficiently capture complex periodic patterns in a time-series.
+Singular spectrum analysis (SSA) is a powerful non-parametric technique by leveraging Hankel matrix as a higher-dimensional embedding of the time-series.
+The resulting Hankel matrix $X$ has the size of $L \times K$, where $L$ represents the lag term, i.e.
+a window length to perform embedding For a weekly data with a hypothesized yearly seasonality, the $L$ is set as 52.
+In theory, the number of $L$ should be between the range of $2 \leq L \leq \frac{N}{2}$, where $N$ is the total length of the time-series.
+
+$$
+X =
+\stackrel{\textrm{Time-series embedding}}{
+  \begin{bmatrix}
+  x_1 & x_2 & \dots & x_{N - L + 1} \\
+  x_2 & x_3 & \dots & x_{N - L + 2} \\
+  \vdots & \vdots & \ddots & \vdots \\
+  x_L & x_{L + 1} & \dots & x_{N} \\
+  \end{bmatrix}
+}
+$$ {#eq-hankel-mtx}
+
+The embedded time-series $X$ is then decomposed using a singular value decomposition (SVD).
+With a matrix $S = X \cdot X^T$, we can extract an eigenvalue $\lambda \ni \{\lambda_1 \geq \dots \geq \lambda_L\}$, where each $\lambda_i$ is a non-negative integer.
+Similarly, we can define $U$ as the eigenvectors of matrix $S$ corresponding to eigenvalues $\lambda$.
+Afterwards, we can extract factor vectors $V$ where the corresponding $V_i = X^T \frac{U_i}{\sqrt{\lambda_i}}$.
+Finally, the eigentriple of $\{\sqrt{\lambda_i}, U_i, V_i^T\}$ is formulated as a row-wise decomposition of matrix $X$ [@Golyandina2020].
+The resulting eigentriple is then used to reconstruct the time-series by eigentriple grouping and diagonal averaging.
+
+In case of complex periodic patterns, sequential SSA is preferred to separate trend from seasonal components [@Golyandina2018].
+A sequential SSA model is performed by first fitting a basic SSA model to reconstruct the first eigentriple, *viz.* the eigentriple that explain most of the variance in the data.
+Then, the residual of the first model is extracted to fit the second SSA model.
+The first SSA model is defined with the lowest possible $L$, which in our case $L = 52$.
+The second SSA model is defined with the largest possible $L$ to capture all patterns, which is conveniently defined as $L = \frac{N}{2}$.
+The decomposed series and its corresponding original data is then extracted from the model alongside all of the oscillating functions which contributes to complex seasonality.
+The original data, trend, residuals, and oscillating functions are plotted for further inspection.
+The original data and trend is further evaluated using Mann-Kendall trend test.

### 2024-02-12 docs/exec-summary/report.qmd
Elaborate the methods, close #11, CU-86cujznkf[closed]

@@
 Data of patients with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
-A medication-claim network was constructed as an undirected graph to capture weighted co-prescription.
-Eigenvector centrality was computed as a measure of relative nodal importance.
-The number of medication claims, number of patients, claim-to-patient ratio, and eigenvector centrality were then extracted as a time-series data.
+Prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca is evaluated at ATC level 3, drugs for nervous system at ATC level 2, and other medications at ATC level 1, totalled to 24 classes of medication.
+A medication-claim network was constructed as an undirected graph to capture dose-adjusted co-prescription.
+Eigenvector centrality was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
+The number of medication claims, number of patients, claim-to-patient ratio, and eigenvector centrality were then extracted as a weekly-aggregated time-series data.
 Singular spectrum analysis was performed to decompose the data into its constituting trend, periodicity, and white noises.
@@
 **Results:**
-Antidepressants (WHO/ATCC `N06A`), antipsychotics (`N05A`), anxiolytics (`N05B`), and hypnotics (`N05C`) are psychopharmaca with high relative importances.
+Antidepressants (ATC `N06A`), antipsychotics (`N05A`), anxiolytics (`N05B`), and hypnotics (`N05C`) are psychopharmaca with high eigenvector centrality.
 These classes of medication are likely to be co-prescribed alongside other medications, including medications for alimentary and metabolism (`A01-A16`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory (`R01-R07`).
-From four important psychopharmaca, only antidepressants and hypnotics have a positive trend for both importance and actual number of claims.
+Only antidepressants and hypnotics have a positive time trend for both eigenvector centrality and actual number of claims.
 
 **Discussion:**
-The data presented with complex periodicity and many underlying oscillating functions, which makes it challenging to extract the trend.
-Positive trends in both importance and claims suggest that increasing uses of antidepressants and hypnotics are related to co-prescription or its combination with other medications from the same class.
+Eight medications, four of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level.
+Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants and hypnotics are related to co-prescription with other medication classes.
 Constructing a medication claim network enriches the exploratory analysis procedure on the population level.
-A thorough data cleaning procedure is paramount to ensure adequate separation between trend, periodicity, and noises.
 
@@
 
+## Analytical procedures
+
+### Source of data
+
+The University of Groningen IADB.nl pharmacy prescription database is a growing database that contains prescription data for 31 years from 1994 till 2024 from approximately 120 community pharmacies and covers an estimated population of 1,120,000 patients.
+Registration in the database is irrespective of health care insurance and age, gender and prescription rates among the database population have been found to be representative of the Netherlands as a whole, and the database has been widely used for research.
+Each person is individually tracked throughout the database period and prescription records contain information on the date of dispensing, the quantity dispensed, the dose regimen, the number of days the prescription is valid, the prescribing physician and the Anatomical Therapeutic Chemical code (ATC code).
+Each patient has a unique anonymous identifier; date of birth and gender are known.
+Due to the high patient-pharmacy commitment in the Netherlands, the medication records for each patient are virtually complete, except for over the counter (OTC) drugs and medication dispensed during hospitalization.
+This analysis include daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.
+
+### Data pre-processing
+
+Daily medication claims is a tabular data containing values from single medication entity for each patients in the cohort.
+Data transformation was performed to construct a square matrix of aggregate medication claim per day, with rows and columns representing groups of medication.
+Each element in the upper and lower triangle represents co-prescriptions, while the diagonal of the matrix represents single prescriptions.
+All elements in the matrix is a tally of drug combination/single prescription in a population level claimed on a daily basis.
+The matrix follows a knowledge graph construct with a subject-predicate-object (s, p, o) triples, i.e.
+`Medication1-PrescribedAlongside-Medication2`.
+The knowledge graph is a representation of medication-claim network, where the edge (predicate) is the number of concurrency.
+Weight was applied on the edges by dividing it by the defined daily dose (DDD).
+Weighting is necessary to regularize the matrix into a unit-free scale, which allow a direct comparison of one drug to another.
+
+$$
+\stackrel{\textrm{Unregularized}}{
+  \begin{bmatrix}
+  n_{1, 1} & \dots & n_{1, N} \\
+  \vdots & \ddots & \vdots \\
+  n_{N, 1} & \dots & n_{N, N} \\
+  \end{bmatrix}
+}
+\to
+\stackrel{\textrm{Regularized by } DDD}{
+  \begin{bmatrix}
+  \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_N}{DDD_N} \right) \\
+  \vdots & \ddots & \vdots \\
+  \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_N}{DDD_N} \right) \\
+  \end{bmatrix}
+}
+$$ {#eq-regularize-mtx}
+
+### Measuring relative importance
+
+As all medications are nodes in a claim network, we can measure the property of each medication using graph theory.
+One way to represent node property is by calculating node centrality, which can be measured as a number of incoming/outgoing edges (degree) or its connectedness to other nodes (importance).
+We measured importance using eigenvector centrality, which reflects medication co-occurrence with other important medications.
+Eigenvector centrality is a recursive measures of how well connected a certain node is to other nodes that is also well connected in the network [@Golbeck2013].
+@eq-eigen-centrality outlines the calculation of eigenvector centrality; $\c_i$ and $\c_j$ are the centralities of node $i$ and $j$, respectively; $\lambda$ is the eigenvalue; $a_{j, i}$ is an element on row $j$ and column $i$ from an adjacency matrix $A$, representing the connection between node $a_i$ and $a_j$.
+
+$$
+\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} a_{j, i} \cdot c_j
+$$ {#eq-eigen-centrality}
+
+{{< include exec-summary/descriptive.qmd >}}
+
+{{< include exec-summary/seasonality.qmd >}}
+
+{{< include exec-summary/arima.qmd >}}
+
+{{< include exec-summary/spectral.qmd >}}
+
 ## Highlighted findings
 
-- @tbl-mean-diff and @sec-pair-plot describe difference in several measures before and during the COVID-19 pandemic
+- @tbl-mean-diff describes difference in several measures before and during the COVID-19 pandemic
   - Further analysis is necessary and will be planned for later investigation
@@
 
-{{< pagebreak >}}
+::: {.content-visible when-profile="summary"}
 
-## Analytical procedures
+\uselandscape
 
-### Source of data
+```{r}
 
-The University of Groningen IADB.nl pharmacy prescription database is a growing database that contains prescription data for 31 years from 1994 till 2024 from approximately 120 community pharmacies and covers an estimated population of 1,120,000 patients.
-Registration in the database is irrespective of health care insurance and age, gender and prescription rates among the database population have been found to be representative of the Netherlands as a whole, and the database has been widely used for research.
-Each person is individually tracked throughout the database period and prescription records contain information on the date of dispensing, the quantity dispensed, the dose regimen, the number of days the prescription is valid, the prescribing physician and the Anatomical Therapeutic Chemical code (ATC code).
-Each patient has a unique anonymous identifier; date of birth and gender are known.
-Due to the high patient-pharmacy commitment in the Netherlands, the medication records for each patient are virtually complete, except for over the counter (OTC) drugs and medication dispensed during hospitalization.
+pkgs <- c("targets", "magrittr")
+pkgs_load <- sapply(pkgs, library, character.only = TRUE)
+options(digits = 2, scipen = 999)
 
-#### Inclusion criteria
+```
 
-- Adult aged 18-65 years old at time of dispensing anxiolytic and/or antidepressant
-- Prescribed for anxiolytics (`N05B`) or antidepressant (`N06A`) at any time in the time span from 2018 to 2022
+## Excerpt on findings
 
-#### Exclusion criteria
+### Pair plot
 
-- (None)
+```{r}
 
-### Data pre-processing
+tar_read(plt_pair)[[17]]
 
-Daily medication claims can be represented as a square matrix, with rows and columns representing medication entities.
-N number of medications will then form an adjacency matrix describing the concurrent use of enlisted drugs.
-Therefore, the matrix diagonal represents using only one medication over the observation period.
-The matrix follows a knowledge graph construct with a subject-predicate-object (s, p, o) triples, i.e.
-`Medication1-PrescribedAlongside-Medication2`.
-The graph object is constructed from recorded prescription claims on a daily epoch.
-The edge (predicate) in this graph represents the number of concurrency, which will differ from one epoch to another depending on the number of patients claiming the prescription.
-To regularize the number of daily claims, it is essential to adjust the weight of the edge by dividing it by the defined daily dose (DDD).
-Regularization will allow direct comparison of one drug to another when calculating the graph metrics.
-Regularization based on DDD essentially transforms the dosage into a unit-free scale, which will be assigned as a weighted edge in the graph object.
+```
 
-### Measuring relative importance
+### Dot plots on weekly time-series
 
-The choice of graph metrics to use would be node centrality, which can be interpreted as node importance in a graph object.
-In our case, each node represents a single medication being claimed on that particular day.
-From various selection of centrality measures, we will focus on using eigenvector centrality, i.e.
-a prestige score.
-By calculating eigenvector centrality, each node will have a relative score.
-A high-scoring node implies that the node is highly connected with other high-scoring nodes.
-In a way, this shall reflect the score of importance when one drug is used alongside other drugs.
-Nodes with high eigenvector centrality can be further interpreted as strongly-connected nodes.
+```{r}
 
-{{< include exec-summary/descriptive.qmd >}}
+tar_read(plt_dot_week)[[1]]
 
-{{< include exec-summary/arima.qmd >}}
+```
 
-{{< include exec-summary/seasonality.qmd >}}
+### Differenced time-series on a weekly interval
 
-{{< include exec-summary/spectral.qmd >}}
+```{r}
+
+tar_read(plt_dot_diff_week)[[1]]
+
+```
+
+### Exploring seasonality within the number of medication claims
+
+```{r}
+
+tar_read(plt_period_month)[[1]]
+tar_read(plt_acf_diff_month)[[1]]
+tar_read(plt_pacf_diff_month)[[1]]
+
+```
+
+### Exploring ARIMA model
+
+```{r}
+
+tar_read(plt_arima_forecast_n_claim)[[17]]
+
+```
+
+### Decomposed time-series with SSA
+
+```{r}
+
+tar_read(plt_ssa_recon_n_claim)[[17]]
+
+```
+
+\normalpapersize
+
+:::

### 2024-02-12 _targets.R

@@ -285,7 +285,7 @@ list(
   ),
 
   # Generate documentation
-  tar_quarto(report, "docs", profile = "report", priority = 0),
+  tar_quarto(report, "docs", profile = "report", extra_files = "docs/exec-summary", priority = 0),
   tar_quarto(summary, "docs", profile = "summary", priority = 0),
   tar_quarto(report_descriptive, "docs", profile = "descriptive", priority = 0),
   tar_quarto(report_arima, "docs", profile = "arima", priority = 0),

### 2024-02-12 src/R/clean.R

@@ -56,6 +56,23 @@ getNeuroMeds <- function() {
   return(res)
 }
 
+isCovid <- function(x, covid_date = "2020-03-11") {
+  #' Annotate COVID-19 Date
+  #'
+  #' Annotate the date with COVID-19 event as announced by the WHO
+  #'
+  #' @param x A variable containing dates
+  #' @param covid_date A date reference of the time COVID-19 was announced as a
+  #' global pandemic
+  #' @return A factor of events
+  require("tsibble")
+  x %<>% as.Date()
+  res <- ifelse(x < covid_date, "Pre-COVID-19", "COVID-19") %>%
+    factor(levels = c("Pre-COVID-19", "COVID-19"))
+
+  return(res)
+}
+
 mergeTS <- function(tbl_metrics, tbl_stats, ...) {
   #' Merge Time Series Data
   #'
@@ -78,9 +95,10 @@ mergeTS <- function(tbl_metrics, tbl_stats, ...) {
   tbl_clean <- tbl %>%
     inset2("group", value = setGroupFactor(.$group)) %>% # Set factor
     inset2("neuro_med", value = .$group %in% getNeuroMeds()) %>% # Neuro meds
-    inset2("event", value = { # Pre/during COVID-19
-      ifelse(.$date < "2020-01-30", "Pre-COVID-19", "COVID-19")
-    }) %>%
+    inset2("event", value = isCovid(.$date)) %>%
+    #inset2("event", value = { # Pre/during COVID-19
+    #  ifelse(.$date < "2020-01-30", "Pre-COVID-19", "COVID-19")
+    #}) %>%
     inset( # Replace `NA` with 0
       c("n_claim", "claim2patient"),
       value = list(

### 2024-02-14 src/R/cluster.R
Assign clustering based on K-Medoids with PAM algorithm #18 CU-86cukv5n8[in-progress]

@@ -1,0 +1,64 @@
+# Functions to perform clustering
+
+fitCluster <- function(arr, ...) {
+  #' Fit Clustering Model
+  #'
+  #' Find K-Medoid clusters from a given array using partitioning around the
+  #' medoids (PAM) algorithm
+  #'
+  #' @param arr An array of number, could be a vector or matrix
+  #' @return A cluster object
+
+  clust <- cluster::pam(arr, pamonce = 6, ...)
+
+  return(clust)
+}
+
+evalCluster <- function(clust, ...) {
+  #' Evaluate Cluster Assignment
+  #'
+  #' Evaluate a cluster object
+  #'
+  #' @param clust A cluster object
+  #' @return A tidy data frame containing evaluation metrics
+
+  res <- cluster::silhouette(clust, ...) %>%
+    data.frame() %>%
+    extract2(3) %>%
+    mean()
+
+  return(res)
+}
+
+findCluster <- function(arr, nclusts = 2:10, ...) {
+  #' Find Clusters
+  #'
+  #' Find the optimal clustering model based on the evaluation metrics
+  #'
+  #' @param arr An array of number, could be a vector or matrix
+  #' @param nclusts An array of cluster parameter to fit
+  #' @return An array of clusters with optimum clustering
+
+  # Create a list of cluster objects
+  clusts <- lapply(nclusts, function(nclust) {
+    fitCluster(arr, k = nclust)
+  })
+
+  # Calculate silhouette scores and return the best-fitting clusters
+  metrics <- sapply(clusts, evalCluster, ...)
+  id      <- metrics %>% {which(. == max(.))}
+  mod     <- clusts[[id]]
+
+  # Ascendingly order the cluster based on its medoids rank
+  lvl <- mod$medoids %>%
+    data.frame() %>%
+    lapply(rank, ties.method = "average") %>%
+    data.frame() %>%
+    rowSums() %>%
+    order(decreasing = TRUE)
+
+  # Return cluster as an ordered array
+  clust <- mod$clustering %>% ordered(levels = lvl) %>% as.numeric()
+
+  return(clust)
+}

### 2024-02-14 src/R/spectral.R
Combine trend and two oscillating functions close #16 CU-86cukv4bk[closed]

@@ -185,3 +185,38 @@ bindReconSsa <- function(ts_list) {
     
   return(tbl)
 }
+
+genReconTs <- function(tbl, n = 2) {
+  #' Generate Reconstructed Time Series
+  #'
+  #' Generate a reconstructed time series based on trend and n number of
+  #' oscillating functions
+  #'
+  #' @param tbl The bound reconstructed time series, usually the output of
+  #' `bindReconSsa`
+  #' @param n The number of n oscillating functions to use. The more
+  #' oscillating functions to use, the close it gets to the original data.
+  #' Using all the oscillating functions will recreate the original data, which
+  #' means re-introducing the white noises. Keep the n number low, preferably n
+  #' = 2.
+  #' @return A tidy time series
+  require("tsibble")
+
+  if (n > 0) {
+    id <- tbl$component %in% c("Trend", paste0("F", 1:n))
+  } else {
+    id <- tbl$component == "Trend"
+  }
+
+  tbl %<>%
+    tsibble::as_tibble() %>%
+    subset(id) %>%
+    dplyr::group_by(metric, date, group) %>%
+    dplyr::summarize("value" = sum(value)) %>%
+    tidyr::pivot_wider(names_from = metric, values_from = value) %>%
+    dplyr::ungroup()
+
+  ts <- tbl %>% tsibble::as_tsibble(key = group, index = date)
+
+  return(ts)
+}

### 2024-02-14 docs/exec-summary/report.qmd
Report eigenvector centrality based on clustering results close #18 CU-86cukv5n8[closed] CU-86cukv59p[cancelled]

@@
+```{r}
+
+pkgs <- c("targets", "magrittr")
+pkgs_load <- sapply(pkgs, library, character.only = TRUE)
+options(digits = 2, scipen = 999)
+
+getGroup <- function(tbl, groupname) {
+  sub_tbl <- tbl %>% subset(.$group == groupname, select = -group)
+  return(sub_tbl)
+}
+
+results <- tar_read(ts_clust) %>%
+  tibble::tibble() %>%
+  dplyr::group_by(group) %>%
+  dplyr::summarize(ce = mean(eigen), nc = mean(n_claim) %>% round() %>% scales::comma())
+
+N06A <- results %>% getGroup("Antidepressants")
+N05A <- results %>% getGroup("Antipsychotics")
+N05B <- results %>% getGroup("Anxiolytics")
+A0x  <- results %>% getGroup("Alimentary and metabolism")
+B0x  <- results %>% getGroup("Blood")
+C0x  <- results %>% getGroup("Cardiovascular")
+N02  <- results %>% getGroup("Analgesics")
+R0x  <- results %>% getGroup("Respiratory")
+
+```
+
 ## Abstract
@@
 **Methods:**
-Exploratory time-series analysis was performed using University of Groningen prescription database, IADB.nl.
-Data of patients with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
-Prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca is evaluated at ATC level 3, drugs for nervous system at ATC level 2, and other medications at ATC level 1, totalled to 24 classes of medication.
+Exploratory time-series analysis was performed using the University of Groningen prescription database, IADB.nl.
+Data from patients with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
+The prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca was evaluated at ATC level 3, drugs for the nervous system at ATC level 2, and other medications at ATC level 1, distinguished into a total of 24 medication classes.
 A medication-claim network was constructed as an undirected graph to capture dose-adjusted co-prescription.
-Eigenvector centrality was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
-The number of medication claims, number of patients, claim-to-patient ratio, and eigenvector centrality were then extracted as a weekly-aggregated time-series data.
+Eigenvector centrality ($c_e$) was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
+The number of medication claims ($n_c$), number of patients, claim-to-patient ratio, and eigenvector centrality were extracted as weekly-aggregated time-series data.
 Singular spectrum analysis was performed to decompose the data into its constituting trend, periodicity, and white noises.
@@
 **Results:**
-Antidepressants (ATC `N06A`), antipsychotics (`N05A`), anxiolytics (`N05B`), and hypnotics (`N05C`) are psychopharmaca with high eigenvector centrality.
-These classes of medication are likely to be co-prescribed alongside other medications, including medications for alimentary and metabolism (`A01-A16`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory (`R01-R07`).
-Only antidepressants and hypnotics have a positive time trend for both eigenvector centrality and actual number of claims.
+Antidepressants (ATC `N06A`, $c_e$ = `r N06A$ce`, $n_c$ = `r N06A$nc`), antipsychotics (`N05A`, $c_e$ = `r N05A$ce`, $n_c$ = `r N05A$nc`), and anxiolytics (`N05B`, $c_e$ = `r N05B$ce`, $n_c$ = `r N05B$nc`) are psychopharmaca with high eigenvector centrality.
+These classes of medication are likely to be co-prescribed alongside other medications.
+Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$ = `r A0x$ce`, $n_c$ = `r A0x$nc`), blood (`B01-B06`, $c_e$ = `r B0x$ce`, $n_c$ = `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$ = `r C0x$ce`, $n_c$ = `r C0x$ne`), analgesics (`N02`, $c_e$ = `r N02$ce`, $n_c$ `r N02$nc`), and respiratory (`R01-R07`, $c_e$ = `r R0x$ce`, $n_c$ = `r R0x$nc`).
+High eigenvector centrality implies that these medications are likely to be co-prescribed with other medications.
+Only antidepressants had a positive time trend for both eigenvector centrality and actual number of claims.
 
 **Discussion:**
-Eight medications, four of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level.
-Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants and hypnotics are related to co-prescription with other medication classes.
-Constructing a medication claim network enriches the exploratory analysis procedure on the population level.
+Eight medications, three of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level.
+Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants are related to co-prescription with other medication classes.
+Constructing a medication claim network enriches the exploratory analysis of medication use at the population level.
 
@@
 
-```{r}
-
-pkgs <- c("targets", "magrittr")
-pkgs_load <- sapply(pkgs, library, character.only = TRUE)
-options(digits = 2, scipen = 999)
-
-```
-
 ## Excerpt on findings

### 2024-02-14 _targets.R

@@ -284,6 +284,12 @@ list(
     )
   ),
 
+  # Generate reconstructed time series based on trend + 2 oscillating functions
+  tar_target(ts_recon, genReconTs(decom_ssa, n = 2)),
+
+  # Cluster the series based on eigenvector centrality
+  tar_target(ts_clust, setCluster(ts_recon, nclusts = 2:10)),
+
   # Generate documentation
   tar_quarto(report, "docs", profile = "report", extra_files = "docs/exec-summary", priority = 0),
   tar_quarto(summary, "docs", profile = "summary", priority = 0),

### 2024-02-14 src/R/cluster.R

@@ -62,3 +62,19 @@ findCluster <- function(arr, nclusts = 2:10, ...) {
 
   return(clust)
 }
+
+setCluster <- function(ts, nclusts = 2:10, ...) {
+  #' Set Cluster
+  #'
+  #' Assign cluster to a data frame
+  #'
+  #' @param ts A tidy time series, usually the output of `genReconTs`
+  #' @param nclusts An array of cluster parameter to fit
+  #' @return A tidy time seires with a clustering variable
+  require("tsibble")
+
+  aug_ts <- ts %>%
+    dplyr::mutate("cluster" = findCluster(eigen, nclusts = nclusts, ...))
+
+  return(aug_ts)
+}

### 2024-02-14 docs/exec-summary/report.qmd
Rephrase the abstract to improve readability

@@
 Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$ = `r A0x$ce`, $n_c$ = `r A0x$nc`), blood (`B01-B06`, $c_e$ = `r B0x$ce`, $n_c$ = `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$ = `r C0x$ce`, $n_c$ = `r C0x$ne`), analgesics (`N02`, $c_e$ = `r N02$ce`, $n_c$ `r N02$nc`), and respiratory (`R01-R07`, $c_e$ = `r R0x$ce`, $n_c$ = `r R0x$nc`).
-High eigenvector centrality implies that these medications are likely to be co-prescribed with other medications.
-Only antidepressants had a positive time trend for both eigenvector centrality and actual number of claims.
+Among eight medications with high eigenvector centrality, only antidepressants had a positive time trend for both eigenvector centrality and actual number of claims.
 

### 2024-02-14 docs/abstract/_abstract.qmd
Separate abstract in a different file, improve naming consistency for included files

--- 2024-02-14 docs/exec-summary/report.qmd
@@
   dplyr::group_by(group) %>%
-  dplyr::summarize(ce = mean(eigen), nc = mean(n_claim) %>% round() %>% scales::comma())
+  dplyr::summarize(
+    ce = mean(eigen),
+    nc = mean(n_claim) %>% round() %>% scales::comma(),
+    lim_ce = 1.96 * sd(eigen) / sqrt(length(eigen)),
+    ce_ci  = sprintf("%.02f [%.02f, %.02f]", ce, ce - lim_ce, ce + lim_ce)
+  )
 
@@
 
-## Abstract
+**Background:**
+Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide.
+People with chronic diseases are at a higher risk of having mental health issues, which in turn potentially worsen their overall well-being.
 
 **Objectives:**  
-Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide.
-People with chronic diseases are at a higher risk of having mental health issues, which in turn potentially worsen their overall well-being.
-This investigation highlights the interrelatedness of mental health problems with other diagnoses, reflected as a relative importance score of psychopharmaca in a medication claim registry.
+Evaluate the interrelatedness of mental health problems with other diagnoses, reflected as a relative importance score of psychopharmaca in a medication claim registry.
 
@@
 Exploratory time-series analysis was performed using the University of Groningen prescription database, IADB.nl.
-Data from patients with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
+A static cohort with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
 The prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca was evaluated at ATC level 3, drugs for the nervous system at ATC level 2, and other medications at ATC level 1, distinguished into a total of 24 medication classes.
@@
 **Results:**
-Antidepressants (ATC `N06A`, $c_e$ = `r N06A$ce`, $n_c$ = `r N06A$nc`), antipsychotics (`N05A`, $c_e$ = `r N05A$ce`, $n_c$ = `r N05A$nc`), and anxiolytics (`N05B`, $c_e$ = `r N05B$ce`, $n_c$ = `r N05B$nc`) are psychopharmaca with high eigenvector centrality.
+Antidepressants (ATC `N06A`, $c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`), antipsychotics (`N05A`, $c_e$: `r N05A$ce`, $n_c$: `r N05A$nc`), and anxiolytics (`N05B`, $c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) are psychopharmaca with high eigenvector centrality.
 These classes of medication are likely to be co-prescribed alongside other medications.
-Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$ = `r A0x$ce`, $n_c$ = `r A0x$nc`), blood (`B01-B06`, $c_e$ = `r B0x$ce`, $n_c$ = `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$ = `r C0x$ce`, $n_c$ = `r C0x$ne`), analgesics (`N02`, $c_e$ = `r N02$ce`, $n_c$ `r N02$nc`), and respiratory (`R01-R07`, $c_e$ = `r R0x$ce`, $n_c$ = `r R0x$nc`).
+Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$: `r A0x$ce`, $n_c$: `r A0x$nc`), blood (`B01-B06`, $c_e$: `r B0x$ce`, $n_c$: `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$: `r C0x$ce`, $n_c$: `r C0x$ne`), analgesics (`N02`, $c_e$: `r N02$ce`, $n_c$ `r N02$nc`), and respiratory (`R01-R07`, $c_e$: `r R0x$ce`, $n_c$: `r R0x$nc`).
 Among eight medications with high eigenvector centrality, only antidepressants had a positive time trend for both eigenvector centrality and actual number of claims.
@@
 Constructing a medication claim network enriches the exploratory analysis of medication use at the population level.
-
-{{< pagebreak >}}
-
-## Analytical procedures
-
-### Source of data
-
-The University of Groningen IADB.nl pharmacy prescription database is a growing database that contains prescription data for 31 years from 1994 till 2024 from approximately 120 community pharmacies and covers an estimated population of 1,120,000 patients.
-Registration in the database is irrespective of health care insurance and age, gender and prescription rates among the database population have been found to be representative of the Netherlands as a whole, and the database has been widely used for research.
-Each person is individually tracked throughout the database period and prescription records contain information on the date of dispensing, the quantity dispensed, the dose regimen, the number of days the prescription is valid, the prescribing physician and the Anatomical Therapeutic Chemical code (ATC code).
-Each patient has a unique anonymous identifier; date of birth and gender are known.
-Due to the high patient-pharmacy commitment in the Netherlands, the medication records for each patient are virtually complete, except for over the counter (OTC) drugs and medication dispensed during hospitalization.
-This analysis include daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.
-
-### Data pre-processing
-
-Daily medication claims is a tabular data containing values from single medication entity for each patients in the cohort.
-Data transformation was performed to construct a square matrix of aggregate medication claim per day, with rows and columns representing groups of medication.
-Each element in the upper and lower triangle represents co-prescriptions, while the diagonal of the matrix represents single prescriptions.
-All elements in the matrix is a tally of drug combination/single prescription in a population level claimed on a daily basis.
-The matrix follows a knowledge graph construct with a subject-predicate-object (s, p, o) triples, i.e.
-`Medication1-PrescribedAlongside-Medication2`.
-The knowledge graph is a representation of medication-claim network, where the edge (predicate) is the number of concurrency.
-Weight was applied on the edges by dividing it by the defined daily dose (DDD).
-Weighting is necessary to regularize the matrix into a unit-free scale, which allow a direct comparison of one drug to another.
-
-$$
-\stackrel{\textrm{Unregularized}}{
-  \begin{bmatrix}
-  n_{1, 1} & \dots & n_{1, N} \\
-  \vdots & \ddots & \vdots \\
-  n_{N, 1} & \dots & n_{N, N} \\
-  \end{bmatrix}
-}
-\to
-\stackrel{\textrm{Regularized by } DDD}{
-  \begin{bmatrix}
-  \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_N}{DDD_N} \right) \\
-  \vdots & \ddots & \vdots \\
-  \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_N}{DDD_N} \right) \\
-  \end{bmatrix}
-}
-$$ {#eq-regularize-mtx}
-
-### Measuring relative importance
-
-As all medications are nodes in a claim network, we can measure the property of each medication using graph theory.
-One way to represent node property is by calculating node centrality, which can be measured as a number of incoming/outgoing edges (degree) or its connectedness to other nodes (importance).
-We measured importance using eigenvector centrality, which reflects medication co-occurrence with other important medications.
-Eigenvector centrality is a recursive measures of how well connected a certain node is to other nodes that is also well connected in the network [@Golbeck2013].
-@eq-eigen-centrality outlines the calculation of eigenvector centrality; $\c_i$ and $\c_j$ are the centralities of node $i$ and $j$, respectively; $\lambda$ is the eigenvalue; $a_{j, i}$ is an element on row $j$ and column $i$ from an adjacency matrix $A$, representing the connection between node $a_i$ and $a_j$.
-
-$$
-\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} a_{j, i} \cdot c_j
-$$ {#eq-eigen-centrality}
-
-{{< include exec-summary/descriptive.qmd >}}
-
-{{< include exec-summary/seasonality.qmd >}}
-
-{{< include exec-summary/arima.qmd >}}
-
-{{< include exec-summary/spectral.qmd >}}
-
-## Highlighted findings
-
-- @tbl-mean-diff describes difference in several measures before and during the COVID-19 pandemic
-  - Further analysis is necessary and will be planned for later investigation
-  - Interrupted time-series analysis should be conducted by considering:
-    1. Counterfactual data using trend before COVID-19
-    1. Counterfactual data using trend during COVID-19 given policy changes
-    1. Calculate the mean percentage changes between counterfactual and actual data
-- @sec-decom-classic-stl displays the data after classical and STL seasonal decomposition
-  - The data still presents with other patterns, implying that seasonality does not completely explains the variance
-  - Eigenvector centrality on daily, weekly, and monthly series suggests high importance of several psychopharmaca, including:
-    1. Antidepressants
-    1. Antipsychotics
-    1. Anxiolytics
-    1. Hypnotic and sedatives
-  - Other medications considered important by eigenvector centrality:
-    1. Alimentary and metabolism
-    1. Cardiovascular
-    1. Analgesics
-    1. Respiratory
-  - High eigenvector centrality implies that these eight medications are often co-prescribed
-- @sec-seasonality demonstrates two repeating patterns in medication claims:
-  - Increasing claims on Monday and decreasing claims on Saturday in the daily data, implying day-to-day differences
-  - Increasing claims in March and December in the monthly data, this pattern is persistent for weekly data as well
-  - Weekly data better captures repeating patterns and should be use for further analysis
-- Model evaluation tables in @sec-arima consistently show high value of intercept
-  - All models for medication claims have a relatively low effect size for AR, MA, or drift term
-  - No model has fitted with a (P, D, Q) term, implying no detected seasonality for models maximizing AICc
-  - Seasonality might be undetected due to the presence of noise and other underlying periodicity
-- @tbl-trend shows differences between the actual and decomposed data
-  - Trend is more visible in the decomposed data due to being free from noises and periodicity
-  - The magnitude of detected trend is naturally larger, and still implies the same monotonicity with the original data
-  - The number of claims in 11 medication classes are declining overtime
-  - The relative importance in 14 medication classes are declining overtime
-  - Changes in claim represents the actual change of the expected number of medication claim in the population.
-Changes in importance represents changes of how likely a medication being prescribed together.
-Differences between relative importance and number of medication claims are observed in:
-    1. Genitourinary: decreasing claim, increasing importance
-    1. Systemic hormonal: increasing claim, decreasing importance
-    1. Antiparkinson: increasing claim, decreasing importance
-    1. Antipsychotics: increasing claim, decreasing importance
-    1. Antidementia: increasing claim, decreasing importance
-    1. Other nervous system drugs: decreasing claim, increasing importance
-    1. Antiparasitics: increasing claim, decreasing importance
-- @tbl-resid-n-claim and @tbl-resid-eigen shows the residuals analysis of the decomposition model using singular spectrum analysis
-  - All residuals are stationary, i.e. having a constant mean and variance
-  - All residuals follow the normal distribution (see especially Shapiro-Wilk statistics, mean, and standard deviation)
-  - These findings imply that the residuals of decomposition models are likely to be evenly and randomly distributed
-- @sec-recon depicts complex periodicity within each time series
-  - These go in line with findings from @sec-seasonality
-  - Despite visible patterns of weekly and yearly seasonality, these patterns are obscured with other oscillating functions
-  - The oscillating functions were ordered based on their contribution in explaining the variance in the data, e.g. `F1` has a higher contribution than `F2`, and so on
-
-::: {.content-visible when-profile="summary"}
-
-\uselandscape
-
-## Excerpt on findings
-
-### Pair plot
-
-```{r}
-
-tar_read(plt_pair)[[17]]
-
-```
-
-### Dot plots on weekly time-series
-
-```{r}
-
-tar_read(plt_dot_week)[[1]]
-
-```
-
-### Differenced time-series on a weekly interval
-
-```{r}
-
-tar_read(plt_dot_diff_week)[[1]]
-
-```
-
-### Exploring seasonality within the number of medication claims
-
-```{r}
-
-tar_read(plt_period_month)[[1]]
-tar_read(plt_acf_diff_month)[[1]]
-tar_read(plt_pacf_diff_month)[[1]]
-
-```
-
-### Exploring ARIMA model
-
-```{r}
-
-tar_read(plt_arima_forecast_n_claim)[[17]]
-
-```
-
-### Decomposed time-series with SSA
-
-```{r}
-
-tar_read(plt_ssa_recon_n_claim)[[17]]
-
-```
-
-\normalpapersize
-
-:::

### 2024-02-14 docs/exec-summary/_arima.qmd
Separate abstract in a different file, improve naming consistency for included files

### Exploratory ARIMA modelling

Accounting for the presence of weekly and yearly seasonality, autoregressive integrated moving average (ARIMA) model was performed on weekly series. Weekly series was selected over daily series because it represents the population dynamic better. The daily series was highly noisy due to differences in the amount of patients claiming their medication, where it peaked on Monday and at its lowest on Saturday. On the other hand, weekly series was selected over monthly series because it preserves the data point while still capturing the seasonal pattern. ARIMA model was fitted using Hyndman-Khandakar algorithm to minimize Akaike Information Criterion (AIC) with a forward-backward stepwise selection. AIC was preferred instead of Bayesian Information Criterion (BIC) since BIC penalizes the number of parameters. However, since the main purpose of Hyndman-Khandakar algorithm is to minimize information criterion, it does not necessarily find the generalizable parameters in the data. In the presence of mixed seasonality and complex periodic patterns, the algorithm might fail to capture the right parameters. As such, an exploratory ARIMA modelling was *not* aimed to find a parsimonious model; rather, it was intended to confirm the presence of simple seasonal pattern.

### 2024-02-14 docs/exec-summary/_descriptive.qmd
Separate abstract in a different file, improve naming consistency for included files

### Exploratory descriptive analysis

The data was extracted as a daily time-series, which then aggregated into weekly and monthly for exploratory data analysis. The data contains five metrics, including the number of daily medication claims, the number of daily patients, claim-to-patient ratio, and eigenvector centrality. For each metrics in each dataset, univariate descriptive analysis was performed by calculating the statistical summary to describe the centrality and spread. Mean, median, standard deviation, and interquartile range were reported to evaluate the distribution. The data is split into pre-COVID-19 and during COVID-19 period, and mean difference was calculated using Welch's T-Test. For visual examination, pair plots were generated for each medication group. The correlations between metrics were calculated by considering pre-COVID-19, during COVID-19, and the overall association. Daily, weekly, and monthly time-series were also plotted and grouped by medications. Classical and seasonal-trend decomposition using LOESS (STL) were performed to extract decomposed trend for further visual evaluation. Each dataset was then detrended by performing a first-degree differencing, i.e. taking the differences between $x_t$ and $x_{t-1}$.

### 2024-02-14 docs/exec-summary/_measure-eigen.qmd
Separate abstract in a different file, improve naming consistency for included files

--- 2024-02-12 docs/exec-summary/report.qmd
@@
-## Abstract
-
-**Objectives:**
-Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide.
-People with chronic diseases are at a higher risk of having mental health issues, which in turn potentially worsen their overall well-being.
-This investigation highlights the interrelatedness of mental health problems with other diagnoses, reflected as a relative importance score of psychopharmaca in a medication claim registry.
-
-**Methods:**
-Exploratory time-series analysis was performed using University of Groningen prescription database, IADB.nl.
-Data of patients with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
-Prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca is evaluated at ATC level 3, drugs for nervous system at ATC level 2, and other medications at ATC level 1, totalled to 24 classes of medication.
-A medication-claim network was constructed as an undirected graph to capture dose-adjusted co-prescription.
-Eigenvector centrality was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
-The number of medication claims, number of patients, claim-to-patient ratio, and eigenvector centrality were then extracted as a weekly-aggregated time-series data.
-Singular spectrum analysis was performed to decompose the data into its constituting trend, periodicity, and white noises.
-
-**Results:**
-Antidepressants (ATC `N06A`), antipsychotics (`N05A`), anxiolytics (`N05B`), and hypnotics (`N05C`) are psychopharmaca with high eigenvector centrality.
-These classes of medication are likely to be co-prescribed alongside other medications, including medications for alimentary and metabolism (`A01-A16`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory (`R01-R07`).
-Only antidepressants and hypnotics have a positive time trend for both eigenvector centrality and actual number of claims.
-
-**Discussion:**
-Eight medications, four of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level.
-Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants and hypnotics are related to co-prescription with other medication classes.
-Constructing a medication claim network enriches the exploratory analysis procedure on the population level.
-
-{{< pagebreak >}}
-
-## Analytical procedures
-
-### Source of data
-
-The University of Groningen IADB.nl pharmacy prescription database is a growing database that contains prescription data for 31 years from 1994 till 2024 from approximately 120 community pharmacies and covers an estimated population of 1,120,000 patients.
-Registration in the database is irrespective of health care insurance and age, gender and prescription rates among the database population have been found to be representative of the Netherlands as a whole, and the database has been widely used for research.
-Each person is individually tracked throughout the database period and prescription records contain information on the date of dispensing, the quantity dispensed, the dose regimen, the number of days the prescription is valid, the prescribing physician and the Anatomical Therapeutic Chemical code (ATC code).
-Each patient has a unique anonymous identifier; date of birth and gender are known.
-Due to the high patient-pharmacy commitment in the Netherlands, the medication records for each patient are virtually complete, except for over the counter (OTC) drugs and medication dispensed during hospitalization.
-This analysis include daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.
-
-### Data pre-processing
-
-Daily medication claims is a tabular data containing values from single medication entity for each patients in the cohort.
-Data transformation was performed to construct a square matrix of aggregate medication claim per day, with rows and columns representing groups of medication.
-Each element in the upper and lower triangle represents co-prescriptions, while the diagonal of the matrix represents single prescriptions.
-All elements in the matrix is a tally of drug combination/single prescription in a population level claimed on a daily basis.
-The matrix follows a knowledge graph construct with a subject-predicate-object (s, p, o) triples, i.e.
-`Medication1-PrescribedAlongside-Medication2`.
-The knowledge graph is a representation of medication-claim network, where the edge (predicate) is the number of concurrency.
-Weight was applied on the edges by dividing it by the defined daily dose (DDD).
-Weighting is necessary to regularize the matrix into a unit-free scale, which allow a direct comparison of one drug to another.
-
-$$
-\stackrel{\textrm{Unregularized}}{
-  \begin{bmatrix}
-  n_{1, 1} & \dots & n_{1, N} \\
-  \vdots & \ddots & \vdots \\
-  n_{N, 1} & \dots & n_{N, N} \\
-  \end{bmatrix}
-}
-\to
-\stackrel{\textrm{Regularized by } DDD}{
-  \begin{bmatrix}
-  \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_N}{DDD_N} \right) \\
-  \vdots & \ddots & \vdots \\
-  \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_N}{DDD_N} \right) \\
-  \end{bmatrix}
-}
-$$ {#eq-regularize-mtx}
-
 ### Measuring relative importance
@@
 $$ {#eq-eigen-centrality}
-
-{{< include exec-summary/descriptive.qmd >}}
-
-{{< include exec-summary/seasonality.qmd >}}
-
-{{< include exec-summary/arima.qmd >}}
-
-{{< include exec-summary/spectral.qmd >}}
-
-## Highlighted findings
-
-- @tbl-mean-diff describes difference in several measures before and during the COVID-19 pandemic
-  - Further analysis is necessary and will be planned for later investigation
-  - Interrupted time-series analysis should be conducted by considering:
-    1. Counterfactual data using trend before COVID-19
-    1. Counterfactual data using trend during COVID-19 given policy changes
-    1. Calculate the mean percentage changes between counterfactual and actual data
-- @sec-decom-classic-stl displays the data after classical and STL seasonal decomposition
-  - The data still presents with other patterns, implying that seasonality does not completely explains the variance
-  - Eigenvector centrality on daily, weekly, and monthly series suggests high importance of several psychopharmaca, including:
-    1. Antidepressants
-    1. Antipsychotics
-    1. Anxiolytics
-    1. Hypnotic and sedatives
-  - Other medications considered important by eigenvector centrality:
-    1. Alimentary and metabolism
-    1. Cardiovascular
-    1. Analgesics
-    1. Respiratory
-  - High eigenvector centrality implies that these eight medications are often co-prescribed
-- @sec-seasonality demonstrates two repeating patterns in medication claims:
-  - Increasing claims on Monday and decreasing claims on Saturday in the daily data, implying day-to-day differences
-  - Increasing claims in March and December in the monthly data, this pattern is persistent for weekly data as well
-  - Weekly data better captures repeating patterns and should be use for further analysis
-- Model evaluation tables in @sec-arima consistently show high value of intercept
-  - All models for medication claims have a relatively low effect size for AR, MA, or drift term
-  - No model has fitted with a (P, D, Q) term, implying no detected seasonality for models maximizing AICc
-  - Seasonality might be undetected due to the presence of noise and other underlying periodicity
-- @tbl-trend shows differences between the actual and decomposed data
-  - Trend is more visible in the decomposed data due to being free from noises and periodicity
-  - The magnitude of detected trend is naturally larger, and still implies the same monotonicity with the original data
-  - The number of claims in 11 medication classes are declining overtime
-  - The relative importance in 14 medication classes are declining overtime
-  - Changes in claim represents the actual change of the expected number of medication claim in the population.
-Changes in importance represents changes of how likely a medication being prescribed together.
-Differences between relative importance and number of medication claims are observed in:
-    1. Genitourinary: decreasing claim, increasing importance
-    1. Systemic hormonal: increasing claim, decreasing importance
-    1. Antiparkinson: increasing claim, decreasing importance
-    1. Antipsychotics: increasing claim, decreasing importance
-    1. Antidementia: increasing claim, decreasing importance
-    1. Other nervous system drugs: decreasing claim, increasing importance
-    1. Antiparasitics: increasing claim, decreasing importance
-- @tbl-resid-n-claim and @tbl-resid-eigen shows the residuals analysis of the decomposition model using singular spectrum analysis
-  - All residuals are stationary, i.e. having a constant mean and variance
-  - All residuals follow the normal distribution (see especially Shapiro-Wilk statistics, mean, and standard deviation)
-  - These findings imply that the residuals of decomposition models are likely to be evenly and randomly distributed
-- @sec-recon depicts complex periodicity within each time series
-  - These go in line with findings from @sec-seasonality
-  - Despite visible patterns of weekly and yearly seasonality, these patterns are obscured with other oscillating functions
-  - The oscillating functions were ordered based on their contribution in explaining the variance in the data, e.g. `F1` has a higher contribution than `F2`, and so on
-
-::: {.content-visible when-profile="summary"}
-
-\uselandscape
-
-```{r}
-
-pkgs <- c("targets", "magrittr")
-pkgs_load <- sapply(pkgs, library, character.only = TRUE)
-options(digits = 2, scipen = 999)
-
-```
-
-## Excerpt on findings
-
-### Pair plot
-
-```{r}
-
-tar_read(plt_pair)[[17]]
-
-```
-
-### Dot plots on weekly time-series
-
-```{r}
-
-tar_read(plt_dot_week)[[1]]
-
-```
-
-### Differenced time-series on a weekly interval
-
-```{r}
-
-tar_read(plt_dot_diff_week)[[1]]
-
-```
-
-### Exploring seasonality within the number of medication claims
-
-```{r}
-
-tar_read(plt_period_month)[[1]]
-tar_read(plt_acf_diff_month)[[1]]
-tar_read(plt_pacf_diff_month)[[1]]
-
-```
-
-### Exploring ARIMA model
-
-```{r}
-
-tar_read(plt_arima_forecast_n_claim)[[17]]
-
-```
-
-### Decomposed time-series with SSA
-
-```{r}
-
-tar_read(plt_ssa_recon_n_claim)[[17]]
-
-```
-
-\normalpapersize
-
-:::

### 2024-02-14 docs/exec-summary/_preprocessing.qmd
Separate abstract in a different file, improve naming consistency for included files

--- 2024-02-12 docs/exec-summary/report.qmd
@@
-## Abstract
-
-**Objectives:**
-Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide.
-People with chronic diseases are at a higher risk of having mental health issues, which in turn potentially worsen their overall well-being.
-This investigation highlights the interrelatedness of mental health problems with other diagnoses, reflected as a relative importance score of psychopharmaca in a medication claim registry.
-
-**Methods:**
-Exploratory time-series analysis was performed using University of Groningen prescription database, IADB.nl.
-Data of patients with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
-Prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca is evaluated at ATC level 3, drugs for nervous system at ATC level 2, and other medications at ATC level 1, totalled to 24 classes of medication.
-A medication-claim network was constructed as an undirected graph to capture dose-adjusted co-prescription.
-Eigenvector centrality was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
-The number of medication claims, number of patients, claim-to-patient ratio, and eigenvector centrality were then extracted as a weekly-aggregated time-series data.
-Singular spectrum analysis was performed to decompose the data into its constituting trend, periodicity, and white noises.
-
-**Results:**
-Antidepressants (ATC `N06A`), antipsychotics (`N05A`), anxiolytics (`N05B`), and hypnotics (`N05C`) are psychopharmaca with high eigenvector centrality.
-These classes of medication are likely to be co-prescribed alongside other medications, including medications for alimentary and metabolism (`A01-A16`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory (`R01-R07`).
-Only antidepressants and hypnotics have a positive time trend for both eigenvector centrality and actual number of claims.
-
-**Discussion:**
-Eight medications, four of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level.
-Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants and hypnotics are related to co-prescription with other medication classes.
-Constructing a medication claim network enriches the exploratory analysis procedure on the population level.
-
-{{< pagebreak >}}
-
-## Analytical procedures
-
-### Source of data
-
-The University of Groningen IADB.nl pharmacy prescription database is a growing database that contains prescription data for 31 years from 1994 till 2024 from approximately 120 community pharmacies and covers an estimated population of 1,120,000 patients.
-Registration in the database is irrespective of health care insurance and age, gender and prescription rates among the database population have been found to be representative of the Netherlands as a whole, and the database has been widely used for research.
-Each person is individually tracked throughout the database period and prescription records contain information on the date of dispensing, the quantity dispensed, the dose regimen, the number of days the prescription is valid, the prescribing physician and the Anatomical Therapeutic Chemical code (ATC code).
-Each patient has a unique anonymous identifier; date of birth and gender are known.
-Due to the high patient-pharmacy commitment in the Netherlands, the medication records for each patient are virtually complete, except for over the counter (OTC) drugs and medication dispensed during hospitalization.
-This analysis include daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.
-
 ### Data pre-processing
@@
 $$ {#eq-regularize-mtx}
-
-### Measuring relative importance
-
-As all medications are nodes in a claim network, we can measure the property of each medication using graph theory.
-One way to represent node property is by calculating node centrality, which can be measured as a number of incoming/outgoing edges (degree) or its connectedness to other nodes (importance).
-We measured importance using eigenvector centrality, which reflects medication co-occurrence with other important medications.
-Eigenvector centrality is a recursive measures of how well connected a certain node is to other nodes that is also well connected in the network [@Golbeck2013].
-@eq-eigen-centrality outlines the calculation of eigenvector centrality; $\c_i$ and $\c_j$ are the centralities of node $i$ and $j$, respectively; $\lambda$ is the eigenvalue; $a_{j, i}$ is an element on row $j$ and column $i$ from an adjacency matrix $A$, representing the connection between node $a_i$ and $a_j$.
-
-$$
-\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} a_{j, i} \cdot c_j
-$$ {#eq-eigen-centrality}
-
-{{< include exec-summary/descriptive.qmd >}}
-
-{{< include exec-summary/seasonality.qmd >}}
-
-{{< include exec-summary/arima.qmd >}}
-
-{{< include exec-summary/spectral.qmd >}}
-
-## Highlighted findings
-
-- @tbl-mean-diff describes difference in several measures before and during the COVID-19 pandemic
-  - Further analysis is necessary and will be planned for later investigation
-  - Interrupted time-series analysis should be conducted by considering:
-    1. Counterfactual data using trend before COVID-19
-    1. Counterfactual data using trend during COVID-19 given policy changes
-    1. Calculate the mean percentage changes between counterfactual and actual data
-- @sec-decom-classic-stl displays the data after classical and STL seasonal decomposition
-  - The data still presents with other patterns, implying that seasonality does not completely explains the variance
-  - Eigenvector centrality on daily, weekly, and monthly series suggests high importance of several psychopharmaca, including:
-    1. Antidepressants
-    1. Antipsychotics
-    1. Anxiolytics
-    1. Hypnotic and sedatives
-  - Other medications considered important by eigenvector centrality:
-    1. Alimentary and metabolism
-    1. Cardiovascular
-    1. Analgesics
-    1. Respiratory
-  - High eigenvector centrality implies that these eight medications are often co-prescribed
-- @sec-seasonality demonstrates two repeating patterns in medication claims:
-  - Increasing claims on Monday and decreasing claims on Saturday in the daily data, implying day-to-day differences
-  - Increasing claims in March and December in the monthly data, this pattern is persistent for weekly data as well
-  - Weekly data better captures repeating patterns and should be use for further analysis
-- Model evaluation tables in @sec-arima consistently show high value of intercept
-  - All models for medication claims have a relatively low effect size for AR, MA, or drift term
-  - No model has fitted with a (P, D, Q) term, implying no detected seasonality for models maximizing AICc
-  - Seasonality might be undetected due to the presence of noise and other underlying periodicity
-- @tbl-trend shows differences between the actual and decomposed data
-  - Trend is more visible in the decomposed data due to being free from noises and periodicity
-  - The magnitude of detected trend is naturally larger, and still implies the same monotonicity with the original data
-  - The number of claims in 11 medication classes are declining overtime
-  - The relative importance in 14 medication classes are declining overtime
-  - Changes in claim represents the actual change of the expected number of medication claim in the population.
-Changes in importance represents changes of how likely a medication being prescribed together.
-Differences between relative importance and number of medication claims are observed in:
-    1. Genitourinary: decreasing claim, increasing importance
-    1. Systemic hormonal: increasing claim, decreasing importance
-    1. Antiparkinson: increasing claim, decreasing importance
-    1. Antipsychotics: increasing claim, decreasing importance
-    1. Antidementia: increasing claim, decreasing importance
-    1. Other nervous system drugs: decreasing claim, increasing importance
-    1. Antiparasitics: increasing claim, decreasing importance
-- @tbl-resid-n-claim and @tbl-resid-eigen shows the residuals analysis of the decomposition model using singular spectrum analysis
-  - All residuals are stationary, i.e. having a constant mean and variance
-  - All residuals follow the normal distribution (see especially Shapiro-Wilk statistics, mean, and standard deviation)
-  - These findings imply that the residuals of decomposition models are likely to be evenly and randomly distributed
-- @sec-recon depicts complex periodicity within each time series
-  - These go in line with findings from @sec-seasonality
-  - Despite visible patterns of weekly and yearly seasonality, these patterns are obscured with other oscillating functions
-  - The oscillating functions were ordered based on their contribution in explaining the variance in the data, e.g. `F1` has a higher contribution than `F2`, and so on
-
-::: {.content-visible when-profile="summary"}
-
-\uselandscape
-
-```{r}
-
-pkgs <- c("targets", "magrittr")
-pkgs_load <- sapply(pkgs, library, character.only = TRUE)
-options(digits = 2, scipen = 999)
-
-```
-
-## Excerpt on findings
-
-### Pair plot
-
-```{r}
-
-tar_read(plt_pair)[[17]]
-
-```
-
-### Dot plots on weekly time-series
-
-```{r}
-
-tar_read(plt_dot_week)[[1]]
-
-```
-
-### Differenced time-series on a weekly interval
-
-```{r}
-
-tar_read(plt_dot_diff_week)[[1]]
-
-```
-
-### Exploring seasonality within the number of medication claims
-
-```{r}
-
-tar_read(plt_period_month)[[1]]
-tar_read(plt_acf_diff_month)[[1]]
-tar_read(plt_pacf_diff_month)[[1]]
-
-```
-
-### Exploring ARIMA model
-
-```{r}
-
-tar_read(plt_arima_forecast_n_claim)[[17]]
-
-```
-
-### Decomposed time-series with SSA
-
-```{r}
-
-tar_read(plt_ssa_recon_n_claim)[[17]]
-
-```
-
-\normalpapersize
-
-:::

### 2024-02-14 docs/exec-summary/_report.qmd
Separate abstract in a different file, improve naming consistency for included files

--- 2024-02-12 docs/exec-summary/report.qmd
@@
-## Abstract
-
-**Objectives:**
-Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide.
-People with chronic diseases are at a higher risk of having mental health issues, which in turn potentially worsen their overall well-being.
-This investigation highlights the interrelatedness of mental health problems with other diagnoses, reflected as a relative importance score of psychopharmaca in a medication claim registry.
-
-**Methods:**
-Exploratory time-series analysis was performed using University of Groningen prescription database, IADB.nl.
-Data of patients with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
-Prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca is evaluated at ATC level 3, drugs for nervous system at ATC level 2, and other medications at ATC level 1, totalled to 24 classes of medication.
-A medication-claim network was constructed as an undirected graph to capture dose-adjusted co-prescription.
-Eigenvector centrality was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
-The number of medication claims, number of patients, claim-to-patient ratio, and eigenvector centrality were then extracted as a weekly-aggregated time-series data.
-Singular spectrum analysis was performed to decompose the data into its constituting trend, periodicity, and white noises.
-
-**Results:**
-Antidepressants (ATC `N06A`), antipsychotics (`N05A`), anxiolytics (`N05B`), and hypnotics (`N05C`) are psychopharmaca with high eigenvector centrality.
-These classes of medication are likely to be co-prescribed alongside other medications, including medications for alimentary and metabolism (`A01-A16`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory (`R01-R07`).
-Only antidepressants and hypnotics have a positive time trend for both eigenvector centrality and actual number of claims.
-
-**Discussion:**
-Eight medications, four of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level.
-Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants and hypnotics are related to co-prescription with other medication classes.
-Constructing a medication claim network enriches the exploratory analysis procedure on the population level.
-
-{{< pagebreak >}}
-
-## Analytical procedures
-
-### Source of data
-
-The University of Groningen IADB.nl pharmacy prescription database is a growing database that contains prescription data for 31 years from 1994 till 2024 from approximately 120 community pharmacies and covers an estimated population of 1,120,000 patients.
-Registration in the database is irrespective of health care insurance and age, gender and prescription rates among the database population have been found to be representative of the Netherlands as a whole, and the database has been widely used for research.
-Each person is individually tracked throughout the database period and prescription records contain information on the date of dispensing, the quantity dispensed, the dose regimen, the number of days the prescription is valid, the prescribing physician and the Anatomical Therapeutic Chemical code (ATC code).
-Each patient has a unique anonymous identifier; date of birth and gender are known.
-Due to the high patient-pharmacy commitment in the Netherlands, the medication records for each patient are virtually complete, except for over the counter (OTC) drugs and medication dispensed during hospitalization.
-This analysis include daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.
-
-### Data pre-processing
-
-Daily medication claims is a tabular data containing values from single medication entity for each patients in the cohort.
-Data transformation was performed to construct a square matrix of aggregate medication claim per day, with rows and columns representing groups of medication.
-Each element in the upper and lower triangle represents co-prescriptions, while the diagonal of the matrix represents single prescriptions.
-All elements in the matrix is a tally of drug combination/single prescription in a population level claimed on a daily basis.
-The matrix follows a knowledge graph construct with a subject-predicate-object (s, p, o) triples, i.e.
-`Medication1-PrescribedAlongside-Medication2`.
-The knowledge graph is a representation of medication-claim network, where the edge (predicate) is the number of concurrency.
-Weight was applied on the edges by dividing it by the defined daily dose (DDD).
-Weighting is necessary to regularize the matrix into a unit-free scale, which allow a direct comparison of one drug to another.
-
-$$
-\stackrel{\textrm{Unregularized}}{
-  \begin{bmatrix}
-  n_{1, 1} & \dots & n_{1, N} \\
-  \vdots & \ddots & \vdots \\
-  n_{N, 1} & \dots & n_{N, N} \\
-  \end{bmatrix}
-}
-\to
-\stackrel{\textrm{Regularized by } DDD}{
-  \begin{bmatrix}
-  \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_N}{DDD_N} \right) \\
-  \vdots & \ddots & \vdots \\
-  \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_N}{DDD_N} \right) \\
-  \end{bmatrix}
-}
-$$ {#eq-regularize-mtx}
-
-### Measuring relative importance
-
-As all medications are nodes in a claim network, we can measure the property of each medication using graph theory.
-One way to represent node property is by calculating node centrality, which can be measured as a number of incoming/outgoing edges (degree) or its connectedness to other nodes (importance).
-We measured importance using eigenvector centrality, which reflects medication co-occurrence with other important medications.
-Eigenvector centrality is a recursive measures of how well connected a certain node is to other nodes that is also well connected in the network [@Golbeck2013].
-@eq-eigen-centrality outlines the calculation of eigenvector centrality; $\c_i$ and $\c_j$ are the centralities of node $i$ and $j$, respectively; $\lambda$ is the eigenvalue; $a_{j, i}$ is an element on row $j$ and column $i$ from an adjacency matrix $A$, representing the connection between node $a_i$ and $a_j$.
-
-$$
-\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} a_{j, i} \cdot c_j
-$$ {#eq-eigen-centrality}
-
-{{< include exec-summary/descriptive.qmd >}}
-
-{{< include exec-summary/seasonality.qmd >}}
-
-{{< include exec-summary/arima.qmd >}}
-
-{{< include exec-summary/spectral.qmd >}}
-
-## Highlighted findings
-
-- @tbl-mean-diff describes difference in several measures before and during the COVID-19 pandemic
-  - Further analysis is necessary and will be planned for later investigation
-  - Interrupted time-series analysis should be conducted by considering:
-    1. Counterfactual data using trend before COVID-19
-    1. Counterfactual data using trend during COVID-19 given policy changes
-    1. Calculate the mean percentage changes between counterfactual and actual data
-- @sec-decom-classic-stl displays the data after classical and STL seasonal decomposition
-  - The data still presents with other patterns, implying that seasonality does not completely explains the variance
-  - Eigenvector centrality on daily, weekly, and monthly series suggests high importance of several psychopharmaca, including:
-    1. Antidepressants
-    1. Antipsychotics
-    1. Anxiolytics
-    1. Hypnotic and sedatives
-  - Other medications considered important by eigenvector centrality:
-    1. Alimentary and metabolism
-    1. Cardiovascular
-    1. Analgesics
-    1. Respiratory
-  - High eigenvector centrality implies that these eight medications are often co-prescribed
-- @sec-seasonality demonstrates two repeating patterns in medication claims:
-  - Increasing claims on Monday and decreasing claims on Saturday in the daily data, implying day-to-day differences
-  - Increasing claims in March and December in the monthly data, this pattern is persistent for weekly data as well
-  - Weekly data better captures repeating patterns and should be use for further analysis
-- Model evaluation tables in @sec-arima consistently show high value of intercept
-  - All models for medication claims have a relatively low effect size for AR, MA, or drift term
-  - No model has fitted with a (P, D, Q) term, implying no detected seasonality for models maximizing AICc
-  - Seasonality might be undetected due to the presence of noise and other underlying periodicity
-- @tbl-trend shows differences between the actual and decomposed data
-  - Trend is more visible in the decomposed data due to being free from noises and periodicity
-  - The magnitude of detected trend is naturally larger, and still implies the same monotonicity with the original data
-  - The number of claims in 11 medication classes are declining overtime
-  - The relative importance in 14 medication classes are declining overtime
-  - Changes in claim represents the actual change of the expected number of medication claim in the population.
-Changes in importance represents changes of how likely a medication being prescribed together.
-Differences between relative importance and number of medication claims are observed in:
-    1. Genitourinary: decreasing claim, increasing importance
-    1. Systemic hormonal: increasing claim, decreasing importance
-    1. Antiparkinson: increasing claim, decreasing importance
-    1. Antipsychotics: increasing claim, decreasing importance
-    1. Antidementia: increasing claim, decreasing importance
-    1. Other nervous system drugs: decreasing claim, increasing importance
-    1. Antiparasitics: increasing claim, decreasing importance
-- @tbl-resid-n-claim and @tbl-resid-eigen shows the residuals analysis of the decomposition model using singular spectrum analysis
-  - All residuals are stationary, i.e. having a constant mean and variance
-  - All residuals follow the normal distribution (see especially Shapiro-Wilk statistics, mean, and standard deviation)
-  - These findings imply that the residuals of decomposition models are likely to be evenly and randomly distributed
-- @sec-recon depicts complex periodicity within each time series
-  - These go in line with findings from @sec-seasonality
-  - Despite visible patterns of weekly and yearly seasonality, these patterns are obscured with other oscillating functions
-  - The oscillating functions were ordered based on their contribution in explaining the variance in the data, e.g. `F1` has a higher contribution than `F2`, and so on
-
-::: {.content-visible when-profile="summary"}
-
-\uselandscape
-
 ```{r}
@@
 ```
+
+## Abstract
+
+{{< include abstract/_abstract.qmd >}}
+
+:::: {.content-visible when-meta="in.report"}
+
+{{< pagebreak >}}
+
+## Analytical procedures
+
+{{< include exec-summary/_source-data.qmd >}}
+
+{{< include exec-summary/_preprocessing.qmd >}}
+
+{{< include exec-summary/_measure-eigen.qmd >}}
+
+{{< include exec-summary/_descriptive.qmd >}}
+
+{{< include exec-summary/_seasonality.qmd >}}
+
+{{< include exec-summary/_arima.qmd >}}
+
+{{< include exec-summary/_spectral.qmd >}}
+
+## Highlighted findings
+
+{{< include exec-summary/_result-highlights.qmd >}}
+
+::: {.content-visible when-profile="summary"}
+
+\uselandscape
 
@@
 :::
+
+::::

### 2024-02-14 docs/exec-summary/_result-highlights.qmd
Separate abstract in a different file, improve naming consistency for included files

--- 2024-02-12 docs/exec-summary/report.qmd
@@
-## Abstract
-
-**Objectives:**
-Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide.
-People with chronic diseases are at a higher risk of having mental health issues, which in turn potentially worsen their overall well-being.
-This investigation highlights the interrelatedness of mental health problems with other diagnoses, reflected as a relative importance score of psychopharmaca in a medication claim registry.
-
-**Methods:**
-Exploratory time-series analysis was performed using University of Groningen prescription database, IADB.nl.
-Data of patients with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
-Prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca is evaluated at ATC level 3, drugs for nervous system at ATC level 2, and other medications at ATC level 1, totalled to 24 classes of medication.
-A medication-claim network was constructed as an undirected graph to capture dose-adjusted co-prescription.
-Eigenvector centrality was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
-The number of medication claims, number of patients, claim-to-patient ratio, and eigenvector centrality were then extracted as a weekly-aggregated time-series data.
-Singular spectrum analysis was performed to decompose the data into its constituting trend, periodicity, and white noises.
-
-**Results:**
-Antidepressants (ATC `N06A`), antipsychotics (`N05A`), anxiolytics (`N05B`), and hypnotics (`N05C`) are psychopharmaca with high eigenvector centrality.
-These classes of medication are likely to be co-prescribed alongside other medications, including medications for alimentary and metabolism (`A01-A16`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory (`R01-R07`).
-Only antidepressants and hypnotics have a positive time trend for both eigenvector centrality and actual number of claims.
-
-**Discussion:**
-Eight medications, four of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level.
-Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants and hypnotics are related to co-prescription with other medication classes.
-Constructing a medication claim network enriches the exploratory analysis procedure on the population level.
-
-{{< pagebreak >}}
-
-## Analytical procedures
-
-### Source of data
-
-The University of Groningen IADB.nl pharmacy prescription database is a growing database that contains prescription data for 31 years from 1994 till 2024 from approximately 120 community pharmacies and covers an estimated population of 1,120,000 patients.
-Registration in the database is irrespective of health care insurance and age, gender and prescription rates among the database population have been found to be representative of the Netherlands as a whole, and the database has been widely used for research.
-Each person is individually tracked throughout the database period and prescription records contain information on the date of dispensing, the quantity dispensed, the dose regimen, the number of days the prescription is valid, the prescribing physician and the Anatomical Therapeutic Chemical code (ATC code).
-Each patient has a unique anonymous identifier; date of birth and gender are known.
-Due to the high patient-pharmacy commitment in the Netherlands, the medication records for each patient are virtually complete, except for over the counter (OTC) drugs and medication dispensed during hospitalization.
-This analysis include daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.
-
-### Data pre-processing
-
-Daily medication claims is a tabular data containing values from single medication entity for each patients in the cohort.
-Data transformation was performed to construct a square matrix of aggregate medication claim per day, with rows and columns representing groups of medication.
-Each element in the upper and lower triangle represents co-prescriptions, while the diagonal of the matrix represents single prescriptions.
-All elements in the matrix is a tally of drug combination/single prescription in a population level claimed on a daily basis.
-The matrix follows a knowledge graph construct with a subject-predicate-object (s, p, o) triples, i.e.
-`Medication1-PrescribedAlongside-Medication2`.
-The knowledge graph is a representation of medication-claim network, where the edge (predicate) is the number of concurrency.
-Weight was applied on the edges by dividing it by the defined daily dose (DDD).
-Weighting is necessary to regularize the matrix into a unit-free scale, which allow a direct comparison of one drug to another.
-
-$$
-\stackrel{\textrm{Unregularized}}{
-  \begin{bmatrix}
-  n_{1, 1} & \dots & n_{1, N} \\
-  \vdots & \ddots & \vdots \\
-  n_{N, 1} & \dots & n_{N, N} \\
-  \end{bmatrix}
-}
-\to
-\stackrel{\textrm{Regularized by } DDD}{
-  \begin{bmatrix}
-  \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_N}{DDD_N} \right) \\
-  \vdots & \ddots & \vdots \\
-  \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_N}{DDD_N} \right) \\
-  \end{bmatrix}
-}
-$$ {#eq-regularize-mtx}
-
-### Measuring relative importance
-
-As all medications are nodes in a claim network, we can measure the property of each medication using graph theory.
-One way to represent node property is by calculating node centrality, which can be measured as a number of incoming/outgoing edges (degree) or its connectedness to other nodes (importance).
-We measured importance using eigenvector centrality, which reflects medication co-occurrence with other important medications.
-Eigenvector centrality is a recursive measures of how well connected a certain node is to other nodes that is also well connected in the network [@Golbeck2013].
-@eq-eigen-centrality outlines the calculation of eigenvector centrality; $\c_i$ and $\c_j$ are the centralities of node $i$ and $j$, respectively; $\lambda$ is the eigenvalue; $a_{j, i}$ is an element on row $j$ and column $i$ from an adjacency matrix $A$, representing the connection between node $a_i$ and $a_j$.
-
-$$
-\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} a_{j, i} \cdot c_j
-$$ {#eq-eigen-centrality}
-
-{{< include exec-summary/descriptive.qmd >}}
-
-{{< include exec-summary/seasonality.qmd >}}
-
-{{< include exec-summary/arima.qmd >}}
-
-{{< include exec-summary/spectral.qmd >}}
-
-## Highlighted findings
-
 - @tbl-mean-diff describes difference in several measures before and during the COVID-19 pandemic
@@
   - The oscillating functions were ordered based on their contribution in explaining the variance in the data, e.g. `F1` has a higher contribution than `F2`, and so on
-
-::: {.content-visible when-profile="summary"}
-
-\uselandscape
-
-```{r}
-
-pkgs <- c("targets", "magrittr")
-pkgs_load <- sapply(pkgs, library, character.only = TRUE)
-options(digits = 2, scipen = 999)
-
-```
-
-## Excerpt on findings
-
-### Pair plot
-
-```{r}
-
-tar_read(plt_pair)[[17]]
-
-```
-
-### Dot plots on weekly time-series
-
-```{r}
-
-tar_read(plt_dot_week)[[1]]
-
-```
-
-### Differenced time-series on a weekly interval
-
-```{r}
-
-tar_read(plt_dot_diff_week)[[1]]
-
-```
-
-### Exploring seasonality within the number of medication claims
-
-```{r}
-
-tar_read(plt_period_month)[[1]]
-tar_read(plt_acf_diff_month)[[1]]
-tar_read(plt_pacf_diff_month)[[1]]
-
-```
-
-### Exploring ARIMA model
-
-```{r}
-
-tar_read(plt_arima_forecast_n_claim)[[17]]
-
-```
-
-### Decomposed time-series with SSA
-
-```{r}
-
-tar_read(plt_ssa_recon_n_claim)[[17]]
-
-```
-
-\normalpapersize
-
-:::

### 2024-02-14 docs/exec-summary/_source-data.qmd
Separate abstract in a different file, improve naming consistency for included files

--- 2024-02-12 docs/exec-summary/report.qmd
@@
-## Abstract
-
-**Objectives:**
-Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide.
-People with chronic diseases are at a higher risk of having mental health issues, which in turn potentially worsen their overall well-being.
-This investigation highlights the interrelatedness of mental health problems with other diagnoses, reflected as a relative importance score of psychopharmaca in a medication claim registry.
-
-**Methods:**
-Exploratory time-series analysis was performed using University of Groningen prescription database, IADB.nl.
-Data of patients with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
-Prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca is evaluated at ATC level 3, drugs for nervous system at ATC level 2, and other medications at ATC level 1, totalled to 24 classes of medication.
-A medication-claim network was constructed as an undirected graph to capture dose-adjusted co-prescription.
-Eigenvector centrality was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
-The number of medication claims, number of patients, claim-to-patient ratio, and eigenvector centrality were then extracted as a weekly-aggregated time-series data.
-Singular spectrum analysis was performed to decompose the data into its constituting trend, periodicity, and white noises.
-
-**Results:**
-Antidepressants (ATC `N06A`), antipsychotics (`N05A`), anxiolytics (`N05B`), and hypnotics (`N05C`) are psychopharmaca with high eigenvector centrality.
-These classes of medication are likely to be co-prescribed alongside other medications, including medications for alimentary and metabolism (`A01-A16`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory (`R01-R07`).
-Only antidepressants and hypnotics have a positive time trend for both eigenvector centrality and actual number of claims.
-
-**Discussion:**
-Eight medications, four of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level.
-Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants and hypnotics are related to co-prescription with other medication classes.
-Constructing a medication claim network enriches the exploratory analysis procedure on the population level.
-
-{{< pagebreak >}}
-
-## Analytical procedures
-
 ### Source of data
@@
 This analysis include daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.
-
-### Data pre-processing
-
-Daily medication claims is a tabular data containing values from single medication entity for each patients in the cohort.
-Data transformation was performed to construct a square matrix of aggregate medication claim per day, with rows and columns representing groups of medication.
-Each element in the upper and lower triangle represents co-prescriptions, while the diagonal of the matrix represents single prescriptions.
-All elements in the matrix is a tally of drug combination/single prescription in a population level claimed on a daily basis.
-The matrix follows a knowledge graph construct with a subject-predicate-object (s, p, o) triples, i.e.
-`Medication1-PrescribedAlongside-Medication2`.
-The knowledge graph is a representation of medication-claim network, where the edge (predicate) is the number of concurrency.
-Weight was applied on the edges by dividing it by the defined daily dose (DDD).
-Weighting is necessary to regularize the matrix into a unit-free scale, which allow a direct comparison of one drug to another.
-
-$$
-\stackrel{\textrm{Unregularized}}{
-  \begin{bmatrix}
-  n_{1, 1} & \dots & n_{1, N} \\
-  \vdots & \ddots & \vdots \\
-  n_{N, 1} & \dots & n_{N, N} \\
-  \end{bmatrix}
-}
-\to
-\stackrel{\textrm{Regularized by } DDD}{
-  \begin{bmatrix}
-  \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_N}{DDD_N} \right) \\
-  \vdots & \ddots & \vdots \\
-  \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_N}{DDD_N} \right) \\
-  \end{bmatrix}
-}
-$$ {#eq-regularize-mtx}
-
-### Measuring relative importance
-
-As all medications are nodes in a claim network, we can measure the property of each medication using graph theory.
-One way to represent node property is by calculating node centrality, which can be measured as a number of incoming/outgoing edges (degree) or its connectedness to other nodes (importance).
-We measured importance using eigenvector centrality, which reflects medication co-occurrence with other important medications.
-Eigenvector centrality is a recursive measures of how well connected a certain node is to other nodes that is also well connected in the network [@Golbeck2013].
-@eq-eigen-centrality outlines the calculation of eigenvector centrality; $\c_i$ and $\c_j$ are the centralities of node $i$ and $j$, respectively; $\lambda$ is the eigenvalue; $a_{j, i}$ is an element on row $j$ and column $i$ from an adjacency matrix $A$, representing the connection between node $a_i$ and $a_j$.
-
-$$
-\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} a_{j, i} \cdot c_j
-$$ {#eq-eigen-centrality}
-
-{{< include exec-summary/descriptive.qmd >}}
-
-{{< include exec-summary/seasonality.qmd >}}
-
-{{< include exec-summary/arima.qmd >}}
-
-{{< include exec-summary/spectral.qmd >}}
-
-## Highlighted findings
-
-- @tbl-mean-diff describes difference in several measures before and during the COVID-19 pandemic
-  - Further analysis is necessary and will be planned for later investigation
-  - Interrupted time-series analysis should be conducted by considering:
-    1. Counterfactual data using trend before COVID-19
-    1. Counterfactual data using trend during COVID-19 given policy changes
-    1. Calculate the mean percentage changes between counterfactual and actual data
-- @sec-decom-classic-stl displays the data after classical and STL seasonal decomposition
-  - The data still presents with other patterns, implying that seasonality does not completely explains the variance
-  - Eigenvector centrality on daily, weekly, and monthly series suggests high importance of several psychopharmaca, including:
-    1. Antidepressants
-    1. Antipsychotics
-    1. Anxiolytics
-    1. Hypnotic and sedatives
-  - Other medications considered important by eigenvector centrality:
-    1. Alimentary and metabolism
-    1. Cardiovascular
-    1. Analgesics
-    1. Respiratory
-  - High eigenvector centrality implies that these eight medications are often co-prescribed
-- @sec-seasonality demonstrates two repeating patterns in medication claims:
-  - Increasing claims on Monday and decreasing claims on Saturday in the daily data, implying day-to-day differences
-  - Increasing claims in March and December in the monthly data, this pattern is persistent for weekly data as well
-  - Weekly data better captures repeating patterns and should be use for further analysis
-- Model evaluation tables in @sec-arima consistently show high value of intercept
-  - All models for medication claims have a relatively low effect size for AR, MA, or drift term
-  - No model has fitted with a (P, D, Q) term, implying no detected seasonality for models maximizing AICc
-  - Seasonality might be undetected due to the presence of noise and other underlying periodicity
-- @tbl-trend shows differences between the actual and decomposed data
-  - Trend is more visible in the decomposed data due to being free from noises and periodicity
-  - The magnitude of detected trend is naturally larger, and still implies the same monotonicity with the original data
-  - The number of claims in 11 medication classes are declining overtime
-  - The relative importance in 14 medication classes are declining overtime
-  - Changes in claim represents the actual change of the expected number of medication claim in the population.
-Changes in importance represents changes of how likely a medication being prescribed together.
-Differences between relative importance and number of medication claims are observed in:
-    1. Genitourinary: decreasing claim, increasing importance
-    1. Systemic hormonal: increasing claim, decreasing importance
-    1. Antiparkinson: increasing claim, decreasing importance
-    1. Antipsychotics: increasing claim, decreasing importance
-    1. Antidementia: increasing claim, decreasing importance
-    1. Other nervous system drugs: decreasing claim, increasing importance
-    1. Antiparasitics: increasing claim, decreasing importance
-- @tbl-resid-n-claim and @tbl-resid-eigen shows the residuals analysis of the decomposition model using singular spectrum analysis
-  - All residuals are stationary, i.e. having a constant mean and variance
-  - All residuals follow the normal distribution (see especially Shapiro-Wilk statistics, mean, and standard deviation)
-  - These findings imply that the residuals of decomposition models are likely to be evenly and randomly distributed
-- @sec-recon depicts complex periodicity within each time series
-  - These go in line with findings from @sec-seasonality
-  - Despite visible patterns of weekly and yearly seasonality, these patterns are obscured with other oscillating functions
-  - The oscillating functions were ordered based on their contribution in explaining the variance in the data, e.g. `F1` has a higher contribution than `F2`, and so on
-
-::: {.content-visible when-profile="summary"}
-
-\uselandscape
-
-```{r}
-
-pkgs <- c("targets", "magrittr")
-pkgs_load <- sapply(pkgs, library, character.only = TRUE)
-options(digits = 2, scipen = 999)
-
-```
-
-## Excerpt on findings
-
-### Pair plot
-
-```{r}
-
-tar_read(plt_pair)[[17]]
-
-```
-
-### Dot plots on weekly time-series
-
-```{r}
-
-tar_read(plt_dot_week)[[1]]
-
-```
-
-### Differenced time-series on a weekly interval
-
-```{r}
-
-tar_read(plt_dot_diff_week)[[1]]
-
-```
-
-### Exploring seasonality within the number of medication claims
-
-```{r}
-
-tar_read(plt_period_month)[[1]]
-tar_read(plt_acf_diff_month)[[1]]
-tar_read(plt_pacf_diff_month)[[1]]
-
-```
-
-### Exploring ARIMA model
-
-```{r}
-
-tar_read(plt_arima_forecast_n_claim)[[17]]
-
-```
-
-### Decomposed time-series with SSA
-
-```{r}
-
-tar_read(plt_ssa_recon_n_claim)[[17]]
-
-```
-
-\normalpapersize
-
-:::

### 2024-02-14 docs/index.qmd
Elaborate the methods, close #11, CU-86cujznkf[closed]
Separate abstract in a different file, improve naming consistency for included files

--- 2024-01-26 docs/index.qmd
@@
+---
+knitr:
+  opts_chunk:
+    fig.width: 18
+    fig.height: 12
+---
+
+```{r}
+
+pkgs <- c("targets", "magrittr")
+pkgs_load <- sapply(pkgs, library, character.only = TRUE)
+options(digits = 2, scipen = 999)
+
+```
+
 # Executive Summary {-}
 
+::: {.content-visible when-meta="in.report"}
+{{< include exec-summary/_report.qmd >}}
+:::
+
+::: {.content-visible when-profile="descriptive"}
+{{< include exec-summary/_descriptive.qmd >}}
+:::
+
+::: {.content-visible when-profile="arima"}
+{{< include exec-summary/_arima.qmd >}}
+:::
+
 ::: {.content-visible when-profile="seasonality"}
+{{< include exec-summary/_seasonality.qmd >}}
+:::
 
-Exploration on seasonality is done on monthly data with a first-order difference
+::: {.content-visible when-profile="spectral"}
+{{< include exec-summary/_spectral.qmd >}}
+:::
 
+:::: {.content-visible when-meta="in.report"}
+
+## Contents
+
+- @sec-descriptive contains a descriptive explanation of the dataset
+- @sec-seasonality reports exploration of seasonality on detrended data
+- @sec-arima showcases results obtained from ARIMA models
+- @sec-spectral outlines the decomposed time series using singular-spectrum analysis
+
+## References
+
+::: {#refs}
 :::
+
+::::

### 2024-02-14 _targets.R

@@ -291,6 +291,7 @@ list(
   tar_target(ts_clust, setCluster(ts_recon, nclusts = 2:10)),
 
   # Generate documentation
+  tar_quarto(abstract, "docs/abstract/abstract.qmd"),
   tar_quarto(report, "docs", profile = "report", extra_files = "docs/exec-summary", priority = 0),
   tar_quarto(summary, "docs", profile = "summary", priority = 0),
   tar_quarto(report_descriptive, "docs", profile = "descriptive", priority = 0),

### 2024-03-07 docs/abstract/_abstract.qmd
Plan the modelling procedures

@@
 These classes of medication are likely to be co-prescribed alongside other medications.
-Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$: `r A0x$ce`, $n_c$: `r A0x$nc`), blood (`B01-B06`, $c_e$: `r B0x$ce`, $n_c$: `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$: `r C0x$ce`, $n_c$: `r C0x$ne`), analgesics (`N02`, $c_e$: `r N02$ce`, $n_c$ `r N02$nc`), and respiratory (`R01-R07`, $c_e$: `r R0x$ce`, $n_c$: `r R0x$nc`).
+Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$: `r A0x$ce`, $n_c$: `r A0x$nc`), blood (`B01-B06`, $c_e$: `r B0x$ce`, $n_c$: `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$: `r C0x$ce`, $n_c$: `r C0x$nc`), analgesics (`N02`, $c_e$: `r N02$ce`, $n_c$: `r N02$nc`), and respiratory (`R01-R07`, $c_e$: `r R0x$ce`, $n_c$: `r R0x$nc`).
 Among eight medications with high eigenvector centrality, only antidepressants had a positive time trend for both eigenvector centrality and actual number of claims.

### 2024-03-07 docs/exec-summary/_models.qmd
Plan the modelling procedures

### Exploratory Model Comparison

#### Baseline models

Simple methods are useful as a benchmark when evaluating and comparing multiple models. In a data with simple pattern and seasonality, baseline models are sufficiently effective in projecting forecasts. Methods incorporated in the baseline models are mean, naive, seasonal naive, and drift method. Mean method simply takes the mean value of all preceding time points to forecast the future, which may fit rather well in time-series data without a trend. Naive method takes the most recent value as a projection of the forecast, which could be reasonable in a series following a random-walk. Seasonal naive method is similar to the naive methods while taking into account the presence of seasonality, *viz.* by taking the most recent value in the last occurring season. Drift method is equivalent with the naive method while allowing the projection to drift in a positive or negative trend. In a way, drift method is akin to drawing a line between the first-point and the last-point of observation. While useful, these four methods are highly constrained by the data. The presence of complex periodic patterns or alternating trend may result in low accuracy.

#### Time-series linear model

#### Holt's exponential smoothing

#### Automatic (S)ARIMA

### 2024-03-07 docs/results/descriptive.qmd
Plan the modelling procedures

@@
 
-tar_read(plt_decom_ts_day_1.week_classic_n_claim)
-tar_read(plt_decom_ts_day_1.week_classic_eigen)
+tar_read(plt_dot_decom_ts_day_1.week_classic_n_claim)
+tar_read(plt_dot_decom_ts_day_1.week_classic_eigen)
 
@@
 
-tar_read(plt_decom_ts_week_1.month_classic_n_claim)
-tar_read(plt_decom_ts_week_1.month_classic_eigen)
+tar_read(plt_dot_decom_ts_week_1.month_classic_n_claim)
+tar_read(plt_dot_decom_ts_week_1.month_classic_eigen)
 
@@
 
-tar_read(plt_decom_ts_month_1.year_classic_n_claim)
-tar_read(plt_decom_ts_month_1.year_classic_eigen)
+tar_read(plt_dot_decom_ts_month_1.year_classic_n_claim)
+tar_read(plt_dot_decom_ts_month_1.year_classic_eigen)
 

### 2024-03-07 docs/results/spectral.qmd
Plan the modelling procedures

@@
   tidyr::pivot_wider(names_from = component, values_from = eigen:n_claim) %>%
-  set_colnames(c("ATCC Group", rep(c("Original", "Trend"), 2))) %>%
+  set_colnames(c("ATC Group", rep(c("Original", "Trend"), 2))) %>%
   knitr::kable(longtable = TRUE, booktabs = TRUE) %>%
@@
 \uselandscape
+
+```{r}
+
+tar_read(plt_dot_recon_n_claim)
+tar_read(plt_dot_recon_eigen)
+
+```
+
+\useportrait
 
@@
 
-{{< pagebreak >}}
+\uselandscape
 

### 2024-03-07 _targets.R

@@ -62,7 +62,7 @@ list(
   ),
 
   # Set iteration parameters of metrics and scales for visualization
-  tar_target(vizDotParams, data.frame(
+  tar_target(vizdot_params, data.frame(
     "metrics" = c("n_claim", "n_patient", "claim2patient", "eigen", "strength"),
     "scales"  = c("free_y", "free_y", "fixed", "fixed", "fixed")
   )),
@@ -78,59 +78,59 @@ list(
     tar_target(ts_diff2, timeDiff(ts, n = 2)),
 
     # Assess stationarity using the Augmented Dickey-Fuller test
-    tar_target(ts_uroot, evalUnitRoot(ts, y = vizDotParams$metrics), pattern = map(vizDotParams)),
-    tar_target(ts_diff_uroot, evalUnitRoot(ts_diff, y = vizDotParams$metrics), pattern = map(vizDotParams)),
-    tar_target(ts_diff2_uroot, evalUnitRoot(ts_diff2, y = vizDotParams$metrics), pattern = map(vizDotParams)),
+    tar_target(ts_uroot, evalUnitRoot(ts, y = vizdot_params$metrics), pattern = map(vizdot_params)),
+    tar_target(ts_diff_uroot, evalUnitRoot(ts_diff, y = vizdot_params$metrics), pattern = map(vizdot_params)),
+    tar_target(ts_diff2_uroot, evalUnitRoot(ts_diff2, y = vizdot_params$metrics), pattern = map(vizdot_params)),
 
     # Visualize the dot plot
     tar_target(
       plt_dot,
-      vizDot(ts, y = vizDotParams$metrics, scales = vizDotParams$scales, nrow = 4),
-      pattern = map(vizDotParams),
+      vizDot(ts, y = vizdot_params$metrics, scales = vizdot_params$scales, nrow = 4),
+      pattern = map(vizdot_params),
       iteration = "list"
     ),
 
     tar_target(
       plt_dot_diff,
-      vizDot(ts_diff, y = vizDotParams$metrics, scales = vizDotParams$scales, nrow = 4),
-      pattern = map(vizDotParams),
+      vizDot(ts_diff, y = vizdot_params$metrics, scales = vizdot_params$scales, nrow = 4),
+      pattern = map(vizdot_params),
       iteration = "list"
     ),
 
     # Visualize the pair plot, ACF, and PACF
     tar_target(
       plt_acf,
[…]

### 2024-03-11 src/R/model.R
Fit multiple models as a mable #2 CU-86cuh2vn3

@@ -81,3 +81,40 @@ fitSsa <- function(ts, method = NULL, ...) {
   return(mod)
 
 }
+
+compareModel <- function(ts, y) {
+  #' Compare Models
+  #'
+  #' Fit Multiple Models for Comparison
+  #'
+  #' @param ts A time series data frame, will accept a `tsibble` object
+  #' @param y The variable to fit
+  #' @return A mable object (model table)
+  require("tsibble")
+
+  # Get variable name with englue
+  varname <- rlang::englue("{{ y }}")
+
+  # Generate formulas for specific models
+  forms <- list(
+    "snaive" = "%s ~ lag(52)",
+    "drift"  = "%s ~ drift()",
+    "tslm"   = "%s ~ trend()",
+    "ets"    = "%s ~ error('A') + trend('N') + season('N')"
+  ) %>%
+    lapply(\(form) sprintf(form, varname) %>% formula())
+
+  # Fit multiple models as a mable
+  model <- ts %>%
+    fabletools::model(
+      "mean"   = fable::MEAN({{ y }}),
+      "naive"  = fable::NAIVE({{ y }}),
+      "snaive" = fable::SNAIVE(forms$snaive),
+      "drift"  = fable::RW(forms$drift),
+      "tslm"   = fable::TSLM(forms$tslm),
+      "ets"    = fable::ETS(forms$ets),
+      "arima"  = fable::ARIMA({{ y }})
+    )
+
+  return(model)
+}

### 2024-03-11 src/R/model.R
Implement training-testing data set splitting, close #3, CU-86cuh2y3f[closed]

@@ -82,6 +82,30 @@ fitSsa <- function(ts, method = NULL, ...) {
 
 }
 
+splitTs <- function(ts, ratio = 0.2) {
+  #' Split Time-Series
+  #'
+  #' Split the time-series into training and testing dataset based on the ratio
+  #'
+  #' @param ts A time series dta frame, will accept a `tsibble` object
+  #' @param ratio The testing:training ratio, set to 0.2 by default
+  #' @return A list containing training and testing dataset
+
+  # Date of the most recent dataset
+  dates  <- ts$date %>% unique()
+  id     <- floor(ratio * length(dates))
+  recent <- dates %>% extract2(length(.) - id)
+
+  # Subset the dataset
+  sub_ts <- list(
+    "train" = ts %>% subset(.$date <= recent),
+    "test"  = ts %>% subset(.$date >  recent)
+  )
+
+  return(sub_ts)
+
+}
+
 compareModel <- function(ts, y) {
   #' Compare Models
   #'

### 2024-03-21 docs/abstract/_abstract-eupha.qmd
Add abstract for EUPHA

---
title: Eigenvector centrality signifies antidepressants as a central hub of the co-medication network
---

Background: Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide. People with chronic diseases are at a higher risk of having mental health issues. We evaluate the interrelatedness of mental health problems with other diagnoses, reflected as a relative importance score of psychopharmaca in a medication claim registry.

Methods: Exploratory time-series analysis was performed in a static cohort from IADB.nl with at least one prescription of psychopharmaca from 2018 to 2022. The prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification. A medication-claim network was constructed to capture dose-adjusted co-prescription. Eigenvector centrality (ce) was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network. The number of medication claims (nc) and eigenvector centrality were extracted as weekly-aggregated time-series data.

Results: Antidepressants (ce: 0.11, nc: 28,993), antipsychotics (ce: 0.07, nc: 14,027), and anxiolytics (ce: 0.08, nc: 14,061) are psychopharmaca with high eigenvector centrality. These classes of medication are likely to be co-prescribed alongside other medications. Other groups with high eigenvector centrality were medications for alimentary and metabolism (ce: 0.15, nc: 53,602), blood (ce: 0.06, nc: 13,310), cardiovascular (ce: 0.14, nc: 44,802), analgesics (ce: 0.09, nc: 13,847), and respiratory (ce: 0.09, nc: 25,034). Only antidepressants had a positive time trend for both eigenvector centrality and the number of claims.

Conclusion: Eight medications have a high concurrence on a population level. Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants are related to co-prescription with other medication classes. We recommend constructing a medication claim network to evaluate periodic co-prescription as a public health monitoring procedure.

### 2024-03-25 docs/article.qmd
Draft an initial report using Elsevier template

---
title: >
  Eigenvector centrality as a metric of polypharmacy signifies antidepressants
  as a central hub of the psychopharmaca co-prescription network

format:
  elsevier-pdf:
    latex-output-dir: _render
    include-in-header:
      file: _header.tex
    journal:
      formatting: review

funding: "The author(s) received no specific funding for this work."
keywords:
  - Graph Theory
  - Prescription Registry
  - Polypharmacy
  - Mental Health   
  - Public Health Monitoring

metadata-files:
  - _author.yml
  - _abstract.yml
  - _knitr-bib.yml

in:
  article: true
---

```{r}

pkgs <- c("targets", "magrittr")
pkgs_load <- sapply(pkgs, library, character.only = TRUE)
options(digits = 2, scipen = 999)

```

# Introduction

- Mental health as a common co-morbidity
- Polypharmacy in mental disorder
- The need of a systematic public health monitoring

# Methods

## Source of data

{{< include exec-summary/_source-data.qmd >}}

## Data pre-processing

{{< include exec-summary/_preprocessing.qmd >}}

## Measuring relative importance

{{< include exec-summary/_measure-eigen.qmd >}}

## Exploratory descriptive analysis

{{< include exec-summary/_descriptive.qmd >}}

## Exploring seasonality in the dataset

{{< include exec-summary/_seasonality.qmd >}}

## Exploratory ARIMA modelling

{{< include exec-summary/_arima.qmd >}}

## Decomposition with singular spectrum analysis

{{< include exec-summary/_spectral.qmd >}}

# Results

# Discussion

# References

### 2024-03-29 docs/article.qmd
Brief an introduction to polypharmacy in general and psychiatry

@@
 
+Mental disorders are a common comorbidity affecting nearly two billion people worldwide which prevalence remains relatively stable overtime [@Kessler2009; @Steel2014; @Richter2019].
+Having a chronic mental disorder is one factor which may lead to polypharmacy, *viz.* the use of multiple medications in treating complex clinical conditions [@Halli2019].
+Polypharmacy is a prominent issue in modern medicine with a prevalence of 37% [@Delara2022], mainly contributed by the presence of multiple long-term comorbidity, i.e.
+multimorbidity, in the population.
+In resolving multimorbidity, the general edict of the evidence-based medicine is to follow an established clinical guideline in treating a particular clinical condition.
+However, these guidelines are tailored for a single disease without considering multimorbidity, resulting in the use of one or more medications per condition, leading to polypharmacy prescribed for one patient with multiple conditions [@Molokhia2017].
+Albeit clinical improvements offered by polypharmacy, risks of drug interaction and adverse effects also become more apparent, engendering a public health issue.
+Hitherto, no indicator of polypharmacy has been universally standardized [@Sirois2016], where the number of prescription is merely relied on as a crude metric [@Molokhia2017; @Delara2022].
+
+In psychiatry, polypharmacy is defined as a patient with at least two concurrent psychiatric medications [@Shrivastava2013].
+With a prevalence between 13-90%, psychiatric polypharmacy manifests in five categories, namely same-class, multi-class, adjunctive, augmentation, and total polypharmacy.
+Same-class polypharmacy is the use of multiple medications from the same class.
+Multi-class polypharmacy is the use of multiple medications from different classes indicated for the same symptom cluster.
+Adjunctive polypharmacy is the use of additional medications to treat side effects due to other medications.
+Augmentation polypharmacy is the use of full-dose and sub-dose medications from a different class for the same symptom cluster.
+Finally, total polypharmacy is the total count of all medications used by a patient, both psychopharmaca and other classes alike.
+
 - Mental health as a common co-morbidity
@@
 - The need of a systematic public health monitoring
+- Although polypharmacy is mostly researched in geriatric patients, younger population are also at risk of inappropriate multiple medication uses [@Menditto2019].
+
+@Sirois2016
+- No agreement on a quantitative indicator of polypharmacy
+- Problem of exposure: Polypharmacy can be defined as cumulative or simultaneous prescriptions
+
+@Delara2022
+- The prevalence of polypharmacy in all medication classes is 37% [95% CI: 31-43%]
+- Difference of prevalence measure is due to different numerical thresholds, study setting, and publication year
+
+@Cavallo2012
+- Create a co-prescription network
+- The weight is the number of time a pair of medications is prescribed together
+- Drugs are classified per ATC code using five different levels
+- The co-prescription network has a scale-free property, suggesting that the probability new links being formed is growing alongside the degree of the target node
+- The scale-free property of the network might be explained by the physician's prescribing habit: The physician tends to prescribe medications with known medications
+
+@Bazzoni2015
+- Drug-prescription network is highly dense and clustered at the global level
+- Drug-prescription network is organized into anatomically homogeneous modules at the local level
 
@@
 
-## Exploratory ARIMA modelling
-
-{{< include exec-summary/_arima.qmd >}}
-
 ## Decomposition with singular spectrum analysis
@@
 
+@Shrivastava2013
+- Among diagnoses, polypharmacy is often found in patients with schizophrenia, schizotypal, and delusional disorder
+- Multi-class polypharmacy is the most common (20.9%), usually the combination of SSRI and benzodiazepine or TCA and benzodiazepine
+- Five factors associated with psychiatric polypharmacy:
+  - Scientific: Emphasis on biogenic amines roles in depression and schizophrenia expanded the early clinical evidence of psychotropic medications
+  - Clinical: Standardization attempt resulted in overlapping diagnoses with limited validity; poly-nosology an polypharmacy go hand-in-hand
+  - Economic: Pharmaceutical company influenced the demand of psychopharmaca uses
+  - Political: US FDA imposes minimal guidelines for drug approval only for specific conditions
+  - Cultural: Large cultural appetite for pharmacological treatments
+
+@Stassen2021
+- Attending psychiatrist is the main determinant of polypharmaca prescription
+- Previous medical history and case severity at baseline only play a minor role in polypharmaca
+- Adverse drug reaction in polypharmaca is 2-3 times higher compared to monotherapy, and not attributed to particular drug or drug combination; it implies that any drug and its combination can virtually trigger the side effect
+- No advantage of polypharmacy over monotherapy, suggesting that polypharmacy regimens are not equally suited for every patient
+
+@Molokhia2017
+- The alternative measure is pre-defined criteria, e.g. BEERS, STOPP, and START
+- Each additional medication contributes to 16% increased risk of errors
+
 # References

### 2024-03-29 docs/article.qmd
Reorganize the introduction structure

--- 2024-03-25 docs/article.qmd
@@
       formatting: review
+      cite-style: authoryear
 
@@
 
-- Mental health as a common co-morbidity
-- Polypharmacy in mental disorder
-- The need of a systematic public health monitoring
+Mental disorders are a common comorbidity affecting nearly two billion people worldwide with a prevalence that remains relatively stable overtime [@Kessler2009; @Steel2014; @Richter2019].
+Having a chronic mental disorder is one factor which may lead to polypharmacy, *viz.* the use of multiple medications in treating complex clinical conditions [@Halli2019].
+Polypharmacy is a prominent issue in modern medicine with a prevalence of 37% [@Delara2022], mainly attributed to the presence of multiple long-term comorbidity, i.e.
+multimorbidity, in the population.
+In resolving multimorbidity, the general edict of the evidence-based medicine is to follow an established clinical guideline to treat a particular clinical condition.
+However, these guidelines are tailored for a single disease without considering multimorbidity, resulting in the use of one or more medications per condition, leading to polypharmacy regimens for one patient with multiple conditions [@Molokhia2017].
+Albeit clinical improvements offered by polypharmacy, risks of drug interaction and adverse effects also become more apparent, engendering a public health issue.
+Hitherto, no indicator of polypharmacy has been universally standardized [@Sirois2016], where the number of prescription is merely relied on as a crude metric [@Molokhia2017; @Delara2022].
+
+In psychiatry, polypharmacy is defined as a patient with at least two concurrent psychiatric medications [@Shrivastava2013].
+With a prevalence between 13-90%, psychiatric polypharmacy manifests in five categories, namely same-class, multi-class, adjunctive, augmentation, and total polypharmacy.
+Same-class polypharmacy is the use of multiple medications from the same class.
+Multi-class polypharmacy is the use of multiple medications from different classes indicated for the same symptom cluster.
+Adjunctive polypharmacy is the use of additional medications to treat side effects due to other medications.
+Augmentation polypharmacy is the use of full-dose and sub-dose medications from a different class for the same symptom cluster.
+Finally, total polypharmacy is the total count of all medications used by a patient, both psychopharmaca and other classes alike.
+
+Paragraph layout:
+
+- Mental disorders as a common co-morbidity contributes to polypharmacy in general
+- Specific types of polypharmacy in mental disorders
+- Problem: The need of a systematic public health monitoring for polypharmacy
+- Definition and purpose of the study:
+  - Proposed solution: Drug prescription network and network analysis to evaluate polypharmacy
+  - Question: How do we implement network analysis approach to quantitatively identify polypharmacy?
+  - Objective: Use graph centrality measure as a quantitative indicator of polypharmacy to enable systematic public health monitoring
+
+@Sirois2016
+
+- No agreement on a quantitative indicator of polypharmacy
+- Problem of exposure: Polypharmacy can be defined as cumulative or simultaneous prescriptions
+
+@Delara2022
+
+- The prevalence of polypharmacy in all medication classes is 37% [95% CI: 31-43%]
+- Difference of prevalence measure is due to different numerical thresholds, study setting, and publication year
+
+@Cavallo2012
+
+- Create a co-prescription network
+- The weight is the number of time a pair of medications is prescribed together
+- Drugs are classified per ATC code using five different levels
+- The co-prescription network has a scale-free property, suggesting that the probability new links being formed is growing alongside the degree of the target node
+- The scale-free property of the network might be explained by the physician's prescribing habit: The physician tends to prescribe medications with known medications
+
+@Bazzoni2015
+
+- Drug-prescription network is highly dense and clustered at the global level
+- Drug-prescription network is organized into anatomically homogeneous modules at the local level
 
@@
 
+@Menditto2019
+
+- Although polypharmacy is mostly researched in geriatric patients, younger population are also at risk of inappropriate multiple medication uses
+
+@Shrivastava2013
+
+- Among diagnoses, polypharmacy is often found in patients with schizophrenia, schizotypal, and delusional disorder
+- Multi-class polypharmacy is the most common (20.9%), usually the combination of SSRI and benzodiazepine or TCA and benzodiazepine
+- Five factors associated with psychiatric polypharmacy:
+  - Scientific: Emphasis on biogenic amines roles in depression and schizophrenia expanded the early clinical evidence of psychotropic medications
+  - Clinical: Standardization attempt resulted in overlapping diagnoses with limited validity; poly-nosology an polypharmacy go hand-in-hand
+  - Economic: Pharmaceutical company influenced the demand of psychopharmaca uses
+  - Political: US FDA imposes minimal guidelines for drug approval only for specific conditions
+  - Cultural: Large cultural appetite for pharmacological treatments
+
+@Stassen2021
+
+- Attending psychiatrist is the main determinant of polypharmaca prescription
+- Previous medical history and case severity at baseline only play a minor role in polypharmaca
+- Adverse drug reaction in polypharmaca is 2-3 times higher compared to monotherapy, and not attributed to particular drug or drug combination; it implies that any drug and its combination can virtually trigger the side effect
+- No advantage of polypharmacy over monotherapy, suggesting that polypharmacy regimens are not equally suited for every patient
+
+@Molokhia2017
+
+- The alternative measure is pre-defined criteria, e.g. BEERS, STOPP, and START
+- Each additional medication contributes to 16% increased risk of errors
+
 # References

### 2024-04-02 docs/article.qmd
Draft initial intro and methods

@@
   Eigenvector centrality as a metric of polypharmacy signifies antidepressants
-  as a central hub of the psychopharmaca co-prescription network
+  as a central hub of the drug prescription network
 
@@
   elsevier-pdf:
-    latex-output-dir: _render
     include-in-header:
@@
   - Mental Health   
-  - Public Health Monitoring
+  - Public Health Surveillance
 
@@
 Augmentation polypharmacy is the use of full-dose and sub-dose medications from a different class for the same symptom cluster.
-Finally, total polypharmacy is the total count of all medications used by a patient, both psychopharmaca and other classes alike.
+Finally, total polypharmacy is the total count of all medications used by a patient, both psychopharmaca and other classes alike [@Shrivastava2013].
+For policymakers, differences in defining polypharmacy pose a challenge to design a surveillance system [@Sirois2016].
 
-Paragraph layout:
+Surveilling polypharmacy regimens requires a holistic approach since drug prescription highly depends on the physician's prescribing habits [@Stassen2021], patient-physician relationship, and pharmaceutical market, which all bear an interplay with the decision-making process [@Cavallo2012].
+A holistic polypharmacy surveillance system needs to describe the importance of polypharmacy by incorporating both qualitative and quantitative measures [@Sirois2016].
+Quantitatively attributing importance to each medication is challenging, accounting for polypharmacy as a complex and interlinked medication uses.
+To reduce the complexity, graph theory offers a complementary approach by analyzing polypharmacy as a drug prescription network (DPN).
+Transforming prescription registry into a DPN has been previously investigated, where DPN-based approach represented the general trend in co-prescription [@Cavallo2012; @Bazzoni2015].
 
-- Mental disorders as a common co-morbidity contributes to polypharmacy in general
-- Specific types of polypharmacy in mental disorders
-- Problem: The need of a systematic public health monitoring for polypharmacy
-- Definition and purpose of the study:
-  - Proposed solution: Drug prescription network and network analysis to evaluate polypharmacy
-  - Question: How do we implement network analysis approach to quantitatively identify polypharmacy?
-  - Objective: Use graph centrality measure as a quantitative indicator of polypharmacy to enable systematic public health monitoring
+A DPN is constructed as a matrix which rows to columns represent pairs of medication being taken by a patient in a day.
+Since there is no limit for the number of rows and columns, a DPN can contain virtually every possible combination of polypharmacy regimens.
+A DPN is generalizable as a population aggregate by coalescing all single-patient DPN through matrix addition [@Cavallo2012].
+Constructing a DPN allows examining co-prescription dynamics in the population as graph measures, which is also attributable to each medication.
+One of such measures is graph centrality, where we calculate scores representing the number of co-medications, number of connecting paths, average distance, and relative importance [@Askar2021].
+The relative importance score is of particular interest to address concerns raised by @Sirois2016 and @Delara2022 regarding standardized quantitative indicator of polypharmacy.
+Relative importance, most commonly measured by eigenvector centrality, represents the connection to vital medications.
+A high eigenvector centrality in a DPN indicates more prescriptions with highly-prescribed medications.
+Following up @Cavallo2012 and @Bazzoni2015, we hypothesize that eigenvector centrality as a measure of relative importance is attributable to indicate polypharmacy.
+Our investigation showcases eigenvector centrality as a quantitative indicator of polypharmacy to promote a systematic public health surveillance system.
 
-@Sirois2016
-
-- No agreement on a quantitative indicator of polypharmacy
-- Problem of exposure: Polypharmacy can be defined as cumulative or simultaneous prescriptions
-
-@Delara2022
-
-- The prevalence of polypharmacy in all medication classes is 37% [95% CI: 31-43%]
-- Difference of prevalence measure is due to different numerical thresholds, study setting, and publication year
-
-@Cavallo2012
-
-- Create a co-prescription network
-- The weight is the number of time a pair of medications is prescribed together
-- Drugs are classified per ATC code using five different levels
-- The co-prescription network has a scale-free property, suggesting that the probability new links being formed is growing alongside the degree of the target node
-- The scale-free property of the network might be explained by the physician's prescribing habit: The physician tends to prescribe medications with known medications
-
-@Bazzoni2015
-
-- Drug-prescription network is highly dense and clustered at the global level
-- Drug-prescription network is organized into anatomically homogeneous modules at the local level
+::: {.content-hidden}
+> **"How do we implement a network analysis approach to quantitatively attribute polypharmacy?"**
+:::
 
@@
 
-## Exploratory descriptive analysis
+## Data analysis
+
+### Exploratory descriptive analysis
 
@@
 
-## Exploring seasonality in the dataset
+### Exploring seasonality in the dataset
 
@@
 
-## Decomposition with singular spectrum analysis
+### Decomposition with singular spectrum analysis
 
@@
 # Discussion
+
+@Delara2022
+
+- The prevalence of polypharmacy in all medication classes is 37% [95% CI: 31-43%]
+- Difference of prevalence measure is due to different numerical thresholds, study setting, and publication year
+
+@Sirois2016
+
+- Problem of exposure: Polypharmacy can be defined as cumulative or simultaneous prescriptions
+- Cut-off threshold of polypharmacy should be justified by the risk of deleterious health outcomes
+- An ideal surveillance system should describe the importance of polypharmacy
 
@@
 
+@Cavallo2012
+
+- The weight is the number of time a pair of medications is prescribed together
+- The co-prescription network has a scale-free property, suggesting that the probability new links being formed is growing alongside the degree of the target node
+- The scale-free property of the network might be explained by the physician's prescribing habit: The physician tends to prescribe medications with known medications
+
+@Bazzoni2015
+
+- Drug-prescription network is highly dense and clustered at the global level
+- Drug-prescription network is organized into anatomically homogeneous modules at the local level
+
 # References

### 2024-04-02 docs/exec-summary/_preprocessing.qmd
Draft an initial report using Elsevier template
Draft initial intro and methods

@@
+::: {.content-visible unless-meta="in.article"}
 ### Data pre-processing
+:::
 
@@
 `Medication1-PrescribedAlongside-Medication2`.
-The knowledge graph is a representation of medication-claim network, where the edge (predicate) is the number of concurrency.
-Weight was applied on the edges by dividing it by the defined daily dose (DDD).
-Weighting is necessary to regularize the matrix into a unit-free scale, which allow a direct comparison of one drug to another.
+The knowledge graph is a representation of drug prescription network (DPN), where the edge (predicate) is the number of concurrency.
+In the original DPN, the edge weight was the number of claims by assuming that all of defined daily doses (DDD) were equal to 1 [@Cavallo2012].
+To account for augmentation polypharmacy, DDD provides further information due to the presence of a sub-dose medication, where DDD < 1 should be allowed.
+Naturally, an augmentation polypharmacy regimen should have a higher weight since this regimen is intended to increase the efficacy of the augmented medication [@Shrivastava2013].
+Therefore, weight was re-applied on the edges by dividing the number of claims by the DDD.
 

### 2024-04-02 docs/exec-summary/_source-data.qmd
Draft an initial report using Elsevier template
Draft initial intro and methods

@@
+::: {.content-visible unless-meta="in.article"}
 ### Source of data
+:::
 
-The University of Groningen IADB.nl pharmacy prescription database is a growing database that contains prescription data for 31 years from 1994 till 2024 from approximately 120 community pharmacies and covers an estimated population of 1,120,000 patients.
-Registration in the database is irrespective of health care insurance and age, gender and prescription rates among the database population have been found to be representative of the Netherlands as a whole, and the database has been widely used for research.
-Each person is individually tracked throughout the database period and prescription records contain information on the date of dispensing, the quantity dispensed, the dose regimen, the number of days the prescription is valid, the prescribing physician and the Anatomical Therapeutic Chemical code (ATC code).
-Each patient has a unique anonymous identifier; date of birth and gender are known.
-Due to the high patient-pharmacy commitment in the Netherlands, the medication records for each patient are virtually complete, except for over the counter (OTC) drugs and medication dispensed during hospitalization.
+All data in this investigation originated from IADB.nl, a dynamic pharmacy database containing prescription data from 1994 which still grow expansively.
+The database covers approximately 120 community pharmacies serving over one million patients.
+All patients are recorded in the database, irrespective of health care insurance, where the prescription rates, age, and gender are generalizable to represent the Netherlands [@Visser2013].
+The database offers a longitudinal record, where each individual has a uniquely anonymized tracking identifier.
+All records contain fields on the date of medication dispensing, its quantity, dose regimen, number of days prescribed, prescribing physicians, and the Anatomical Therapeutic Chemical (ATC) code.
+Except for the over the counter drugs and medication dispensed during hospitalization, other medication records for each patient are complete, mainly due to high patient-pharmacy commitment in the Netherlands.
 This analysis include daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.

### 2024-04-02 _targets.R

@@ -325,6 +325,7 @@ list(
   tar_quarto(report_arima, "docs", profile = "arima", priority = 0),
   tar_quarto(report_seasonality, "docs", profile = "seasonality", priority = 0),
   tar_quarto(report_spectral, "docs", profile = "spectral", priority = 0),
+  tar_quarto(article, "docs/article.qmd"),
   tar_quarto(readme, "README.qmd", priority = 0)
 
 )

### 2024-04-18 docs/abstract/_abstract-eupha.qmd
Draft abstracts for ISPOR and EUPHA

@@
----
-title: Eigenvector centrality signifies antidepressants as a central hub of the co-medication network
----
-
-Background: Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide.
+**Background:**
+Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide.
 People with chronic diseases are at a higher risk of having mental health issues.
@@
 
-Methods: Exploratory time-series analysis was performed in a static cohort from IADB.nl with at least one prescription of psychopharmaca from 2018 to 2022.
+**Methods:**
+Exploratory time-series analysis was performed in a static cohort from IADB.nl with at least one prescription of psychopharmaca from 2018 to 2022.
 The prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification.
-A medication-claim network was constructed to capture dose-adjusted co-prescription.
-Eigenvector centrality (ce) was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
-The number of medication claims (nc) and eigenvector centrality were extracted as weekly-aggregated time-series data.
+A drug prescription network was constructed to capture dose-adjusted co-prescription.
+Eigenvector centrality ($c_e$) was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
+The number of medication claims ($n_c$) and eigenvector centrality were extracted as weekly-aggregated time-series data.
 
-Results: Antidepressants (ce: 0.11, nc: 28,993), antipsychotics (ce: 0.07, nc: 14,027), and anxiolytics (ce: 0.08, nc: 14,061) are psychopharmaca with high eigenvector centrality.
+**Results:**
+Antidepressants ($c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`), antipsychotics ($c_e$: `r N05A$ce`, $n_c$: `r N05A$nc`), and anxiolytics ($c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) are psychopharmaca with high eigenvector centrality.
 These classes of medication are likely to be co-prescribed alongside other medications.
-Other groups with high eigenvector centrality were medications for alimentary and metabolism (ce: 0.15, nc: 53,602), blood (ce: 0.06, nc: 13,310), cardiovascular (ce: 0.14, nc: 44,802), analgesics (ce: 0.09, nc: 13,847), and respiratory (ce: 0.09, nc: 25,034).
+Further groups with high eigenvector centrality were medications for alimentary and metabolism ($c_e$: `r A0x$ce`, $n_c$: `r A0x$nc`), blood ($c_e$: `r B0x$ce`, $n_c$: `r B0x$nc`), cardiovascular ($c_e$: `r C0x$ce`, $n_c$: `r C0x$nc`), analgesics ($c_e$: `r N02$ce`, $n_c$: `r N02$nc`), and respiratory ($c_e$: `r R0x$ce`, $n_c$: `r R0x$nc`).
 Only antidepressants had a positive time trend for both eigenvector centrality and the number of claims.
 
-Conclusion: Eight medications have a high concurrence on a population level.
+**Conclusion:**
+Eight medications have a high concurrence on a population level.
 Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants are related to co-prescription with other medication classes.

### 2024-04-18 docs/abstract/_abstract-full.qmd
Draft abstracts for ISPOR and EUPHA

--- 2024-03-07 docs/abstract/_abstract.qmd
@@
-```{r}
-
-pkgs <- c("targets", "magrittr")
-pkgs_load <- sapply(pkgs, library, character.only = TRUE)
-options(digits = 2, scipen = 999)
-
-getGroup <- function(tbl, groupname) {
-  sub_tbl <- tbl %>% subset(.$group == groupname, select = -group)
-  return(sub_tbl)
-}
-
-results <- tar_read(ts_clust) %>%
-  tibble::tibble() %>%
-  dplyr::group_by(group) %>%
-  dplyr::summarize(
-    ce = mean(eigen),
-    nc = mean(n_claim) %>% round() %>% scales::comma(),
-    lim_ce = 1.96 * sd(eigen) / sqrt(length(eigen)),
-    ce_ci  = sprintf("%.02f [%.02f, %.02f]", ce, ce - lim_ce, ce + lim_ce)
-  )
-
-N06A <- results %>% getGroup("Antidepressants")
-N05A <- results %>% getGroup("Antipsychotics")
-N05B <- results %>% getGroup("Anxiolytics")
-A0x  <- results %>% getGroup("Alimentary and metabolism")
-B0x  <- results %>% getGroup("Blood")
-C0x  <- results %>% getGroup("Cardiovascular")
-N02  <- results %>% getGroup("Analgesics")
-R0x  <- results %>% getGroup("Respiratory")
-
-```
-
 **Background:**
@@
 The prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca was evaluated at ATC level 3, drugs for the nervous system at ATC level 2, and other medications at ATC level 1, distinguished into a total of 24 medication classes.
-A medication-claim network was constructed as an undirected graph to capture dose-adjusted co-prescription.
+A drug prescription network was constructed as an undirected graph to capture dose-adjusted co-prescription.
 Eigenvector centrality ($c_e$) was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.

### 2024-04-18 docs/abstract/_abstract-ispor.qmd
Draft abstracts for ISPOR and EUPHA

--- 2024-04-18 docs/abstract/_abstract-full.qmd
@@
 **Objectives:**  
-Evaluate the interrelatedness of mental health problems with other diagnoses, reflected as a relative importance score of psychopharmaca in a medication claim registry.
+Evaluate the interrelatedness of mental health problems with other diagnoses, reflected as an importance score of medication uses relative to other medications recorded in a medication claim registry.
 

### 2024-04-18 docs/abstract/_abstract.qmd
Draft abstracts for ISPOR and EUPHA

--- 2024-02-14 docs/abstract/_abstract.qmd
@@
 
-**Background:**
-Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide.
-People with chronic diseases are at a higher risk of having mental health issues, which in turn potentially worsen their overall well-being.
+::: {.content-visible when-meta="in.abstract.full"}
 
-**Objectives:**  
-Evaluate the interrelatedness of mental health problems with other diagnoses, reflected as a relative importance score of psychopharmaca in a medication claim registry.
+{{< include _abstract-full.qmd >}}
 
-**Methods:**
-Exploratory time-series analysis was performed using the University of Groningen prescription database, IADB.nl.
-A static cohort with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
-The prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca was evaluated at ATC level 3, drugs for the nervous system at ATC level 2, and other medications at ATC level 1, distinguished into a total of 24 medication classes.
-A medication-claim network was constructed as an undirected graph to capture dose-adjusted co-prescription.
-Eigenvector centrality ($c_e$) was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
-The number of medication claims ($n_c$), number of patients, claim-to-patient ratio, and eigenvector centrality were extracted as weekly-aggregated time-series data.
-Singular spectrum analysis was performed to decompose the data into its constituting trend, periodicity, and white noises.
+:::
 
-**Results:**
-Antidepressants (ATC `N06A`, $c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`), antipsychotics (`N05A`, $c_e$: `r N05A$ce`, $n_c$: `r N05A$nc`), and anxiolytics (`N05B`, $c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) are psychopharmaca with high eigenvector centrality.
-These classes of medication are likely to be co-prescribed alongside other medications.
-Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$: `r A0x$ce`, $n_c$: `r A0x$nc`), blood (`B01-B06`, $c_e$: `r B0x$ce`, $n_c$: `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$: `r C0x$ce`, $n_c$: `r C0x$ne`), analgesics (`N02`, $c_e$: `r N02$ce`, $n_c$ `r N02$nc`), and respiratory (`R01-R07`, $c_e$: `r R0x$ce`, $n_c$: `r R0x$nc`).
-Among eight medications with high eigenvector centrality, only antidepressants had a positive time trend for both eigenvector centrality and actual number of claims.
+::: {.content-visible when-meta="in.abstract.eupha"}
 
-**Discussion:**
-Eight medications, three of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level.
-Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants are related to co-prescription with other medication classes.
-Constructing a medication claim network enriches the exploratory analysis of medication use at the population level.
+{{< include _abstract-eupha.qmd >}}
+
+:::
+
+::: {.content-visible when-meta="in.abstract.ispor"}
+
+{{< include _abstract-ispor.qmd >}}
+
+:::

### 2024-04-18 _targets.R

@@ -319,6 +319,8 @@ list(
 
   # Generate documentation
   tar_quarto(abstract, "docs/abstract/abstract.qmd"),
+  tar_quarto(abstract_eupha, "docs/abstract/eupha.qmd"),
+  tar_quarto(abstract_ispor, "docs/abstract/ispor.qmd"),
   tar_quarto(report, "docs", profile = "report", extra_files = "docs/exec-summary", priority = 0),
   tar_quarto(summary, "docs", profile = "summary", priority = 0),
   tar_quarto(report_descriptive, "docs", profile = "descriptive", priority = 0),

### 2024-06-02 docs/abstract/_abstract-eupha.qmd
Draft the initial results

@@
 **Results:**
-Antidepressants ($c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`), antipsychotics ($c_e$: `r N05A$ce`, $n_c$: `r N05A$nc`), and anxiolytics ($c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) are psychopharmaca with high eigenvector centrality.
+Antidepressants ($c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics ($c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) are psychopharmaca with high eigenvector centrality.
 These classes of medication are likely to be co-prescribed alongside other medications.
@@
 **Conclusion:**
-Eight medications have a high concurrence on a population level.
+Seven medications have a high concurrence on a population level.
 Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants are related to co-prescription with other medication classes.

### 2024-06-02 docs/abstract/_abstract-full.qmd
Draft the initial results

@@
 **Results:**
-Antidepressants (ATC `N06A`, $c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`), antipsychotics (`N05A`, $c_e$: `r N05A$ce`, $n_c$: `r N05A$nc`), and anxiolytics (`N05B`, $c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) are psychopharmaca with high eigenvector centrality.
+Antidepressants (ATC `N06A`, $c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics (`N05B`, $c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) are psychopharmaca with high eigenvector centrality.
 These classes of medication are likely to be co-prescribed alongside other medications.
@@
 **Discussion:**
-Eight medications, three of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level.
+Seven medications, three of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level.
 Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants are related to co-prescription with other medication classes.

### 2024-06-02 docs/article.qmd
Compile as docx
Draft the initial results

@@
       cite-style: authoryear
+  docx: default
 
@@
 
+### Determining relative importance
+
+Since the sum of all eigenvector centralities $c_i$ in equation [-@eq-eigen-centrality] is equal to one, a network with similarly connected nodes will have an eigenvector centrality $c_i$ = $\frac{1}{n}$ for each node, where $n$ is the number of nodes.
+The value of $c_i = \frac{1}{n}$ is the expected eigenvector centrality in a densely connected network where connection $\mathcal{V}_{i, j}$ from node $\mathcal{V}_i$ to node $\mathcal{V}_j$ has the same probability for every node.
+Per the central limit theorem, the value $\frac{1}{n}$ can be parameterized as a mean of a normal distribution, where all instances of eigenvector centrality will follow the distribution, $c_i \sim \mathcal{N}(\mu, \sigma)$.
+A one-sample Student's T-test was performed to assess how much each eigenvector centrality differs from the expected values.
+As such, eigenvector centrality greater than $\frac{1}{n}$ can be considered high, and the value below it can be considered low.
+The p-values was corrected for a type-I error using Bonferroni method.
+
 # Results
+
+```{r}
+
+tar_load(res_tbl_overview)
+
+n_patient <- prettyNum(res_tbl_overview$total, big.mark = ",", scientific = FALSE)
+hi_claim <- res_tbl_overview$overview |> dplyr::slice_max(mean_claim)
+lo_claim <- res_tbl_overview$overview |> dplyr::slice_min(mean_claim)
+
+hi_mean <- prettyNum(hi_claim$mean_claim, big.mark = ",")
+lo_mean <- prettyNum(lo_claim$mean_claim, big.mark = ",")
+
+```
+
+IADB recorded `r n_patient` patients having at least one prescription of antidepressants or anxiolytics within five years of data extraction.
+The highest average of prescription claim occurred on `r hi_claim$day`, with $\bar{x}$ = `r hi_mean` [`r hi_claim$sd_claim`].
+Meanwhile, the lowest average of claim occurred on `r lo_claim$day`, with $\bar{x}$ = `r lo_mean` [`r lo_claim$sd_claim`].
+A large margin of difference between the highest and lowest average number of claim implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in figure [-@fig-period-day].
+The cyclical patterns are further explained in our supplementary material.
+@tbl-desc shows the total number of claim for each medication class alongside the distribution of DDD and its weight.
+
+```{r tbl-desc}
+#| tbl-cap: Descriptive statistics of prescription data from 2018 to 2022, ordered by the number of claim
+
+tar_read(res_tbl_stat) %>%
+  dplyr::arrange(-n_claim) %>%
+  dplyr::mutate(
+    "mean_sd_dose"      = sprintf("%.2f [%.2f]", dose_mean, dose_sd),
+    "median_IQR_dose"   = sprintf("%.2f [%.2f]", dose_median, dose_IQR),
+    "mean_sd_weight"    = sprintf("%.2f [%.2f]", weight_mean, weight_sd),
+    "median_IQR_weight" = sprintf("%.2f [%.2f]", weight_median, weight_IQR),
+    "range_dose"        = sprintf("%.2f - %.2f", dose_min, dose_max),
+    "range_weight"      = sprintf("%.2f - %.2f", weight_min, weight_max)
+  ) %>%
+  subset(select = c(group, n_claim, mean_sd_dose, median_IQR_dose, range_dose, mean_sd_weight)) %>%
+  flextable::flextable() %>%
+  flextable::set_header_labels(
+    group           = "",
+    n_claim         = "Claim",
+    mean_sd_dose    = "Mean [SD]",
+    median_IQR_dose = "Median [IQR]",
+    range_dose      = "Range",
+    mean_sd_weight  = "Mean [SD]"
+  ) %>%
+  flextable::add_header_row(
+    values    = c("", "Defined Daily Dose", "Weight"),
+    colwidths = c(2, 3, 1),
+    top       = TRUE
+  ) %>%
+  flextable::align(align = "center", part = "all") %>%
+  flextable::align(j = 1, align = "left", part = "body") %>%
+  #flextable::font(fontname = "Times", part = "all") %>%
+  flextable::fontsize(size = 7, part = "all") %>%
+  flextable::line_spacing(space = 0.7, part = "all")
+
+```
+
+```{r fig-period-day}
+#| fig-width: 14
+#| fig-height: 5
+#| fig-cap: Daily cyclical pattern captured on a de-trended data
+
+tar_read(plt_period_day)[[1]]
+
+```
+
+## Time-series decomposition
+
+Using the weekly-aggregated data, we obtained decomposed series using an SSA-based approach.
+@fig-ssa depicts the decomposition result of the number of claim time-series in antidepressants.
+SSA-based decomposition separates the trend from its oscillating functions, as shown in the lower half of the plot.
+The trend explains roughly 90% of the variability, and oscillating functions explain 10%.
+The first two oscillating functions, F1 and F2, captured most of the variability in a series compared to the rest of the functions.
+
+{{< pagebreak >}}
+
+```{r fig-ssa}
+#| fig-width: 16
+#| fig-height: 12
+#| fig-pos: H
+#| fig-cap: An example of time-series decomposition using singular spectrum analysis-based approach
+
+tar_read(plt_ssa_recon_n_claim)[[17]]
+
+```
+
+{{< pagebreak >}}
+
+## Relative importance score
+
+```{r fig-hi-eigen}
+#| fig-cap: Clusters of medication with a higher eigenvector centrality, implying a higher relative importance in polypharmacy regimens
+#| fig-width: 9
+#| fig-height: 10
+
+tar_read(plt_hi_eigen)
+
+```
 

### 2024-06-02 docs/exec-summary/_descriptive.qmd
Draft an initial report using Elsevier template
Draft the initial results

@@
+::: {.content-visible unless-meta="in.article"}
 ### Exploratory descriptive analysis
+:::
 
@@
 Mean, median, standard deviation, and interquartile range were reported to evaluate the distribution.
+
+::: {.content-visible unless-meta="in.article"}
 The data is split into pre-COVID-19 and during COVID-19 period, and mean difference was calculated using Welch's T-Test.
@@
 taking the differences between $x_t$ and $x_{t-1}$.
+:::

### 2024-07-16 _targets.R
Visualize clusters with a high eigenvector centrality

@@ -320,6 +320,10 @@ list(
   # Cluster the series based on eigenvector centrality
   tar_target(ts_clust, setCluster(ts_recon, nclusts = 2:10)),
 
+  # Indicate medication groups with high eigenvector centrality
+  tar_target(plt_hi_eigen, vizEigenCluster(ts_clust, ncol = 3, scales = "free_y")),
+  tar_target(plt_hi_eigen_box, vizEigenBox(ts_clust)),
+
   # Generate documentation
   tar_quarto(abstract, "docs/abstract/abstract.qmd"),
   tar_quarto(abstract_eupha, "docs/abstract/eupha.qmd"),

### 2024-07-16 src/R/visualize.R

@@ -456,3 +456,87 @@ vizForecast <- function(mod_cast, ts) {
 
   return(plt)
 }
+
+vizEigenCluster <- function(ts_clust, ...) {
+  #' Visualize Eigenvector Centrality Cluster
+  #'
+  #' Generate histogram + density plot of eigenvector centrality for each
+  #' medication group.
+  #'
+  #' @param ts_clust An augmented time-series containing cluster and one-sample
+  #' T-test
+  #' @return A GGPlot2 object
+  require("ggplot2")
+
+  tbl       <- ts_clust
+  ref       <- tbl %>% subset(.$hi_eigen) %>% extract2("group") %>% unique()
+  colors    <- genColor()
+  strip_col <- setStripColor(unique(tbl$group), ref = ref)
+
+  note <- tbl %>%
+    subset(select = c(group, estimate, conf.low, conf.high, hi_eigen)) %>%
+    unique() %>%
+    dplyr::mutate(
+      "xpos" = conf.high,
+      "note" = sprintf(
+        "c[e] == '%.3f [%.3f - %.3f]'", estimate, conf.low, conf.high
+      )
+    )
+
+  plt <- ggplot(tbl, aes(x = eigen, fill = hi_eigen, color = hi_eigen)) +
+    geom_density(alpha = 0.4) +
+    geom_histogram(bins = 50, aes(alpha = hi_eigen)) +
+    geom_vline(xintercept = 1/24, linetype = 2, color = "grey60") +
+    annotate("text", label = "Expected value", y = Inf, x = 1/24, hjust = -0.05, vjust = 1.5, color = "grey40") +
+    geom_label(
+      data = note,
+      aes(label = note, y = -Inf, x = -Inf),
+      size  = 3,
+      vjust = -1,
+      hjust = "inward",
+      alpha = 0.4,
+      parse = TRUE,
+      inherit.aes = FALSE
+    ) +
+    ggh4x::facet_wrap2(~group, strip = strip_col, ...) +
+    ggpubr::theme_pubclean() +
+    scale_color_manual(values = c("grey60", colors$green)) +
+    scale_fill_manual(values  = c("grey60", colors$green)) +
+    scale_alpha_manual(values = c(0.4, 0.8)) +
+    labs(x = "Eigenvector centrality", y = "Number of observation") +
+    theme(
+      legend.position = "none"
+    )
+
+  return(plt)
+}
+
+vizEigenBox <- function(ts_clust, ...) {
[…]

### 2024-07-16 src/R/clean.R
Remove non-sensible DDD based on the duration of uses

@@ -180,3 +180,61 @@ aggregateTS <- function(ts, type = "week", ...) {
   return(ts_agg)
 }
 
+checkDose <- function(atc_tbl) {
+  #' Check Dose
+  #'
+  #' Check the dose to exclude entries with high DDD but low period of
+  #' prescription. For instance, the use of intrauterine device would span over
+  #' five years, but only prescribed for a day. This will result in an entry
+  #' with DDD = 1,800. This function checks whether the entry can be directly
+  #' analyze.
+  #' 
+  #' @param atc_tbl A data frame containing split ATC entries
+  #' @return A vector of boolean indicating which entry is eligible to analyze
+
+  startdat <- as.Date(atc_tbl$date)
+  stopdat  <- as.Date(atc_tbl$end)
+  dose     <- as.numeric(atc_tbl$dose)
+  eligible <- {dose / as.numeric(stopdat - startdat)} <= 1
+
+  return(eligible)
+}
+
+cleanDose <- function(atc_tbl, period = NULL) {
+  #' Clean Dose
+  #'
+  #' Clean the dose to regularie entries with DDD > 1.
+  #'
+  #' @param atc_tbl A data frame containing split ATC entries
+  #' @param period Period of use, usually `stopdat` - `startdat`
+  #' @return A split ATC data frame containing entries with cleaned doses
+
+  is_arr <- is.null(dim(atc_tbl)) # Check if array
+
+  if (is_arr) {
+
+    if (is.null(period)) {
+      stop("Period of use should be set using the `period` argument for an array object")
+    }
+
+    dose <- atc_tbl
+
+    res <- ifelse(dose <= 1, dose, dose / period)
+
+  } else {
+
+    startdat <- as.Date(atc_tbl$date)
+    stopdat  <- as.Date(atc_tbl$end)
+    period   <- as.numeric(stopdat - startdat)
+
+    res <- atc_tbl |>
+      dplyr::mutate(
+        ".dose" = dose,
+        "dose"  = cleanDose(atc_tbl$dose, period)
+      )
+
+  }
+
+  return(res)
+}
+

### 2024-07-16 src/R/network.R

@@ -178,7 +178,11 @@ mkGraph <- function(atc_tbl, method = "density", type = "additive") {
   #' @return Medication graph from pairwises of ATC
 
   # Discard entries which become the turning point with `method = "log"`
-  tbl <- atc_tbl %>% subset(.$dose >= 0.1 & .$dose < 10)
+  regular_ddd <- checkDose(atc_tbl)
+
+  tbl <- atc_tbl %>%
+    cleanDose() %>%
+    subset(.$dose >= 0.1 & .$dose < 10 & regular_ddd)
 
   # Generate the graph
   graph <- tryCatch(
@@ -241,3 +245,4 @@ combineMetrics <- function(list_metrics) {
 
   return(tbl)
 }
+

### 2024-07-16 src/R/parse.R

@@ -96,6 +96,7 @@ splitAtc <- function(tbl, atcs) {
   atc_tbls <- apply(tbl, 1, function(entry) {
     anopat   <- entry[1]
     startdat <- entry[2]
+    stopdat  <- entry[3]
     atc      <- entry[4]
 
     atc   %<>% as.character() %>% strsplit(split = ",") %>% unlist()
@@ -105,7 +106,13 @@ splitAtc <- function(tbl, atcs) {
       as.numeric()
 
     tbl <- tibble::tibble(
-      label, dose, "n" = 1, "N" = N, "id" = anopat, "date" = startdat
+      "label" = label,
+      "dose"  = dose,
+      "n"     = 1,
+      "N"     = N,
+      "id"    = anopat,
+      "date"  = startdat,
+      "end"   = stopdat
     ) %>%
       groupAtc() %>%
       subset(.$label != "")

### 2024-07-16 _targets.R
Write split-by-date data under the 'processed/dirname' path

@@ -32,20 +32,27 @@ list(
 
   # Split ATC in each grouped data frame
   tar_target(
-    tbl_iadb_split_atc,
+    tbl_iadb_split_date,
     iterby(tbl_iadb_by_date, "startdat", splitAtc, "atcs"),
     pattern   = map(tbl_iadb_by_date),
     iteration = "vector"
   ),
 
   # Write daily entries as separate files
-  tar_target(dat_iadb_split_atc, writeFiles(tbl_iadb_split_atc)),
+  tar_target(dat_iadb_split_date, writeFiles(tbl_iadb_split_date, "by-month-year")),
+
+  # Concatenate all split ATC data frame
+  tar_target(tbl_concat, catIADB("data/processed/by-month-year"), format = "parquet"),
+
+  # Describe the summary statistics
+  tar_target(res_tbl_overview, overviewData(tbl_concat)),
+  tar_target(res_tbl_stat, summarizeStat(tbl_concat)),
 
   # Generate graph objects from the split ATC data frame
   tar_target(
     iadb_graph,
-    lapply(tbl_iadb_split_atc, mkGraph),
-    pattern   = map(tbl_iadb_split_atc),
+    lapply(tbl_iadb_split_date, mkGraph),
+    pattern   = map(tbl_iadb_split_date),
     iteration = "list",
     priority  = 0
   ),

### 2024-07-16 src/R/parse.R

@@ -146,12 +146,13 @@ iterby <- function(tbl, varname, FUN, ...) {
   return(proc_group)
 }
 
-writeFiles <- function(tbls, ...) {
+writeFiles <- function(tbls, dirname, ...) {
   #' Write Files
   #'
   #' Write a list of data frames into the disk.
   #'
   #' @param tbls A list of data frame
+  #' @param dirname Directory name to contain the output files
   #' @inheritDotParams readr::write_csv
   #' @return Written csv files
 
@@ -159,7 +160,7 @@ writeFiles <- function(tbls, ...) {
 
   lapply(ids, function(id) {
     tbl   <- tbls[[id]]
-    fpath <- sprintf("data/processed/%s.csv", id)
+    fpath <- sprintf("data/processed/%s/%s.csv", dirname, id)
     msg   <- sprintf("Writing %s into the disk", id)
 
     message(msg)
@@ -168,3 +169,26 @@ writeFiles <- function(tbls, ...) {
   })
 
 }
+
+catIADB <- function(fpath) {
+  #' Concatenate IADB Entries
+  #'
+  #' Concatenate all IADB entries stored as different csv files.
+  #'
+  #' @param fpath Path to csv files
+  #' @return an Arrow Table format
+
+  tbl <- arrow::open_dataset(fpath, format = "csv") %>%
+    arrow::as_arrow_table() %>%
+    dplyr::collect() %>%
+    cleanDose() %>%
+    dplyr::filter(
+      dose >= 0.1,
+      dose <  10,
+      {dose / as.numeric(as.Date(end) - as.Date(date))} <= 1
+    ) %>%
+    dplyr::mutate("weight" = weightEntry(n = 1, dose = dose, method = "density"))
+
+  return(tbl)
+}
+

### 2024-07-16 _targets.R
Generate a summary and overview of the dataset

@@ -68,7 +68,7 @@ list(
 
   # Compute the descriptive statistical summary of the daily records
   tar_target(
-    iadb_stats, lapply(tbl_iadb_split_atc, fieldSummary) %>% combineMetrics()
+    iadb_stats, lapply(tbl_iadb_split_date, fieldSummary) %>% combineMetrics()
   ),
 
   # Set iteration parameters of metrics and scales for visualization

### 2024-07-16 src/R/cluster.R

@@ -82,8 +82,12 @@ setCluster <- function(ts, nclusts = 2:10, ...) {
     dplyr::mutate(
       "meandiff" = purrr::map(data, ~ t.test(.x$eigen, mu = 1/24) %>% broom::tidy())
     ) %>%
-    tidyr::unnest(c(data, meandiff)) %>%
-    dplyr::mutate("hi_eigen" = statistic > 0)
+    tidyr::unnest(meandiff) %>%
+    dplyr::mutate( # Perform Bonferroni correction
+      "p_adjust" = p.adjust(p.value, method = "bonferroni"),
+      "hi_eigen" = statistic > 0
+    ) %>%
+    tidyr::unnest(data)
 
   aug_ts <- aug_tbl %>% tsibble::as_tsibble(key = group, index = date)
 

### 2024-07-16 src/R/report.R

@@ -58,3 +58,75 @@ describeMean <- function(ts) {
 
   return(res)
 }
+
+summarizeStat <- function(tbl_concat) {
+  #' Describe the Summary Statistics
+  #'
+  #' Calculate summary statistics from a given arrow dataset.
+  #'
+  #' @param tbl_concat An arrow dataset containing the whole IADB entries
+  #' @return A tidy summary statistics table
+
+  tbl <- tbl_concat %>% dplyr::filter(date >= "2018-01-01", date <= "2022-12-31")
+
+  res <- tbl %>%
+    dplyr::group_by(group) %>%
+    dplyr::summarize(
+      "n_claim"       = sum(n, na.rm = TRUE),
+      "dose_mean"     = mean(dose, na.rm = TRUE),
+      "dose_sd"       = sd(dose, na.rm = TRUE),
+      "dose_median"   = median(dose, na.rm = TRUE),
+      "dose_IQR"      = IQR(dose, na.rm = TRUE),
+      "dose_min"      = min(dose, na.rm = TRUE),
+      "dose_max"      = max(dose, na.rm = TRUE),
+      "weight_mean"   = mean(weight, na.rm = TRUE),
+      "weight_sd"     = sd(weight, na.rm = TRUE),
+      "weight_median" = median(weight, na.rm = TRUE),
+      "weight_IQR"    = IQR(weight, na.rm = TRUE),
+      "weight_min"    = min(weight, na.rm = TRUE),
+      "weight_max"    = max(weight, na.rm = TRUE)
+    ) %>%
+    dplyr::ungroup() %>%
+    dplyr::collect()
+
+  return(res)
+}
+
+overviewData <- function(tbl_concat) {
+  #' Overview Data
+  #'
+  #' Create a descriptive overview of the data.
+  #'
+  #' @param tbl_concat An arrow dataset containing the whole IADB entries
+  #' @return A tidy descriptive overview table
+  require("tsibble")
+
+  tbl <- tbl_concat |>
+    dplyr::filter(date >= "2018-01-01", date <= "2022-12-31") |>
+    dplyr::mutate(
+      "date" = as.Date(date),
+      "day"  = weekdays(date),
+      "week" = tsibble::yearweek(date)
+    )
+
+  total <- tbl$id |> unique() |> length()
+
+  overview <- tbl |>
+    dplyr::group_by(week, day) |>
[…]

### 2024-07-16 docs/abstract/_abstract-eupha.qmd
Initial draft for ISPOR 2024

@@
 **Methods:**
-Exploratory time-series analysis was performed in a static cohort from IADB.nl with at least one prescription of psychopharmaca from 2018 to 2022.
+Exploratory time-series analysis was performed in a closed cohort from IADB.nl with at least one prescription of anxiolytics/antidepressants from 2018 to 2022.
 The prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification.
@@
 **Conclusion:**
-Seven medications have a high concurrence on a population level.
-Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants are related to co-prescription with other medication classes.
-We recommend constructing a medication claim network to evaluate periodic co-prescription as a public health monitoring procedure.
+Seven medications, three of which are psychopharmaca, had a high eigenvector centrality, indicating concurrence with other medication groups on a population level.
+Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants was related to co-prescription with other medication classes.
+Constructing a medication claim network enriches the exploratory analysis of medication use at the population level.

### 2024-07-16 docs/abstract/_abstract-full.qmd
Initial draft for ISPOR 2024

@@
 Exploratory time-series analysis was performed using the University of Groningen prescription database, IADB.nl.
-A static cohort with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
-The prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca was evaluated at ATC level 3, drugs for the nervous system at ATC level 2, and other medications at ATC level 1, distinguished into a total of 24 medication classes.
+A closed cohort with at least one prescription of anxiolytics/antidepressants from 2018 to 2022 was extracted.
+The prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca was evaluated at ATC level 4, drugs for the nervous system at ATC level 3, and other medications at ATC level 1, leading to a total of 24 medication classes.
 A drug prescription network was constructed as an undirected graph to capture dose-adjusted co-prescription.
@@
 Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$: `r A0x$ce`, $n_c$: `r A0x$nc`), blood (`B01-B06`, $c_e$: `r B0x$ce`, $n_c$: `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$: `r C0x$ce`, $n_c$: `r C0x$nc`), analgesics (`N02`, $c_e$: `r N02$ce`, $n_c$: `r N02$nc`), and respiratory (`R01-R07`, $c_e$: `r R0x$ce`, $n_c$: `r R0x$nc`).
-Among eight medications with high eigenvector centrality, only antidepressants had a positive time trend for both eigenvector centrality and actual number of claims.
+Among the seven medication groups with high eigenvector centrality, only antidepressants showed a positive time trend for both eigenvector centrality and actual number of claims.
 
 **Discussion:**
-Seven medications, three of which are psychopharmaca, have a high eigenvector centrality, implying its concurrence on a population level.
-Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants are related to co-prescription with other medication classes.
+Seven medications, three of which are psychopharmaca, had a high eigenvector centrality, indicating concurrence with other medication groups on a population level.
+Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants was related to co-prescription with other medication classes.
 Constructing a medication claim network enriches the exploratory analysis of medication use at the population level.

### 2024-07-16 docs/abstract/_abstract-ispor.qmd
Initial draft for ISPOR 2024

@@
 Exploratory time-series analysis was performed using the University of Groningen prescription database, IADB.nl.
-A static cohort with at least one prescription of psychopharmaca from 2018 to 2022 was extracted.
-The prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca was evaluated at ATC level 3, drugs for the nervous system at ATC level 2, and other medications at ATC level 1, distinguished into a total of 24 medication classes.
+A closed cohort with at least one prescription of anxiolytics/antidepressants from 2018 to 2022 was extracted.
+The prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca was evaluated at ATC level 4, drugs for the nervous system at ATC level 3, and other medications at ATC level 1, distinguished into a total of 24 medication classes.
 A drug prescription network was constructed as an undirected graph to capture dose-adjusted co-prescription.

### 2024-07-16 docs/article.qmd
Initial draft for ISPOR 2024

@@
 title: >
-  Eigenvector centrality as a metric of polypharmacy signifies antidepressants
-  as a central hub of the drug prescription network
+  A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses
 
@@
 
-Surveilling polypharmacy regimens requires a holistic approach since drug prescription highly depends on the physician's prescribing habits [@Stassen2021], patient-physician relationship, and pharmaceutical market, which all bear an interplay with the decision-making process [@Cavallo2012].
+Surveilling polypharmacy regimens requires a holistic approach since drug prescription highly depends on the physician's prescribing habits [@Shrivastava2013], patient-physician relationship, and pharmaceutical market, which all bear an interplay with the decision-making process [@Cavallo2012].
 A holistic polypharmacy surveillance system needs to describe the importance of polypharmacy by incorporating both qualitative and quantitative measures [@Sirois2016].

### 2024-07-29 docs/abstract/_abstract-full.qmd
Update abstract based for ISPOR submission

@@
 **Background:**
-Mental health disorders are prevalent comorbidities affecting nearly two billion people worldwide.
-People with chronic diseases are at a higher risk of having mental health issues, which in turn potentially worsen their overall well-being.
+The implementation of network analysis in medicine and epidemiology started to gain popularity.
+A network-based approach captures the relationships of the building blocks of a complex system.
+Drug co-prescription is a complex issue presenting with one-to-many relationships that may change over time, especially also in mental disorders.
 
 **Objectives:**  
-Evaluate the interrelatedness of mental health problems with other diagnoses, reflected as a relative importance score of psychopharmaca in a medication claim registry.
+Evaluate the temporal relationships of drug treatment for mood disorders with other drug therapies in a pharmacy dispensing database.
 
 **Methods:**
-Exploratory time-series analysis was performed using the University of Groningen prescription database, IADB.nl.
-A closed cohort with at least one prescription of anxiolytics/antidepressants from 2018 to 2022 was extracted.
-The prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca was evaluated at ATC level 4, drugs for the nervous system at ATC level 3, and other medications at ATC level 1, leading to a total of 24 medication classes.
+Exploratory temporal network analysis was performed using the University of Groningen prescription database, IADB.nl.
+A closed cohort with at least one prescription of anxiolytics/antidepressants dispensed anywhere from 2018 to 2022 was extracted.
+The drug prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca was evaluated at ATC level 4, drugs for the nervous system at ATC level 3, and other medications at ATC level 1, distinguished into a total of 24 therapeutic medication classes.
 A drug prescription network was constructed as an undirected graph to capture dose-adjusted co-prescription.
 Eigenvector centrality ($c_e$) was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
-The number of medication claims ($n_c$), number of patients, claim-to-patient ratio, and eigenvector centrality were extracted as weekly-aggregated time-series data.
-Singular spectrum analysis was performed to decompose the data into its constituting trend, periodicity, and white noises.
+The number of prescriptions ($n_c$), number of patients, claim-to-patient ratio, and eigenvector centrality were extracted as weekly-aggregated time-series data.
+Singular spectrum analysis was performed to decompose the data into its constituting trend, harmonics, and noise components.
 
@@
 Antidepressants (ATC `N06A`, $c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics (`N05B`, $c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) are psychopharmaca with high eigenvector centrality.
-These classes of medication are likely to be co-prescribed alongside other medications.
+These classes of medication are likely to be co-prescribed apart from other medications.
 Further groups with high eigenvector centrality were medications for alimentary and metabolism (`A01-A16`, $c_e$: `r A0x$ce`, $n_c$: `r A0x$nc`), blood (`B01-B06`, $c_e$: `r B0x$ce`, $n_c$: `r B0x$nc`), cardiovascular (`C01-C10`, $c_e$: `r C0x$ce`, $n_c$: `r C0x$nc`), analgesics (`N02`, $c_e$: `r N02$ce`, $n_c$: `r N02$nc`), and respiratory (`R01-R07`, $c_e$: `r R0x$ce`, $n_c$: `r R0x$nc`).
@@
 **Discussion:**
-Seven medications, three of which are psychopharmaca, had a high eigenvector centrality, indicating concurrence with other medication groups on a population level.
-Positive time trends in both eigenvector centrality and claims suggest that increasing uses of antidepressants was related to co-prescription with other medication classes.
-Constructing a medication claim network enriches the exploratory analysis of medication use at the population level.
+Seven medication therapy classes, three of which are psychopharmaca, had a high eigenvector centrality, indicating concurrence with other medication groups on a population level in the group of antidepressant or anxiolytic users.
+Positive time trends in both eigenvector centrality and dispensing suggest that increasing uses of antidepressants was related to co-prescription with other medication classes.
+Constructing a prescription network enriches the exploratory analysis of medication use at the population level.

### 2024-08-10 _targets.R
Summarize the reconstructed time series
Calculate the summary statistics of the reconstructed time series, then combine the results to descriptive table of the input dataset. The definition of 'n_claim' is different between 'ts_recon' and 'res_tbl_stat'. In 'ts_recon', the 'n_claim' represents the total number of claim for a particular drug, so one group may have multiple entries in one day. In 'res_tbl_stat', the 'n_claim' represents the number of unique patient claiming for drugs from a particular group throughout the years of observation. We will need to revisit this difference later and cl

@@ -299,6 +299,7 @@ list(
 
   # Generate reconstructed time series based on trend + 2 oscillating functions
   tar_target(ts_recon, genReconTs(decom_ssa, n = 2)),
+  tar_target(res_recon_stat, mergeReconSummary(ts_recon, res_tbl_stat)),
 
   # Plot the reconstructed time-series
   tar_map(

### 2024-08-10 src/R/report.R

@@ -130,3 +130,29 @@ overviewData <- function(tbl_concat) {
   return(res)
 }
 
+mergeReconSummary <- function(ts_recon, res_tbl_stat) {
+  #' Merge Reconstructed Data Summary
+  #'
+  #' Summarize the reconstructed time series, then merge it into
+  #' `res_tbl_stat`.
+  #'
+  #' @param ts_recon The reconstructed data frame
+  #' @param res_tbl_stat A summary of the dataset, containing number of unique
+  #' patients, dose, and weight
+  #' @return A tidy data frame
+
+  ts_stat <- ts_recon |>
+    tibble::tibble() |>
+    dplyr::group_by(group) |>
+    dplyr::summarize(
+      "eigen_mean"   = mean(eigen),
+      "eigen_sd"     = sd(eigen),
+      "eigen_median" = median(eigen),
+      "eigen_IQR"    = IQR(eigen)
+    )
+
+  tbl <- dplyr::inner_join(res_tbl_stat, ts_stat, by = "group")
+
+  return(tbl)
+}
+

### 2024-08-10 docs/article.qmd
Revise the introduction based on suggestion for the ISPOR abstract

@@
   - Mental Health   
-  - Public Health Surveillance
+  - Public Health Monitoring
 
@@
 
+::: {.content-hidden}
+
 Mental disorders are a common comorbidity affecting nearly two billion people worldwide with a prevalence that remains relatively stable overtime [@Kessler2009; @Steel2014; @Richter2019].
@@
 
+:::
+
+The relational characteristics in health research variables has fueled the growing interest of implementing network analysis, making it an indispensable research framework in medicine and epidemiology [@Luke2007].
+Past implementations of network analysis in public health mostly focused on transmission network, social network, and organizational network.
+Only recently, @Cavallo2012 demonstrated a novel framework to describe medication uses on a population level, i.e.
+drug prescription network (DPN), a term which later is coined by @Bazzoni2015.
+Network analysis offers an approach to capture the relationship among building blocks of a complex system.
+From a health system standpoint, polypharmacy is a prescription of multiple drug combinations which can be further evaluated as a network [@Miglio2021].
+DPN is a complex and dynamic system that may change overtime, specifically also in drug prescribed for mental disorders.
+
 In psychiatry, polypharmacy is defined as a patient with at least two concurrent psychiatric medications [@Shrivastava2013].
@@
 Finally, total polypharmacy is the total count of all medications used by a patient, both psychopharmaca and other classes alike [@Shrivastava2013].
-For policymakers, differences in defining polypharmacy pose a challenge to design a surveillance system [@Sirois2016].
+For policymakers, differences in defining polypharmacy pose a challenge to design a monitoring system [@Sirois2016].
 
-Surveilling polypharmacy regimens requires a holistic approach since drug prescription highly depends on the physician's prescribing habits [@Shrivastava2013], patient-physician relationship, and pharmaceutical market, which all bear an interplay with the decision-making process [@Cavallo2012].
-A holistic polypharmacy surveillance system needs to describe the importance of polypharmacy by incorporating both qualitative and quantitative measures [@Sirois2016].
+Monitoring polypharmacy regimens requires a holistic approach since drug prescription highly depends on the physician's prescribing habits [@Shrivastava2013], patient-physician relationship, and pharmaceutical market, which all bear an interplay with the decision-making process [@Cavallo2012].
+A holistic polypharmacy monitoring system needs to describe the importance of polypharmacy by incorporating both qualitative and quantitative measures [@Sirois2016].
 Quantitatively attributing importance to each medication is challenging, accounting for polypharmacy as a complex and interlinked medication uses.
-To reduce the complexity, graph theory offers a complementary approach by analyzing polypharmacy as a drug prescription network (DPN).
+To reduce the complexity, graph theory offers a complementary approach by analyzing polypharmacy as a DPN.
 Transforming prescription registry into a DPN has been previously investigated, where DPN-based approach represented the general trend in co-prescription [@Cavallo2012; @Bazzoni2015].
@@
 Following up @Cavallo2012 and @Bazzoni2015, we hypothesize that eigenvector centrality as a measure of relative importance is attributable to indicate polypharmacy.
-Our investigation showcases eigenvector centrality as a quantitative indicator of polypharmacy to promote a systematic public health surveillance system.
+Our investigation showcases eigenvector centrality as a quantitative indicator of polypharmacy to promote a systematic public health monitoring system.
 

### 2024-08-10 docs/article.qmd
Add descriptive tables on daily number of claims

@@
   elsevier-pdf:
+    keep-tex: true
     include-in-header:
@@
 
-The relational characteristics in health research variables has fueled the growing interest of implementing network analysis, making it an indispensable research framework in medicine and epidemiology [@Luke2007].
+The relational characteristics in health research variables have fueled the growing implementation of network analysis, making it an indispensable research framework in medicine and epidemiology [@Luke2007].
 Past implementations of network analysis in public health mostly focused on transmission network, social network, and organizational network.
@@
 drug prescription network (DPN), a term which later is coined by @Bazzoni2015.
-Network analysis offers an approach to capture the relationship among building blocks of a complex system.
-From a health system standpoint, polypharmacy is a prescription of multiple drug combinations which can be further evaluated as a network [@Miglio2021].
-DPN is a complex and dynamic system that may change overtime, specifically also in drug prescribed for mental disorders.
+Network analysis and graph theory offer an approach to model the relationship among building blocks of a complex system.
+From a complex system standpoint, polypharmacy is a prescription of multiple drug combinations which can be modelled as a network [@Miglio2021].
+DPN captures a complex and dynamic system that may vary overtime, which is highly relevant to drug prescribed for mental disorders.
 
@@
 Quantitatively attributing importance to each medication is challenging, accounting for polypharmacy as a complex and interlinked medication uses.
-To reduce the complexity, graph theory offers a complementary approach by analyzing polypharmacy as a DPN.
+To adequately address the complexity, network analysis is a viable framework for analyzing polypharmacy.
 Transforming prescription registry into a DPN has been previously investigated, where DPN-based approach represented the general trend in co-prescription [@Cavallo2012; @Bazzoni2015].
@@
 The cyclical patterns are further explained in our supplementary material.
-@tbl-desc shows the total number of claim for each medication class alongside the distribution of DDD and its weight.
+@tbl-desc shows the number of prescriptions for each medication class alongside the distribution of DDD and its weight.
 
-```{r tbl-desc}
-#| tbl-cap: Descriptive statistics of prescription data from 2018 to 2022, ordered by the number of claim
+```{r tbl-overview-patient}
+#| tbl-cap: "Number of participating patients with at least one claim of antidepressants or anxiolytics from 2018 to 2022"
 
-tar_read(res_tbl_stat) %>%
-  dplyr::arrange(-n_claim) %>%
+tar_read(res_tbl_patient) |>
   dplyr::mutate(
-    "mean_sd_dose"      = sprintf("%.2f [%.2f]", dose_mean, dose_sd),
-    "median_IQR_dose"   = sprintf("%.2f [%.2f]", dose_median, dose_IQR),
-    "mean_sd_weight"    = sprintf("%.2f [%.2f]", weight_mean, weight_sd),
-    "median_IQR_weight" = sprintf("%.2f [%.2f]", weight_median, weight_IQR),
-    "range_dose"        = sprintf("%.2f - %.2f", dose_min, dose_max),
-    "range_weight"      = sprintf("%.2f - %.2f", weight_min, weight_max)
-  ) %>%
-  subset(select = c(group, n_claim, mean_sd_dose, median_IQR_dose, range_dose, mean_sd_weight)) %>%
-  flextable::flextable() %>%
+    "year"       = as.character(year),
+    "Total"      = n_male + n_female,
+    "male"       = sprintf("%s (%s)", prettyNum(n_male,   big.mark = ","), scales::percent(p_male)),
+    "female"     = sprintf("%s (%s)", prettyNum(n_female, big.mark = ","), scales::percent(p_female)),
+    "male_age"   = sprintf("%.2f (%.2f)", age_male, age_sd_male),
+    "female_age" = sprintf("%.2f (%.2f)", age_female, age_sd_female)
+  ) |>
+  dplyr::select(year, male, female, Total, male_age, female_age) |>
+  flextable::flextable() |>
   flextable::set_header_labels(
-    group           = "",
-    n_claim         = "Claim",
-    mean_sd_dose    = "Mean [SD]",
-    median_IQR_dose = "Median [IQR]",
-    range_dose      = "Range",
-    mean_sd_weight  = "Mean [SD]"
-  ) %>%
+    year       = "Year",
+    male       = "Male",
+    female     = "Female",
+    male_age   = "Male",
+    female_age = "Female"
+  ) |>
   flextable::add_header_row(
-    values    = c("", "Defined Daily Dose", "Weight"),
-    colwidths = c(2, 3, 1),
+    values    = c("", "Number of Patients (%)", "Mean Age (SD)"),
+    colwidths = c(1, 3, 2),
     top       = TRUE
-  ) %>%
-  flextable::align(align = "center", part = "all") %>%
-  flextable::align(j = 1, align = "left", part = "body") %>%
-  #flextable::font(fontname = "Times", part = "all") %>%
-  flextable::fontsize(size = 7, part = "all") %>%
+  ) |>
+  flextable::align(align = "center", part = "all") |>
+  flextable::align(j = 1, align = "left", part = "all") |>
+  #flextable::font(fontname = "Times", part = "all") |>
+  flextable::fontsize(size = 7, part = "all") |>
+  flextable::autofit(add_w = 0, add_h = 0) |>
+  flextable::line_spacing(space = 0.7, part = "all")
+
+```
+
+```{r tbl-overview-daily}
+#| tbl-cap: "Daily prescription from 2018 to 2022 among patients with at least one claim of antidepressants or anxiolytics"
+
+res_tbl_overview$overview |>
+  dplyr::mutate(
+    "mean_sd" = sprintf("%s (%.2f)", prettyNum(mean_claim, big.mark = ","), sd_claim),
+    "median_IQR" = sprintf("%s (%.2f)", prettyNum(median_claim, big.mark = ","), IQR_claim),
+    "Range" = sprintf("%s - %s", prettyNum(min_claim, big.mark = ","), prettyNum(max_claim, big.mark = ","))
+  ) |>
+  dplyr::select(day, mean_sd, median_IQR, Range) |>
+  flextable::flextable() |>
+  flextable::set_header_labels(
+    day = "Day",
+    mean_sd = "Mean (SD)",
+    median_IQR = "Median (IQR)"
+  ) |>
+  flextable::add_header_row(
+    values    = c("", "Number of Claims"),
+    colwidths = c(1, 3),
+    top       = TRUE
+  ) |>
+  flextable::align(align = "center", part = "all") |>
+  flextable::align(j = 1, align = "left", part = "all") |>
+  #flextable::font(fontname = "Times", part = "all") |>
+  flextable::fontsize(size = 7, part = "all") |>
+  flextable::autofit(add_w = 0, add_h = 0) |>
   flextable::line_spacing(space = 0.7, part = "all")
@@
 
+```{r tbl-desc}
+#| tbl-cap: Descriptive statistics of prescription data from 2018 to 2022, ordered by Eigenvector centrality as an indicator of nodal importance
+
+tar_read(res_recon_stat) |>
+  dplyr::arrange(-eigen_mean) |>
+  dplyr::mutate(
+    "mean_sd_eigen"     = sprintf("%.3f [%.3f]", eigen_mean, eigen_sd),
+    "median_IQR_eigen"  = sprintf("%.3f [%.3f]", eigen_median, eigen_IQR),
+    "mean_sd_dose"      = sprintf("%.2f [%.2f]", dose_mean, dose_sd),
+    "median_IQR_dose"   = sprintf("%.2f [%.2f]", dose_median, dose_IQR),
+    "mean_sd_weight"    = sprintf("%.2f [%.2f]", weight_mean, weight_sd),
+    "median_IQR_weight" = sprintf("%.2f [%.2f]", weight_median, weight_IQR),
+    "range_dose"        = sprintf("%.2f - %.2f", dose_min, dose_max),
+    "range_weight"      = sprintf("%.2f - %.2f", weight_min, weight_max)
+  ) |>
+  subset(select = c(group, n_claim, mean_sd_eigen, mean_sd_dose, median_IQR_dose, mean_sd_weight)) |>
+  flextable::flextable() |>
+  flextable::set_header_labels(
+    group            = "",
+    n_claim          = "Claim",
+    mean_sd_eigen    = "Mean [SD]",
+    mean_sd_dose     = "Mean [SD]",
+    median_IQR_dose  = "Median [IQR]",
+    mean_sd_weight   = "Mean [SD]"
+  ) |>
+  flextable::add_header_row(
+    values    = c("", "Importance", "Defined Daily Dose", "Weight"),
+    colwidths = c(2, 1, 2, 1),
+    top       = TRUE
+  ) |>
+  flextable::align(align = "center", part = "all") |>
+  flextable::align(j = 1, align = "left", part = "body") |>
+  #flextable::font(fontname = "Times", part = "all") |>
+  flextable::fontsize(size = 7, part = "all") |>
+  flextable::autofit(add_w = 0, add_h = 0) |>
+  flextable::line_spacing(space = 0.7, part = "all")
+
+```
+
 ```{r fig-hi-eigen}
@@
 
-tar_read(plt_hi_eigen)
+tar_read(plt_hi_eigen_box)
 
@@
 - Cut-off threshold of polypharmacy should be justified by the risk of deleterious health outcomes
-- An ideal surveillance system should describe the importance of polypharmacy
+- An ideal monitoring system should describe the importance of polypharmacy
 

### 2024-08-10 _targets.R

@@ -47,6 +47,7 @@ list(
   # Describe the summary statistics
   tar_target(res_tbl_overview, overviewData(tbl_concat)),
   tar_target(res_tbl_stat, summarizeStat(tbl_concat)),
+  tar_target(res_tbl_patient, readr::read_csv("data/processed/iadb-desc/patient.csv")),
 
   # Generate graph objects from the split ATC data frame
   tar_target(

### 2024-08-10 src/R/report.R

@@ -101,11 +101,21 @@ overviewData <- function(tbl_concat) {
   #' @return A tidy descriptive overview table
   require("tsibble")
 
+  days <- c(
+    "Monday",
+    "Tuesday",
+    "Wednesday",
+    "Thursday",
+    "Friday",
+    "Saturday",
+    "Sunday"
+  )
+
   tbl <- tbl_concat |>
     dplyr::filter(date >= "2018-01-01", date <= "2022-12-31") |>
     dplyr::mutate(
       "date" = as.Date(date),
-      "day"  = weekdays(date),
+      "day"  = weekdays(date) |> factor(levels = days),
       "week" = tsibble::yearweek(date)
     )
 
@@ -148,7 +158,9 @@ mergeReconSummary <- function(ts_recon, res_tbl_stat) {
       "eigen_mean"   = mean(eigen),
       "eigen_sd"     = sd(eigen),
       "eigen_median" = median(eigen),
-      "eigen_IQR"    = IQR(eigen)
+      "eigen_IQR"    = IQR(eigen),
+      "eigen_lo"     = eigen_mean - 1.96 * eigen_sd / sqrt(dplyr::n()),
+      "eigen_hi"     = eigen_mean + 1.96 * eigen_sd / sqrt(dplyr::n())
     )
 
   tbl <- dplyr::inner_join(res_tbl_stat, ts_stat, by = "group")

### 2024-08-14 docs/abstract/_abstract-full.qmd
Incorporate revision suggested by Spyros

@@
 **Background:**
-The implementation of network analysis in medicine and epidemiology started to gain popularity.
-A network-based approach captures the relationships of the building blocks of a complex system.
-Drug co-prescription is a complex issue presenting with one-to-many relationships that may change over time, especially also in mental disorders.
+Networks have been used in different scientific fields to model complex systems.
+In medicine and epidemiology, drug prescription networks (DPN) have been proposed as a modeling tool for studying the temporal dynamics of medication distribution and consumption within a population.
 
 **Objectives:**  
-Evaluate the temporal relationships of drug treatment for mood disorders with other drug therapies in a pharmacy dispensing database.
+Evaluate the structural properties of temporal DPNs that are constructed from the observed daily co-prescriptions between treatments for mental health problems and other drug therapies in a pharmacy dispensing database.
 
 **Methods:**
-Exploratory temporal network analysis was performed using the University of Groningen prescription database, IADB.nl.
+For  exploratory time series analysis, and network construction, we utilized the IADB.nl database that collects prescriptions from 128 pharmacies in the Netherlands.
 A closed cohort with at least one prescription of anxiolytics/antidepressants dispensed anywhere from 2018 to 2022 was extracted.
 The drug prescription was evaluated daily using anatomical therapeutic chemical (ATC) classification, where psychopharmaca was evaluated at ATC level 4, drugs for the nervous system at ATC level 3, and other medications at ATC level 1, distinguished into a total of 24 therapeutic medication classes.
-A drug prescription network was constructed as an undirected graph to capture dose-adjusted co-prescription.
-Eigenvector centrality ($c_e$) was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
+Symmetric daily dose-adjusted co-prescriptions were used to construct time-varying DPNs as undirected graphs.
+Subsequently, eigenvector centrality ($c_e$) was computed as a measure of relative nodal importance, which reflects the degree of medication concurrence in a network.
 The number of prescriptions ($n_c$), number of patients, claim-to-patient ratio, and eigenvector centrality were extracted as weekly-aggregated time-series data.

### 2024-08-14 docs/article.qmd
Narrate the main findings

@@
 title: >
-  A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses
+  A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands 2018-2022
 
@@
       cite-style: authoryear
-  docx: default
+  docx:
+    pandoc-options: ["--mathml"]
 
@@
 IADB recorded `r n_patient` patients having at least one prescription of antidepressants or anxiolytics within five years of data extraction.
-The highest average of prescription claim occurred on `r hi_claim$day`, with $\bar{x}$ = `r hi_mean` [`r hi_claim$sd_claim`].
-Meanwhile, the lowest average of claim occurred on `r lo_claim$day`, with $\bar{x}$ = `r lo_mean` [`r lo_claim$sd_claim`].
-A large margin of difference between the highest and lowest average number of claim implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in figure [-@fig-period-day].
-The cyclical patterns are further explained in our supplementary material.
-@tbl-desc shows the number of prescriptions for each medication class alongside the distribution of DDD and its weight.
+@tbl-overview-patient depicts the dynamics of the population from 2018 to 2022.
+The ratio of male to female did not vary by a large margin, and the average age steadily increased over the year.
+These findings imply that the cohort stays relatively stable overtime without any indication of sudden demographic changes.
 
@@
 ```
+
+The highest average of prescription claim occurred on `r hi_claim$day`, with an average of `r hi_mean` [SD: `r hi_claim$sd_claim`] prescriptions.
+Meanwhile, the lowest average of claim occurred on `r lo_claim$day`, with an average of `r lo_mean` [SD: `r lo_claim$sd_claim`] prescriptions.
+A large margin of difference between the highest and lowest average number of claim implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in table [-@tbl-overview-daily] and figure [-@fig-period-day].
+The cyclical patterns are further explained in our supplementary material.
+@tbl-desc shows the number of prescriptions for each medication class alongside the distribution of DDD and its weight.
 
@@
 @fig-ssa depicts the decomposition result of the number of claim time-series in antidepressants.
-SSA-based decomposition separates the trend from its oscillating functions, as shown in the lower half of the plot.
-The trend explains roughly 90% of the variability, and oscillating functions explain 10%.
-The first two oscillating functions, F1 and F2, captured most of the variability in a series compared to the rest of the functions.
-
-{{< pagebreak >}}
+SSA-based decomposition separates the trend from its harmonics, as shown in the lower half of the plot.
+The trend explains roughly 90% of the variability, and harmonics explain 10%.
+The first two harmonics, F1 and F2, captured most of the variability in a series compared to the rest of it.
 
@@
 
-{{< pagebreak >}}
+## Relative importance score
 
-## Relative importance score
+```{r}
+
+tar_load(res_recon_stat)
+
+antidepressants <- res_recon_stat %>% subset(.$group == "Antidepressants")
+anxiolytics     <- res_recon_stat %>% subset(.$group == "Anxiolytics")
+
+respiratory <- res_recon_stat %>% subset(.$group == "Respiratory")
+analgesics  <- res_recon_stat %>% subset(.$group == "Analgesics")
+
+reportMedClaim <- function(med_obj) {
+  res <- with(med_obj, prettyNum(n_claim, big.mark = ","))
+
+  return(res)
+}
+
+reportMedEigen <- function(med_obj) {
+  res <- with(med_obj, sprintf("%.4f [SD: %.4f]", eigen_mean, eigen_sd))
+
+  return(res)
+}
+
+diffMed <- function(med_obj1, med_obj2, FUN) {
+  med_rep1 <- FUN(med_obj1)
+  med_rep2 <- FUN(med_obj2)
+
+  res <- sprintf("%s vs %s", med_rep1, med_rep2)
+
+  return(res)
+}
+
+```
+
+Seven medications had a high relative importance as suggested by figure [-@fig-hi-eigen] and table [-@tbl-desc].
+It is notable that highly prescribed medications usually have a high eigenvector centrality as well, which is theoretically supported by equation [-@eq-eigen-centrality].
+However, despite higher prescription numbers (`r diffMed(antidepressants, respiratory, reportMedClaim)`), antidepressants had lower eigenvector centrality than medications for the respiratory system (`r diffMed(antidepressants, respiratory, reportMedEigen)`).
+We confirmed similar findings with anxiolytics, which had higher prescription numbers (`r diffMed(anxiolytics, analgesics, reportMedClaim)`) but lower eigenvector centrality (`r diffMed(anxiolytics, analgesics, reportMedEigen)`) than analgesics.
+The difference of eigenvector centrality became more pronounced as the number of prescriptions decreased.
 
@@
 
-tar_read(res_recon_stat) |>
+res_recon_stat |>
   dplyr::arrange(-eigen_mean) |>

### 2024-09-05 docs/article.qmd
Configure line spacing in flextable when rendering to LaTeX

@@
   flextable::autofit(add_w = 0, add_h = 0) |>
-  flextable::line_spacing(space = 0.7, part = "all")
+  flextable::set_table_properties(opts_pdf = list("arraystretch" = 1, "tabcolsep" = 0))
 

### 2024-09-05 docs/article.qmd
Report the descriptive polypharmacy category #25

@@
   flextable::autofit(add_w = 0, add_h = 0) |>
-  flextable::line_spacing(space = 0.7, part = "all")
+  flextable::set_table_properties(opts_pdf = list("arraystretch" = 1, "tabcolsep" = 0))
+
+```
+
+```{r tbl-res-poly}
+#| tbl-cap: Summary statistics of different psychiatric polypharmacy categories
+
+tar_read(res_tbl_poly) |>
+  dplyr::mutate(
+    "year" = as.character(year),
+    "mean_sd" = sprintf("%.2f [%.2f]", mean, sd),
+    "median_iqr" = sprintf("%.2f (%.2f)", median, IQR)
+  ) |>
+  dplyr::select(type:medication, sum, mean_sd) |>
+  tidyr::pivot_wider(names_from = type, values_from = c(sum, mean_sd)) |>
+  dplyr::select(year, medication, sum_same, sum_multi, mean_sd_same, mean_sd_multi, dplyr::contains("total")) |>
+  flextable::flextable() |>
+  flextable::set_header_labels(
+    year = "Year",
+    medication = "Medication",
+    sum_same = "Same-class",
+    sum_multi = "Multi-class",
+    mean_sd_same = "Same-class",
+    mean_sd_multi = "Multi-class",
+    sum_total = "N",
+    mean_sd_total = "Mean [SD]"
+  ) |>
+  flextable::add_header_row(
+    values    = c("", "Population Level (N)", "Per Person (Mean [SD])", "Total Polypharmacy"),
+    colwidths = c(2, 2, 2, 2),
+    top       = TRUE
+  ) |>
+  flextable::footnote(
+    i = 1,
+    j = c(3, 5),
+    ref_symbols = c("1", "2"),
+    part = "header",
+    value = flextable::as_paragraph(
+      c(
+        "The total occurrence of polypharmacy on the population level/perscription-day",
+        "The expected occurrence of polypharmacy per person/perscription-day",
+        "Prescription day is defined as the number of prescribed medication per day"
+      )
+    )
+  ) |>
+  flextable::align(align = "center", part = "all") |>
+  flextable::align(j = 1:2, align = "left", part = "all") |>
+  flextable::fontsize(size = 7, part = "all") |>
+  #flextable::font(fontname = "Times", part = "all") |>
+  flextable::width(j = c(1:8), c(1, rep(1.8, 7)), unit = "cm") |>
+  flextable::set_table_properties(opts_pdf = list("arraystretch" = 1, "tabcolsep" = 0))
 

### 2024-09-05 _targets.R

@@ -50,8 +50,8 @@ list(
 
   # Generate summary statistics for polypharmacy
   tar_map(
-    unlist = "FALSE",
-    values = data.frame("medication" = c("anxiolytics", "antidepressants")),
+    unlist = FALSE,
+    values = data.frame("medication" = c("Anxiolytics", "Antidepressants")),
     tar_target(
       res_tbl_poly,
       summarizePolypharmacy(sub_tbl_iadb_by_date, medication = medication),
@@ -59,6 +59,8 @@ list(
       iteration = "vector"
     )
   ),
+
+  tar_target(res_tbl_poly, catResPoly(res_tbl_poly_Antidepressants, res_tbl_poly_Anxiolytics, start_year = 2018)),
 
   # Describe the summary statistics
   tar_target(res_tbl_overview, overviewData(tbl_concat)),

### 2024-09-05 src/R/report.R

@@ -191,7 +191,8 @@ detectPolypharmacy <- function(atc_entry, medication = "antidepressants", type =
   # Clean and list all the ATC codes
   atc_list <- strsplit(atc_entry, split = ",") |>
     lapply(\(atc) gsub(x = atc, ";.*", "")) |>
-    unlist()
+    unlist() |>
+    unique() # Prevent counting the same medication more than once
 
   # Create a regex reference to categorize polypharmacy
   ref <- switch(
@@ -256,9 +257,54 @@ summarizePolypharmacy <- function(sub_tbl_iadb, ...) {
   # Generate the summary statistics
   tbl_poly_stat <- do.call(cbind, stats) |>
     set_colnames(names(FUNS)) |>
-    data.frame() %>%
+    data.frame() |>
+    tibble::add_column(..., .before = 1) %>%
     tibble::add_column("type" = rownames(.), .before = 1) |>
     tibble::tibble()
 
   return(tbl_poly_stat)
+}
+
+addYearToResPoly <- function(tbl_res_poly, start_year = 2018) {
+  #' Add Year
+  #'
+  #' Add year to a table containing polypharmacy statistics for multiple years.
+  #' Usually, the statistics is ordered by year ascendingly. It means that the
+  #' first row represents the earliest year in the dataset. Since the table
+  #' summary contains three measures per year, the added year is repeated three
+  #' times, resulting in $n \times 3$ row, where $n$ is the number of years
+  #' added.
+  #'
+  #' @param tbl_res_poly A tidy data frame representing the summary statistics
+  #' of polypharmacy
+  #' @param start_year The starting year to annotate
+  #' @return An annotated tidy data frame of the summary statistics
+
+  # Set the number of repetition and number of years
+  reps  <- 3
+  nyear <- round(nrow(tbl_res_poly) / reps)
+  years <- seq(start_year, length.out = nyear) |> rep(each = reps)
+
+  # Annotate years to the
+  tbl  <- tbl_res_poly |> tibble::add_column("year" = years, .after = 1)
+
+  return(tbl)
+}
+
+catResPoly <- function(..., start_year = 2018) {
+  #' Concatenate Polypharmacy Summary Tables
+  #'
+  #' Concatenate multiple polypharmacy summary tables generated by
+  #' `summarizePolypharmacy`
+  #'
+  #' @param ... Multiple tidy data frames representing the summary
+  #' statistics of polypharmacy
[…]

### 2024-11-06 docs/index.qmd
Plan the modelling procedures
Include the report directly to the index
This patch will avoid recursive file searching, which apparently introduces error when run with 'targets'.

@@
 
-::: {.content-visible when-meta="in.report"}
-{{< include exec-summary/_report.qmd >}}
+:::: {.content-visible when-meta="in.report"}
+
+## Analytical procedures
+
+{{< include exec-summary/_source-data.qmd >}}
+
+{{< include exec-summary/_preprocessing.qmd >}}
+
+{{< include exec-summary/_measure-eigen.qmd >}}
+
+{{< include exec-summary/_descriptive.qmd >}}
+
+{{< include exec-summary/_seasonality.qmd >}}
+
+{{< include exec-summary/_arima.qmd >}}
+
+{{< include exec-summary/_spectral.qmd >}}
+
+## Highlighted findings
+
+{{< include exec-summary/_result-highlights.qmd >}}
+
+::: {.content-visible when-profile="summary"}
+
+\uselandscape
+
+## Excerpt on findings
+
+### Pair plot
+
+```{r}
+
+tar_read(plt_pair)[[17]]
+
+```
+
+### Dot plots on weekly time-series
+
+```{r}
+
+tar_read(plt_dot_week)[[1]]
+
+```
+
+### Differenced time-series on a weekly interval
+
+```{r}
+
+tar_read(plt_dot_diff_week)[[1]]
+
+```
+
+### Exploring seasonality within the number of medication claims
+
+```{r}
+
+tar_read(plt_period_month)[[1]]
+tar_read(plt_acf_diff_month)[[1]]
+tar_read(plt_pacf_diff_month)[[1]]
+
+```
+
+### Exploring ARIMA model
+
+```{r}
+
+tar_read(plt_arima_forecast_n_claim)[[17]]
+
+```
+
+### Decomposed time-series with SSA
+
+```{r}
+
+tar_read(plt_ssa_recon_n_claim)[[17]]
+
+```
+
+\normalpapersize
+
 :::
+
+::::
 
@@
 
+::: {.content-visible when-profile="models"}
+{{< include exec-summary/_models.qmd >}}
+:::
+
 :::: {.content-visible when-meta="in.report"}

### 2024-11-25 docs/exec-summary/_preprocessing.qmd
Draft the initial results
Explain the weighting method used for adjusting DDD #23

@@
 Each element in the upper and lower triangle represents co-prescriptions, while the diagonal of the matrix represents single prescriptions.
-All elements in the matrix is a tally of drug combination/single prescription in a population level claimed on a daily basis.
-The matrix follows a knowledge graph construct with a subject-predicate-object (s, p, o) triples, i.e.
-`Medication1-PrescribedAlongside-Medication2`.
-The knowledge graph is a representation of drug prescription network (DPN), where the edge (predicate) is the number of concurrency.
+All elements in the matrix is a tally of drug combination/single prescription in the population claimed on a daily basis.
+The matrix follows a graph construct, where we can denote the row-to-column as `Medication1-PrescribedAlongside-Medication2`.
+The graph is a representation of drug prescription network (DPN), where the edge is the number of concurrency.
 In the original DPN, the edge weight was the number of claims by assuming that all of defined daily doses (DDD) were equal to 1 [@Cavallo2012].
-To account for augmentation polypharmacy, DDD provides further information due to the presence of a sub-dose medication, where DDD < 1 should be allowed.
-Naturally, an augmentation polypharmacy regimen should have a higher weight since this regimen is intended to increase the efficacy of the augmented medication [@Shrivastava2013].
-Therefore, weight was re-applied on the edges by dividing the number of claims by the DDD.
+However, not all medications were prescribed with DDD equals to 1, and discarding these entries would lead to loss of information.
+Therefore, we applied weights based on DDD, where the weight is the highest if DDD equals to 1, and gradually diminishes as it is getting further from 1.
+To adjust the weight, first we set the baseline weight as $\omega_B = 1$.
+Then, we calculated the weight based on the expected density of a normal distribution, where the expected value is $\mu = \omega_B$ and standard deviation is $\sigma = \frac{\omega_B}{3}$.
+The expected value was set to $\omega_B$ because we expect entries with DDD equals to 1.
+The standard deviation was set to $\frac{\omega_B}{3}$ to represent an equidistant deviation from the expected value to 0.
+As a result, we obtained the weighted DDD as $\omega$.
+
+$$\omega = \frac{1}{\frac{\omega_B}{3} \sqrt{2 \pi}} e^{-\frac{1}{2}\left(\frac{DDD - \omega_B}{\omega_B/3}\right)^2}$$ {#eq-weighted-DDD}
 
@@
   \begin{bmatrix}
-  \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_1}{DDD_1} + \frac{n_N}{DDD_N} \right) \\
+  \frac{1}{2} \cdot \left(\omega_1 + \omega_1 \right) & \dots & \frac{1}{2} \cdot \left(\omega_1 + \omega_N \right) \\
   \vdots & \ddots & \vdots \\
-  \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_1}{DDD_1} \right) & \dots & \frac{1}{2} \cdot \left(\frac{n_N}{DDD_N} + \frac{n_N}{DDD_N} \right) \\
+  \frac{1}{2} \cdot \left(\omega_N + \omega_1 \right) & \dots & \frac{1}{2} \cdot \left(\omega_N + \omega_N \right) \\
   \end{bmatrix}

### 2024-11-26 docs/supplementary.qmd
Move the daily-variation figure to the supplementary #24

--- 2024-08-14 docs/article.qmd
@@
----
-title: >
-  A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands 2018-2022
-
-format:
-  elsevier-pdf:
-    keep-tex: true
-    include-in-header:
-      file: _header.tex
-    journal:
-      formatting: review
-      cite-style: authoryear
-  docx:
-    pandoc-options: ["--mathml"]
-
-funding: "The author(s) received no specific funding for this work."
-keywords:
-  - Graph Theory
-  - Prescription Registry
-  - Polypharmacy
-  - Mental Health   
-  - Public Health Monitoring
-
-metadata-files:
-  - _author.yml
-  - _abstract.yml
-  - _knitr-bib.yml
-
-in:
-  article: true
----
-
 ```{r}
@@
 options(digits = 2, scipen = 999)
-
-```
-
-# Introduction
-
-::: {.content-hidden}
-
-Mental disorders are a common comorbidity affecting nearly two billion people worldwide with a prevalence that remains relatively stable overtime [@Kessler2009; @Steel2014; @Richter2019].
-Having a chronic mental disorder is one factor which may lead to polypharmacy, *viz.* the use of multiple medications in treating complex clinical conditions [@Halli2019].
-Polypharmacy is a prominent issue in modern medicine with a prevalence of 37% [@Delara2022], mainly attributed to the presence of multiple long-term comorbidity, i.e.
-multimorbidity, in the population.
-In resolving multimorbidity, the general edict of the evidence-based medicine is to follow an established clinical guideline to treat a particular clinical condition.
-However, these guidelines are tailored for a single disease without considering multimorbidity, resulting in the use of one or more medications per condition, leading to polypharmacy regimens for one patient with multiple conditions [@Molokhia2017].
-Albeit clinical improvements offered by polypharmacy, risks of drug interaction and adverse effects also become more apparent, engendering a public health issue.
-Hitherto, no indicator of polypharmacy has been universally standardized [@Sirois2016], where the number of prescription is merely relied on as a crude metric [@Molokhia2017; @Delara2022].
-
-:::
-
-The relational characteristics in health research variables have fueled the growing implementation of network analysis, making it an indispensable research framework in medicine and epidemiology [@Luke2007].
-Past implementations of network analysis in public health mostly focused on transmission network, social network, and organizational network.
-Only recently, @Cavallo2012 demonstrated a novel framework to describe medication uses on a population level, i.e.
-drug prescription network (DPN), a term which later is coined by @Bazzoni2015.
-Network analysis and graph theory offer an approach to model the relationship among building blocks of a complex system.
-From a complex system standpoint, polypharmacy is a prescription of multiple drug combinations which can be modelled as a network [@Miglio2021].
-DPN captures a complex and dynamic system that may vary overtime, which is highly relevant to drug prescribed for mental disorders.
-
-In psychiatry, polypharmacy is defined as a patient with at least two concurrent psychiatric medications [@Shrivastava2013].
-With a prevalence between 13-90%, psychiatric polypharmacy manifests in five categories, namely same-class, multi-class, adjunctive, augmentation, and total polypharmacy.
-Same-class polypharmacy is the use of multiple medications from the same class.
-Multi-class polypharmacy is the use of multiple medications from different classes indicated for the same symptom cluster.
-Adjunctive polypharmacy is the use of additional medications to treat side effects due to other medications.
-Augmentation polypharmacy is the use of full-dose and sub-dose medications from a different class for the same symptom cluster.
-Finally, total polypharmacy is the total count of all medications used by a patient, both psychopharmaca and other classes alike [@Shrivastava2013].
-For policymakers, differences in defining polypharmacy pose a challenge to design a monitoring system [@Sirois2016].
-
-Monitoring polypharmacy regimens requires a holistic approach since drug prescription highly depends on the physician's prescribing habits [@Shrivastava2013], patient-physician relationship, and pharmaceutical market, which all bear an interplay with the decision-making process [@Cavallo2012].
-A holistic polypharmacy monitoring system needs to describe the importance of polypharmacy by incorporating both qualitative and quantitative measures [@Sirois2016].
-Quantitatively attributing importance to each medication is challenging, accounting for polypharmacy as a complex and interlinked medication uses.
-To adequately address the complexity, network analysis is a viable framework for analyzing polypharmacy.
-Transforming prescription registry into a DPN has been previously investigated, where DPN-based approach represented the general trend in co-prescription [@Cavallo2012; @Bazzoni2015].
-
-A DPN is constructed as a matrix which rows to columns represent pairs of medication being taken by a patient in a day.
-Since there is no limit for the number of rows and columns, a DPN can contain virtually every possible combination of polypharmacy regimens.
-A DPN is generalizable as a population aggregate by coalescing all single-patient DPN through matrix addition [@Cavallo2012].
-Constructing a DPN allows examining co-prescription dynamics in the population as graph measures, which is also attributable to each medication.
-One of such measures is graph centrality, where we calculate scores representing the number of co-medications, number of connecting paths, average distance, and relative importance [@Askar2021].
-The relative importance score is of particular interest to address concerns raised by @Sirois2016 and @Delara2022 regarding standardized quantitative indicator of polypharmacy.
-Relative importance, most commonly measured by eigenvector centrality, represents the connection to vital medications.
-A high eigenvector centrality in a DPN indicates more prescriptions with highly-prescribed medications.
-Following up @Cavallo2012 and @Bazzoni2015, we hypothesize that eigenvector centrality as a measure of relative importance is attributable to indicate polypharmacy.
-Our investigation showcases eigenvector centrality as a quantitative indicator of polypharmacy to promote a systematic public health monitoring system.
-
-::: {.content-hidden}
-> **"How do we implement a network analysis approach to quantitatively attribute polypharmacy?"**
-:::
-
-# Methods
-
-## Source of data
-
-{{< include exec-summary/_source-data.qmd >}}
-
-## Data pre-processing
-
-{{< include exec-summary/_preprocessing.qmd >}}
-
-## Measuring relative importance
-
-{{< include exec-summary/_measure-eigen.qmd >}}
-
-## Data analysis
-
-### Exploratory descriptive analysis
-
-{{< include exec-summary/_descriptive.qmd >}}
-
-### Exploring seasonality in the dataset
-
-{{< include exec-summary/_seasonality.qmd >}}
-
-### Decomposition with singular spectrum analysis
-
-{{< include exec-summary/_spectral.qmd >}}
-
-### Determining relative importance
-
-Since the sum of all eigenvector centralities $c_i$ in equation [-@eq-eigen-centrality] is equal to one, a network with similarly connected nodes will have an eigenvector centrality $c_i$ = $\frac{1}{n}$ for each node, where $n$ is the number of nodes.
-The value of $c_i = \frac{1}{n}$ is the expected eigenvector centrality in a densely connected network where connection $\mathcal{V}_{i, j}$ from node $\mathcal{V}_i$ to node $\mathcal{V}_j$ has the same probability for every node.
-Per the central limit theorem, the value $\frac{1}{n}$ can be parameterized as a mean of a normal distribution, where all instances of eigenvector centrality will follow the distribution, $c_i \sim \mathcal{N}(\mu, \sigma)$.
-A one-sample Student's T-test was performed to assess how much each eigenvector centrality differs from the expected values.
-As such, eigenvector centrality greater than $\frac{1}{n}$ can be considered high, and the value below it can be considered low.
-The p-values was corrected for a type-I error using Bonferroni method.
-
-# Results
-
-```{r}
-
-tar_load(res_tbl_overview)
-
-n_patient <- prettyNum(res_tbl_overview$total, big.mark = ",", scientific = FALSE)
-hi_claim <- res_tbl_overview$overview |> dplyr::slice_max(mean_claim)
-lo_claim <- res_tbl_overview$overview |> dplyr::slice_min(mean_claim)
-
-hi_mean <- prettyNum(hi_claim$mean_claim, big.mark = ",")
-lo_mean <- prettyNum(lo_claim$mean_claim, big.mark = ",")
-
-```
-
-IADB recorded `r n_patient` patients having at least one prescription of antidepressants or anxiolytics within five years of data extraction.
-@tbl-overview-patient depicts the dynamics of the population from 2018 to 2022.
-The ratio of male to female did not vary by a large margin, and the average age steadily increased over the year.
-These findings imply that the cohort stays relatively stable overtime without any indication of sudden demographic changes.
-
-```{r tbl-overview-patient}
-#| tbl-cap: "Number of participating patients with at least one claim of antidepressants or anxiolytics from 2018 to 2022"
-
-tar_read(res_tbl_patient) |>
-  dplyr::mutate(
-    "year"       = as.character(year),
-    "Total"      = n_male + n_female,
-    "male"       = sprintf("%s (%s)", prettyNum(n_male,   big.mark = ","), scales::percent(p_male)),
-    "female"     = sprintf("%s (%s)", prettyNum(n_female, big.mark = ","), scales::percent(p_female)),
-    "male_age"   = sprintf("%.2f (%.2f)", age_male, age_sd_male),
-    "female_age" = sprintf("%.2f (%.2f)", age_female, age_sd_female)
-  ) |>
-  dplyr::select(year, male, female, Total, male_age, female_age) |>
-  flextable::flextable() |>
-  flextable::set_header_labels(
-    year       = "Year",
-    male       = "Male",
-    female     = "Female",
-    male_age   = "Male",
-    female_age = "Female"
-  ) |>
-  flextable::add_header_row(
-    values    = c("", "Number of Patients (%)", "Mean Age (SD)"),
-    colwidths = c(1, 3, 2),
-    top       = TRUE
-  ) |>
-  flextable::align(align = "center", part = "all") |>
-  flextable::align(j = 1, align = "left", part = "all") |>
-  #flextable::font(fontname = "Times", part = "all") |>
-  flextable::fontsize(size = 7, part = "all") |>
-  flextable::autofit(add_w = 0, add_h = 0) |>
-  flextable::line_spacing(space = 0.7, part = "all")
-
-```
-
-The highest average of prescription claim occurred on `r hi_claim$day`, with an average of `r hi_mean` [SD: `r hi_claim$sd_claim`] prescriptions.
-Meanwhile, the lowest average of claim occurred on `r lo_claim$day`, with an average of `r lo_mean` [SD: `r lo_claim$sd_claim`] prescriptions.
-A large margin of difference between the highest and lowest average number of claim implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in table [-@tbl-overview-daily] and figure [-@fig-period-day].
-The cyclical patterns are further explained in our supplementary material.
-@tbl-desc shows the number of prescriptions for each medication class alongside the distribution of DDD and its weight.
-
-```{r tbl-overview-daily}
-#| tbl-cap: "Daily prescription from 2018 to 2022 among patients with at least one claim of antidepressants or anxiolytics"
-
-res_tbl_overview$overview |>
-  dplyr::mutate(
-    "mean_sd" = sprintf("%s (%.2f)", prettyNum(mean_claim, big.mark = ","), sd_claim),
-    "median_IQR" = sprintf("%s (%.2f)", prettyNum(median_claim, big.mark = ","), IQR_claim),
-    "Range" = sprintf("%s - %s", prettyNum(min_claim, big.mark = ","), prettyNum(max_claim, big.mark = ","))
-  ) |>
-  dplyr::select(day, mean_sd, median_IQR, Range) |>
-  flextable::flextable() |>
-  flextable::set_header_labels(
-    day = "Day",
-    mean_sd = "Mean (SD)",
-    median_IQR = "Median (IQR)"
-  ) |>
-  flextable::add_header_row(
-    values    = c("", "Number of Claims"),
-    colwidths = c(1, 3),
-    top       = TRUE
-  ) |>
-  flextable::align(align = "center", part = "all") |>
-  flextable::align(j = 1, align = "left", part = "all") |>
-  #flextable::font(fontname = "Times", part = "all") |>
-  flextable::fontsize(size = 7, part = "all") |>
-  flextable::autofit(add_w = 0, add_h = 0) |>
-  flextable::line_spacing(space = 0.7, part = "all")
 
@@
 ```
-
-## Time-series decomposition
-
-Using the weekly-aggregated data, we obtained decomposed series using an SSA-based approach.
-@fig-ssa depicts the decomposition result of the number of claim time-series in antidepressants.
-SSA-based decomposition separates the trend from its harmonics, as shown in the lower half of the plot.
-The trend explains roughly 90% of the variability, and harmonics explain 10%.
-The first two harmonics, F1 and F2, captured most of the variability in a series compared to the rest of it.
-
-```{r fig-ssa}
-#| fig-width: 16
-#| fig-height: 12
-#| fig-pos: H
-#| fig-cap: An example of time-series decomposition using singular spectrum analysis-based approach
-
-tar_read(plt_ssa_recon_n_claim)[[17]]
-
-```
-
-## Relative importance score
-
-```{r}
-
-tar_load(res_recon_stat)
-
-antidepressants <- res_recon_stat %>% subset(.$group == "Antidepressants")
-anxiolytics     <- res_recon_stat %>% subset(.$group == "Anxiolytics")
-
-respiratory <- res_recon_stat %>% subset(.$group == "Respiratory")
-analgesics  <- res_recon_stat %>% subset(.$group == "Analgesics")
-
-reportMedClaim <- function(med_obj) {
-  res <- with(med_obj, prettyNum(n_claim, big.mark = ","))
-
-  return(res)
-}
-
-reportMedEigen <- function(med_obj) {
-  res <- with(med_obj, sprintf("%.4f [SD: %.4f]", eigen_mean, eigen_sd))
-
-  return(res)
-}
-
-diffMed <- function(med_obj1, med_obj2, FUN) {
-  med_rep1 <- FUN(med_obj1)
-  med_rep2 <- FUN(med_obj2)
-
-  res <- sprintf("%s vs %s", med_rep1, med_rep2)
-
-  return(res)
-}
-
-```
-
-Seven medications had a high relative importance as suggested by figure [-@fig-hi-eigen] and table [-@tbl-desc].
-It is notable that highly prescribed medications usually have a high eigenvector centrality as well, which is theoretically supported by equation [-@eq-eigen-centrality].
-However, despite higher prescription numbers (`r diffMed(antidepressants, respiratory, reportMedClaim)`), antidepressants had lower eigenvector centrality than medications for the respiratory system (`r diffMed(antidepressants, respiratory, reportMedEigen)`).
-We confirmed similar findings with anxiolytics, which had higher prescription numbers (`r diffMed(anxiolytics, analgesics, reportMedClaim)`) but lower eigenvector centrality (`r diffMed(anxiolytics, analgesics, reportMedEigen)`) than analgesics.
-The difference of eigenvector centrality became more pronounced as the number of prescriptions decreased.
-
-```{r tbl-desc}
-#| tbl-cap: Descriptive statistics of prescription data from 2018 to 2022, ordered by Eigenvector centrality as an indicator of nodal importance
-
-res_recon_stat |>
-  dplyr::arrange(-eigen_mean) |>
-  dplyr::mutate(
-    "mean_sd_eigen"     = sprintf("%.3f [%.3f]", eigen_mean, eigen_sd),
-    "median_IQR_eigen"  = sprintf("%.3f [%.3f]", eigen_median, eigen_IQR),
-    "mean_sd_dose"      = sprintf("%.2f [%.2f]", dose_mean, dose_sd),
-    "median_IQR_dose"   = sprintf("%.2f [%.2f]", dose_median, dose_IQR),
-    "mean_sd_weight"    = sprintf("%.2f [%.2f]", weight_mean, weight_sd),
-    "median_IQR_weight" = sprintf("%.2f [%.2f]", weight_median, weight_IQR),
-    "range_dose"        = sprintf("%.2f - %.2f", dose_min, dose_max),
-    "range_weight"      = sprintf("%.2f - %.2f", weight_min, weight_max)
-  ) |>
-  subset(select = c(group, n_claim, mean_sd_eigen, mean_sd_dose, median_IQR_dose, mean_sd_weight)) |>
-  flextable::flextable() |>
-  flextable::set_header_labels(
-    group            = "",
-    n_claim          = "Claim",
-    mean_sd_eigen    = "Mean [SD]",
-    mean_sd_dose     = "Mean [SD]",
-    median_IQR_dose  = "Median [IQR]",
-    mean_sd_weight   = "Mean [SD]"
-  ) |>
-  flextable::add_header_row(
-    values    = c("", "Importance", "Defined Daily Dose", "Weight"),
-    colwidths = c(2, 1, 2, 1),
-    top       = TRUE
-  ) |>
-  flextable::align(align = "center", part = "all") |>
-  flextable::align(j = 1, align = "left", part = "body") |>
-  #flextable::font(fontname = "Times", part = "all") |>
-  flextable::fontsize(size = 7, part = "all") |>
-  flextable::autofit(add_w = 0, add_h = 0) |>
-  flextable::line_spacing(space = 0.7, part = "all")
-
-```
-
-```{r fig-hi-eigen}
-#| fig-cap: Clusters of medication with a higher eigenvector centrality, implying a higher relative importance in polypharmacy regimens
-#| fig-width: 9
-#| fig-height: 10
-
-tar_read(plt_hi_eigen_box)
-
-```
-
-# Discussion
-
-@Delara2022
-
-- The prevalence of polypharmacy in all medication classes is 37% [95% CI: 31-43%]
-- Difference of prevalence measure is due to different numerical thresholds, study setting, and publication year
-
-@Sirois2016
-
-- Problem of exposure: Polypharmacy can be defined as cumulative or simultaneous prescriptions
-- Cut-off threshold of polypharmacy should be justified by the risk of deleterious health outcomes
-- An ideal monitoring system should describe the importance of polypharmacy
-
-@Menditto2019
-
-- Although polypharmacy is mostly researched in geriatric patients, younger population are also at risk of inappropriate multiple medication uses
-
-@Shrivastava2013
-
-- Among diagnoses, polypharmacy is often found in patients with schizophrenia, schizotypal, and delusional disorder
-- Multi-class polypharmacy is the most common (20.9%), usually the combination of SSRI and benzodiazepine or TCA and benzodiazepine
-- Five factors associated with psychiatric polypharmacy:
-  - Scientific: Emphasis on biogenic amines roles in depression and schizophrenia expanded the early clinical evidence of psychotropic medications
-  - Clinical: Standardization attempt resulted in overlapping diagnoses with limited validity; poly-nosology an polypharmacy go hand-in-hand
-  - Economic: Pharmaceutical company influenced the demand of psychopharmaca uses
-  - Political: US FDA imposes minimal guidelines for drug approval only for specific conditions
-  - Cultural: Large cultural appetite for pharmacological treatments
-
-@Stassen2021
-
-- Attending psychiatrist is the main determinant of polypharmaca prescription
-- Previous medical history and case severity at baseline only play a minor role in polypharmaca
-- Adverse drug reaction in polypharmaca is 2-3 times higher compared to monotherapy, and not attributed to particular drug or drug combination; it implies that any drug and its combination can virtually trigger the side effect
-- No advantage of polypharmacy over monotherapy, suggesting that polypharmacy regimens are not equally suited for every patient
-
-@Molokhia2017
-
-- The alternative measure is pre-defined criteria, e.g. BEERS, STOPP, and START
-- Each additional medication contributes to 16% increased risk of errors
-
-@Cavallo2012
-
-- The weight is the number of time a pair of medications is prescribed together
-- The co-prescription network has a scale-free property, suggesting that the probability new links being formed is growing alongside the degree of the target node
-- The scale-free property of the network might be explained by the physician's prescribing habit: The physician tends to prescribe medications with known medications
-
-@Bazzoni2015
-
-- Drug-prescription network is highly dense and clustered at the global level
-- Drug-prescription network is organized into anatomically homogeneous modules at the local level
-
-# References

### 2024-11-26 docs/article.qmd
Move the daily-variation figure to the supplementary #24
Use scientific notation consistently

@@
 pkgs_load <- sapply(pkgs, library, character.only = TRUE)
-options(digits = 2, scipen = 999)
+options(digits = 2)
 
@@
 
-```{r fig-period-day}
-#| fig-width: 14
-#| fig-height: 5
-#| fig-cap: Daily cyclical pattern captured on a de-trended data
-
-tar_read(plt_period_day)[[1]]
-
-```
-
 ## Time-series decomposition
@@
 reportMedEigen <- function(med_obj) {
-  res <- with(med_obj, sprintf("%.4f [SD: %.4f]", eigen_mean, eigen_sd))
+  res <- with(med_obj, sprintf("%.2e [SD: %.2e]", eigen_mean, eigen_sd))
 
@@
   dplyr::mutate(
-    "mean_sd_eigen"     = sprintf("%.3f [%.3f]", eigen_mean, eigen_sd),
-    "median_IQR_eigen"  = sprintf("%.3f [%.3f]", eigen_median, eigen_IQR),
-    "mean_sd_dose"      = sprintf("%.2f [%.2f]", dose_mean, dose_sd),
-    "median_IQR_dose"   = sprintf("%.2f [%.2f]", dose_median, dose_IQR),
-    "mean_sd_weight"    = sprintf("%.2f [%.2f]", weight_mean, weight_sd),
-    "median_IQR_weight" = sprintf("%.2f [%.2f]", weight_median, weight_IQR),
-    "range_dose"        = sprintf("%.2f - %.2f", dose_min, dose_max),
-    "range_weight"      = sprintf("%.2f - %.2f", weight_min, weight_max)
+    "mean_sd_eigen"     = sprintf("%.2e [%.2e]", eigen_mean, eigen_sd),
+    "median_IQR_eigen"  = sprintf("%.2e [%.2e]", eigen_median, eigen_IQR),
+    "mean_sd_dose"      = sprintf("%.2e [%.2e]", dose_mean, dose_sd),
+    "median_IQR_dose"   = sprintf("%.2e [%.2e]", dose_median, dose_IQR),
+    "mean_sd_weight"    = sprintf("%.2e [%.2e]", weight_mean, weight_sd),
+    "median_IQR_weight" = sprintf("%.2e [%.2e]", weight_median, weight_IQR),
+    "range_dose"        = sprintf("%.2e - %.2e", dose_min, dose_max),
+    "range_weight"      = sprintf("%.2e - %.2e", weight_min, weight_max)
   ) |>
-  subset(select = c(group, n_claim, mean_sd_eigen, mean_sd_dose, median_IQR_dose, mean_sd_weight)) |>
+  subset(select = c(group, n_claim, mean_sd_eigen, mean_sd_dose, mean_sd_weight)) |>
   flextable::flextable() |>
@@
     n_claim          = "Claim",
-    mean_sd_eigen    = "Mean [SD]",
-    mean_sd_dose     = "Mean [SD]",
-    median_IQR_dose  = "Median [IQR]",
-    mean_sd_weight   = "Mean [SD]"
+    mean_sd_eigen    = "Importance",
+    mean_sd_dose     = "DDD",
+    mean_sd_weight   = "Weight"
   ) |>
   flextable::add_header_row(
-    values    = c("", "Importance", "Defined Daily Dose", "Weight"),
-    colwidths = c(2, 1, 2, 1),
+    values    = c("", "Mean [SD]"),
+    colwidths = c(2, 3),
     top       = TRUE

### 2024-12-04 docs/abstract/_abstract-full.qmd
Incorporate suggestion from Spyros

@@
 Networks have been used in different scientific fields to model complex systems.
-In medicine and epidemiology, drug prescription networks (DPN) have been proposed as a modeling tool for studying the temporal dynamics of medication distribution and consumption within a population.
+In medicine and epidemiology, drug prescription networks (DPN) have been proposed as a modeling tool for studying the temporal dynamics of medication co-prescription within a population.
 
 **Objectives:**  
-Evaluate the structural properties of temporal DPNs that are constructed from the observed daily co-prescriptions between treatments for mental health problems and other drug therapies in a pharmacy dispensing database.
+This study aims to assess the structural characteristics of temporal DPNs, derived from daily co-prescriptions between treatments for mental health conditions and other therapeutic drug classes, as recorded in pharmacy dispensing database.
 

### 2024-12-04 docs/article.qmd
Incorporate suggestion from Spyros

@@
 
-The relational characteristics in health research variables have fueled the growing implementation of network analysis, making it an indispensable research framework in medicine and epidemiology [@Luke2007].
+The inherently complex nature of health-related phenomena have fueled the growing implementation of network analysis, making it an indispensable research framework in medicine and epidemiology [@Luke2007].
 Past implementations of network analysis in public health mostly focused on transmission network, social network, and organizational network.
@@
 From a complex system standpoint, polypharmacy is a prescription of multiple drug combinations which can be modelled as a network [@Miglio2021].
-DPN captures a complex and dynamic system that may vary overtime, which is highly relevant to drug prescribed for mental disorders.
+DPN can capture the complex relationships of a system that may vary overtime, which is highly relevant to drug prescribed for mental disorders.
 
@@
 Quantitatively attributing importance to each medication is challenging, accounting for polypharmacy as a complex and interlinked medication uses.
-To adequately address the complexity, network analysis is a viable framework for analyzing polypharmacy.
-Transforming prescription registry into a DPN has been previously investigated, where DPN-based approach represented the general trend in co-prescription [@Cavallo2012; @Bazzoni2015].
+Network analysis is a viable framework for analyzing polypharmacy.
+Constructing DPNs from drug prescription data has been previously investigated, where DPN-based approach represented the general trend in co-prescription [@Cavallo2012; @Bazzoni2015].
 
@@
 
+## Graph theory
+
+- What characterizes a graph?
+- When a graph is directed/undirected?
+- Intuition behind an adjacency matrix
+
 ## Data pre-processing
@@
 {{< include exec-summary/_preprocessing.qmd >}}
+
+## Centrality measures in graph theory
+
+- Discuss about centrality measures in social network analysis
+- What can centrality measures offer in analyzing polypharmacy networks
+- Check the structure of complex network: theory and application by Estrada
 
@@
 Since the sum of all eigenvector centralities $c_i$ in equation [-@eq-eigen-centrality] is equal to one, a network with similarly connected nodes will have an eigenvector centrality $c_i$ = $\frac{1}{n}$ for each node, where $n$ is the number of nodes.
-The value of $c_i = \frac{1}{n}$ is the expected eigenvector centrality in a densely connected network where connection $\mathcal{V}_{i, j}$ from node $\mathcal{V}_i$ to node $\mathcal{V}_j$ has the same probability for every node.
+The value of $c_i = \frac{1}{n}$ is the expected eigenvector centrality in a densely connected network where connection $(i, j) \in \mathcal{E}$ from node $\mathcal{V}_i$ to node $\mathcal{V}_j$ has the same probability for every node.
 Per the central limit theorem, the value $\frac{1}{n}$ can be parameterized as a mean of a normal distribution, where all instances of eigenvector centrality will follow the distribution, $c_i \sim \mathcal{N}(\mu, \sigma)$.

### 2024-12-04 docs/exec-summary/_spectral.qmd
Draft an initial report using Elsevier template
Incorporate suggestion from Spyros

--- 2024-02-12 docs/exec-summary/spectral.qmd
@@
+::: {.content-visible unless-meta="in.article"}
 ### Decomposition with singular spectrum analysis
+:::
 
@@
 Singular spectrum analysis (SSA) is a powerful non-parametric technique by leveraging Hankel matrix as a higher-dimensional embedding of the time-series.
-The resulting Hankel matrix $X$ has the size of $L \times K$, where $L$ represents the lag term, i.e.
-a window length to perform embedding For a weekly data with a hypothesized yearly seasonality, the $L$ is set as 52.
-In theory, the number of $L$ should be between the range of $2 \leq L \leq \frac{N}{2}$, where $N$ is the total length of the time-series.
+The resulting Hankel matrix $X$ has the size of $L \times K$, where $L$ represents the lag term.
+The lag term is the length of data point in a time-series being taken to construct the higher-dimensional embedding.
+For a weekly data with a hypothesized yearly seasonality, the $L$ is set as 52, representing the number of week in a year.
+In theory, the number of $L$ should be between the range of $2 \leq L \leq \frac{N}{2}$, where $N$ is the total length of the time-series [@Golyandina2020].
 
 $$
+\tau =
+\stackrel{\textrm{Time-series data}}{
+  \begin{bmatrix}
+  x_1 & x_2 & \cdots & x_{N-1} & x_N \\
+  \end{bmatrix}
+}
+\quad \to \quad
 X =
@@
 With a matrix $S = X \cdot X^T$, we can extract an eigenvalue $\lambda \ni \{\lambda_1 \geq \dots \geq \lambda_L\}$, where each $\lambda_i$ is a non-negative integer.
-Similarly, we can define $U$ as the eigenvectors of matrix $S$ corresponding to eigenvalues $\lambda$.
+Similarly, we can define $U \ni \{U_1, \dots, U_L\}$ as the eigenvectors of matrix $S$ corresponding to eigenvalues $\lambda$.
 Afterwards, we can extract factor vectors $V$ where the corresponding $V_i = X^T \frac{U_i}{\sqrt{\lambda_i}}$.

### 2024-12-05 docs/article.qmd
Explain graph in mathematics

@@
 
-- What characterizes a graph?
-- When a graph is directed/undirected?
-- Intuition behind an adjacency matrix
+Graph theory is a formal concept depicting connections among objects.
+A graph consists of nodes and edges, denoted as $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
+The nodes form a finite set, $\mathcal{V} = \{\mathcal{v}_1, \mathcal{v}_2, \dots, \mathcal{v}_n$, while the edges $\mathcal{E}$ represent the connection between these nodes.
+In a directed graph, the edge is an ordered pair of nodes, $(\mathcal{v}_i, \mathcal{v}_j) \in \mathcal{E}$, where the order of $i, j$ matters.
+Directed graphs may contain self connections $(\mathcal{v}_i, \mathcal{v}_i) \in \mathcal{E}$.
+In an undirected graph, the edge is an unordered set of nodes $\{\mathcal{v}_i, \mathcal{v}_j\} \in \mathcal{E}$, where the order of $i, j$ does not matter.
+Typically, undirected graphs do not contain self connections $\{\mathcal{v}_i, \mathcal{v}_i\} \notin \mathcal{E}$ [@estrada2012structure].
+
+A graph can be represented as an adjacency matrix $A$.
+The adjacency matrix $A$ has dimensions of $|\mathcal{V}| \times |\mathcal{V}|$, and $|\mathcal{V}|$ is the number of nodes in a graph.
+Each element of $a_{ij}$ is the edge: $(\mathcal{v}_i, \mathcal{v}_j) \in \mathcal{E}$ in a directed graph, or $\{\mathcal{v}_i, \mathcal{v}_j\} \in \mathcal{E}$ in an undirected graph.
+In an unweighted graph, $a_{ij} = 1$ if a connection exists between $\mathcal{v}_i$ and $\mathcal{v}_j$, and $a_{ij} = 0$ otherwise.
+In a weighted graph, $a_{ij}$ can take any real value ($a_{ij} \in \mathbb{R}$) depending on the application [@estrada2012structure].
 
@@
 
-- Discuss about centrality measures in social network analysis
-- What can centrality measures offer in analyzing polypharmacy networks
-- Check the structure of complex network: theory and application by Estrada
+Centrality measures formalize the identification of important nodes in a graph [@estrada2012structure].
+The centrality of a node is measured differently depending on the context of analysis.
+Previous publication on DPN highlighted four common centrality measures, namely degree, betweenness, closeness, and eigenvector centrality [@Miglio2021].
+Degree centrality in a DPN describes the number of co-prescription with the medication of interest.
+High (low) degree centrality means the medication is often (seldom) co-prescribed.
+Betweenness centrality indicates the frequency of a medication connecting two other medications by the shortest possible path.
+High (low) betweenness centrality means the medication is (not) a "bridge" between different kind of medications.
+Closeness centrality is the average distance between one medication to all other medications in the DPN.
+High (low) closeness centrality means that the medication is (not) commonly co-prescribed.
+Eigenvector centrality reflects the number of co-prescription with medications that have vital role in the DPN.
+High (low) eigenvector centrality means that the medication is often (seldom) co-prescribed with other important medications.
+
+The choice of centrality largely depends on the objective of network analysis.
+As a general guide, degree centrality is useful to identify popular medication and monitor drug overuse.
+Betweenness centrality is suitable for targeting for drug-interaction study and optimizing therapy plan.
+Closeness centrality indicates widely-used key medications and efficiency in treatment networks.
+Eigenvector centrality is helpful to identify influential medications and narrow down high-impact medications for drug monitoring.
+This study focused on eigenvector centrality to evaluate which medications have a significant influence on how antidepressants and anxiolytics are prescribed.
 

### 2024-12-10 docs/article.qmd
Revise the formal definition following the cited references

@@
 A graph consists of nodes and edges, denoted as $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
-The nodes form a finite set, $\mathcal{V} = \{\mathcal{v}_1, \mathcal{v}_2, \dots, \mathcal{v}_n$, while the edges $\mathcal{E}$ represent the connection between these nodes.
+The nodes form a finite set, $\mathcal{V} = \{\mathcal{v}_1, \mathcal{v}_2, \dots, \mathcal{v}_n\}$, while the edges $\mathcal{E}$ represent the connection between these nodes.
 In a directed graph, the edge is an ordered pair of nodes, $(\mathcal{v}_i, \mathcal{v}_j) \in \mathcal{E}$, where the order of $i, j$ matters.
-Directed graphs may contain self connections $(\mathcal{v}_i, \mathcal{v}_i) \in \mathcal{E}$.
-In an undirected graph, the edge is an unordered set of nodes $\{\mathcal{v}_i, \mathcal{v}_j\} \in \mathcal{E}$, where the order of $i, j$ does not matter.
-Typically, undirected graphs do not contain self connections $\{\mathcal{v}_i, \mathcal{v}_i\} \notin \mathcal{E}$ [@estrada2012structure].
+Directed graphs may contain self connections, $(\mathcal{v}_i, \mathcal{v}_i) \in \mathcal{E}$.
+In an undirected graph, the edge is an unordered set of nodes, $\{\mathcal{v}_i, \mathcal{v}_j\} \in \mathcal{E}$, where the order of $i, j$ does not matter.
+Typically, undirected graphs do not contain self connections, $\{\mathcal{v}_i, \mathcal{v}_i\} \notin \mathcal{E}$ [@estrada2012structure].
 
 A graph can be represented as an adjacency matrix $A$.
-The adjacency matrix $A$ has dimensions of $|\mathcal{V}| \times |\mathcal{V}|$, and $|\mathcal{V}|$ is the number of nodes in a graph.
+The adjacency matrix $A$ has dimensions of $|\mathcal{V}| \times |\mathcal{V}|$, where $|\mathcal{V}|$ is the number of nodes in a graph.
 Each element of $a_{ij}$ is the edge: $(\mathcal{v}_i, \mathcal{v}_j) \in \mathcal{E}$ in a directed graph, or $\{\mathcal{v}_i, \mathcal{v}_j\} \in \mathcal{E}$ in an undirected graph.
@@
 Since the sum of all eigenvector centralities $c_i$ in equation [-@eq-eigen-centrality] is equal to one, a network with similarly connected nodes will have an eigenvector centrality $c_i$ = $\frac{1}{n}$ for each node, where $n$ is the number of nodes.
-The value of $c_i = \frac{1}{n}$ is the expected eigenvector centrality in a densely connected network where connection $(i, j) \in \mathcal{E}$ from node $\mathcal{V}_i$ to node $\mathcal{V}_j$ has the same probability for every node.
+The value of $c_i = \frac{1}{n}$ is the expected eigenvector centrality in a densely connected network where the occurrence of an edge $\{\mathcal{v}_i, \mathcal{v}_j\} \in \mathcal{E}$ has the same probability for all nodes.
 Per the central limit theorem, the value $\frac{1}{n}$ can be parameterized as a mean of a normal distribution, where all instances of eigenvector centrality will follow the distribution, $c_i \sim \mathcal{N}(\mu, \sigma)$.

### 2024-12-10 docs/exec-summary/_measure-eigen.qmd
Draft an initial report using Elsevier template
Revise the formal definition following the cited references

@@
+::: {.content-visible unless-meta="in.article"}
 ### Measuring relative importance
+:::
 
@@
 Eigenvector centrality is a recursive measures of how well connected a certain node is to other nodes that is also well connected in the network [@Golbeck2013].
-@eq-eigen-centrality outlines the calculation of eigenvector centrality; $\c_i$ and $\c_j$ are the centralities of node $i$ and $j$, respectively; $\lambda$ is the eigenvalue; $a_{j, i}$ is an element on row $j$ and column $i$ from an adjacency matrix $A$, representing the connection between node $a_i$ and $a_j$.
+@eq-eigen-centrality outlines the calculation of eigenvector centrality; $c_i$ and $c_j$ are the centralities of node $\mathcal{v}_i$ and $\mathcal{v}_j$, respectively; $\lambda$ is the eigenvalue; $a_{ji}$ is an element on row $j$ and column $i$ from an adjacency matrix $A$, representing the connection between node $\mathcal{v}_j$ and $\mathcal{v}_i$.
 
 $$
-\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} a_{j, i} \cdot c_j
+\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} a_{ji} \cdot c_j
 $$ {#eq-eigen-centrality}

### 2024-12-10 docs/exec-summary/_preprocessing.qmd
Incorporate suggestion from Spyros
Revise the formal definition following the cited references

@@
 
-Daily medication claims is a tabular data containing values from single medication entity for each patients in the cohort.
-Data transformation was performed to construct a square matrix of aggregate medication claim per day, with rows and columns representing groups of medication.
-Each element in the upper and lower triangle represents co-prescriptions, while the diagonal of the matrix represents single prescriptions.
-All elements in the matrix is a tally of drug combination/single prescription in the population claimed on a daily basis.
-The matrix follows a graph construct, where we can denote the row-to-column as `Medication1-PrescribedAlongside-Medication2`.
-The graph is a representation of drug prescription network (DPN), where the edge is the number of concurrency.
-In the original DPN, the edge weight was the number of claims by assuming that all of defined daily doses (DDD) were equal to 1 [@Cavallo2012].
-However, not all medications were prescribed with DDD equals to 1, and discarding these entries would lead to loss of information.
-Therefore, we applied weights based on DDD, where the weight is the highest if DDD equals to 1, and gradually diminishes as it is getting further from 1.
-To adjust the weight, first we set the baseline weight as $\omega_B = 1$.
-Then, we calculated the weight based on the expected density of a normal distribution, where the expected value is $\mu = \omega_B$ and standard deviation is $\sigma = \frac{\omega_B}{3}$.
-The expected value was set to $\omega_B$ because we expect entries with DDD equals to 1.
-The standard deviation was set to $\frac{\omega_B}{3}$ to represent an equidistant deviation from the expected value to 0.
-As a result, we obtained the weighted DDD as $\omega$.
+Daily medication claims are represented as tabular data where each row corresponds to an individual patient’s prescriptions.
+The data was transformed into a square matrix summarizing co-prescriptions and single prescriptions to construct a graph-based representation.
+The rows and columns of the matrix represent groups of medications, while each matrix element indicates the frequency of a specific prescription pattern.
+Elements in the off-diagonal positions represent co-prescriptions between two medications, while diagonal elements represent single prescriptions.
+This matrix can be interpreted as a graph, where each medication is a node, and the edges represent co-prescription frequencies.
+The weight of the edge is derived from the number of daily claims.
+Originally, all defined daily doses (DDD) were assumed to equal 1, leading to straightforward edge weights based on raw counts.
+However, since not all medications have DDD values of 1, this assumption could lead to inaccurate representations.
+To address this, weights were adjusted using the density of a normal distribution.
+The expected value ($\mu$) was set to 1 to prioritize DDD = 1, and the standard deviation ($\sigma$) was set to $\frac{1}{3}$ to allow for a gradual reduction in weight as DDD deviates from 1.
+This adjustment ensures a more accurate weighting system that reflects real-world prescription patterns while preserving information about medications with non-standard DDD values.
 
@@
 }
-\to
+\quad \to \quad
 \stackrel{\textrm{Regularized by } DDD}{

### 2024-12-11 docs/article.qmd
Explain table 2 in the result section

@@
 @tbl-overview-patient depicts the dynamics of the population from 2018 to 2022.
-The ratio of male to female did not vary by a large margin, and the average age steadily increased over the year.
+The ratio of male to female only varied slightly, and the average age steadily increased over the year.
 These findings imply that the cohort stays relatively stable overtime without any indication of sudden demographic changes.
@@
 ```
+
+@tbl-res-poly outlines the type of polypharmacy in the population.
+The summary statistics was based on prescription-day data on the population level over the year.
+Prescription-day is the number of dispensed medication in a day.
+For example, if seven medication is prescribed for 1 days, then it has 7 prescription-day.
+Same-class polypharmacy is co-prescription of psychopharmaca from the same class, e.g.
+combination of antidepressants.
+Multi-class polypharmacy is co-prescription of psychopharmaca from different classes, e.g.
+combination of antidepressants and anxiolytics.
+Total polypharmacy is the total number of co-prescription regardless of its class, which may contain medications other than psychopharmaca.
+There are two reported statistics in @tbl-res-poly, namely the sum and the mean alongside its standard deviation.
+The sum reflects the total prescription-day of polypharmacy occurring in a year.
+Meanwhile, the mean and its standard deviation reflect the expected duration in days a person may receive any polypharmacy regimen.
+As such, we can read the findings as follow:
+
+> *"In 2018, same-class polypharmacy of antidepressants occur for 73,528 prescription-day in the population, with the expected duration of 0.06 prescription-day per person."*
+
+The phrase *"0.06 prescription-day per person"* may sound confusing at first.
+However, it directly corresponds with the expected duration in days per 100 days a person might receive polypharmacy regimens.
+Therefore, it is interpretable as:
+
+> *"In 2018, a person prescribed with antidepressants is expected to receive same-class polypharmacy regimens for 6 out of 100 days."*
 

### 2024-12-11 docs/article.qmd
Rearrange the results section to improve readability and reading flow

--- 2024-12-10 docs/article.qmd
@@
 
+## Description of the population
+
 ```{r}
@@
 IADB recorded `r n_patient` patients having at least one prescription of antidepressants or anxiolytics within five years of data extraction.
-@tbl-overview-patient depicts the dynamics of the population from 2018 to 2022.
-The ratio of male to female did not vary by a large margin, and the average age steadily increased over the year.
-These findings imply that the cohort stays relatively stable overtime without any indication of sudden demographic changes.
+@tbl-overview-patient captures the dynamics of the population from 2018 to 2022.
+The ratio of male to female only varied slightly, and the average age steadily increased over the year.
+These findings imply that the population demography stays relatively stable overtime without any indication of sudden changes.
 
@@
 ```
+
+## Weekly variation of prescription dispensing
+
+The highest average of prescription dispensing occurred on `r hi_claim$day`, with an average of `r hi_mean` [SD: `r hi_claim$sd_claim`] prescriptions.
+Meanwhile, the lowest average of claim occurred on `r lo_claim$day`, with an average of `r lo_mean` [SD: `r lo_claim$sd_claim`] prescriptions.
+A large margin of difference between the highest and lowest average number of claim implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in @tbl-overview-daily.
+The cyclical patterns are further explained in our supplementary material.
+@tbl-desc shows the number of prescriptions for each medication class alongside the distribution of DDD and its weight.
+
+```{r tbl-overview-daily}
+#| tbl-cap: "Daily prescription from 2018 to 2022 among patients with at least one claim of antidepressants or anxiolytics"
+
+res_tbl_overview$overview |>
+  dplyr::mutate(
+    "mean_sd" = sprintf("%s (%.2f)", prettyNum(mean_claim, big.mark = ","), sd_claim),
+    "median_IQR" = sprintf("%s (%.2f)", prettyNum(median_claim, big.mark = ","), IQR_claim),
+    "Range" = sprintf("%s - %s", prettyNum(min_claim, big.mark = ","), prettyNum(max_claim, big.mark = ","))
+  ) |>
+  dplyr::select(day, mean_sd, median_IQR, Range) |>
+  flextable::flextable() |>
+  flextable::set_header_labels(
+    day = "Day",
+    mean_sd = "Mean (SD)",
+    median_IQR = "Median (IQR)"
+  ) |>
+  flextable::add_header_row(
+    values    = c("", "Number of Claims"),
+    colwidths = c(1, 3),
+    top       = TRUE
+  ) |>
+  flextable::align(align = "center", part = "all") |>
+  flextable::align(j = 1, align = "left", part = "all") |>
+  #flextable::font(fontname = "Times", part = "all") |>
+  flextable::fontsize(size = 7, part = "all") |>
+  flextable::autofit(add_w = 0, add_h = 0) |>
+  flextable::set_table_properties(opts_pdf = list("arraystretch" = 1, "tabcolsep" = 0))
+
+```
+
+## Time-series decomposition
+
+Using the weekly-aggregated data, we obtained decomposed series using an SSA-based approach.
+@fig-ssa depicts the decomposition result of the number of claim time-series in antidepressants.
+SSA-based decomposition separates the trend from its harmonics, as shown in the lower half of the plot.
+The trend explains roughly 90% of the variability, and harmonics explain 10%.
+The first two harmonics, F1 and F2, captured most of the variability in a series compared to the rest of it.
+
+```{r fig-ssa}
+#| fig-width: 16
+#| fig-height: 12
+#| fig-pos: H
+#| fig-cap: An example of time-series decomposition using singular spectrum analysis-based approach
+
+tar_read(plt_ssa_recon_n_claim)[[17]]
+
+```
+
+## Polypharmacy in the population
+
+@tbl-res-poly outlines the type of polypharmacy in the population.
+The summary statistics were based on prescription-day data aggregated at the population level over the year.
+Prescription-day is the number of medications dispensed on a given day.
+For example, if seven medications are prescribed for one day, it accounts for 7 prescription-days.
+Same-class polypharmacy refers to co-prescription of psychopharmaca from the same class, such as a combination of antidepressants.
+Multi-class polypharmacy involves co-prescription of psychopharmaca from different classes, such as combining antidepressants and anxiolytics.
+Total polypharmacy refers to the overall number of co-prescriptions, including those involving medications outside psychopharmaca classes.
+Two statistics are reported in @tbl-res-poly: the sum and the mean with its standard deviation.
+The sum indicates the total prescription-days of polypharmacy within a year.
+The mean and standard deviation represent the average number of prescription-days per person for any polypharmacy regimen.
+Thus, we can read the findings as follow:
+
+> *"In 2018, same-class polypharmacy of antidepressants occurred for a total of 73,528 prescription-days across the population, with an average of 0.06 prescription-days per person.
+For every 100 people prescribed with antidepressants, there were approximately 6 days in total during which polypharmacy regimens occurred."*
 
@@
   flextable::set_table_properties(opts_pdf = list("arraystretch" = 1, "tabcolsep" = 0))
-
-```
-
-The highest average of prescription claim occurred on `r hi_claim$day`, with an average of `r hi_mean` [SD: `r hi_claim$sd_claim`] prescriptions.
-Meanwhile, the lowest average of claim occurred on `r lo_claim$day`, with an average of `r lo_mean` [SD: `r lo_claim$sd_claim`] prescriptions.
-A large margin of difference between the highest and lowest average number of claim implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in table [-@tbl-overview-daily] and figure [-@fig-period-day].
-The cyclical patterns are further explained in our supplementary material.
-@tbl-desc shows the number of prescriptions for each medication class alongside the distribution of DDD and its weight.
-
-```{r tbl-overview-daily}
-#| tbl-cap: "Daily prescription from 2018 to 2022 among patients with at least one claim of antidepressants or anxiolytics"
-
-res_tbl_overview$overview |>
-  dplyr::mutate(
-    "mean_sd" = sprintf("%s (%.2f)", prettyNum(mean_claim, big.mark = ","), sd_claim),
-    "median_IQR" = sprintf("%s (%.2f)", prettyNum(median_claim, big.mark = ","), IQR_claim),
-    "Range" = sprintf("%s - %s", prettyNum(min_claim, big.mark = ","), prettyNum(max_claim, big.mark = ","))
-  ) |>
-  dplyr::select(day, mean_sd, median_IQR, Range) |>
-  flextable::flextable() |>
-  flextable::set_header_labels(
-    day = "Day",
-    mean_sd = "Mean (SD)",
-    median_IQR = "Median (IQR)"
-  ) |>
-  flextable::add_header_row(
-    values    = c("", "Number of Claims"),
-    colwidths = c(1, 3),
-    top       = TRUE
-  ) |>
-  flextable::align(align = "center", part = "all") |>
-  flextable::align(j = 1, align = "left", part = "all") |>
-  #flextable::font(fontname = "Times", part = "all") |>
-  flextable::fontsize(size = 7, part = "all") |>
-  flextable::autofit(add_w = 0, add_h = 0) |>
-  flextable::set_table_properties(opts_pdf = list("arraystretch" = 1, "tabcolsep" = 0))
-
-```
-
-## Time-series decomposition
-
-Using the weekly-aggregated data, we obtained decomposed series using an SSA-based approach.
-@fig-ssa depicts the decomposition result of the number of claim time-series in antidepressants.
-SSA-based decomposition separates the trend from its harmonics, as shown in the lower half of the plot.
-The trend explains roughly 90% of the variability, and harmonics explain 10%.
-The first two harmonics, F1 and F2, captured most of the variability in a series compared to the rest of it.
-
-```{r fig-ssa}
-#| fig-width: 16
-#| fig-height: 12
-#| fig-pos: H
-#| fig-cap: An example of time-series decomposition using singular spectrum analysis-based approach
-
-tar_read(plt_ssa_recon_n_claim)[[17]]
 

### 2024-12-11 docs/article.qmd
Discuss about polypharmacy findings

@@
 
+This study is an egocentric network analysis of two population groups: individuals receiving antidepressants and those receiving anxiolytics.
+On average, each person received 6 days of polypharmacy regimens in a year.
+The rate of polypharmacy differs between these two groups.
+Same-class polypharmacy is more prevalent among individuals treated with antidepressants than among those treated with anxiolytics.
+Conversely, multi-class polypharmacy is more common in individuals treated with anxiolytics.
+In both groups, multi-class polypharmacy is ten times more prevalent than same-class polypharmacy.
+The high prevalence of multi-class polypharmacy in our findings aligns with previous studies, which show that antidepressants and anxiolytics are often co-prescribed with other medications [@Shrivastava2013], and multi-class regimens contribute the most to the prevalence of psychopharmaca polypharmacy [@de2004polypharmacy].
+
+The rate of total polypharmacy in people prescribed with antidepressants
+
+• First paragraph: Discuss about polypharmacy
+• Second paragraph: Explain the concordance with other literatures
+• Third paragraph: Explain about the DPN
+• Fourth paragraph: Strength
+• Fifth paragraph: Limitation
+  • Lost of individual values
+  • Add limitation about weighting the DDD $\to$ How does it reflect augmented polypharmacy?
+
 @Delara2022

### 2024-12-11 src/R/visualize.R
Visualize the time-series before and after reconstruction

@@ -568,3 +568,22 @@ vizConnectivity <- function(graph_concat) {
 
   return(plt)
 }
+
+vizReconResult <- function(ts, ts_recon, ...) {
+  #' Visualize the Reconstruction Results
+  #'
+  #' Visualize the reconstructed time-series side-by-side with the original
+  #' time-series data.
+  #'
+  #' @param ts The original time-series data
+  #' @param ts_recon The reconstructed time-series data
+  #' @param ... Parameters being passed on to `vizDot`
+  #' @return A GGPlot2 object
+  require("ggplot2")
+
+  plt1 <- vizDot(ts, ...)
+  plt2 <- vizDot(ts_recon, ...)
+  plt  <- ggpubr::ggarrange(plt1, plt2, nrow = 1, align = "v")
+
+  return(plt)
+}

### 2024-12-11 docs/article.qmd
Finalize the first draft

--- 2024-12-11 docs/article.qmd
@@
 title: >
-  A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands 2018-2022
+  A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands from 2018 to 2022
 
@@
 
-The inherently complex nature of health-related phenomena have fueled the growing implementation of network analysis, making it an indispensable research framework in medicine and epidemiology [@Luke2007].
+The inherently complex nature of health-related phenomena have fueled the growing implementation of network analysis, making it an important research framework in medicine and epidemiology [@Luke2007].
 Past implementations of network analysis in public health mostly focused on transmission network, social network, and organizational network.
@@
 Constructing a DPN allows examining co-prescription dynamics in the population as graph measures, which is also attributable to each medication.
-One of such measures is graph centrality, where we calculate scores representing the number of co-medications, number of connecting paths, average distance, and relative importance [@Askar2021].
+One of such measures is graph centrality, where we calculate scores representing the number of co-prescriptions, number of connecting paths, average distance, and relative importance [@Askar2021].
 The relative importance score is of particular interest to address concerns raised by @Sirois2016 and @Delara2022 regarding standardized quantitative indicator of polypharmacy.
@@
 
-## Time-series decomposition
-
-Using the weekly-aggregated data, we obtained decomposed series using an SSA-based approach.
-@fig-ssa depicts the decomposition result of the number of claim time-series in antidepressants.
-SSA-based decomposition separates the trend from its harmonics, as shown in the lower half of the plot.
-The trend explains roughly 90% of the variability, and harmonics explain 10%.
-The first two harmonics, F1 and F2, captured most of the variability in a series compared to the rest of it.
-
-```{r fig-ssa}
-#| fig-width: 16
-#| fig-height: 12
-#| fig-pos: H
-#| fig-cap: An example of time-series decomposition using singular spectrum analysis-based approach
-
-tar_read(plt_ssa_recon_n_claim)[[17]]
-
-```
-
 ## Polypharmacy in the population
@@
 > *"In 2018, same-class polypharmacy of antidepressants occurred for a total of 73,528 prescription-days across the population, with an average of 0.06 prescription-days per person.
-For every 100 people prescribed with antidepressants, there were approximately 6 days in total during which polypharmacy regimens occurred."*
+For every 100 people prescribed with antidepressants, there were approximately 6 days in total during which same-class polypharmacy regimens occurred."*
 
@@
 
+## Time-series decomposition
+
+Using the weekly-aggregated data, we obtained decomposed series using an SSA-based approach.
+@fig-ssa depicts the decomposition result of the number of claim time-series in antidepressants.
+SSA-based decomposition separates the trend from its harmonics, as shown in the lower half of the plot.
+The trend explains roughly 90% of the variability, and harmonics explain 10%.
+The first two harmonics, F1 and F2, captured most of the variability in a series compared to the rest of it.
+The trend, F1, and F2 were used to reconstruct the time series.
+
+```{r fig-ssa}
+#| fig-width: 16
+#| fig-height: 12
+#| fig-pos: H
+#| fig-cap: An example of time-series decomposition using singular spectrum analysis-based approach
+
+tar_read(plt_ssa_recon_n_claim)[[17]]
+
+```
+
 ## Relative importance score
@@
 
-Seven medications had a high relative importance as suggested by figure [-@fig-hi-eigen] and table [-@tbl-desc].
+Seven medication classes had a high relative importance as suggested by figure [-@fig-hi-eigen] and table [-@tbl-desc].
 It is notable that highly prescribed medications usually have a high eigenvector centrality as well, which is theoretically supported by equation [-@eq-eigen-centrality].
@@
 We confirmed similar findings with anxiolytics, which had higher prescription numbers (`r diffMed(anxiolytics, analgesics, reportMedClaim)`) but lower eigenvector centrality (`r diffMed(anxiolytics, analgesics, reportMedEigen)`) than analgesics.
-The difference of eigenvector centrality became more pronounced as the number of prescriptions decreased.
+The difference of eigenvector centralities became more pronounced as the number of prescriptions decreased.
 
@@
 
-@Delara2022
+This study is an egocentric network analysis of two population groups: individuals receiving antidepressants and those receiving anxiolytics.
+By examining co-prescription patterns, we aimed to understand the prevalence and nature of polypharmacy within these groups.
+The rate of polypharmacy differs between these two groups.
+While same-class polypharmacy is more prevalent among individuals treated with antidepressants than among those treated with anxiolytics, multi-class polypharmacy predominates among those treated with anxiolytics.
+In both groups, multi-class polypharmacy is ten times more prevalent than same-class polypharmacy.
+The high prevalence of multi-class polypharmacy in our findings aligns with previous studies, which show that antidepressants and anxiolytics are often co-prescribed with other medications [@Shrivastava2013], and multi-class regimens contribute the most to the prevalence of psychopharmaca polypharmacy [@de2004polypharmacy].
+This highlights the interconnected nature of psychopharmaca prescription patterns.
 
-- The prevalence of polypharmacy in all medication classes is 37% [95% CI: 31-43%]
-- Difference of prevalence measure is due to different numerical thresholds, study setting, and publication year
+To better understand these co-prescription patterns, the DPN was constructed to identify medication classes with strong centralities in relation to antidepressants and anxiolytics.
+Following @Cavallo2012, the weight of the adjacency matrix was the frequency of co-prescriptions or single prescriptions.
+We adjusted the weight to account for varying prescription dosages, alleviating previous limitation where the DDD was restricted to 1 [@Cavallo2012].
+Seven medication classes clustered together, forming a modular structure.
+This modularity reflects the organization of medications into anatomically or functionally related groups, where certain drugs were found to form densely interconnected nodes preferentially linked to each other [@Bazzoni2015].
+These network properties highlight the utility of DPNs in revealing prescribing patterns and their underlying clinical rationale.
 
-@Sirois2016
+Seven medication classes were identified with a high eigenvector centrality in our DPN.
+Unsurprisingly, antidepressants and anxiolytics exhibited high centrality, as these medication classes were central to our DPN.
+Beyond these, medication classes with high centrality included those for the alimentary tract and metabolism (WHO ATC code `A`), blood and blood-forming organs (code `B`), cardiovascular system (code `C`), respiratory system (code `R`), and analgesics (code `N02`).
+These classes are closely associated with chronic illnesses.
+This finding aligns with previous investigation highlighting the bidirectional associations between depression/anxiety and chronic physical illnesses [@qi2024longitudinal].
+For instance, a study demonstrated that diabetes mellitus, thyroid disorders, and asthma increased the risk of depression [@jang2024temporal].
+Moreover, these conditions often necessitate long-term pharmacological interventions, increasing the likelihood of co-prescription.
+Similarly, fears of worsening symptoms in chronic diseases can lead to heightened health-related anxiety [@lebel2020health].
+The frequent coexistence of physical and mental health conditions in chronic diseases underscores the rationale for polypharmacy regimens [@nizamie2015rational].
 
-- Problem of exposure: Polypharmacy can be defined as cumulative or simultaneous prescriptions
-- Cut-off threshold of polypharmacy should be justified by the risk of deleterious health outcomes
-- An ideal monitoring system should describe the importance of polypharmacy
+We acknowledge several limitations in this study.
+First, data aggregation at the population level resulted in the loss of individual-level information, limiting interpretation to population trends.
+Second, while the adjustment of weights based on DDD introduces a novel element to the analysis, it is important to note that DDD values are not always equal to one, as defined by the WHO ATC system.
+However, our approach aligns with the general recommendation of @Cavallo2012, where DDD of 1 forms the basic of network edges.
+The adjusted weighting penalizes values deviating significantly from 1, reducing their impact on the network.
+Future studies should explore alternative weighting methods to further refine the analysis.
 
-@Menditto2019
+Despite the limitations, our study demonstrates the utility of DPN as a powerful, data-driven approach to analyzing prescription dispensing data.
+By modelling intricate co-prescription patterns, DPN filters medication classes based on network properties, offering deeper insights into prescribing behaviors.
+These insights can reveal important trends in medication use, which can be essential to public health monitoring.
+By capturing the complexity of drug prescription relationships, DPN holds significant potential to improve decision-making in both clinical and administrative contexts
 
-- Although polypharmacy is mostly researched in geriatric patients, younger population are also at risk of inappropriate multiple medication uses
+# Conclusion
 
-@Shrivastava2013
-
-- Among diagnoses, polypharmacy is often found in patients with schizophrenia, schizotypal, and delusional disorder
-- Multi-class polypharmacy is the most common (20.9%), usually the combination of SSRI and benzodiazepine or TCA and benzodiazepine
-- Five factors associated with psychiatric polypharmacy:
-  - Scientific: Emphasis on biogenic amines roles in depression and schizophrenia expanded the early clinical evidence of psychotropic medications
-  - Clinical: Standardization attempt resulted in overlapping diagnoses with limited validity; poly-nosology an polypharmacy go hand-in-hand
-  - Economic: Pharmaceutical company influenced the demand of psychopharmaca uses
-  - Political: US FDA imposes minimal guidelines for drug approval only for specific conditions
-  - Cultural: Large cultural appetite for pharmacological treatments
-
-@Stassen2021
-
-- Attending psychiatrist is the main determinant of polypharmaca prescription
-- Previous medical history and case severity at baseline only play a minor role in polypharmaca
-- Adverse drug reaction in polypharmaca is 2-3 times higher compared to monotherapy, and not attributed to particular drug or drug combination; it implies that any drug and its combination can virtually trigger the side effect
-- No advantage of polypharmacy over monotherapy, suggesting that polypharmacy regimens are not equally suited for every patient
-
-@Molokhia2017
-
-- The alternative measure is pre-defined criteria, e.g. BEERS, STOPP, and START
-- Each additional medication contributes to 16% increased risk of errors
-
-@Cavallo2012
-
-- The weight is the number of time a pair of medications is prescribed together
-- The co-prescription network has a scale-free property, suggesting that the probability new links being formed is growing alongside the degree of the target node
-- The scale-free property of the network might be explained by the physician's prescribing habit: The physician tends to prescribe medications with known medications
-
-@Bazzoni2015
-
-- Drug-prescription network is highly dense and clustered at the global level
-- Drug-prescription network is organized into anatomically homogeneous modules at the local level
+This study utilized DPN to evaluate the influence of specific medication classes on prescribing patterns of antidepressants and anxiolytics.
+By focusing on co-prescription patterns, we identified seven medication classes with significant eigenvector centrality, reflecting their critical role in polypharmacy regimens.
+This study highlights the potential of network-based approaches to narrow down high-impact medications for further evaluation.
 

### 2025-03-12 docs/abstract/_abstract-short.qmd
Revise the abstract to below 250 words

**Background:**
Drug prescription networks (DPNs) model the temporal dynamics of medication co-prescription within a population. Understanding these networks can provide insights into polypharmacy and prescribing behaviors.

**Objectives:**
This study assesses the structural characteristics of temporal DPNs derived from daily co-prescriptions of antidepressants, anxiolytics, and other therapeutic drug classes. By analyzing these networks using eigenvector centrality, we identify influential medications and prescribing patterns.

**Methods:**
We utilized the IADB.nl database, including prescriptions from 128 Dutch pharmacies (2018–2022). A closed cohort of patients prescribed antidepressants/anxiolytics was extracted. Medications were classified using the Anatomical Therapeutic Chemical (ATC) system into 24 therapeutic classes. Time-varying DPNs were constructed as undirected graphs using symmetric daily dose-adjusted co-prescriptions. Eigenvector centrality ($c_e$) quantified relative nodal importance. Weekly-aggregated data included prescriptions ($n_c$), number of patients, claim-to-patient ratio, and eigenvector centrality. Singular spectrum analysis decomposed trends.

**Results:**
Antidepressants (ATC `N06A`, $c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics (`N05B`, $c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) had high eigenvector centrality, indicating frequent co-prescription. Additional high-centrality groups included medications for alimentary and metabolism (`A01-A16`), blood (`B01-B06`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory (`R01-R07`).

**Discussion:**
DPNs reveal key polypharmacy patterns. High-centrality medications highlight potential targets for drug monitoring. This approach aids in identifying influential medications and refining prescribing oversight.

### 2025-03-12 docs/article.qmd
Revise the abstract to below 250 words

@@
       cite-style: authoryear
+    output-file: iadb-network-analysis.pdf
   docx:
     pandoc-options: ["--mathml"]
+    output-file: iadb-network-analysis.docx
 
@@
   - _author.yml
-  - _abstract.yml
+  - _abstract-short.yml
   - _knitr-bib.yml
@@
 Past implementations of network analysis in public health mostly focused on transmission network, social network, and organizational network.
-Only recently, @Cavallo2012 demonstrated a novel framework to describe medication uses on a population level, i.e.
+Only recently, @Cavallo2012 demonstrated a novel framework to describe medication use on a population level, i.e.
 drug prescription network (DPN), a term which later is coined by @Bazzoni2015.
@@
 From a complex system standpoint, polypharmacy is a prescription of multiple drug combinations which can be modelled as a network [@Miglio2021].
-DPN can capture the complex relationships of a system that may vary overtime, which is highly relevant to drug prescribed for mental disorders.
+DPN can capture the complex relationships of a system that may vary over time, which is highly relevant to drugs prescribed for mental disorders.
 
-In psychiatry, polypharmacy is defined as a patient with at least two concurrent psychiatric medications [@Shrivastava2013].
-With a prevalence between 13-90%, psychiatric polypharmacy manifests in five categories, namely same-class, multi-class, adjunctive, augmentation, and total polypharmacy.
+In psychiatry, polypharmacy is defined as a patient with at least two concurrent psychiatric medications.
+With a prevalence between 13-90%, psychiatric polypharmacy manifests in five categories, namely same-class, multi-class, adjunctive, augmentation, and total polypharmacy [@Shrivastava2013].
 Same-class polypharmacy is the use of multiple medications from the same class.
@@
 This study is an egocentric network analysis of two population groups: individuals receiving antidepressants and those receiving anxiolytics.
-By examining co-prescription patterns, we aimed to understand the prevalence and nature of polypharmacy within these groups.
+By examining co-prescription patterns, we aimed to understand the nature of polypharmacy within these groups.
 The rate of polypharmacy differs between these two groups.
@@
 In both groups, multi-class polypharmacy is ten times more prevalent than same-class polypharmacy.
-The high prevalence of multi-class polypharmacy in our findings aligns with previous studies, which show that antidepressants and anxiolytics are often co-prescribed with other medications [@Shrivastava2013], and multi-class regimens contribute the most to the prevalence of psychopharmaca polypharmacy [@de2004polypharmacy].
+The high occurrence of multi-class polypharmacy in our findings aligns with previous studies, which show that antidepressants and anxiolytics are often co-prescribed with other medications [@Shrivastava2013], and multi-class regimens contribute the most to the occurrence of psychopharmaca polypharmacy [@de2004polypharmacy].
 This highlights the interconnected nature of psychopharmaca prescription patterns.

### 2025-03-12 _targets.R

@@ -358,6 +358,7 @@ list(
   tar_quarto(abstract, "docs/abstract/abstract.qmd"),
   tar_quarto(abstract_eupha, "docs/abstract/eupha.qmd"),
   tar_quarto(abstract_ispor, "docs/abstract/ispor.qmd"),
+  tar_quarto(abstract_short, "docs/abstract/short.qmd"),
   tar_quarto(report, "docs", profile = "report", extra_files = "docs/exec-summary", priority = 0),
   tar_quarto(summary, "docs", profile = "summary", priority = 0),
   tar_quarto(report_descriptive, "docs", profile = "descriptive", priority = 0),

### 2025-03-12 docs/article.qmd
Reword the introduction to improve clarity

@@
 
+::: {.content-hidden}
+
 Monitoring polypharmacy regimens requires a holistic approach since drug prescription highly depends on the physician's prescribing habits [@Shrivastava2013], patient-physician relationship, and pharmaceutical market, which all bear an interplay with the decision-making process [@Cavallo2012].
@@
 
-A DPN is constructed as a matrix which rows to columns represent pairs of medication being taken by a patient in a day.
-Since there is no limit for the number of rows and columns, a DPN can contain virtually every possible combination of polypharmacy regimens.
-A DPN is generalizable as a population aggregate by coalescing all single-patient DPN through matrix addition [@Cavallo2012].
-Constructing a DPN allows examining co-prescription dynamics in the population as graph measures, which is also attributable to each medication.
-One of such measures is graph centrality, where we calculate scores representing the number of co-prescriptions, number of connecting paths, average distance, and relative importance [@Askar2021].
-The relative importance score is of particular interest to address concerns raised by @Sirois2016 and @Delara2022 regarding standardized quantitative indicator of polypharmacy.
-Relative importance, most commonly measured by eigenvector centrality, represents the connection to vital medications.
-A high eigenvector centrality in a DPN indicates more prescriptions with highly-prescribed medications.
-Following up @Cavallo2012 and @Bazzoni2015, we hypothesize that eigenvector centrality as a measure of relative importance is attributable to indicate polypharmacy.
-Our investigation showcases eigenvector centrality as a quantitative indicator of polypharmacy to promote a systematic public health monitoring system.
+:::
+
+A DPN is a graphical representation where medications correspond to nodes, and edges represent co-prescription relationships between them.
+Typically, simple undirected graphs are represented by a square symmetric adjacency matrix $A$, where each nonzero element $a_{ij}$ indicates that medications $i$ and $j$ were co-prescribed on a given day.
+A population-level DPN can be constructed by aggregating individual patient networks through matrix addition [@Cavallo2012].
+Analyzing the structural characteristics of a DPN using both local (medication-level) and global (network-level) graph measures provides insights into co-prescription dynamics.
+
+Node centrality measures, such as eigenvector centrality, quantify the importance of a medication in polypharmacy patterns [@Askar2021].
+Addressing concerns about standardized polypharmacy indicators raised by @Sirois2016 and @Delara2022, we highlight eigenvector centrality as a key measure of a medication’s connection to highly prescribed drugs.
+A high eigenvector centrality suggests frequent co-prescription with commonly used medications, reflecting prescribing trends.
+Building on prior studies [@Cavallo2012; @Bazzoni2015], we hypothesize that eigenvector centrality serves as a meaningful quantitative indicator of polypharmacy.
+Therefore, this study aims to assess the structural characteristics of temporal DPNs, focusing on the role of eigenvector centrality in identifying influential medications and prescribing patterns in mental health treatments.
 

### 2025-03-12 docs/article.qmd
Revise the methods section

@@
 
-Graph theory is a formal concept depicting connections among objects.
-A graph consists of nodes and edges, denoted as $\mathcal{G} = (\mathcal{V}, \mathcal{E})$.
-The nodes form a finite set, $\mathcal{V} = \{\mathcal{v}_1, \mathcal{v}_2, \dots, \mathcal{v}_n\}$, while the edges $\mathcal{E}$ represent the connection between these nodes.
-In a directed graph, the edge is an ordered pair of nodes, $(\mathcal{v}_i, \mathcal{v}_j) \in \mathcal{E}$, where the order of $i, j$ matters.
-Directed graphs may contain self connections, $(\mathcal{v}_i, \mathcal{v}_i) \in \mathcal{E}$.
-In an undirected graph, the edge is an unordered set of nodes, $\{\mathcal{v}_i, \mathcal{v}_j\} \in \mathcal{E}$, where the order of $i, j$ does not matter.
+Mathematically, a graph $\mathcal{G}$ is a pair $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ is the set of nodes and $\mathcal{E}$ is the set of edges.
+In a DPN, the node set $\mathcal{V} = \{\mathcal{v}_1, \mathcal{v}_2, \dots, \mathcal{v}_n\}$ represents a finite set of $n$ medications.
+Additionally, $\mathcal{E}$ is a finite set of edges, where each edge is a pair of nodes that corresponds to a co-prescription.
+In an undirected graph, the order of $i, j$ does not matter.
 Typically, undirected graphs do not contain self connections, $\{\mathcal{v}_i, \mathcal{v}_i\} \notin \mathcal{E}$ [@estrada2012structure].
@@
 The adjacency matrix $A$ has dimensions of $|\mathcal{V}| \times |\mathcal{V}|$, where $|\mathcal{V}|$ is the number of nodes in a graph.
-Each element of $a_{ij}$ is the edge: $(\mathcal{v}_i, \mathcal{v}_j) \in \mathcal{E}$ in a directed graph, or $\{\mathcal{v}_i, \mathcal{v}_j\} \in \mathcal{E}$ in an undirected graph.
-In an unweighted graph, $a_{ij} = 1$ if a connection exists between $\mathcal{v}_i$ and $\mathcal{v}_j$, and $a_{ij} = 0$ otherwise.
+Each element of $a_{ij}$ is the edge, where in an unweighted graph, $a_{ij} = 1$ if a connection exists between $\mathcal{v}_i$ and $\mathcal{v}_j$, and $a_{ij} = 0$ otherwise.
 In a weighted graph, $a_{ij}$ can take any real value ($a_{ij} \in \mathbb{R}$) depending on the application [@estrada2012structure].
@@
 Centrality measures formalize the identification of important nodes in a graph [@estrada2012structure].
-The centrality of a node is measured differently depending on the context of analysis.
-Previous publication on DPN highlighted four common centrality measures, namely degree, betweenness, closeness, and eigenvector centrality [@Miglio2021].
+Different node centrality measures quantify different structural properties of a node.
+Previous work on DPNs highlighted four centrality measures that could be used to assess the importance of a medication within a co-prescription network [@Miglio2021].
 Degree centrality in a DPN describes the number of co-prescription with the medication of interest.
@@
 This study focused on eigenvector centrality to evaluate which medications have a significant influence on how antidepressants and anxiolytics are prescribed.
+@eq-eigen-centrality outlines the calculation of eigenvector centrality; $c_i$ and $c_j$ are the centralities of node $\mathcal{v}_i$ and $\mathcal{v}_j$, respectively; $\lambda$ is the eigenvalue; $a_{ji}$ is an element on row $j$ and column $i$ from an adjacency matrix $A$, representing the connection between node $\mathcal{v}_j$ and $\mathcal{v}_i$.
 
-## Measuring relative importance
-
-{{< include exec-summary/_measure-eigen.qmd >}}
+$$
+\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} a_{ji} \cdot c_j
+$$ {#eq-eigen-centrality}
 
@@
 
-{{< include exec-summary/_spectral.qmd >}}
+Classical and seasonal-trend decomposition techniques may not fully capture complex periodic patterns in time-series data.
+Singular spectrum analysis (SSA) is a non-parametric method that leverages Hankel matrix embedding for decomposition.
+In this study, SSA was applied to identify trends and seasonal components in weekly aggregated prescription data.
+To better isolate trend and seasonal components, sequential SSA was applied.
+First, a basic SSA model with the lag parameter $L$ = 52 was used to extract the dominant trend.
+The residuals were then analyzed with a second SSA model using $L = \frac{N}{2}$ to capture complex periodic patterns.
+The extracted trend, residuals, and oscillatory components were evaluated visually and statistically, with Mann-Kendall trend tests applied to assess long-term changes.
+A complete documentation of this approach and its rationale was included in the supplementary file section S1.1.
 

### 2025-03-12 docs/exec-summary/_descriptive.qmd
Revise the methods section

@@
 
-The data was extracted as a daily time-series, which then aggregated into weekly and monthly for exploratory data analysis.
-The data contains five metrics, including the number of daily medication claims, the number of daily patients, claim-to-patient ratio, and eigenvector centrality.
-For each metrics in each dataset, univariate descriptive analysis was performed by calculating the statistical summary to describe the centrality and spread.
-Mean, median, standard deviation, and interquartile range were reported to evaluate the distribution.
+The data was extracted as a daily time series and aggregated into weekly and monthly intervals for analysis.
+It includes four metrics: daily medication claims, daily patients, claim-to-patient ratio, and eigenvector centrality.
+For each metric, a univariate descriptive analysis was performed, reporting the mean, median, standard deviation, and interquartile range to summarize centrality and dispersion.
 

### 2025-03-12 docs/exec-summary/_source-data.qmd
Add date of database access #23
Revise the methods section

@@
 
-All data in this investigation originated from IADB.nl, a dynamic pharmacy database containing prescription data from 1994 which still grow expansively.
-The database covers approximately 120 community pharmacies serving over one million patients.
+All data in this study originated from IADB.nl, a dynamic pharmacy database containing prescription data from 1994 which still grow expansively.
+The database covers approximately 120 community pharmacies serving over one million patients and was accessed on the 20^th^of September, 2023.
 All patients are recorded in the database, irrespective of health care insurance, where the prescription rates, age, and gender are generalizable to represent the Netherlands [@Visser2013].
@@
 Except for the over the counter drugs and medication dispensed during hospitalization, other medication records for each patient are complete, mainly due to high patient-pharmacy commitment in the Netherlands.
-This analysis include daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.
+This analysis includes daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.

### 2025-03-12 docs/exec-summary/_spectral.qmd
Revise the formal definition following the cited references
Revise the methods section

@@
 
-Classical and STL-based decomposition technique may not sufficiently capture complex periodic patterns in a time-series.
+Classical and Seasonal-Trend decomposition technique may not sufficiently capture complex periodic patterns in a time-series.
 Singular spectrum analysis (SSA) is a powerful non-parametric technique by leveraging Hankel matrix as a higher-dimensional embedding of the time-series.
@@
 Similarly, we can define $U \ni \{U_1, \dots, U_L\}$ as the eigenvectors of matrix $S$ corresponding to eigenvalues $\lambda$.
-Afterwards, we can extract factor vectors $V$ where the corresponding $V_i = X^T \frac{U_i}{\sqrt{\lambda_i}}$.
+Afterwards, we can extract factor vectors $V \ni \{V_1, \dots, V_L\}$ where the corresponding $V_i = X^T \frac{U_i}{\sqrt{\lambda_i}}$.
 Finally, the eigentriple of $\{\sqrt{\lambda_i}, U_i, V_i^T\}$ is formulated as a row-wise decomposition of matrix $X$ [@Golyandina2020].

### 2025-03-12 docs/supplementary.qmd
Restructure the supplementary file

@@
+---
+title: >
+  Supplementary: A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands from 2018 to 2022
+
+format:
+  pdf:
+    keep-tex: false
+    include-in-header:
+      - file: _header.tex
+      - text: |
+          \renewcommand*{\thesection}{S\arabic{section}}
+    output-file: iadb-network-analysis-supplementary.pdf
+    number-sections: true
+    number-depth: 3
+  docx:
+    pandoc-options: ["--mathml"]
+    output-file: iadb-network-analysis-supplementary.docx
+
+metadata-files:
+  - _author.yml
+  - _knitr-bib.yml
+
+in:
+  article: true
+---
+
 ```{r}
@@
 pkgs_load <- sapply(pkgs, library, character.only = TRUE)
-options(digits = 2, scipen = 999)
+options(digits = 2)
 
 ```
+
+# Methods
+
+## Decomposition with singular spectrum analysis
+
+{{< include exec-summary/_spectral.qmd >}}
+
+# Results
+
+## Cyclical patterns on de-trended data
 
@@
 ```
+
+# References {-}

### 2025-03-17 docs/supplementary.tex
Track intermediary TeX files

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[inner=2cm,outer=3cm,top=2cm,bottom=2.5cm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{3}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{longtable}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{float}
\usepackage{typearea}
\floatplacement{figure}{htbp}
\floatplacement{table}{htbp}
\AtBeginDocument{%
  \storeareas\normalpapersize
}
\BeforeRestoreareas{\cleardoublepage}
\newcommand*\uselandscape{%
  \cleardoublepage
  \KOMAoptions{paper=landscape}%
  \recalctypearea
  \areaset{1.2\textwidth}{1.2\textheight}%
}
\renewcommand*{\thesection}{S\arabic{section}}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplementary: A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands from 2018 to 2022},
  pdfauthor={Aly Lamuri; Spyros Balafas; Eelko Hak; Jens H. Bos; Frederike Jörg; Talitha L. Feenstra},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Supplementary: A temporal network analysis of drug
co-prescription around antidepressants and anxiolytics uses in the
Netherlands from 2018 to 2022}
\author{Aly Lamuri \and Spyros Balafas \and Eelko Hak \and Jens H.
Bos \and Frederike Jörg \and Talitha L. Feenstra}
\date{}

\begin{document}
\maketitle

\section{Methods}\label{methods}

\subsection{Decomposition with singular spectrum
analysis}\label{decomposition-with-singular-spectrum-analysis}

Classical and Seasonal-Trend decomposition technique may not
sufficiently capture complex periodic patterns in a time-series.
Singular spectrum analysis (SSA) is a powerful non-parametric technique
by leveraging Hankel matrix as a higher-dimensional embedding of the
time-series. The resulting Hankel matrix \(X\) has the size of
\(L \times K\), where \(L\) represents the lag term. The lag term is the
length of data point in a time-series being taken to construct the
higher-dimensional embedding. For a weekly data with a hypothesized
yearly seasonality, the \(L\) is set as 52, representing the number of
week in a year. In theory, the number of \(L\) should be between the
range of \(2 \leq L \leq \frac{N}{2}\), where \(N\) is the total length
of the time-series (Golyandina and Zhigljavsky 2020).

\begin{equation}\phantomsection\label{eq-hankel-mtx}{
\tau =
\stackrel{\textrm{Time-series data}}{
  \begin{bmatrix}
  x_1 & x_2 & \cdots & x_{N-1} & x_N \\
  \end{bmatrix}
}
\quad \to \quad
X =
\stackrel{\textrm{Time-series embedding}}{
  \begin{bmatrix}
  x_1 & x_2 & \dots & x_{N - L + 1} \\
  x_2 & x_3 & \dots & x_{N - L + 2} \\
  \vdots & \vdots & \ddots & \vdots \\
  x_L & x_{L + 1} & \dots & x_{N} \\
  \end{bmatrix}
}
}\end{equation}

The embedded time-series \(X\) is then decomposed using a singular value
decomposition (SVD). With a matrix \(S = X \cdot X^T\), we can extract
an eigenvalue \(\lambda \ni \{\lambda_1 \geq \dots \geq \lambda_L\}\),
where each \(\lambda_i\) is a non-negative integer. Similarly, we can
define \(U \ni \{U_1, \dots, U_L\}\) as the eigenvectors of matrix \(S\)
corresponding to eigenvalues \(\lambda\). Afterwards, we can extract
factor vectors \(V \ni \{V_1, \dots, V_L\}\) where the corresponding
\(V_i = X^T \frac{U_i}{\sqrt{\lambda_i}}\). Finally, the eigentriple of
\(\{\sqrt{\lambda_i}, U_i, V_i^T\}\) is formulated as a row-wise
decomposition of matrix \(X\) (Golyandina and Zhigljavsky 2020). The
resulting eigentriple is then used to reconstruct the time-series by
eigentriple grouping and diagonal averaging.

In case of complex periodic patterns, sequential SSA is preferred to
separate trend from seasonal components (Golyandina, Korobeynikov, and
Zhigljavsky 2018). A sequential SSA model is performed by first fitting
a basic SSA model to reconstruct the first eigentriple, \emph{viz.} the
eigentriple that explain most of the variance in the data. Then, the
residual of the first model is extracted to fit the second SSA model.
The first SSA model is defined with the lowest possible \(L\), which in
our case \(L = 52\). The second SSA model is defined with the largest
possible \(L\) to capture all patterns, which is conveniently defined as
\(L = \frac{N}{2}\). The decomposed series and its corresponding
original data is then extracted from the model alongside all of the
oscillating functions which contributes to complex seasonality. The
original data, trend, residuals, and oscillating functions are plotted
for further inspection. The original data and trend is further evaluated
using Mann-Kendall trend test.

\uselandscape

\section{Results}\label{results}

\subsection{Cyclical patterns on de-trended
data}\label{cyclical-patterns-on-de-trended-data}

\begin{figure}

\centering{

\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/fig-period-day-1.pdf}

}

\caption{\label{fig-period-day}Daily cyclical pattern captured on a
de-trended data}

\end{figure}%

\normalpapersize

\subsection{Time-series decomposition}\label{time-series-decomposition}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-1.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-2.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-3.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-4.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-5.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-6.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-7.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-8.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-9.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-10.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-11.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-12.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-13.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-14.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-15.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-16.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-17.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-18.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-19.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-20.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-21.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-22.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-23.pdf}

}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

\end{figure}%

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Golyandina2018}
Golyandina, Nina, Anton Korobeynikov, and Anatoly Zhigljavsky. 2018.
\emph{Singular Spectrum Analysis with r}. \emph{Use R!} Springer Berlin
Heidelberg. \url{https://doi.org/10.1007/978-3-662-57380-8}.

\bibitem[\citeproctext]{ref-Golyandina2020}
Golyandina, Nina, and Anatoly Zhigljavsky. 2020. \emph{Singular Spectrum
Analysis for Time Series}. \emph{SpringerBriefs in Statistics}. Springer
Berlin Heidelberg. \url{https://doi.org/10.1007/978-3-662-62436-4}.

\end{CSLReferences}

\end{document}

### 2025-03-17 docs/article.qmd
Revise the results

@@
 
+### Summarizing polypharmacy
+
+This study explored same-class, multi-class, and total polypharmacy.
+The summary statistics were based on prescription-day data aggregated at the population level over the year.
+Prescription-day is the number of medications dispensed on a given day.
+For example, if seven medications are prescribed for one day, it accounts for 7 prescription-days.
+The mean and standard deviation represent the average number of prescription-days per person for any polypharmacy regimen.
+
 ### Decomposition with singular spectrum analysis
@@
 
-IADB recorded `r n_patient` patients having at least one prescription of antidepressants or anxiolytics within five years of data extraction.
+IADB recorded `r n_patient` patients having at least one dispensing of antidepressants or anxiolytics within five years of data extraction.
 @tbl-overview-patient captures the dynamics of the population from 2018 to 2022.
@@
 ```{r tbl-overview-patient}
-#| tbl-cap: "Number of participating patients with at least one claim of antidepressants or anxiolytics from 2018 to 2022"
+#| tbl-cap: "Number of participating patients with at least one dispensing of antidepressants or anxiolytics from 2018 to 2022"
 
@@
 
-## Weekly variation of prescription dispensing
+## Weekly variation of medication dispensing
 
-The highest average of prescription dispensing occurred on `r hi_claim$day`, with an average of `r hi_mean` [SD: `r hi_claim$sd_claim`] prescriptions.
-Meanwhile, the lowest average of claim occurred on `r lo_claim$day`, with an average of `r lo_mean` [SD: `r lo_claim$sd_claim`] prescriptions.
-A large margin of difference between the highest and lowest average number of claim implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in @tbl-overview-daily.
-The cyclical patterns are further explained in our supplementary material.
-@tbl-desc shows the number of prescriptions for each medication class alongside the distribution of DDD and its weight.
+The highest average of medication dispensing occurred on `r hi_claim$day`, with an average of `r hi_mean` [SD: `r hi_claim$sd_claim`].
+Meanwhile, the lowest average of medication dispensing occurred on `r lo_claim$day`, with an average of `r lo_mean` [SD: `r lo_claim$sd_claim`] dispensing.
+A large margin of difference between the highest and lowest average number of dispensing implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in @tbl-overview-daily.
+The cyclical patterns are detailed in the supplementary material section S2.1.
 
 ```{r tbl-overview-daily}
-#| tbl-cap: "Daily prescription from 2018 to 2022 among patients with at least one claim of antidepressants or anxiolytics"
+#| tbl-cap: "Daily dispensing from 2018 to 2022 among patients with at least one dispensing of antidepressants or anxiolytics"
 
@@
   flextable::add_header_row(
-    values    = c("", "Number of Claims"),
+    values    = c("", "Number of Dispensing"),
     colwidths = c(1, 3),
@@
 @tbl-res-poly outlines the type of polypharmacy in the population.
-The summary statistics were based on prescription-day data aggregated at the population level over the year.
-Prescription-day is the number of medications dispensed on a given day.
-For example, if seven medications are prescribed for one day, it accounts for 7 prescription-days.
-Same-class polypharmacy refers to co-prescription of psychopharmaca from the same class, such as a combination of antidepressants.
-Multi-class polypharmacy involves co-prescription of psychopharmaca from different classes, such as combining antidepressants and anxiolytics.
-Total polypharmacy refers to the overall number of co-prescriptions, including those involving medications outside psychopharmaca classes.
 Two statistics are reported in @tbl-res-poly: the sum and the mean with its standard deviation.
 The sum indicates the total prescription-days of polypharmacy within a year.
-The mean and standard deviation represent the average number of prescription-days per person for any polypharmacy regimen.
 Thus, we can read the findings as follow:
 
-> *"In 2018, same-class polypharmacy of antidepressants occurred for a total of 73,528 prescription-days across the population, with an average of 0.06 prescription-days per person.
-For every 100 people prescribed with antidepressants, there were approximately 6 days in total during which same-class polypharmacy regimens occurred."*
+> "In 2018, same-class polypharmacy of antidepressants occurred for a total of 73,528 prescription-days across the population, with an average of 0.06 prescription-days per person.
+For every 100 people prescribed with antidepressants, there were approximately 6 days in total during which same-class polypharmacy regimens occurred."
 
@@
   flextable::add_header_row(
-    values    = c("", "Population Level (N)", "Per Person (Mean [SD])", "Total Polypharmacy"),
+    values    = c("", "Population Level", "Per Person (Mean [SD])", "Total Polypharmacy"),
     colwidths = c(2, 2, 2, 2),
@@
         "The expected occurrence of polypharmacy per person/perscription-day",
-        "Prescription day is defined as the number of prescribed medication per day"
+        "Prescription day is defined as the number of dispensed medication per day"
       )
@@
 
-Using the weekly-aggregated data, we obtained decomposed series using an SSA-based approach.
-@fig-ssa depicts the decomposition result of the number of claim time-series in antidepressants.
+For brevity, @fig-ssa only depicts the decomposition result of antidepressants dispensing over the years.
 SSA-based decomposition separates the trend from its harmonics, as shown in the lower half of the plot.
@@
 The trend, F1, and F2 were used to reconstruct the time series.
+The largest graph in @fig-ssa represents the reconstructed time-series (green line) and its original data points (gray line).
+Other decomposition results are reported in the supplementary file section S2.2.
 
@@
 #| fig-pos: H
-#| fig-cap: An example of time-series decomposition using singular spectrum analysis-based approach
+#| fig-cap: Time-series decomposition of antidepressants dispensing data using singular spectrum analysis-based approach
 
@@
 
-## Relative importance score
+## Eigenvector centrality measures
 
@@
 
-Seven medication classes had a high relative importance as suggested by figure [-@fig-hi-eigen] and table [-@tbl-desc].
-It is notable that highly prescribed medications usually have a high eigenvector centrality as well, which is theoretically supported by equation [-@eq-eigen-centrality].
-However, despite higher prescription numbers (`r diffMed(antidepressants, respiratory, reportMedClaim)`), antidepressants had lower eigenvector centrality than medications for the respiratory system (`r diffMed(antidepressants, respiratory, reportMedEigen)`).
-We confirmed similar findings with anxiolytics, which had higher prescription numbers (`r diffMed(anxiolytics, analgesics, reportMedClaim)`) but lower eigenvector centrality (`r diffMed(anxiolytics, analgesics, reportMedEigen)`) than analgesics.
-The difference of eigenvector centralities became more pronounced as the number of prescriptions decreased.
+Seven medication classes exhibited high centrality, as shown in @fig-hi-eigen and @tbl-desc.
+Notably, highly dispensed medications generally had high eigenvector centrality, which aligns with the theoretical expectations from @eq-eigen-centrality.
+However, despite a higher number of dispensing (`r diffMed(antidepressants, respiratory, reportMedClaim)`), antidepressants had lower eigenvector centrality than medications for the respiratory system (`r diffMed(antidepressants, respiratory, reportMedEigen)`).
+A similar pattern was observed for anxiolytics, which had more dispensing than analgesics (`r diffMed(anxiolytics, analgesics, reportMedClaim)`) but lower eigenvector centrality (`r diffMed(anxiolytics, analgesics, reportMedEigen)`).
 
 ```{r tbl-desc}
-#| tbl-cap: Descriptive statistics of prescription data from 2018 to 2022, ordered by Eigenvector centrality as an indicator of nodal importance
+#| tbl-cap: Descriptive statistics of dispensing data from 2018 to 2022, ordered by Eigenvector centrality
 
@@
     group            = "",
-    n_claim          = "Claim",
-    mean_sd_eigen    = "Importance",
+    n_claim          = "Dispensing",
+    mean_sd_eigen    = "Centrality",
     mean_sd_dose     = "DDD",
@@
 ```{r fig-hi-eigen}
-#| fig-cap: Clusters of medication with a higher eigenvector centrality, implying a higher relative importance in polypharmacy regimens
+#| fig-cap: Clusters of medication with a significant influence on how antidepressants and anxiolytics are prescribed
 #| fig-width: 9

### 2025-03-17 docs/supplementary.qmd
Revise the results

@@
   pdf:
-    keep-tex: false
+    keep-tex: true
     include-in-header:
@@
     number-depth: 3
+    geometry:
+      - inner=2cm
+      - outer=3cm
+      - top=2cm
+      - bottom=2.5cm
   docx:
@@
 
+\uselandscape
+
 # Results
@@
 
+\normalpapersize
+
+## Time-series decomposition
+
+```{r}
+#| fig-width: 16
+#| fig-height: 12
+#| fig-pos: H
+#| fig-cap: Time-series decomposition using singular spectrum analysis-based approach
+
+tar_read(plt_ssa_recon_n_claim)[[1]]
+tar_read(plt_ssa_recon_n_claim)[[2]]
+tar_read(plt_ssa_recon_n_claim)[[3]]
+tar_read(plt_ssa_recon_n_claim)[[4]]
+tar_read(plt_ssa_recon_n_claim)[[5]]
+tar_read(plt_ssa_recon_n_claim)[[6]]
+tar_read(plt_ssa_recon_n_claim)[[7]]
+tar_read(plt_ssa_recon_n_claim)[[8]]
+tar_read(plt_ssa_recon_n_claim)[[9]]
+tar_read(plt_ssa_recon_n_claim)[[10]]
+tar_read(plt_ssa_recon_n_claim)[[11]]
+tar_read(plt_ssa_recon_n_claim)[[12]]
+tar_read(plt_ssa_recon_n_claim)[[13]]
+tar_read(plt_ssa_recon_n_claim)[[14]]
+tar_read(plt_ssa_recon_n_claim)[[15]]
+tar_read(plt_ssa_recon_n_claim)[[16]]
+tar_read(plt_ssa_recon_n_claim)[[18]]
+tar_read(plt_ssa_recon_n_claim)[[19]]
+tar_read(plt_ssa_recon_n_claim)[[20]]
+tar_read(plt_ssa_recon_n_claim)[[21]]
+tar_read(plt_ssa_recon_n_claim)[[22]]
+tar_read(plt_ssa_recon_n_claim)[[23]]
+tar_read(plt_ssa_recon_n_claim)[[24]]
+
+```
+
 # References {-}

### 2025-03-17 src/R/visualize.R

@@ -28,7 +28,7 @@ getLabel <- function(metric) {
   #' @return A character vector signifying the label name
 
   labelname <- dplyr::case_when(
-    metric == "n_claim" ~ "The number of medication claims",
+    metric == "n_claim" ~ "The number of medication dispensing",
     metric == "n_patient" ~ "The number of patients prescribed for a medication",
     metric == "claim2patient" ~ "Medication claim to patient ratio",
     metric == "eigen" ~ "Eigenvector centrality",
@@ -389,12 +389,12 @@ vizReconSsa <- function(tidy_recon, ...) {
   plt1 <- ggplot(tbl, aes(x = date)) +
     geom_point(aes(y = Original), color = colors$black, alpha = 0.4, size = 2, shape = 18) +
     geom_line(aes(y = Original, color = "Data"), alpha  = 0.2, linewidth = 1.2) +
-    geom_line(aes(y = Trend, color = "Trend"), alpha  = 0.8, linewidth = 2) +
+    geom_line(aes(y = Trend, color = "Reconstructed"), alpha  = 0.8, linewidth = 2) +
     labs(title = plt_title, x = "", y = "") +
     scale_date +
     scale_color_manual(
       name = "",
-      values = c("Data" = colors$black, "Trend" = colors$green),
+      values = c("Data" = colors$black, "Reconstructed" = colors$green),
       guide = guide_legend(override.aes = aes(fill = NA))
     ) +
     ggpubr::theme_pubclean() +

### 2025-03-17 docs/article.qmd
Restructure the discussion

@@
 
-This study is an egocentric network analysis of two population groups: individuals receiving antidepressants and those receiving anxiolytics.
-By examining co-prescription patterns, we aimed to understand the nature of polypharmacy within these groups.
-The rate of polypharmacy differs between these two groups.
-While same-class polypharmacy is more prevalent among individuals treated with antidepressants than among those treated with anxiolytics, multi-class polypharmacy predominates among those treated with anxiolytics.
-In both groups, multi-class polypharmacy is ten times more prevalent than same-class polypharmacy.
-The high occurrence of multi-class polypharmacy in our findings aligns with previous studies, which show that antidepressants and anxiolytics are often co-prescribed with other medications [@Shrivastava2013], and multi-class regimens contribute the most to the occurrence of psychopharmaca polypharmacy [@de2004polypharmacy].
-This highlights the interconnected nature of psychopharmaca prescription patterns.
+This network analysis of dispensing data in individuals using antidepressants or anxiolytics revealed distinct polypharmacy patterns between these groups.
+While same-class polypharmacy was more common among antidepressant users, multi-class polypharmacy predominated among those receiving anxiolytics.
+Notably, in both groups, multi-class polypharmacy was at least ten times more prevalent than same-class polypharmacy.
+Seven medication classes exhibited high eigenvector centrality, indicating their strong influence on co-prescription dynamics.
+These include medications for the alimentary tract and metabolism (ATC code `A`), blood and blood-forming organs (`B`), cardiovascular system (`C`), respiratory system (`R`), and analgesics (`N02`).
+These classes do not merely appear frequently but also serve as key connectors within prescribing networks, linking psychiatric treatments to chronic disease management.
+Their centrality suggests that they play a role in structuring multi-class polypharmacy, either as standard co-prescriptions due to clinical guidelines or as necessary adjuncts in managing comorbidities.
 
-To better understand these co-prescription patterns, the DPN was constructed to identify medication classes with strong centralities in relation to antidepressants and anxiolytics.
-Following @Cavallo2012, the weight of the adjacency matrix was the frequency of co-prescriptions or single prescriptions.
-We adjusted the weight to account for varying prescription dosages, alleviating previous limitation where the DDD was restricted to 1 [@Cavallo2012].
-Seven medication classes clustered together, forming a modular structure.
-This modularity reflects the organization of medications into anatomically or functionally related groups, where certain drugs were found to form densely interconnected nodes preferentially linked to each other [@Bazzoni2015].
-These network properties highlight the utility of DPNs in revealing prescribing patterns and their underlying clinical rationale.
+Our findings align with previous research showing that antidepressants and anxiolytics are frequently co-prescribed with other medications [@Shrivastava2013], and that multi-class regimens contribute most to psychopharmaca polypharmacy [@de2004polypharmacy].
+Furthermore, there have been established bidirectional associations between depression/anxiety and chronic illnesses [@qi2024longitudinal].
+Conditions such as diabetes mellitus, thyroid disorders, and asthma have been linked to an increased risk of depression [@jang2024temporal].
+The need for long-term pharmacological management further drives co-prescription patterns.
+Additionally, chronic illness-related anxiety can contribute to heightened prescribing of anxiolytics [@lebel2020health].
+This underscores the interconnected nature of psychopharmaca prescribing patterns and highlights the complexity of medication management in these populations.
 
-Seven medication classes were identified with a high eigenvector centrality in our DPN.
-Unsurprisingly, antidepressants and anxiolytics exhibited high centrality, as these medication classes were central to our DPN.
-Beyond these, medication classes with high centrality included those for the alimentary tract and metabolism (WHO ATC code `A`), blood and blood-forming organs (code `B`), cardiovascular system (code `C`), respiratory system (code `R`), and analgesics (code `N02`).
-These classes are closely associated with chronic illnesses.
-This finding aligns with previous investigation highlighting the bidirectional associations between depression/anxiety and chronic physical illnesses [@qi2024longitudinal].
-For instance, a study demonstrated that diabetes mellitus, thyroid disorders, and asthma increased the risk of depression [@jang2024temporal].
-Moreover, these conditions often necessitate long-term pharmacological interventions, increasing the likelihood of co-prescription.
-Similarly, fears of worsening symptoms in chronic diseases can lead to heightened health-related anxiety [@lebel2020health].
-The frequent coexistence of physical and mental health conditions in chronic diseases underscores the rationale for polypharmacy regimens [@nizamie2015rational].
+DPN complements traditional drug utilization analyses by capturing the structural properties of prescribing behaviors.
+Beyond evaluating individual drug utilization or basic pairwise co-prescriptions, DPN provides a structural perspective by mapping the interconnections between medications within a broader prescribing network [@Bazzoni2015].
+The network approach is a particularly useful method for understanding complex prescribing dynamics, which allows for the identification of central medication classes that influence polypharmacy patterns.
+The high centrality of certain medication classes suggests they serve as critical connectors in treatment regimens, providing the basis for further monitoring and evaluation.
+
+By mapping the relationships between medications, DPN enables the detection of patterns that would be challenging to observe through standard statistical methods.
+For instance, the high centrality of certain medication classes suggests that they play a pivotal role in multi-class polypharmacy, likely due to their involvement in managing both psychiatric and non-psychiatric conditions.
+As such, network analysis is a suitable approach for generating hypothesis, which has also been thoroughly discussed by @Askar2021.
 
@@
 Second, while the adjustment of weights based on DDD introduces a novel element to the analysis, it is important to note that DDD values are not always equal to one, as defined by the WHO ATC system.
-However, our approach aligns with the general recommendation of @Cavallo2012, where DDD of 1 forms the basic of network edges.
+Our study adopted a DDD-based weighting approach to refine network edges, aligning with the recommendation of @Cavallo2012.
 The adjusted weighting penalizes values deviating significantly from 1, reducing their impact on the network.
-Future studies should explore alternative weighting methods to further refine the analysis.
+Future research should explore alternative weighting techniques, such as patient-level dosage adjustments, to enhance network precision.
 
-Despite the limitations, our study demonstrates the utility of DPN as a powerful, data-driven approach to analyzing prescription dispensing data.
-By modelling intricate co-prescription patterns, DPN filters medication classes based on network properties, offering deeper insights into prescribing behaviors.
-These insights can reveal important trends in medication use, which can be essential to public health monitoring.
-By capturing the complexity of drug prescription relationships, DPN holds significant potential to improve decision-making in both clinical and administrative contexts
+Despite the limitations, our study demonstrates the utility of DPN as a powerful, data-driven approach to analyzing medication dispensing data.
+By modelling intricate co-prescription patterns, DPN filters medication classes based on network properties, offering insights into prescribing behaviors.
+These insights can reveal important trends in medication use, which can be useful to public health monitoring.
+By capturing the complexity of drug prescription relationships, DPN holds significant potential to improve decision-making in both clinical and administrative contexts.
+
+Future DPN studies on individuals using antidepressants or anxiolytics should adopt a more fine-grained ATC classification to identify specific medications driving polypharmacy patterns within the currently identified seven medication classes.
+A more granular approach could reveal whether certain drugs disproportionately contribute to multi-class polypharmacy and whether these prescribing trends vary across patient demographics or healthcare settings.
+Such insights could refine our understanding of prescribing behaviors and inform targeted interventions for optimizing medication regimens.
+
+::: {.content-hidden}
+- Following @Cavallo2012, the weight of the adjacency matrix was the frequency of co-prescriptions or single prescriptions.
+We adjusted the weight to account for varying prescription dosages, alleviating previous limitation where the DDD was restricted to 1 [@Cavallo2012].
+- Additionally, the predominance of multi-class polypharmacy in individuals using antidepressants or anxiolytics suggests the need for a more integrated approach to managing patients receiving psychotropic medications, ensuring that treatment decisions account for both psychiatric and non-psychiatric conditions.
+:::
 
@@
 This study utilized DPN to evaluate the influence of specific medication classes on prescribing patterns of antidepressants and anxiolytics.
-By focusing on co-prescription patterns, we identified seven medication classes with significant eigenvector centrality, reflecting their critical role in polypharmacy regimens.
+By focusing on co-prescription patterns, we identified seven medication classes with significant eigenvector centrality, reflecting their critical role in polypharmacy regimens for individuals using anxiolytics and antidepressants.
 This study highlights the potential of network-based approaches to narrow down high-impact medications for further evaluation.

### 2025-03-17 _targets.R
Render the supplementary file

@@ -366,6 +366,7 @@ list(
   tar_quarto(report_seasonality, "docs", profile = "seasonality", priority = 0),
   tar_quarto(report_spectral, "docs", profile = "spectral", priority = 0),
   tar_quarto(article, "docs/article.qmd"),
+  tar_quarto(supplementary, "docs/supplementary.qmd"),
   tar_quarto(readme, "README.qmd", priority = 0)
 
 )

### 2025-04-08 src/R/network.R
Omit the diagonal of adjacency matrices from the DPN

@@ -199,16 +199,22 @@ mkGraph <- function(atc_tbl, method = "density", type = "additive") {
   return(graph)
 }
 
-getMetrics <- function(graph) {
+getMetrics <- function(graph, rm_loop = TRUE) {
   #' Calculate Graph Metrics
   #'
   #' Calculate graph metrics from a given medication graphs
   #' @param graph Medication graph from pairwises of ATC
+  #' @param rm_loop A boolean indicating whether to remove the loop
   #' @return A data frame containing node names and its metrics
 
   is_graph <- igraph::is_igraph(graph)
 
   if (is_graph) {
+
+    # Remove loops (diagonal) as indicated
+    graph %<>% igraph::simplify(remove.loops = rm_loop)
+
+    # Calculat the metrics
     degree   <- igraph::degree(graph)
     strength <- igraph::strength(graph)
     pagerank <- igraph::page_rank(graph) %>% extract2("vector")
@@ -216,6 +222,7 @@ getMetrics <- function(graph) {
       extract2("vector") %>%
       divide_by(sum(.))
 
+    # Tabulate the metrics
     metrics <- data.frame(eigen, pagerank, degree, strength) %>%
       tibble::add_column("group" = rownames(.), .before = 1)
 

### 2025-05-02 docs/article.qmd
Distinguish co-prescription from polypharmacy

@@
 title: >
-  A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands from 2018 to 2022
+  A temporal network analysis of drug co-prescription during antidepressant and anxiolytic dispensing in the Netherlands from 2018 to 2022
 
@@
   - Prescription Registry
-  - Polypharmacy
+  - Co-prescription
   - Mental Health   
@@
 
-In psychiatry, polypharmacy is defined as a patient with at least two concurrent psychiatric medications.
+In psychiatry, polypharmacy is defined as a patient with at least two concurrent psychiatric medications [@Shrivastava2013].
 With a prevalence between 13-90%, psychiatric polypharmacy manifests in five categories, namely same-class, multi-class, adjunctive, augmentation, and total polypharmacy [@Shrivastava2013].
@@
 
-## Data pre-processing
+## Data pre-processing to build the data matrix
 
@@
 
-### Summarizing polypharmacy
+### Summarizing co-prescription
 
-This study explored same-class, multi-class, and total polypharmacy.
+This study explored same-class, multi-class, and total co-prescription.
 The summary statistics were based on prescription-day data aggregated at the population level over the year.
@@
 For example, if seven medications are prescribed for one day, it accounts for 7 prescription-days.
-The mean and standard deviation represent the average number of prescription-days per person for any polypharmacy regimen.
+The mean and standard deviation represent the average number of prescription-days per person for any co-prescription regimen.
 
@@
 IADB recorded `r n_patient` patients having at least one dispensing of antidepressants or anxiolytics within five years of data extraction.
-@tbl-overview-patient captures the dynamics of the population from 2018 to 2022.
+@tbl-overview-patient captures the demographical dynamics of the population from 2018 to 2022.
 The ratio of male to female only varied slightly, and the average age steadily increased over the year.
@@
 
-## Polypharmacy in the population
+## Co-prescription in the population
 
-@tbl-res-poly outlines the type of polypharmacy in the population.
+@tbl-res-poly outlines the type of co-prescription in the population.
 Two statistics are reported in @tbl-res-poly: the sum and the mean with its standard deviation.
-The sum indicates the total prescription-days of polypharmacy within a year.
+The sum indicates the total prescription-days of co-prescription within a year.
 Thus, we can read the findings as follow:
 
-> "In 2018, same-class polypharmacy of antidepressants occurred for a total of 73,528 prescription-days across the population, with an average of 0.06 prescription-days per person.
-For every 100 people prescribed with antidepressants, there were approximately 6 days in total during which same-class polypharmacy regimens occurred."
+> "In 2018, same-class co-prescription of antidepressants occurred for a total of 73,528 prescription-days across the population, with an average of 0.06 prescription-days per person.
+For every 100 people prescribed with antidepressants, there were approximately 6 days in total during which same-class co-prescription regimens occurred."
 
 ```{r tbl-res-poly}
-#| tbl-cap: Summary statistics of different psychiatric polypharmacy categories
+#| tbl-cap: Summary statistics of different psychiatric co-prescription categories
 
@@
   flextable::add_header_row(
-    values    = c("", "Population Level", "Per Person (Mean [SD])", "Total Polypharmacy"),
+    values    = c("", "Population Level", "Per Person (Mean [SD])", "Total Co-prescription"),
     colwidths = c(2, 2, 2, 2),
@@
       c(
-        "The total occurrence of polypharmacy on the population level/perscription-day",
-        "The expected occurrence of polypharmacy per person/perscription-day",
-        "Prescription day is defined as the number of dispensed medication per day"
+        "The total occurrence of co-prescription on the population level/perscription-day",
+        "The expected occurrence of co-prescription per person/perscription-day",
+        "Prescription day is defined as the number of dispensed medication per day",
+        "Multi-class co-prescription is defined as the co-prescription of medications from different ATC classification"
       )
@@
 ```{r fig-hi-eigen}
-#| fig-cap: Clusters of medication with a significant influence on how antidepressants and anxiolytics are prescribed
+#| fig-cap: Clusters of medication with a significant co-prescription patterns on antidepressant and anxiolytic dispensing
 #| fig-width: 9
@@
 
-This network analysis of dispensing data in individuals using antidepressants or anxiolytics revealed distinct polypharmacy patterns between these groups.
-While same-class polypharmacy was more common among antidepressant users, multi-class polypharmacy predominated among those receiving anxiolytics.
-Notably, in both groups, multi-class polypharmacy was at least ten times more prevalent than same-class polypharmacy.
+This network analysis of dispensing data in individuals using antidepressants or anxiolytics revealed distinct co-prescription patterns between these groups.
+While same-class co-prescription was more common among antidepressant users, multi-class co-prescription predominated among those receiving anxiolytics.
+Notably, in both groups, multi-class co-prescription was at least ten times more prevalent than same-class co-prescription.
 Seven medication classes exhibited high eigenvector centrality, indicating their strong influence on co-prescription dynamics.
@@
 These classes do not merely appear frequently but also serve as key connectors within prescribing networks, linking psychiatric treatments to chronic disease management.
-Their centrality suggests that they play a role in structuring multi-class polypharmacy, either as standard co-prescriptions due to clinical guidelines or as necessary adjuncts in managing comorbidities.
+Their centrality suggests that they play a role in structuring multi-class co-prescription, either as standard co-prescriptions due to clinical guidelines or as necessary adjuncts in managing comorbidities.
 
@@
 Beyond evaluating individual drug utilization or basic pairwise co-prescriptions, DPN provides a structural perspective by mapping the interconnections between medications within a broader prescribing network [@Bazzoni2015].
-The network approach is a particularly useful method for understanding complex prescribing dynamics, which allows for the identification of central medication classes that influence polypharmacy patterns.
+The network approach is a particularly useful method for understanding complex prescribing dynamics, which allows for the identification of central medication classes that influence co-prescription patterns.
 The high centrality of certain medication classes suggests they serve as critical connectors in treatment regimens, providing the basis for further monitoring and evaluation.
@@
 By mapping the relationships between medications, DPN enables the detection of patterns that would be challenging to observe through standard statistical methods.
-For instance, the high centrality of certain medication classes suggests that they play a pivotal role in multi-class polypharmacy, likely due to their involvement in managing both psychiatric and non-psychiatric conditions.
-As such, network analysis is a suitable approach for generating hypothesis, which has also been thoroughly discussed by @Askar2021.
+For instance, the high centrality of certain medication classes suggests that they play a pivotal role in multi-class co-prescription, likely due to their involvement in managing both psychiatric and non-psychiatric conditions.
+As such, network analysis is a suitable approach for generating hypotheses for further causal or predictive studies, which has also been thoroughly discussed by @Askar2021.
 
@@
 By modelling intricate co-prescription patterns, DPN filters medication classes based on network properties, offering insights into prescribing behaviors.
-These insights can reveal important trends in medication use, which can be useful to public health monitoring.
+These insights can reveal important trends in medication use, which can be useful to pharmaceutical reviews and public health monitoring.
 By capturing the complexity of drug prescription relationships, DPN holds significant potential to improve decision-making in both clinical and administrative contexts.
 
-Future DPN studies on individuals using antidepressants or anxiolytics should adopt a more fine-grained ATC classification to identify specific medications driving polypharmacy patterns within the currently identified seven medication classes.
-A more granular approach could reveal whether certain drugs disproportionately contribute to multi-class polypharmacy and whether these prescribing trends vary across patient demographics or healthcare settings.
+Future DPN studies on individuals using antidepressants or anxiolytics should adopt a more fine-grained ATC classification to identify specific medications driving co-prescription patterns within the currently identified seven medication classes.
+A more granular approach could reveal whether certain drugs disproportionately contribute to multi-class co-prescription and whether these prescribing trends vary across patient demographics or healthcare settings.
 Such insights could refine our understanding of prescribing behaviors and inform targeted interventions for optimizing medication regimens.

### 2025-05-02 docs/exec-summary/_source-data.qmd
Distinguish co-prescription from polypharmacy

@@
 Except for the over the counter drugs and medication dispensed during hospitalization, other medication records for each patient are complete, mainly due to high patient-pharmacy commitment in the Netherlands.
-This analysis includes daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.
+This analysis includes daily medication dispensing from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.

### 2025-05-07 docs/abstract/_abstract-short.qmd
Focus the manuscript on co-prescription instead of polypharmacy

@@
 **Background:**
-Drug prescription networks (DPNs) model the temporal dynamics of medication co-prescription within a population.
-Understanding these networks can provide insights into polypharmacy and prescribing behaviors.
+Drug prescription networks (DPNs) model the temporal dynamics of medication co-prescription within a population. Understanding prescription networks can provide insights into prescribing behaviors.
 
 **Objectives:**
-This study assesses the structural characteristics of temporal DPNs derived from daily co-prescriptions of antidepressants, anxiolytics, and other therapeutic drug classes.
-By analyzing these networks using eigenvector centrality, we identify influential medications and prescribing patterns.
+This study assesses the characteristics of temporal DPNs derived from daily co-prescriptions of antidepressants, anxiolytics, and all other therapeutic drug classes.
+By analyzing these networks using eigenvector centrality, we identified influential medications and prescribing patterns.
 
 **Methods:**
-We utilized the IADB.nl database, including prescriptions from 128 Dutch pharmacies (2018–2022).
-A closed cohort of patients prescribed antidepressants/anxiolytics was extracted.
+Data were obtained from the University of Groningen IADB.nl database, including prescriptions from 128 Dutch pharmacies (2018–2022).
+A static cohort of patients prescribed antidepressants (ATC `N06A`) / anxiolytics (`N05B`) was extracted.
 Medications were classified using the Anatomical Therapeutic Chemical (ATC) system into 24 therapeutic classes.
@@
 Eigenvector centrality ($c_e$) quantified relative nodal importance.
-Weekly-aggregated data included prescriptions ($n_c$), number of patients, claim-to-patient ratio, and eigenvector centrality.
+Weekly-aggregated data included prescriptions ($n_c$), number of patients, dispensing-to-patient ratio, and eigenvector centrality.
 Singular spectrum analysis decomposed trends.
@@
 **Results:**
-Antidepressants (ATC `N06A`, $c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics (`N05B`, $c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) had high eigenvector centrality, indicating frequent co-prescription.
-Additional high-centrality groups included medications for alimentary and metabolism (`A01-A16`), blood (`B01-B06`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory (`R01-R07`).
+Antidepressants ($c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics ($c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) had high eigenvector centrality, indicating frequent co-prescription.
+Additional high-centrality groups included medications for alimentary and metabolism (`A01-A16`), blood (`B01-B06`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory diseases (`R01-R07`).
 
 **Discussion:**
-DPNs reveal key polypharmacy patterns.
-High-centrality medications highlight potential targets for drug monitoring.
-This approach aids in identifying influential medications and refining prescribing oversight.
+DPNs revealed key co-prescription patterns. High-centrality medications highlight potential targets for drug monitoring.

### 2025-05-07 docs/article.qmd
Focus the manuscript on co-prescription instead of polypharmacy

@@
 A DPN is a graphical representation where medications correspond to nodes, and edges represent co-prescription relationships between them.
-Typically, simple undirected graphs are represented by a square symmetric adjacency matrix $A$, where each nonzero element $a_{ij}$ indicates that medications $i$ and $j$ were co-prescribed on a given day.
+Typically, simple undirected graphs are represented by a square symmetric adjacency matrix $A$, where each nonzero element $A_{ij}$ indicates that medications $i$ and $j$ were co-prescribed on a given day.
 A population-level DPN can be constructed by aggregating individual patient networks through matrix addition [@Cavallo2012].
@@
 Building on prior studies [@Cavallo2012; @Bazzoni2015], we hypothesize that eigenvector centrality serves as a meaningful quantitative indicator of polypharmacy.
-Therefore, this study aims to assess the structural characteristics of temporal DPNs, focusing on the role of eigenvector centrality in identifying influential medications and prescribing patterns in mental health treatments.
+Therefore, this study aimed to assess the structural characteristics of temporal DPNs, focusing on the role of eigenvector centrality in identifying associated medications in adult patients prescribed for antidepressant or anxiolytic.
 
@@
 
-## Source of data
+## Source of data and study population
 
@@
 The adjacency matrix $A$ has dimensions of $|\mathcal{V}| \times |\mathcal{V}|$, where $|\mathcal{V}|$ is the number of nodes in a graph.
-Each element of $a_{ij}$ is the edge, where in an unweighted graph, $a_{ij} = 1$ if a connection exists between $\mathcal{v}_i$ and $\mathcal{v}_j$, and $a_{ij} = 0$ otherwise.
-In a weighted graph, $a_{ij}$ can take any real value ($a_{ij} \in \mathbb{R}$) depending on the application [@estrada2012structure].
+Each element of $A_{ij}$ is the edge, where in an unweighted graph, $A_{ij} = 1$ if a connection exists between $\mathcal{v}_i$ and $\mathcal{v}_j$, and $A_{ij} = 0$ otherwise.
+In a weighted graph, $A_{ij}$ can take any real value ($A_{ij} \in \mathbb{R}$) depending on the application [@estrada2012structure].
 
@@
 Eigenvector centrality is helpful to identify influential medications and narrow down high-impact medications for drug monitoring.
+We defined high and low eigenvector centrality relative to the expected value $\frac{1}{n}$, based on the null model of uniform connectivity (see "Determining relative importance").
 This study focused on eigenvector centrality to evaluate which medications have a significant influence on how antidepressants and anxiolytics are prescribed.
-@eq-eigen-centrality outlines the calculation of eigenvector centrality; $c_i$ and $c_j$ are the centralities of node $\mathcal{v}_i$ and $\mathcal{v}_j$, respectively; $\lambda$ is the eigenvalue; $a_{ji}$ is an element on row $j$ and column $i$ from an adjacency matrix $A$, representing the connection between node $\mathcal{v}_j$ and $\mathcal{v}_i$.
+@eq-eigen-centrality outlines the calculation of eigenvector centrality; $c_i$ and $c_j$ are the centralities of node $\mathcal{v}_i$ and $\mathcal{v}_j$, respectively; $\lambda$ is the eigenvalue; $A_{ji}$ is an element on row $j$ and column $i$ from an adjacency matrix $A$, representing the connection between node $\mathcal{v}_j$ and $\mathcal{v}_i$.
 
 $$
-\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} a_{ji} \cdot c_j
+\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} A_{ji} \cdot c_j
 $$ {#eq-eigen-centrality}
@@
 
-Since the sum of all eigenvector centralities $c_i$ in equation [-@eq-eigen-centrality] is equal to one, a network with similarly connected nodes will have an eigenvector centrality $c_i$ = $\frac{1}{n}$ for each node, where $n$ is the number of nodes.
-The value of $c_i = \frac{1}{n}$ is the expected eigenvector centrality in a densely connected network where the occurrence of an edge $\{\mathcal{v}_i, \mathcal{v}_j\} \in \mathcal{E}$ has the same probability for all nodes.
-Per the central limit theorem, the value $\frac{1}{n}$ can be parameterized as a mean of a normal distribution, where all instances of eigenvector centrality will follow the distribution, $c_i \sim \mathcal{N}(\mu, \sigma)$.
-A one-sample Student's T-test was performed to assess how much each eigenvector centrality differs from the expected values.
-As such, eigenvector centrality greater than $\frac{1}{n}$ can be considered high, and the value below it can be considered low.
-The p-values was corrected for a type-I error using Bonferroni method.
+Since the sum of all eigenvector centralities $c_i$ in equation [-@eq-eigen-centrality] equals 1, the expected eigenvector centrality for each node in a uniformly connected network is $\frac{1}{n}$, where $n$ is the total number of nodes.
+In such a network, each node has an equal probability of being connected to any other, and thus no node is more "influential" than another.
+This expected value value, $\frac{1}{n}$, serves as a baseline under a null model of uniform connectivity.
+Assuming eigenvector centrality scores approximately follow a normal distribution, we applied a one-sample Student's T-test with Bonferroni correction to assess how much each eigenvector centrality differs from the expected values.
+Nodes with $c_i$ greater than $\frac{1}{n}$ were categorized as having high eigenvector centrality, and those below the expected value were considered low.
 
@@
 
-## Weekly variation of medication dispensing
+## Cyclicality and seasonality of medication dispensing
 
-The highest average of medication dispensing occurred on `r hi_claim$day`, with an average of `r hi_mean` [SD: `r hi_claim$sd_claim`].
-Meanwhile, the lowest average of medication dispensing occurred on `r lo_claim$day`, with an average of `r lo_mean` [SD: `r lo_claim$sd_claim`] dispensing.
-A large margin of difference between the highest and lowest average number of dispensing implies daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in @tbl-overview-daily.
+Visual inspection of daily dispensing volumes revealed consistent weekly cycles.
+Dispensing peaked on `r hi_claim$day`, with an average of `r hi_mean` [SD: `r hi_claim$sd_claim`] and dropped to its lowest on `r lo_claim$day`, with an average of `r lo_mean` [SD: `r lo_claim$sd_claim`] dispensing.
+The variation between weekends and weekdays suggested a regular and repeating structure in the data.
+A large margin of difference between the highest and lowest average number of dispensing implied daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in @tbl-overview-daily.
 The cyclical patterns are detailed in the supplementary material section S2.1.
+Seasonality was explored as dependencies at daily and weekly lags and further described in the supplementary material section S2.2.
 
@@
 The largest graph in @fig-ssa represents the reconstructed time-series (green line) and its original data points (gray line).
-Other decomposition results are reported in the supplementary file section S2.2.
+Other decomposition results are reported in the supplementary file section S2.3.
 
@@
 Seven medication classes exhibited high centrality, as shown in @fig-hi-eigen and @tbl-desc.
-Notably, highly dispensed medications generally had high eigenvector centrality, which aligns with the theoretical expectations from @eq-eigen-centrality.
-However, despite a higher number of dispensing (`r diffMed(antidepressants, respiratory, reportMedClaim)`), antidepressants had lower eigenvector centrality than medications for the respiratory system (`r diffMed(antidepressants, respiratory, reportMedEigen)`).
+Notably, highly dispensed medications generally had high eigenvector centrality, consistent with the theoretical expectations from @eq-eigen-centrality.
+However, this relationship was not strictly proportional.
+For example, although antidepressants had a higher number of dispensing compared to medications for the respiratory system (`r diffMed(antidepressants, respiratory, reportMedClaim)`), they exhibited lower eigenvector centrality (`r diffMed(antidepressants, respiratory, reportMedEigen)`).
 A similar pattern was observed for anxiolytics, which had more dispensing than analgesics (`r diffMed(anxiolytics, analgesics, reportMedClaim)`) but lower eigenvector centrality (`r diffMed(anxiolytics, analgesics, reportMedEigen)`).
+This reflects that eigenvector centrality captures not just volume but also the influence of connection sin the network, highlighting that commonly dispensed drug within a population may not necessarily occupy the most central network positions.
 
@@
 
-This network analysis of dispensing data in individuals using antidepressants or anxiolytics revealed distinct co-prescription patterns between these groups.
+This network analysis of dispensing data in individuals using antidepressants or anxiolytics revealed distinct co-prescription patterns.
 While same-class co-prescription was more common among antidepressant users, multi-class co-prescription predominated among those receiving anxiolytics.
@@
 These classes do not merely appear frequently but also serve as key connectors within prescribing networks, linking psychiatric treatments to chronic disease management.
-Their centrality suggests that they play a role in structuring multi-class co-prescription, either as standard co-prescriptions due to clinical guidelines or as necessary adjuncts in managing comorbidities.
+Their centrality suggests that they play a role in structuring multi-class co-prescription, either as standard co-prescriptions due to clinical guidelines or as necessary adjuncts in managing comorbidities or side effects, e.g., ATC `A` class.
 
-Our findings align with previous research showing that antidepressants and anxiolytics are frequently co-prescribed with other medications [@Shrivastava2013], and that multi-class regimens contribute most to psychopharmaca polypharmacy [@de2004polypharmacy].
-Furthermore, there have been established bidirectional associations between depression/anxiety and chronic illnesses [@qi2024longitudinal].
+The predomination of multi-class co-prescription among anxiolytics recipients is consistent with the recommendations in the Dutch Huisartsengenootschap [NHG; @NHG2019Anxiety].
+Specifically, the NHG guideline for anxiety disorders advises short-term benzodiazepine use, limited to two to four weeks, as an adjunct to Selective Serotonin Reuptake Inhibitors (SSRIs) during treatment initiation.
+In contrast, the NHG guideline for depressive disorders recommends initiating pharmacotherapy with a single SSRI and discourages the combination of multiple antidepressants [@NHG2023Depression].
+Therefore, the higher rate of multi-class co-prescription observed among anxiolytic users is consistent with evidence-based clinical practice, rather than an artifact of sampling or measurement methods.
+
+Our findings also align with previous research showing that antidepressants and anxiolytics are frequently co-prescribed with other medications [@Shrivastava2013], and that multi-class regimens contribute most to psychopharmaca polypharmacy [@de2004polypharmacy].
+Additionally, our study offers a more granular view of these patterns by characterizing their network properties.
+By distinguishing between same-class and multi-class co-prescriptions and evaluating medication centrality, we discover that certain drug classes function as hubs within the prescribing landscape.
+These characteristics likely reflect the underlying burden of multimorbidity in the population, where the bidirectional associations between depression/anxiety and chronic illnesses is well established [@qi2024longitudinal].
 Conditions such as diabetes mellitus, thyroid disorders, and asthma have been linked to an increased risk of depression [@jang2024temporal].
@@
 
-This study utilized DPN to evaluate the influence of specific medication classes on prescribing patterns of antidepressants and anxiolytics.
-By focusing on co-prescription patterns, we identified seven medication classes with significant eigenvector centrality, reflecting their critical role in polypharmacy regimens for individuals using anxiolytics and antidepressants.
-This study highlights the potential of network-based approaches to narrow down high-impact medications for further evaluation.
+This study demonstrates the utility of DPN in uncovering the patterns of co-prescriptions among antidepressant and anxiolytic recipients.
+We found that multi-class regimens were markedly more prevalent, particularly among anxiolytic users, consistent with clinical guidelines.
+Moreover, we identified seven highly central medication classes that act as hubs in the prescribing network, linking psychiatric medications to the management of chronic somatic conditions.
+These findings emphasize the role of multimorbidity in shaping co-prescription behaviors and highlight the importance of these seven classes in both psychiatric care and broader chronic disease management.
+Our study contributes a network-based perspective to drug utilization research, offering an alternative approach to identifying high-impact medication classes that warrant further monitoring and future investigation.
 

### 2025-05-07 docs/exec-summary/_preprocessing.qmd
Explain table 2 in the result section
Focus the manuscript on co-prescription instead of polypharmacy

@@
 
-Daily medication claims are represented as tabular data where each row corresponds to an individual patient’s prescriptions.
-The data was transformed into a square matrix summarizing co-prescriptions and single prescriptions to construct a graph-based representation.
-The rows and columns of the matrix represent groups of medications, while each matrix element indicates the frequency of a specific prescription pattern.
-Elements in the off-diagonal positions represent co-prescriptions between two medications, while diagonal elements represent single prescriptions.
-This matrix can be interpreted as a graph, where each medication is a node, and the edges represent co-prescription frequencies.
-The weight of the edge is derived from the number of daily claims.
-Originally, all defined daily doses (DDD) were assumed to equal 1, leading to straightforward edge weights based on raw counts.
-However, since not all medications have DDD values of 1, this assumption could lead to inaccurate representations.
-To address this, weights were adjusted using the density of a normal distribution.
-The expected value ($\mu$) was set to 1 to prioritize DDD = 1, and the standard deviation ($\sigma$) was set to $\frac{1}{3}$ to allow for a gradual reduction in weight as DDD deviates from 1.
-This adjustment ensures a more accurate weighting system that reflects real-world prescription patterns while preserving information about medications with non-standard DDD values.
+At the individual level, each patient's daily prescription record at time $t$ was encoded into a square matrix $A_t^{(i)}$, where rows and columns represent medication classes according to the ATC classification.
+An off-diagonal entry $A_{t_{jk}}^{(i)} = 1$ indicates that medication classes $i$ and $k$ were co-prescribed on the same day for individual $i$, while a diagonal entry $A_{t_{jj}}^{(i)} = 1$ captures the presence of a single prescription of medication $j$.
+To derive the population-level DPN, all individual-level daily prescription matrix $A^{(i)}$ were aggregated by computing their element-wise sum.
+
+$$A_t = \displaystyle \sum_i A_t^{(i)}$$ {#eq-DPN}
+
+The population matrix $A_t$ captures the frequency of co-prescriptions (off-diagonal) and single prescriptions (diagonal) across the dataset at the specified time $t$.
+Each element $A_{t_{jk}}$ in the matrix was interpreted as the number of patients being prescribed with medication classes $j$ and $k$ on the same day $t$.
+$A_t$ was represented as a weighted undirected graph, where each node corresponds to a medication class and edges reflect co-prescription frequencies.
+In the original work of DPN, all defined daily dose (DDD) were assumed equal to 1, allowing for applying raw counts as the edge weights.
+However, since not all medications have DDD = 1, this assumption could lead to inaccurate representations.
+To enhance the accuracy of edge weights, we accounted for the heterogeneity in DDD.
+The weights were adjusted using the density of a normal distribution.
+The expected value ($\mu$) was set to the base weight $\omega_B$ of 1 to prioritize DDD = 1, and the standard deviation ($\sigma$) was set to $\frac{1}{3}$ to allow for a gradual reduction in weight as DDD deviates from 1.
 

### 2025-05-07 docs/exec-summary/_source-data.qmd
Focus the manuscript on co-prescription instead of polypharmacy

--- 2024-04-02 docs/exec-summary/_source-data.qmd
@@
 
-All data in this investigation originated from IADB.nl, a dynamic pharmacy database containing prescription data from 1994 which still grow expansively.
-The database covers approximately 120 community pharmacies serving over one million patients.
+All data in this study originated from the University of Groningen IADB.nl, a dynamic pharmacy database containing prescription data from 1994 which still grows expansively.
+The database covers approximately 128 community pharmacies serving over one million patients and was accessed on the 20^th^of September, 2023.
 All patients are recorded in the database, irrespective of health care insurance, where the prescription rates, age, and gender are generalizable to represent the Netherlands [@Visser2013].
@@
 Except for the over the counter drugs and medication dispensed during hospitalization, other medication records for each patient are complete, mainly due to high patient-pharmacy commitment in the Netherlands.
-This analysis include daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.
+
+This analysis includes daily medication dispensing from a static cohort of adults aged 18-65 years old and prescribed for anxiolytic or antidepressant at least once in the time span from 2018 to 2022.

### 2025-05-07 docs/supplementary.qmd
Focus the manuscript on co-prescription instead of polypharmacy

@@
 #| fig-width: 14
-#| fig-height: 5
+#| fig-height: 8
 #| fig-cap: Daily cyclical pattern captured on a de-trended data
@@
 
+\pagebreak
+
+## Daily ACF and PACF plots
+
+```{r fig-season-day}
+#| fig-width: 14
+#| fig-height: 8
+#| fig-cap: Daily cyclical pattern captured on a de-trended data
+
+tar_read(plt_acf_day)[[4]]
+tar_read(plt_pacf_day)[[4]]
+
+```
+
+\pagebreak
+
+## Weekly ACF and PACF plots
+
+```{r fig-season-week}
+#| fig-width: 14
+#| fig-height: 8
+#| fig-cap: Daily cyclical pattern captured on a de-trended data
+
+tar_read(plt_acf_week)[[4]]
+tar_read(plt_pacf_week)[[4]]
+
+```
+
 \normalpapersize
 
-## Time-series decomposition
+## Time-series decomposition of medication dispensing records
 
@@
 #| fig-width: 16
-#| fig-height: 12
+#| fig-height: 9
 #| fig-pos: H

### 2025-05-07 docs/supplementary.tex
Focus the manuscript on co-prescription instead of polypharmacy

@@
 oscillating functions which contributes to complex seasonality. The
-original data, trend, residuals, and oscillating functions are plotted
-for further inspection. The original data and trend is further evaluated
-using Mann-Kendall trend test.
+oscillatory components extracted from SSA correspond to harmonics,
+namely a distinct periodic signals with different frequencies. These
+harmonics form complex seasonality and captured in pairs of
+eigentriples. The original data, trend, residuals, and oscillating
+functions are plotted for further inspection. The original data and
+trend is further evaluated using Mann-Kendall trend test.
 
@@
 
+\pagebreak
+
+\subsection{Daily ACF and PACF plots}\label{daily-acf-and-pacf-plots}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/fig-season-day-1.pdf}
+
+}
+
+\caption{\label{fig-season-day-1}Daily cyclical pattern captured on a
+de-trended data}
+
+\end{figure}%
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/fig-season-day-2.pdf}
+
+}
+
+\caption{\label{fig-season-day-2}Daily cyclical pattern captured on a
+de-trended data}
+
+\end{figure}%
+
+\pagebreak
+
+\subsection{Weekly ACF and PACF plots}\label{weekly-acf-and-pacf-plots}
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/fig-season-week-1.pdf}
+
+}
+
+\caption{\label{fig-season-week-1}Daily cyclical pattern captured on a
+de-trended data}
+
+\end{figure}%
+
+\begin{figure}
+
+\centering{
+
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/fig-season-week-2.pdf}
+
+}
+
+\caption{\label{fig-season-week-2}Daily cyclical pattern captured on a
+de-trended data}
+
+\end{figure}%
+
 \normalpapersize
 
-\subsection{Time-series decomposition}\label{time-series-decomposition}
+\subsection{Time-series decomposition of medication dispensing
+records}\label{time-series-decomposition-of-medication-dispensing-records}
 

### 2025-07-08 docs/articleSB.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  authoryear,
  review]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\usepackage{fontspec}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{colortbl}
\usepackage{hhline}
\newlength\Oldarrayrulewidth
\newlength\Oldtabcolsep
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{float}
\usepackage{typearea}
\floatplacement{figure}{htbp}
\floatplacement{table}{htbp}
\AtBeginDocument{%
  \storeareas\normalpapersize
}
\BeforeRestoreareas{\cleardoublepage}
\newcommand*\uselandscape{%
  \cleardoublepage
  \KOMAoptions{paper=landscape}%
  \recalctypearea
  \areaset{1.2\textwidth}{1.2\textheight}%
}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands from 2018 to 2022},
  pdfauthor={Aly Lamuri; Spyros Balafas; Eelko Hak; Jens H. Bos; Frederike Jörg; Talitha L. Feenstra},
  pdfkeywords={Graph Theory, Prescription Registry, Polypharmacy, Mental
Health, Public Health Monitoring},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\setlength{\parindent}{6pt}
\begin{document}

\begin{frontmatter}
\title{A temporal network analysis of drug co-prescription around
antidepressants and anxiolytics uses in the Netherlands from 2018 to
2022}
\author[1,2]{Aly Lamuri%
\corref{cor1}%
}
 \ead{a.l.m.lamuri.murdani@rug.nl} 
\author[1]{Spyros Balafas%
%
}

\author[1]{Eelko Hak%
%
}

\author[1]{Jens H. Bos%
%
}

\author[1,3]{Frederike Jörg%
%
}

\author[1]{Talitha L. Feenstra%
%
}

\affiliation[1]{organization={University of
Groningen},city={Groningen},country={Netherlands},countrysep={,},postcodesep={}}
\affiliation[2]{organization={University of
Indonesia},city={Depok},country={Indonesia},countrysep={,},postcodesep={}}
\affiliation[3]{organization={University Medical Centre
Groningen},city={Groningen},country={Netherlands},countrysep={,},postcodesep={}}

\cortext[cor1]{Corresponding author}

\begin{abstract}
\textbf{Background:} Drug prescription networks (DPNs) model the
temporal dynamics of medication co-prescription within a population.
Understanding these networks can provide insights into polypharmacy and
prescribing behaviors.

\textbf{Objectives:} This study assesses the structural characteristics
of temporal DPNs derived from daily co-prescriptions of antidepressants,
anxiolytics, and other therapeutic drug classes. By analyzing these
networks using eigenvector centrality, we identify influential
medications and prescribing patterns.

\textbf{Methods:} We utilized the IADB.nl database, including
prescriptions from 128 Dutch pharmacies (2018--2022). A closed cohort of
patients prescribed antidepressants/anxiolytics was extracted.
Medications were classified using the Anatomical Therapeutic Chemical
(ATC) system into 24 therapeutic classes. Time-varying DPNs were
constructed as undirected graphs using symmetric daily dose-adjusted
co-prescriptions. Eigenvector centrality (\(c_e\)) quantified relative
nodal importance. Weekly-aggregated data included prescriptions
(\(n_c\)), number of patients, claim-to-patient ratio, and eigenvector
centrality. Singular spectrum analysis decomposed trends.

\textbf{Results:} Antidepressants (ATC \texttt{N06A}, \(c_e\): 0.09,
\(n_c\): 28,993) and anxiolytics (\texttt{N05B}, \(c_e\): 0.04, \(n_c\):
14,061) had high eigenvector centrality, indicating frequent
co-prescription. Additional high-centrality groups included medications
for alimentary and metabolism (\texttt{A01-A16}), blood
(\texttt{B01-B06}), cardiovascular (\texttt{C01-C10}), analgesics
(\texttt{N02}), and respiratory (\texttt{R01-R07}).

\textbf{Discussion:} DPNs reveal key polypharmacy patterns.
High-centrality medications highlight potential targets for drug
monitoring. This approach aids in identifying influential medications
and refining prescribing oversight.
\end{abstract}

\begin{keyword}
    Graph Theory \sep Prescription
Registry \sep Polypharmacy \sep Mental Health \sep 
    Public Health Monitoring
\end{keyword}
\end{frontmatter}

\section{Introduction}\label{introduction}

The complexity of health-related phenomena has led to the growing application of network analysis in medicine and epidemiology \citep{Luke2007,Miglio2021}. Graph theory provides the mathematical foundation for network analysis, offering an approach to study the relationships among the entities of a complex system. The early implementations of network analysis focused primarily on transmission, social, and organizational networks. More recently, \citet{Cavallo2012} introduced drug prescription networks (DPNs) to model population-level drug prescription data. \citet{Bazzoni2015} formalized the term, emphasizing its utility in understanding polypharmacy.

Polypharmacy is defined as a patient with at least two concurrent medications. With a prevalence between 13-90\%, polypharmacy in psychiatry manifests itself in five categories, namely same-class, multiclass, adjunctive, augmentation, and total polypharmacy \citep{Shrivastava2013}. Same-class polypharmacy is the use
of multiple drugs of the same class. Multiclass polypharmacy is
the use of multiple medications of different classes indicated for the
same cluster of symptoms. Adjunctive polypharmacy is the use of additional
medications to treat side effects of other medications. Augmentation
polypharmacy is the use of full-dose and sub-dose medications from a
different class for the same symptom cluster. Finally, total
polypharmacy is the total count of all medications used by a patient, psychopharmaca and other classes as well \citep{Shrivastava2013}. For
policy makers, differences in the definition of polypharmacy pose a challenge in
designing a monitoring system \citep{Sirois2016}. DPN can capture
the complex relationships of a system that can vary over time, which is
very relevant for drugs prescribed for mental disorders.

A DPN for an individual on a given day can be formalized as a simple undirected graph where medications correspond to nodes, and edges connecting pairs of nodes represent co-prescription relationships between medications. Typically, simple undirected graphs are represented by a square symmetric matrix with zeros on the diagonal called the adjacency matrix \citep{estrada2012structure}. In the adjacency matrix of the individual-level DPN, nonzero off-diagonal elements correspond to two medications being co-prescribed on a given day.

A population-level DPN on a given day can be constructed from individual-level DPNs through matrix addition of the corresponding adjacency matrices \citep{Cavallo2012}. A DPN at the population level on a given day is then formulated as a weighted undirected graph, which is characterized by a weighted adjacency matrix with weights equal to the counts of medication co-prescription occurrences. Therefore, analyzing the structural characteristics of a DPN over time using both local (medication-level) and global (network-level) graph measures offers valuable insights into co-prescription dynamics and can deepen our understanding of polypharmacy.

Local network statistics, such as node centrality measures, quantify the
importance of a drug in polypharmacy patterns \citep{Askar2021}. Addressing concerns about standardized polypharmacy indicators raised by \citet{Sirois2016} and \citet{Delara2022}, we highlight eigenvector centrality as a key measure for identifying drugs frequently prescribed alongside other influential drugs. Thus, high eigenvector centrality suggests frequent co-prescription with commonly used medications, reflecting co-prescribing trends. Based on previous studies \citep{Cavallo2012, Bazzoni2015}, we hypothesize that eigenvector centrality serves as a meaningful quantitative indicator of polypharmacy. Therefore, this study aims to assess the structural characteristics of temporal DPNs, focusing on the role of eigenvector centrality in identifying influential medications and prescribing patterns in mental health treatments.

\section{Methods}\label{methods}

\subsection{Source of data}\label{source-of-data}

The data used in this study are exported from IADB.nl, a dynamic pharmacy database containing prescription data from 1994, which continues to grow expansively. The database covers approximately 120 community pharmacies serving over one million patients and was accessed on the 20\textsuperscript{th}of September, 2023. All patients are recorded in the database, regardless of health care insurance, where prescription rates, age, and gender can be generalizable to represent the Netherlands \citep{Visser2013}. The database offers a longitudinal record, where each individual has a uniquely anonymized tracking identifier. All records contain fields on the date of drug dispensing, its quantity, dose regimen, number of days prescribed, prescribing physicians, and the Anatomical Therapeutic Chemical (ATC) code. Except for the over the counter drugs and medication dispensed during hospitalization, other medication records for each patient are complete, mainly due to high patient-pharmacy commitment in the Netherlands. This analysis includes daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.

\subsection{Graph theory}\label{graph-theory}

Mathematically, a simple undirected graph \(\mathcal{G}\) is a pair
\(\mathcal{G} = (\mathcal{V}, \mathcal{E})\), where \(\mathcal{V}=\left(1,\dots,n \right)\) is the finite set of nodes and \(\mathcal{E}=\left(\{i,j\} \ |\ i,j\in \mathcal{V},\ i\neq j \right)\) is the finite set of edges with \(\{i,j\}=\{j,i\}\). The adjacency matrix $A\in \{0,1\}^{n\times n}$ of a simple undirected graph \(\mathcal{G}\) with \(|\mathcal{V}|=n\) nodes, is a square symmetric matrix of dimension \(n\times n\) defined as, \[
A_{ij} = 
\begin{cases}
1 & \text{if } \{i, j\} \in \mathcal{E} \\
0 & \text{otherwise}
\end{cases}
\] with \( A_{ij} = A_{ji} \), for all \( i, j \in  \mathcal{V}\) where $i\neq j$. For each day $t$,$t=1,\dots,T$ and each individual $p$, $p=1,\dots,P$ we the adjacency matrix of a simple undirected graph

In a DPN, the
node set
\(\mathcal{V} = \{\mathcal{v}_1, \mathcal{v}_2, \dots, \mathcal{v}_n\}\)
represents a finite set of \(n\) medications. Additionally,
\(\mathcal{E}\) is a finite set of edges, where each edge is a pair of
nodes that corresponds to a co-prescription. In an undirected graph, the
order of \(i, j\) does not matter. Typically, undirected graphs do not
contain self connections,
\(\{\mathcal{v}_i, \mathcal{v}_i\} \notin \mathcal{E}\)
\citep{estrada2012structure}.

A graph can be represented as an adjacency matrix \(A\). The adjacency
matrix \(A\) has dimensions of \(|\mathcal{V}| \times |\mathcal{V}|\),
where \(|\mathcal{V}|\) is the number of nodes in a graph. Each element
of \(a_{ij}\) is the edge, where in an unweighted graph, \(a_{ij} = 1\)
if a connection exists between \(\mathcal{v}_i\) and \(\mathcal{v}_j\),
and \(a_{ij} = 0\) otherwise. In a weighted graph, \(a_{ij}\) can take
any real value (\(a_{ij} \in \mathbb{R}\)) depending on the application
\citep{estrada2012structure}.

\subsection{Data pre-processing}\label{data-pre-processing}

Daily medication claims are represented as tabular data where each row
corresponds to an individual patient's prescriptions. The data was
transformed into a square matrix summarizing co-prescriptions and single
prescriptions to construct a graph-based representation. The rows and
columns of the matrix represent groups of medications, while each matrix
element indicates the frequency of a specific prescription pattern.
Elements in the off-diagonal positions represent co-prescriptions
between two medications, while diagonal elements represent single
prescriptions. This matrix can be interpreted as a graph, where each
medication is a node, and the edges represent co-prescription
frequencies. The weight of the edge is derived from the number of daily
claims. Originally, all defined daily doses (DDD) were assumed to equal
1, leading to straightforward edge weights based on raw counts. However,
since not all medications have DDD values of 1, this assumption could
lead to inaccurate representations. To address this, weights were
adjusted using the density of a normal distribution. The expected value
(\(\mu\)) was set to 1 to prioritize DDD = 1, and the standard deviation
(\(\sigma\)) was set to \(\frac{1}{3}\) to allow for a gradual reduction
in weight as DDD deviates from 1.

\begin{equation}\phantomsection\label{eq-weighted-DDD}{\omega = \frac{1}{\frac{\omega_B}{3} \sqrt{2 \pi}} e^{-\frac{1}{2}\left(\frac{DDD - \omega_B}{\omega_B/3}\right)^2}}\end{equation}

\colorbox{yellow}{What is $\omega_B$ in the formula? Where is $\mu$ that you mention in the text above?}
\colorbox{yellow}{What is the index $B$ in the formula?}\\
\colorbox{yellow}{Why $\mu$ was set to 1? That is the maximum ddd right?}

\begin{equation}\phantomsection\label{eq-regularize-mtx}{
\stackrel{\textrm{Unregularized}}{
  \begin{bmatrix}
  n_{1, 1} & \dots & n_{1, N} \\
  \vdots & \ddots & \vdots \\
  n_{N, 1} & \dots & n_{N, N} \\
  \end{bmatrix}
}
\quad \to \quad
\stackrel{\textrm{Regularized by } DDD}{
  \begin{bmatrix}
  \frac{1}{2} \cdot \left(\omega_1 + \omega_1 \right) & \dots & \frac{1}{2} \cdot \left(\omega_1 + \omega_N \right) \\
  \vdots & \ddots & \vdots \\
  \frac{1}{2} \cdot \left(\omega_N + \omega_1 \right) & \dots & \frac{1}{2} \cdot \left(\omega_N + \omega_N \right) \\
  \end{bmatrix}
}
}\end{equation}

\colorbox{yellow}{The terms $n_{i,j}$, $\omega_1$, $\omega_2$, etc are not defined somewhere.}\\
\colorbox{yellow}{Having nonzero diagonal is not a usual network representation.}\\
\colorbox{yellow}{What happens to your centrality measures if you set the diagonal equal to zero?}\\
\colorbox{yellow}{I would expect a simpler network structure.}
\begin{center}
    \colorbox{yellow}{Proposal:}
\end{center}
\colorbox{yellow}{For a given day and individual there is an edge with weight equal to 1}\\
\colorbox{yellow}{if there are nonzero ddds in the corresponding pair of drugs.}\\

\subsection{Centrality measures in graph
theory}\label{centrality-measures-in-graph-theory}

Centrality measures formalize the identification of important nodes in a
graph \citep{estrada2012structure}. Different node centrality measures
quantify different structural properties of a node. Previous work on
DPNs highlighted four centrality measures that could be used to assess
the importance of a medication within a co-prescription network
\citep{Miglio2021}. Degree centrality in a DPN describes the number of
co-prescription with the medication of interest. High (low) degree
centrality means the medication is often (seldom) co-prescribed.
Betweenness centrality indicates the frequency of a medication
connecting two other medications by the shortest possible path. High
(low) betweenness centrality means the medication is (not) a ``bridge''
between different kind of medications. Closeness centrality is the
average distance between one medication to all other medications in the
DPN. High (low) closeness centrality means that the medication is (not)
commonly co-prescribed. Eigenvector centrality reflects the number of
co-prescription with medications that have vital role in the DPN. High
(low) eigenvector centrality means that the medication is often (seldom)
co-prescribed with other important medications.

The choice of centrality largely depends on the objective of network
analysis. As a general guide, degree centrality is useful to identify
popular medication and monitor drug overuse. Betweenness centrality is
suitable for targeting for drug-interaction study and optimizing therapy
plan. Closeness centrality indicates widely-used key medications and
efficiency in treatment networks. Eigenvector centrality is helpful to
identify influential medications and narrow down high-impact medications
for drug monitoring. This study focused on eigenvector centrality to
evaluate which medications have a significant influence on how
antidepressants and anxiolytics are prescribed.
Equation~\ref{eq-eigen-centrality} outlines the calculation of
eigenvector centrality; \(c_i\) and \(c_j\) are the centralities of node
\(\mathcal{v}_i\) and \(\mathcal{v}_j\), respectively; \(\lambda\) is
the eigenvalue; \(a_{ji}\) is an element on row \(j\) and column \(i\)
from an adjacency matrix \(A\), representing the connection between node
\(\mathcal{v}_j\) and \(\mathcal{v}_i\).

\begin{equation}\phantomsection\label{eq-eigen-centrality}{
\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} a_{ji} \cdot c_j
}\end{equation}

\subsection{Data analysis}\label{data-analysis}

\subsubsection{Exploratory descriptive
analysis}\label{exploratory-descriptive-analysis}

The data was extracted as a daily time series and aggregated into weekly
and monthly intervals for analysis. It includes four metrics: daily
medication claims, daily patients, claim-to-patient ratio, and
eigenvector centrality. For each metric, a univariate descriptive
analysis was performed, reporting the mean, median, standard deviation,
and interquartile range to summarize centrality and dispersion.

\subsubsection{Exploring seasonality in the
dataset}\label{exploring-seasonality-in-the-dataset}

Exploration on seasonality was done on detrended daily, weekly, and
monthly data by generating seasonal plots and calculating the
autocorrelation (ACF) and partial autocorrelation function (PACF).
Seasonal plots were generated for weekly and yearly pattern by using
daily and monthly data, respectively. To generate the seasonal plots,
the data was first deconstructed based on its period. For daily data,
the weekly period was used; while for monthly data, the yearly period
was used. The weekly period was obtained by creating an ordered value
formatted as year - week, e.g.~\texttt{2018\ -\ W01}. Similarly, monthly
period was obtained by creating an ordered value formatted as year -
month, e.g.~\texttt{2018\ -\ M01}. We then grouped the series by its
deconstructed period and visually examine seasonality as overlapping
pattern in most periods. To substantiate the findings, ACF and PACF
plots were used to check on statistical significance of a given pattern.

\subsubsection{Summarizing polypharmacy}\label{summarizing-polypharmacy}

This study explored same-class, multi-class, and total polypharmacy. The
summary statistics were based on prescription-day data aggregated at the
population level over the year. Prescription-day is the number of
medications dispensed on a given day. For example, if seven medications
are prescribed for one day, it accounts for 7 prescription-days. The
mean and standard deviation represent the average number of
prescription-days per person for any polypharmacy regimen.

\subsubsection{Decomposition with singular spectrum
analysis}\label{decomposition-with-singular-spectrum-analysis}

Classical and seasonal-trend decomposition techniques may not fully
capture complex periodic patterns in time-series data. Singular spectrum
analysis (SSA) is a non-parametric method that leverages Hankel matrix
embedding for decomposition. In this study, SSA was applied to identify
trends and seasonal components in weekly aggregated prescription data.
To better isolate trend and seasonal components, sequential SSA was
applied. First, a basic SSA model with the lag parameter \(L\) = 52 was
used to extract the dominant trend. The residuals were then analyzed
with a second SSA model using \(L = \frac{N}{2}\) to capture complex
periodic patterns. The extracted trend, residuals, and oscillatory
components were evaluated visually and statistically, with Mann-Kendall
trend tests applied to assess long-term changes. A complete
documentation of this approach and its rationale was included in the
supplementary file section S1.1.

\subsubsection{Determining relative
importance}\label{determining-relative-importance}

Since the sum of all eigenvector centralities \(c_i\) in equation
\ref{eq-eigen-centrality} is equal to one, a network with similarly
connected nodes will have an eigenvector centrality \(c_i\) =
\(\frac{1}{n}\) for each node, where \(n\) is the number of nodes. The
value of \(c_i = \frac{1}{n}\) is the expected eigenvector centrality in
a densely connected network where the occurrence of an edge
\(\{\mathcal{v}_i, \mathcal{v}_j\} \in \mathcal{E}\) has the same
probability for all nodes. Per the central limit theorem, the value
\(\frac{1}{n}\) can be parameterized as a mean of a normal distribution,
where all instances of eigenvector centrality will follow the
distribution, \(c_i \sim \mathcal{N}(\mu, \sigma)\). A one-sample
Student's T-test was performed to assess how much each eigenvector
centrality differs from the expected values. As such, eigenvector
centrality greater than \(\frac{1}{n}\) can be considered high, and the
value below it can be considered low. The p-values was corrected for a
type-I error using Bonferroni method.

\section{Results}\label{results}

\subsection{Description of the
population}\label{description-of-the-population}

IADB recorded 149,071 patients having at least one dispensing of
antidepressants or anxiolytics within five years of data extraction.
Table~\ref{tbl-overview-patient} captures the dynamics of the population
from 2018 to 2022. The ratio of male to female only varied slightly, and
the average age steadily increased over the year. These findings imply
that the population demography stays relatively stable overtime without
any indication of sudden changes.

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{0.43in}|p{0.94in}|p{0.94in}|p{0.59in}|p{0.85in}|p{0.85in}}

\caption{\label{tbl-overview-patient}Number of participating patients
with at least one dispensing of antidepressants or anxiolytics from 2018
to 2022}

\tabularnewline

\ascline{1.5pt}{666666}{1-6}

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 2.47in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Number\ of\ Patients\ (\%)}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.7in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ Age\ (SD)}}}} \\

\ascline{1.5pt}{666666}{1-6}

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Year}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Male}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Female}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Total}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Male}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Female}}}} \\

\ascline{1.5pt}{666666}{1-6}\endfirsthead

\ascline{1.5pt}{666666}{1-6}

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 2.47in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Number\ of\ Patients\ (\%)}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.7in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ Age\ (SD)}}}} \\

\ascline{1.5pt}{666666}{1-6}

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Year}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Male}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Female}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Total}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Male}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Female}}}} \\

\ascline{1.5pt}{666666}{1-6}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2018}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,164\ (36.6\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{73,124\ (63.4\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{115,288}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.72\ (12.33)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.02\ (12.80)}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2019}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,427\ (36.7\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{73,109\ (63.3\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{115,536}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{49.26\ (12.62)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.54\ (13.02)}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2020}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,010\ (36.6\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{72,700\ (63.4\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{114,710}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{49.77\ (12.79)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{49.15\ (13.16)}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2021}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,016\ (36.7\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{72,532\ (63.3\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{114,548}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{50.15\ (13.04)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{49.55\ (13.42)}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2022}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{39,464\ (36.7\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{67,930\ (63.3\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{107,394}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{50.82\ (13.12)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{50.38\ (13.50)}}}} \\

\ascline{1.5pt}{666666}{1-6}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\subsection{Weekly variation of medication
dispensing}\label{weekly-variation-of-medication-dispensing}

The highest average of medication dispensing occurred on Monday, with an
average of 7,222 {[}SD: 999.79{]}. Meanwhile, the lowest average of
medication dispensing occurred on Saturday, with an average of 2,808
{[}SD: 174.08{]} dispensing. A large margin of difference between the
highest and lowest average number of dispensing implies daily variation
and cyclicality, where it peaks on Monday, starts declining afterwards,
and is at the lowest during weekends, as shown in
Table~\ref{tbl-overview-daily}. The cyclical patterns are detailed in
the supplementary material section S2.1.

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{0.75in}|p{0.91in}|p{0.91in}|p{0.84in}}

\caption{\label{tbl-overview-daily}Daily dispensing from 2018 to 2022
among patients with at least one dispensing of antidepressants or
anxiolytics}

\tabularnewline

\ascline{1.5pt}{666666}{1-4}

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 2.66in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Number\ of\ Dispensing}}}} \\

\ascline{1.5pt}{666666}{1-4}

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Day}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ (SD)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Median\ (IQR)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.84in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Range}}}} \\

\ascline{1.5pt}{666666}{1-4}\endfirsthead

\ascline{1.5pt}{666666}{1-4}

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 2.66in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Number\ of\ Dispensing}}}} \\

\ascline{1.5pt}{666666}{1-4}

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Day}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ (SD)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Median\ (IQR)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.84in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Range}}}} \\

\ascline{1.5pt}{666666}{1-4}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Monday}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,222\ (999.79)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,400\ (524.00)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.84in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,935\ -\ 9,194}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Tuesday}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6,793\ (640.76)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6,821\ (483.00)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.84in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3,164\ -\ 8,620}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Wednesday}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6,865\ (601.11)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6,852\ (566.00)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.84in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3,915\ -\ 8,503}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Thursday}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,109\ (592.11)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,136\ (579.00)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.84in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4,156\ -\ 8,608}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Friday}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6,726\ (535.52)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6,771\ (597.00)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.84in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3,589\ -\ 8,712}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Saturday}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,808\ (174.08)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,803\ (169.00)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.84in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,293\ -\ 4,533}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Sunday}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,991\ (166.44)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3,010\ (161.25)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.84in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,381\ -\ 3,478}}}} \\

\ascline{1.5pt}{666666}{1-4}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\subsection{Polypharmacy in the
population}\label{polypharmacy-in-the-population}

Table~\ref{tbl-res-poly} outlines the type of polypharmacy in the
population. Two statistics are reported in Table~\ref{tbl-res-poly}: the
sum and the mean with its standard deviation. The sum indicates the
total prescription-days of polypharmacy within a year. Thus, we can read
the findings as follow:

\begin{quote}
``In 2018, same-class polypharmacy of antidepressants occurred for a
total of 73,528 prescription-days across the population, with an average
of 0.06 prescription-days per person. For every 100 people prescribed
with antidepressants, there were approximately 6 days in total during
which same-class polypharmacy regimens occurred.''
\end{quote}

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{0.39in}|p{0.71in}|p{0.71in}|p{0.71in}|p{0.71in}|p{0.71in}|p{0.71in}|p{0.71in}}

\caption{\label{tbl-res-poly}Summary statistics of different psychiatric
polypharmacy categories}

\tabularnewline

\ascline{1.5pt}{666666}{1-8}

\multicolumn{2}{>{\raggedright}m{\dimexpr 1.1in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.42in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Population\ Level}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.42in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Per\ Person\ (Mean\ [SD])}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.42in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Total\ Polypharmacy}}}} \\

\ascline{1.5pt}{666666}{1-8}

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Year}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Medication}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Same-class}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Multi-class}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Same-class}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Multi-class}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{N}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ [SD]}}}} \\

\ascline{1.5pt}{666666}{1-8}\endfirsthead

\ascline{1.5pt}{666666}{1-8}

\multicolumn{2}{>{\raggedright}m{\dimexpr 1.1in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.42in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Population\ Level}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.42in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Per\ Person\ (Mean\ [SD])}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.42in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Total\ Polypharmacy}}}} \\

\ascline{1.5pt}{666666}{1-8}

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Year}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Medication}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Same-class}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Multi-class}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Same-class}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Multi-class}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{N}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ [SD]}}}} \\

\ascline{1.5pt}{666666}{1-8}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2018}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidepressants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{73,528}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{844,789}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.06\ [0.25]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.69\ [1.17]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,264,585}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.90\ [4.18]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2019}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidepressants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{75,794}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{821,726}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.06\ [0.25]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.65\ [1.13]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,489,533}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.92\ [4.17]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2020}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidepressants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{74,924}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{828,043}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.06\ [0.25]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.65\ [1.13]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,564,952}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.93\ [4.15]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2021}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidepressants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{75,549}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{804,264}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.06\ [0.25]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.64\ [1.12]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,466,014}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.91\ [4.17]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2022}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidepressants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{74,026}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{797,843}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.06\ [0.25]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.64\ [1.12]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,474,032}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.95\ [4.17]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2018}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anxiolytics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{34,122}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,049,590}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.03\ [0.17]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.85\ [1.21]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,264,585}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.90\ [4.18]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2019}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anxiolytics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{31,955}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,044,683}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.03\ [0.16]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.83\ [1.18]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,489,533}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.92\ [4.17]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2020}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anxiolytics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{32,249}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,053,849}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.03\ [0.16]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.83\ [1.17]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,564,952}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.93\ [4.15]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2021}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anxiolytics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{29,912}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,035,388}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.02\ [0.16]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.82\ [1.16]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,466,014}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.91\ [4.17]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 0.39in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2022}}}} & \multicolumn{1}{>{\raggedright}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anxiolytics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{31,527}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,027,019}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.03\ [0.16]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{0.82\ [1.16]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7,474,032}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.71in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.95\ [4.17]}}}} \\

\ascline{1.5pt}{666666}{1-8}

\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{The\ total\ occurrence\ of\ polypharmacy\ on\ the\ population\ level/perscription-day}}}} \\

\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{The\ expected\ occurrence\ of\ polypharmacy\ per\ person/perscription-day}}}} \\

\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Prescription\ day\ is\ defined\ as\ the\ number\ of\ dispensed\ medication\ per\ day}}}} \\

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\subsection{Time-series decomposition}\label{time-series-decomposition}

For brevity, Figure~\ref{fig-ssa} only depicts the decomposition result
of antidepressants dispensing over the years. SSA-based decomposition
separates the trend from its harmonics, as shown in the lower half of
the plot. The trend explains roughly 90\% of the variability, and
harmonics explain 10\%. The first two harmonics, F1 and F2, captured
most of the variability in a series compared to the rest of it. The
trend, F1, and F2 were used to reconstruct the time series. The largest
graph in Figure~\ref{fig-ssa} represents the reconstructed time-series
(green line) and its original data points (gray line). Other
decomposition results are reported in the supplementary file section
S2.2.

\begin{figure}[H]

\centering{

\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{article_files/figure-pdf/fig-ssa-1.pdf}

}

\caption{\label{fig-ssa}Time-series decomposition of antidepressants
dispensing data using singular spectrum analysis-based approach}

\end{figure}%

\subsection{Eigenvector centrality
measures}\label{eigenvector-centrality-measures}

Seven medication classes exhibited high centrality, as shown in
Figure~\ref{fig-hi-eigen} and Table~\ref{tbl-desc}. Notably, highly
dispensed medications generally had high eigenvector centrality, which
aligns with the theoretical expectations from
Equation~\ref{eq-eigen-centrality}. However, despite a higher number of
dispensing (6,108,776 vs 5,492,900), antidepressants had lower
eigenvector centrality than medications for the respiratory system
(8.94e-02 {[}SD: 1.99e-03{]} vs 8.95e-02 {[}SD: 3.39e-03{]}). A similar
pattern was observed for anxiolytics, which had more dispensing than
analgesics (2,644,309 vs 2,557,528) but lower eigenvector centrality
(4.43e-02 {[}SD: 4.36e-03{]} vs 4.99e-02 {[}SD: 4.26e-03{]}).

\global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}

\global\setlength{\Oldtabcolsep}{\tabcolsep}

\setlength{\tabcolsep}{0pt}

\renewcommand*{\arraystretch}{1}

\providecommand{\ascline}[3]{\noalign{\global\arrayrulewidth #1}\arrayrulecolor[HTML]{#2}\cline{#3}}

\begin{longtable}[c]{|p{1.57in}|p{0.74in}|p{1.16in}|p{1.16in}|p{1.16in}}

\caption{\label{tbl-desc}Descriptive statistics of dispensing data from
2018 to 2022, ordered by Eigenvector centrality}

\tabularnewline

\ascline{1.5pt}{666666}{1-5}

\multicolumn{2}{>{\centering}m{\dimexpr 2.31in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 3.49in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ [SD]}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\centering}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Dispensing}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Centrality}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{DDD}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Weight}}}} \\

\ascline{1.5pt}{666666}{1-5}\endfirsthead

\ascline{1.5pt}{666666}{1-5}

\multicolumn{2}{>{\centering}m{\dimexpr 2.31in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 3.49in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ [SD]}}}} \\

\ascline{1.5pt}{666666}{1-5}

\multicolumn{1}{>{\centering}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Dispensing}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Centrality}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{DDD}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Weight}}}} \\

\ascline{1.5pt}{666666}{1-5}\endhead

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Alimentary\ and\ metabolism}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{11,512,424}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.07e-01\ [6.07e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.97e-01\ [3.26e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.28e-01\ [2.06e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Cardiovascular}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9,778,030}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.91e-01\ [1.01e-02]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.38e-01\ [3.05e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.92e-01\ [2.00e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Respiratory}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5,492,900}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.95e-02\ [3.39e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.55e-01\ [3.25e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.70e-01\ [2.15e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidepressants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6,108,776}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.94e-02\ [1.99e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.36e-01\ [3.09e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.92e-01\ [2.03e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Blood}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,908,944}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.27e-02\ [5.29e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.93e-01\ [3.91e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.78e-01\ [2.13e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Analgesics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,557,528}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.99e-02\ [4.26e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.23e-01\ [2.60e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.16e-01\ [1.66e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anxiolytics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,644,309}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.43e-02\ [4.36e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.63e-01\ [2.88e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.35e-01\ [1.73e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Dermatologicals}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,086,095}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.37e-02\ [1.20e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.08e-01\ [3.39e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.62e-01\ [2.09e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Musculoskeletal}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,449,535}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.26e-02\ [1.36e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.59e-01\ [3.26e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.10e-01\ [2.11e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Systemic\ hormonal}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,602,716}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.13e-02\ [1.61e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.97e-01\ [2.76e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.55e-01\ [1.66e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antipsychotics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,473,609}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.08e-02\ [3.38e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.04e-01\ [2.65e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.10e-01\ [1.69e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Genitourinary}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,099,833}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.81e-02\ [8.79e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.46e-01\ [3.69e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.29e-01\ [2.12e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Hypnotics\ and\ sedatives}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,467,752}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.71e-02\ [2.92e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.31e-01\ [3.16e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.49e-01\ [2.09e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiepileptics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,078,266}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.65e-02\ [2.42e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.29e-01\ [2.52e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.25e-01\ [1.66e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Systemic\ anti-infectives}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{734,706}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.63e-02\ [1.25e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.34e-01\ [3.23e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.64e-01\ [2.21e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antineoplastics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{449,030}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.17e-03\ [3.65e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.13e-01\ [3.01e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.49e-01\ [2.05e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Other\ nervous\ system\ drugs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{362,624}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.81e-03\ [9.30e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.23e-01\ [3.16e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.78e-01\ [1.93e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiparkinson}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{306,541}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.80e-03\ [4.93e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.53e-01\ [2.21e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.74e-01\ [1.37e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Psychostimulants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{459,207}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.16e-03\ [6.27e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.20e-01\ [3.13e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.74e-01\ [1.90e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Sensory}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{196,513}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.66e-03\ [4.64e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.66e-01\ [2.87e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.37e-01\ [1.80e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiparasitics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{88,760}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.24e-03\ [9.37e-05]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.24e-01\ [2.53e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.72e-01\ [1.65e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anesthetic}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{39,455}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.76e-04\ [1.54e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.45e-01\ [4.47e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.39e-01\ [2.31e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Others}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{18,157}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.37e-04\ [3.90e-05]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.55e-01\ [2.73e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.37e-01\ [1.77e-01]}}}} \\

\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidementia}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9,937}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.58e-04\ [3.59e-05]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.80e-01\ [2.85e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.87e-01\ [2.02e-01]}}}} \\

\ascline{1.5pt}{666666}{1-5}

\end{longtable}

\arrayrulecolor[HTML]{000000}

\global\setlength{\arrayrulewidth}{\Oldarrayrulewidth}

\global\setlength{\tabcolsep}{\Oldtabcolsep}

\renewcommand*{\arraystretch}{1}

\begin{figure}

\centering{

\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{article_files/figure-pdf/fig-hi-eigen-1.pdf}

}

\caption{\label{fig-hi-eigen}Clusters of medication with a significant
influence on how antidepressants and anxiolytics are prescribed}

\end{figure}%

\section{Discussion}\label{discussion}

This network analysis of dispensing data in individuals using
antidepressants or anxiolytics revealed distinct polypharmacy patterns
between these groups. While same-class polypharmacy was more common
among antidepressant users, multi-class polypharmacy predominated among
those receiving anxiolytics. Notably, in both groups, multi-class
polypharmacy was at least ten times more prevalent than same-class
polypharmacy. Seven medication classes exhibited high eigenvector
centrality, indicating their strong influence on co-prescription
dynamics. These include medications for the alimentary tract and
metabolism (ATC code \texttt{A}), blood and blood-forming organs
(\texttt{B}), cardiovascular system (\texttt{C}), respiratory system
(\texttt{R}), and analgesics (\texttt{N02}). These classes do not merely
appear frequently but also serve as key connectors within prescribing
networks, linking psychiatric treatments to chronic disease management.
Their centrality suggests that they play a role in structuring
multi-class polypharmacy, either as standard co-prescriptions due to
clinical guidelines or as necessary adjuncts in managing comorbidities.

Our findings align with previous research showing that antidepressants
and anxiolytics are frequently co-prescribed with other medications
\citep{Shrivastava2013}, and that multi-class regimens contribute most
to psychopharmaca polypharmacy \citep{de2004polypharmacy}. Furthermore,
there have been established bidirectional associations between
depression/anxiety and chronic illnesses \citep{qi2024longitudinal}.
Conditions such as diabetes mellitus, thyroid disorders, and asthma have
been linked to an increased risk of depression \citep{jang2024temporal}.
The need for long-term pharmacological management further drives
co-prescription patterns. Additionally, chronic illness-related anxiety
can contribute to heightened prescribing of anxiolytics
\citep{lebel2020health}. This underscores the interconnected nature of
psychopharmaca prescribing patterns and highlights the complexity of
medication management in these populations.

DPN complements traditional drug utilization analyses by capturing the
structural properties of prescribing behaviors. Beyond evaluating
individual drug utilization or basic pairwise co-prescriptions, DPN
provides a structural perspective by mapping the interconnections
between medications within a broader prescribing network
\citep{Bazzoni2015}. The network approach is a particularly useful
method for understanding complex prescribing dynamics, which allows for
the identification of central medication classes that influence
polypharmacy patterns. The high centrality of certain medication classes
suggests they serve as critical connectors in treatment regimens,
providing the basis for further monitoring and evaluation.

By mapping the relationships between medications, DPN enables the
detection of patterns that would be challenging to observe through
standard statistical methods. For instance, the high centrality of
certain medication classes suggests that they play a pivotal role in
multi-class polypharmacy, likely due to their involvement in managing
both psychiatric and non-psychiatric conditions. As such, network
analysis is a suitable approach for generating hypothesis, which has
also been thoroughly discussed by \citet{Askar2021}.

We acknowledge several limitations in this study. First, data
aggregation at the population level resulted in the loss of
individual-level information, limiting interpretation to population
trends. Second, while the adjustment of weights based on DDD introduces
a novel element to the analysis, it is important to note that DDD values
are not always equal to one, as defined by the WHO ATC system. Our study
adopted a DDD-based weighting approach to refine network edges, aligning
with the recommendation of \citet{Cavallo2012}. The adjusted weighting
penalizes values deviating significantly from 1, reducing their impact
on the network. Future research should explore alternative weighting
techniques, such as patient-level dosage adjustments, to enhance network
precision.

Despite the limitations, our study demonstrates the utility of DPN as a
powerful, data-driven approach to analyzing medication dispensing data.
By modelling intricate co-prescription patterns, DPN filters medication
classes based on network properties, offering insights into prescribing
behaviors. These insights can reveal important trends in medication use,
which can be useful to public health monitoring. By capturing the
complexity of drug prescription relationships, DPN holds significant
potential to improve decision-making in both clinical and administrative
contexts.

Future DPN studies on individuals using antidepressants or anxiolytics
should adopt a more fine-grained ATC classification to identify specific
medications driving polypharmacy patterns within the currently
identified seven medication classes. A more granular approach could
reveal whether certain drugs disproportionately contribute to
multi-class polypharmacy and whether these prescribing trends vary
across patient demographics or healthcare settings. Such insights could
refine our understanding of prescribing behaviors and inform targeted
interventions for optimizing medication regimens.

\section{Conclusion}\label{conclusion}

This study utilized DPN to evaluate the influence of specific medication
classes on prescribing patterns of antidepressants and anxiolytics. By
focusing on co-prescription patterns, we identified seven medication
classes with significant eigenvector centrality, reflecting their
critical role in polypharmacy regimens for individuals using anxiolytics
and antidepressants. This study highlights the potential of
network-based approaches to narrow down high-impact medications for
further evaluation.

\renewcommand\refname{References}
  \bibliography{ref.bib}

\end{document}

### 2025-07-09 docs/abstract/_abstract-short.qmd
Revise the reporting approaches to make it more objective

@@
 Antidepressants ($c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics ($c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) had high eigenvector centrality, indicating frequent co-prescription.
-Additional high-centrality groups included medications for alimentary and metabolism (`A01-A16`), blood (`B01-B06`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory diseases (`R01-R07`).
+Other drug groups with high centrality included those for the alimentary tract and metabolism (`A01-A16`), blood and blood-forming organs (`B01-B06`), cardiovascular system (`C01-C10`), analgesics (`N02`), and respiratory system (`R01-R07`).
 
 **Discussion:**
-DPNs revealed key co-prescription patterns. High-centrality medications highlight potential targets for drug monitoring.
+DPNs revealed key co-prescription patterns.
+High-centrality medications highlight potential targets for drug monitoring, such as identifying co-prescription trends that may warrant evaluation for safety, appropriateness, or policy oversight.
+This approach aids in identifying influential medications and refining prescribing oversight.

### 2025-07-09 docs/article.qmd
Revise the reporting approaches to make it more objective

@@
 title: >
-  A temporal network analysis of drug co-prescription during antidepressant and anxiolytic dispensing in the Netherlands from 2018 to 2022
+  A temporal network analysis of drug co-prescription during antidepressants and anxiolytics dispensing in the Netherlands from 2018 to 2022
 
@@
 Augmentation polypharmacy is the use of full-dose and sub-dose medications from a different class for the same symptom cluster.
-Finally, total polypharmacy is the total count of all medications used by a patient, both psychopharmaca and other classes alike [@Shrivastava2013].
-For policymakers, differences in defining polypharmacy pose a challenge to design a monitoring system [@Sirois2016].
+Finally, total polypharmacy is the overall number of medications a patient uses, including those prescribed for multiple psychiatric symptom clusters as well as for comorbid non-psychiatric conditions [@Shrivastava2013].
+For policymakers, differences in defining polypharmacy pose a challenge to design an effective monitoring system [@Sirois2016].
+Such monitoring is essential to identify prevalent co-prescription pattern that may impact treatment appropriateness and healthcare policy development.
 
@@
 Building on prior studies [@Cavallo2012; @Bazzoni2015], we hypothesize that eigenvector centrality serves as a meaningful quantitative indicator of polypharmacy.
-Therefore, this study aimed to assess the structural characteristics of temporal DPNs, focusing on the role of eigenvector centrality in identifying associated medications in adult patients prescribed for antidepressant or anxiolytic.
+Therefore, this study aimed to assess the structural characteristics of temporal DPNs, focusing on the role of eigenvector centrality in identifying associated medications in adult patients prescribed for antidepressants or anxiolytics.
 
@@
 
-This study explored same-class, multi-class, and total co-prescription.
-The summary statistics were based on prescription-day data aggregated at the population level over the year.
-Prescription-day is the number of medications dispensed on a given day.
-For example, if seven medications are prescribed for one day, it accounts for 7 prescription-days.
-The mean and standard deviation represent the average number of prescription-days per person for any co-prescription regimen.
+This study explored same-class, multi-class, and total co-prescription categories.
+These three groups were selected as they can be directly inferred from medication dispensing data aggregated at the population level over the year.
+The statistics were summarized as prescription-day, defined as the number of medications dispensed on a given day.
+For example, seven medications prescribed for one day account for 7 prescription-days.
+The mean and standard deviation represented the average number of prescription-days per person for any co-prescription regimen.
+
+Although five polypharmacy categories were described by @Shrivastava2013, augmentation and adjunctive polypharmacy require clinical context such as diagnoses to determine the rationale for combined prescriptions, which is not available in our data source.
+Therefore, focusing on the three categories that rely solely on medication class information is the most reasonable approach for this study.
 
@@
 Dispensing peaked on `r hi_claim$day`, with an average of `r hi_mean` [SD: `r hi_claim$sd_claim`] and dropped to its lowest on `r lo_claim$day`, with an average of `r lo_mean` [SD: `r lo_claim$sd_claim`] dispensing.
-The variation between weekends and weekdays suggested a regular and repeating structure in the data.
-A large margin of difference between the highest and lowest average number of dispensing implied daily variation and cyclicality, where it peaks on Monday, starts declining afterwards, and is at the lowest during weekends, as shown in @tbl-overview-daily.
+The variation between weekends and weekdays showed a regular and repeating structure in the data.
+There was a large margin of difference between the highest and lowest average number of prescription dispensed, with a peak on Monday, followed by a decline throughout the week and the lowest levels occurring during weekends, as shown in @tbl-overview-daily.
 The cyclical patterns are detailed in the supplementary material section S2.1.
@@
   flextable::add_header_row(
-    values    = c("", "Number of Dispensing"),
+    values    = c("", "Number of Prescriptions Dispensed"),
     colwidths = c(1, 3),
@@
 
-@tbl-res-poly outlines the type of co-prescription in the population.
-Two statistics are reported in @tbl-res-poly: the sum and the mean with its standard deviation.
-The sum indicates the total prescription-days of co-prescription within a year.
-Thus, we can read the findings as follow:
+@tbl-res-poly outlines the type of co-prescription in the population and reports two statistics: the sum and the mean with its standard deviation.
+The sum indicates the total prescription-days of co-prescription within a year, and the mean with its standard deviation represents the average number of co-prescription days per person.
+For example, in 2018, same-class co-prescription of antidepressants occurred for a total of 73,528 prescription-days across the population, with an average of 0.06 prescription-days per person, interpreted as:
 
-> "In 2018, same-class co-prescription of antidepressants occurred for a total of 73,528 prescription-days across the population, with an average of 0.06 prescription-days per person.
-For every 100 people prescribed with antidepressants, there were approximately 6 days in total during which same-class co-prescription regimens occurred."
+> "For every 100 people treated with antidepressants, there were approximately 6 days in total during which same-class co-prescription regimens occurred."
+
+While these average numbers per person may appear low, they are not intended to reflect the absolute epidemiological importance of co-prescriptions.
+Instead, prescription-days serve as a relative metric to compare the extent of co-prescription across categories and over time.
+For instance, @tbl-res-poly shows that multi-class polypharmacy generally exhibits higher prescription-day values than same-class polypharmacy among individuals prescribed antidepressants.
+Therefore, prescription-day counts should be interpreted in the context of relative prescribing patterns, rather than as a direct indicator of epidemiological significance.
 
@@
     i = 1,
-    j = c(3, 5),
-    ref_symbols = c("1", "2"),
+    j = c(3, 5, 7),
+    ref_symbols = c("1", "2", "3"),
     part = "header",
@@
         "The expected occurrence of co-prescription per person/perscription-day",
+        "The overall number of medications a patient uses, including those prescribed for multiple psychiatric symptom clusters as well as for comorbid non-psychiatric conditions",
         "Prescription day is defined as the number of dispensed medication per day",
@@
 
-For brevity, @fig-ssa only depicts the decomposition result of antidepressants dispensing over the years.
+For brevity, @fig-ssa only depicts the decomposition result of antidepressants dispensed over the years.
 SSA-based decomposition separates the trend from its harmonics, as shown in the lower half of the plot.
@@
 The trend, F1, and F2 were used to reconstruct the time series.
-The largest graph in @fig-ssa represents the reconstructed time-series (green line) and its original data points (gray line).
-Other decomposition results are reported in the supplementary file section S2.3.
+The largest panel in @fig-ssa displays the reconstructed time-series (green line) overlaid on the original data points (gray line).
+
+Additional decomposition results for other medication classes are presented in the supplementary section S2.3.
+Broadly antidepressants exhibited a steady increasing trend over time, while anxiolytics showed a gradual decline both in dispensing frequency and eigenvector centrality.
+Notably, the decomposition made long-term directional patterns more discernible across all medication classes, emphasizing the utility of SSA in isolating interpretable temporal dynamics from complex dispensing data.
+These decomposed trends provides the reconstructed data for the subsequent analysis.
 
@@
 However, this relationship was not strictly proportional.
-For example, although antidepressants had a higher number of dispensing compared to medications for the respiratory system (`r diffMed(antidepressants, respiratory, reportMedClaim)`), they exhibited lower eigenvector centrality (`r diffMed(antidepressants, respiratory, reportMedEigen)`).
+For example, although antidepressants had a higher number of prescription dispensed compared to medications for the respiratory system (`r diffMed(antidepressants, respiratory, reportMedClaim)`), they exhibited lower eigenvector centrality (`r diffMed(antidepressants, respiratory, reportMedEigen)`).
 A similar pattern was observed for anxiolytics, which had more dispensing than analgesics (`r diffMed(anxiolytics, analgesics, reportMedClaim)`) but lower eigenvector centrality (`r diffMed(anxiolytics, analgesics, reportMedEigen)`).
-This reflects that eigenvector centrality captures not just volume but also the influence of connection sin the network, highlighting that commonly dispensed drug within a population may not necessarily occupy the most central network positions.
+These discrepancies show that higher centrality scores capture more than just a high dispensing volume.
 
@@
 ```{r fig-hi-eigen}
-#| fig-cap: Clusters of medication with a significant co-prescription patterns on antidepressant and anxiolytic dispensing
+#| fig-cap: Clusters of medication with a significant co-prescription patterns on antidepressants and anxiolytics dispensing
 #| fig-width: 9
@@
 Their centrality suggests that they play a role in structuring multi-class co-prescription, either as standard co-prescriptions due to clinical guidelines or as necessary adjuncts in managing comorbidities or side effects, e.g., ATC `A` class.
+These findings align with the theoretical basis of eigenvector centrality, which incorporates not only the frequency of a node but also the influence of its connections.
+Accordingly, medications with high dispensing volume may have lower centrality if they are co-prescribed with less central or sparsely connected drug classes.
 
@@
 
-This study demonstrates the utility of DPN in uncovering the patterns of co-prescriptions among antidepressant and anxiolytic recipients.
+This study demonstrates the utility of DPN in uncovering the patterns of co-prescriptions among antidepressants and anxiolytics recipients.
 We found that multi-class regimens were markedly more prevalent, particularly among anxiolytic users, consistent with clinical guidelines.

### 2025-07-09 docs/exec-summary/_source-data.qmd
Revise the reporting approaches to make it more objective

--- 2025-05-02 docs/exec-summary/_source-data.qmd
@@
 
-All data in this study originated from IADB.nl, a dynamic pharmacy database containing prescription data from 1994 which still grow expansively.
-The database covers approximately 120 community pharmacies serving over one million patients and was accessed on the 20^th^of September, 2023.
+All data in this study originated from the University of Groningen IADB.nl, a dynamic pharmacy database containing prescription data since 1994 which still grows expansively.
+The database covers approximately 128 community pharmacies serving over one million patients and was accessed on the 20^th^of September, 2023.
 All patients are recorded in the database, irrespective of health care insurance, where the prescription rates, age, and gender are generalizable to represent the Netherlands [@Visser2013].
@@
 All records contain fields on the date of medication dispensing, its quantity, dose regimen, number of days prescribed, prescribing physicians, and the Anatomical Therapeutic Chemical (ATC) code.
-Except for the over the counter drugs and medication dispensed during hospitalization, other medication records for each patient are complete, mainly due to high patient-pharmacy commitment in the Netherlands.
+Except for the over the counter drugs and medication dispensed during hospitalization, all medication records for each patient are complete, mainly due to high patient-pharmacy commitment in the Netherlands.
+
 This analysis includes daily medication dispensing from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.

### 2025-07-10 docs/article.qmd
Render the revision of the methods and results

@@
     keep-tex: true
+    keep-md: true
     include-in-header:
@@
 
-Mathematically, a graph $\mathcal{G}$ is a pair $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, where $\mathcal{V}$ is the set of nodes and $\mathcal{E}$ is the set of edges.
+Mathematically, a simple undirected graph $\mathcal{G}$ is a pair $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, where $\mathcal{V} = \left(1, \dots, n \right)$ is the set of nodes and $\mathcal{E} = \left(\{j, k\} \ | \ j, k \in \mathcal{V}, \ j \neq k \right)$ is the finite set of edges with $\{j, k\} = \{k, j\}$.
+The adjacency matrix $A \in \{0, 1\}^{n \times n}$ of a simple undirected graph $\mathcal{G}$ with $\mathcal{V}$ nodes is a square symmetric matrix of dimension $n \times n$ defined as @eq-graph-theory, with $A_{jk} = A_{kj}$ for all $j, k \in \mathcal{V}$ where $j \neq k$.
+For each day $t = \left(1, \dots, T \right)$ and each individual $p = \left(1, \dots, P \right)$, the adjacency matrix represented a simple undirected graph.
+
+$$
+A_{jk} = 
+\begin{cases}
+1 & \text{if } \{j, k\} \in \mathcal{E} \\
+0 & \text{otherwise}
+\end{cases}
+$$ {#eq-graph-theory}
+
 In a DPN, the node set $\mathcal{V} = \{\mathcal{v}_1, \mathcal{v}_2, \dots, \mathcal{v}_n\}$ represents a finite set of $n$ medications.
@@
 In an undirected graph, the order of $i, j$ does not matter.
-Typically, undirected graphs do not contain self connections, $\{\mathcal{v}_i, \mathcal{v}_i\} \notin \mathcal{E}$ [@estrada2012structure].
+Typically, undirected graphs do not contain self connections, $\{\mathcal{v}_i, \mathcal{v}_i\} \notin \mathcal{E}$ [j].
 
@@
       c(
-        "The total occurrence of co-prescription on the population level/perscription-day",
-        "The expected occurrence of co-prescription per person/perscription-day",
-        "The overall number of medications a patient uses, including those prescribed for multiple psychiatric symptom clusters as well as for comorbid non-psychiatric conditions",
-        "Prescription day is defined as the number of dispensed medication per day",
-        "Multi-class co-prescription is defined as the co-prescription of medications from different ATC classification"
+        "The total occurrence of co-prescription on the population level/prescription-day.",
+        "The expected occurrence of co-prescription per person/prescription-day.",
+        "The overall number of medications a patient uses, including those prescribed for multiple psychiatric symptom clusters as well as for comorbid non-psychiatric conditions.",
+        "Prescription day is defined as the number of dispensed medication per day.",
+        "Multi-class co-prescription is defined as the co-prescription of medications from different ATC classification."
       )
@@
   ) |>
+  flextable::footnote(
+    i = 2,
+    j = c(4, 5),
+    ref_symbols = c("1", "2"),
+    part = "header",
+    value = flextable::as_paragraph(
+      c(
+        "Defined Daily Dose, representing the assumed average maintenance dose per day for a drug used for its main indication in adults (WHO definition).",
+        "Edge weight assigned to each medication class in the drug prescription network, reflecting the strength of co-prescription connections (see Methods: Data pre-processing to build the data matrix)."
+      )
+    )
+  ) |>
   flextable::align(align = "center", part = "all") |>
-  flextable::align(j = 1, align = "left", part = "body") |>
+  flextable::align(j = 1, align = "left", part = "all") |>
   #flextable::font(fontname = "Times", part = "all") |>

### 2025-07-10 docs/exec-summary/_preprocessing.qmd
Render the revision of the methods and results

@@
 At the individual level, each patient's daily prescription record at time $t$ was encoded into a square matrix $A_t^{(i)}$, where rows and columns represent medication classes according to the ATC classification.
-An off-diagonal entry $A_{t_{jk}}^{(i)} = 1$ indicates that medication classes $i$ and $k$ were co-prescribed on the same day for individual $i$, while a diagonal entry $A_{t_{jj}}^{(i)} = 1$ captures the presence of a single prescription of medication $j$.
+An off-diagonal entry $A_{t_{jk}}^{(i)} = 1$ indicates that medication classes $j$ and $k$ were co-prescribed on the same day for individual $i$, while a diagonal entry $A_{t_{jj}}^{(i)} = 1$ captures the presence of a single prescription of medication $j$.
 To derive the population-level DPN, all individual-level daily prescription matrix $A^{(i)}$ were aggregated by computing their element-wise sum.
@@
 However, since not all medications have DDD = 1, this assumption could lead to inaccurate representations.
-To enhance the accuracy of edge weights, we accounted for the heterogeneity in DDD.
-The weights were adjusted using the density of a normal distribution.
-The expected value ($\mu$) was set to the base weight $\omega_B$ of 1 to prioritize DDD = 1, and the standard deviation ($\sigma$) was set to $\frac{1}{3}$ to allow for a gradual reduction in weight as DDD deviates from 1.
+To enhance the accuracy of edge weights, we introduced a weighting function to adjust the contribution of each co-prescription.
+Specifically, each co-prescribed medication class was assigned a weight $\omega_j$ based on its DDD value using a Gaussian kernel centered at the baseline weight $\omega_B = 1$, i.e., the expected DDD, with standard deviation $\sigma = \frac{1}{3}$ to allow for a gradual reduction in weight as DDD deviates from 1.
 
-$$\omega = \frac{1}{\frac{\omega_B}{3} \sqrt{2 \pi}} e^{-\frac{1}{2}\left(\frac{DDD - \omega_B}{\omega_B/3}\right)^2}$$ {#eq-weighted-DDD}
+$$\omega_j = \frac{1}{\frac{\omega_B}{3} \sqrt{2 \pi}} e^{-\frac{1}{2}\left(\frac{DDD - \omega_B}{\omega_B/3}\right)^2}$$ {#eq-weighted-DDD}
+
+The edge weight between medication classes $j$ and $k$ was computed as the average of their individual weights:
 
@@
 $$ {#eq-regularize-mtx}
+
+This weighting approach scaled the edge weight that deviate substantially from the standard $\omega_B = 1$, improving comparability across medication classes.
+To remain consistent with standard network representations and avoid confounding self-loops, the diagonal elements were omitted.

### 2025-07-10 src/R/spectral.R

@@ -186,7 +186,7 @@ bindReconSsa <- function(ts_list) {
   return(tbl)
 }
 
-genReconTs <- function(tbl, n = 2, detrend = FALSE) {
+genReconTs <- function(tbl, n = 2, detrend = FALSE, widen = TRUE) {
   #' Generate Reconstructed Time Series
   #'
   #' Generate a reconstructed time series based on trend and n number of
@@ -201,6 +201,7 @@ genReconTs <- function(tbl, n = 2, detrend = FALSE) {
   #' = 2.
   #' @param detrend A boolean indicating whether to return a detrended series
   #' or not
+  #' @param widen Will return a wide table when set to `TRUE`
   #' @return A tidy time series
   require("tsibble")
 
@@ -227,8 +228,11 @@ genReconTs <- function(tbl, n = 2, detrend = FALSE) {
     subset(id) %>%
     dplyr::group_by(metric, date, group) %>%
     dplyr::summarize("value" = sum(value)) %>%
-    tidyr::pivot_wider(names_from = metric, values_from = value) %>%
     dplyr::ungroup()
+
+  if (widen) {
+    tbl %<>% tidyr::pivot_wider(names_from = metric, values_from = value)
+  }
 
   ts <- tbl %>% tsibble::as_tsibble(key = group, index = date)
 

### 2025-07-10 src/R/visualize.R

@@ -365,14 +365,23 @@ vizReconSsa <- function(tidy_recon, ...) {
   #' @param tidy_recon A tidy data frame obtained from `tidyReconSsa`
   #' @return A GGPlot2 object
   require("ggplot2")
+  require("tsibble")
   
   # Separate oscillating functions + noise from the rest
   id      <- grepl(x = tidy_recon$component, "^F")
   tbl_fun <- subset(tidy_recon, id)
   resid   <- tidy_recon %>% subset(.$component == "Residuals")
-  tbl     <- tidy_recon %>%
+  ts      <- tidy_recon %>%
     subset(!{id | .$component == "Residuals"}) %>%
     tidyr::pivot_wider(names_from = component, values_from = value)
+
+  # Reconstruct the time series based on the trend, F1, and F2
+  recon <- genReconTs(tidy_recon, n = 2, detrend = FALSE, widen = FALSE)
+
+  # Merge the time-series and its reconstructed data points
+  tbl <- ts |>
+    dplyr::inner_join(recon, by = c("metric", "date", "group")) |>
+    dplyr::rename("Recon" = value)
 
   # Set labels and colors
   med <- unique(tidy_recon$group)
@@ -385,16 +394,16 @@ vizReconSsa <- function(tidy_recon, ...) {
     date_breaks = "1 month", date_labels = "%b %Y", expand = expansion(add = c(10, 30))
   )
 
-  # Plot for original and trend
+  # Plot for original and the reconstructed data
   plt1 <- ggplot(tbl, aes(x = date)) +
     geom_point(aes(y = Original), color = colors$black, alpha = 0.4, size = 2, shape = 18) +
-    geom_line(aes(y = Original, color = "Data"), alpha  = 0.2, linewidth = 1.2) +
-    geom_line(aes(y = Trend, color = "Reconstructed"), alpha  = 0.8, linewidth = 2) +
+    geom_line(aes(y = Original, color = "Original Data"), alpha  = 0.2, linewidth = 1.2) +
+    geom_line(aes(y = Recon, color = "Reconstructed Series"), alpha  = 0.8, linewidth = 2) +
     labs(title = plt_title, x = "", y = "") +
     scale_date +
     scale_color_manual(
       name = "",
-      values = c("Data" = colors$black, "Reconstructed" = colors$green),
+      values = c("Original Data" = colors$black, "Reconstructed Series" = colors$green),
       guide = guide_legend(override.aes = aes(fill = NA))
     ) +
     ggpubr::theme_pubclean() +

### 2025-07-10 docs/abstract/_abstract-short.qmd
Finalize the first draft

--- 2025-03-12 docs/abstract/_abstract-short.qmd
@@
 We utilized the IADB.nl database, including prescriptions from 128 Dutch pharmacies (2018–2022).
-A closed cohort of patients prescribed antidepressants/anxiolytics was extracted.
+A cohort of patients prescribed antidepressants/anxiolytics was extracted.
 Medications were classified using the Anatomical Therapeutic Chemical (ATC) system into 24 therapeutic classes.
@@
 **Results:**
-Antidepressants (ATC `N06A`, $c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics (`N05B`, $c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) had high eigenvector centrality, indicating frequent co-prescription.
-Additional high-centrality groups included medications for alimentary and metabolism (`A01-A16`), blood (`B01-B06`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory (`R01-R07`).
+Antidepressants ($c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics ($c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) had high eigenvector centrality, demonstrating frequent co-prescription.
+Other ATC groups with high centrality included those for the alimentary tract and metabolism (`A01-A16`), blood and blood-forming organs (`B01-B06`), cardiovascular system (`C01-C10`), respiratory system (`R01-R07`), and analgesics (`N02`).
 
 **Discussion:**
-DPNs reveal key polypharmacy patterns.
-High-centrality medications highlight potential targets for drug monitoring.
+DPNs revealed key co-prescription patterns.
+High-centrality medications highlight potential targets for drug monitoring, such as identifying co-prescription trends that may warrant evaluation for safety, appropriateness, or policy oversight.
 This approach aids in identifying influential medications and refining prescribing oversight.

### 2025-07-10 docs/article.qmd
Finalize the first draft

@@
     journal:
+      name: International Journal of Epidemiology
       formatting: review
-      cite-style: authoryear
+      cite-style: numbername
     output-file: iadb-network-analysis.pdf
@@
 
-The inherently complex nature of health-related phenomena have fueled the growing implementation of network analysis, making it an important research framework in medicine and epidemiology [@Luke2007].
-Past implementations of network analysis in public health mostly focused on transmission network, social network, and organizational network.
-Only recently, @Cavallo2012 demonstrated a novel framework to describe medication use on a population level, i.e.
-drug prescription network (DPN), a term which later is coined by @Bazzoni2015.
-Network analysis and graph theory offer an approach to model the relationship among building blocks of a complex system.
-From a complex system standpoint, polypharmacy is a prescription of multiple drug combinations which can be modelled as a network [@Miglio2021].
-DPN can capture the complex relationships of a system that may vary over time, which is highly relevant to drugs prescribed for mental disorders.
+The complexity of health-related phenomena has led to the growing application of network analysis in medicine and epidemiology [@Luke2007; @Miglio2021].
+Graph theory provides the mathematical foundation for network analysis, offering an approach to study the relationships among the entities of a complex system.
+The early implementations of network analysis focused primarily on transmission, social, and organizational networks.
+More recently, @Cavallo2012 introduced drug prescription networks (DPNs) to model population-level drug prescription data.
+@Bazzoni2015 formalized the term, emphasizing its utility in understanding polypharmacy.
 
-In psychiatry, polypharmacy is defined as a patient with at least two concurrent psychiatric medications [@Shrivastava2013].
+Psychiatric polypharmacy is defined as a patient with at least two concurrent psychiatric medications [@Shrivastava2013].
 With a prevalence between 13-90%, psychiatric polypharmacy manifests in five categories, namely same-class, multi-class, adjunctive, augmentation, and total polypharmacy [@Shrivastava2013].
@@
 
-Node centrality measures, such as eigenvector centrality, quantify the importance of a medication in polypharmacy patterns [@Askar2021].
+A DPN for an individual on a given day can be formalized as a simple undirected graph where medications correspond to nodes, and edges connecting pairs of nodes represent co-prescription relationships between medications [@Cavallo2012].
+Typically, simple undirected graphs are represented by a square symmetric matrix with zeros on the diagonal called the adjacency matrix [@estrada2012structure].
+In the adjacency matrix of the individual-level DPN, nonzero off-diagonal elements correspond to two medications being co-prescribed on a given day.
+
+A population-level DPN on a given day can be constructed from individual-level DPNs through matrix addition of the corresponding adjacency matrices [@Cavallo2012].
+A DPN at the population level on a given day is then formulated as a weighted undirected graph, which is characterized by a weighted adjacency matrix with weights equal to the counts of medication co-prescription occurrences.
+Therefore, analyzing the structural characteristics of a DPN over time using both local (medication-level) and global (network-level) graph measures offers valuable insights into co-prescription dynamics and can deepen our understanding of polypharmacy.
+
+Local network statistics, such as node centrality measures, quantify the importance of a medication in polypharmacy patterns [@Askar2021].
 Addressing concerns about standardized polypharmacy indicators raised by @Sirois2016 and @Delara2022, we highlight eigenvector centrality as a key measure of a medication’s connection to highly prescribed drugs.
@@
 
-Mathematically, a simple undirected graph $\mathcal{G}$ is a pair $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, where $\mathcal{V} = \left(1, \dots, n \right)$ is the set of nodes and $\mathcal{E} = \left(\{j, k\} \ | \ j, k \in \mathcal{V}, \ j \neq k \right)$ is the finite set of edges with $\{j, k\} = \{k, j\}$.
-The adjacency matrix $A \in \{0, 1\}^{n \times n}$ of a simple undirected graph $\mathcal{G}$ with $\mathcal{V}$ nodes is a square symmetric matrix of dimension $n \times n$ defined as @eq-graph-theory, with $A_{jk} = A_{kj}$ for all $j, k \in \mathcal{V}$ where $j \neq k$.
-For each day $t = \left(1, \dots, T \right)$ and each individual $p = \left(1, \dots, P \right)$, the adjacency matrix represented a simple undirected graph.
+Mathematically, a simple undirected graph $\mathcal{G}$ is a pair $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, where $\mathcal{V} = \left(1, \dots, n \right)$ is the set of nodes and $\mathcal{E} = \left(\{i, j\} \ | \ i, j \in \mathcal{V}, \ i \neq j \right)$ is the finite set of edges with $\{i, j\} = \{j, i\}$.
+The adjacency matrix $A \in \{0, 1\}^{n \times n}$ of a simple undirected graph $\mathcal{G}$ with $\mathcal{V}$ nodes is a square symmetric matrix of dimension $n \times n$ defined as @eq-graph-theory, with $A_{ij} = A_{ji}$ for all $i, j \in \mathcal{V}$ where $i \neq j$.
+For each day $t = \left(1, \dots, T \right)$ and each individual $p = \left(1, \dots, P \right)$, the adjacency matrix represented a simple undirected graph [@estrada2012structure].
 
 $$
-A_{jk} = 
+A_{ij} = 
 \begin{cases}
-1 & \text{if } \{j, k\} \in \mathcal{E} \\
+1 & \text{if} \{i, j\} \in \mathcal{E} \\
 0 & \text{otherwise}
@@
 Typically, undirected graphs do not contain self connections, $\{\mathcal{v}_i, \mathcal{v}_i\} \notin \mathcal{E}$ [j].
-
-A graph can be represented as an adjacency matrix $A$.
-The adjacency matrix $A$ has dimensions of $|\mathcal{V}| \times |\mathcal{V}|$, where $|\mathcal{V}|$ is the number of nodes in a graph.
-Each element of $A_{ij}$ is the edge, where in an unweighted graph, $A_{ij} = 1$ if a connection exists between $\mathcal{v}_i$ and $\mathcal{v}_j$, and $A_{ij} = 0$ otherwise.
-In a weighted graph, $A_{ij}$ can take any real value ($A_{ij} \in \mathbb{R}$) depending on the application [@estrada2012structure].
 
@@
 
-The predomination of multi-class co-prescription among anxiolytics recipients is consistent with the recommendations in the Dutch Huisartsengenootschap [NHG; @NHG2019Anxiety].
+The predomination of multi-class co-prescription among anxiolytics recipients is consistent with the recommendations in the Dutch College of General Practitioner (*Nederlands Huisartsen Genootschap*/NHG) [@NHG2019Anxiety].
 Specifically, the NHG guideline for anxiety disorders advises short-term benzodiazepine use, limited to two to four weeks, as an adjunct to Selective Serotonin Reuptake Inhibitors (SSRIs) during treatment initiation.

### 2025-07-10 docs/exec-summary/_preprocessing.qmd
Finalize the first draft

@@
 
-At the individual level, each patient's daily prescription record at time $t$ was encoded into a square matrix $A_t^{(i)}$, where rows and columns represent medication classes according to the ATC classification.
-An off-diagonal entry $A_{t_{jk}}^{(i)} = 1$ indicates that medication classes $j$ and $k$ were co-prescribed on the same day for individual $i$, while a diagonal entry $A_{t_{jj}}^{(i)} = 1$ captures the presence of a single prescription of medication $j$.
-To derive the population-level DPN, all individual-level daily prescription matrix $A^{(i)}$ were aggregated by computing their element-wise sum.
+At the individual level, each patient's daily prescription record at time $t$ was encoded into a square matrix $A_t^{(p)}$, where rows and columns represent medication classes according to the ATC classification.
+An off-diagonal entry $A_{t_{ij}}^{(p)} = 1$ indicates that medication classes $i$ and $j$ were co-prescribed on the same day for individual $p$, while a diagonal entry $A_{t_{ii}}^{(p)} = 1$ captures the presence of a single prescription of medication $i$.
+To derive the population-level DPN, all individual-level daily prescription matrix $A^{(p)}$ were aggregated by computing their element-wise sum.
 
-$$A_t = \displaystyle \sum_i A_t^{(i)}$$ {#eq-DPN}
+$$A_t = \displaystyle \sum_i A_t^{(p)}$$ {#eq-DPN}
 
 The population matrix $A_t$ captures the frequency of co-prescriptions (off-diagonal) and single prescriptions (diagonal) across the dataset at the specified time $t$.
-Each element $A_{t_{jk}}$ in the matrix was interpreted as the number of patients being prescribed with medication classes $j$ and $k$ on the same day $t$.
+Each element $A_{t_{ij}}$ in the matrix was interpreted as the number of patients being prescribed with medication classes $i$ and $j$ on the same day $t$.
 $A_t$ was represented as a weighted undirected graph, where each node corresponds to a medication class and edges reflect co-prescription frequencies.
@@
 
-The edge weight between medication classes $j$ and $k$ was computed as the average of their individual weights:
+The edge weight between medication classes $i$ and $j$ was computed as the average of their individual weights:
 

### 2025-07-10 docs/supplementary.qmd
Finalize the first draft

@@
       - bottom=2.5cm
-  docx:
-    pandoc-options: ["--mathml"]
-    output-file: iadb-network-analysis-supplementary.docx
 
@@
 
+## Time-series decomposition of medication dispensing records
+
+```{r}
+#| fig-width: 14
+#| fig-height: 8
+#| fig-cap: Reconstructed time series data using the SSA-based approach
+
+tar_read(plt_dot_recon_n_claim)
+tar_read(plt_dot_recon_eigen)
+
+```
+
 \normalpapersize
 
-## Time-series decomposition of medication dispensing records
+```{r tbl-trend}
+#| tbl-cap: Trend of medication uses alongside its measure of relative importance
+
+prettyRound <- function(x, ...) {
+  x %<>% round(...) %>% {ifelse(. == 0, "<0.001", as.character(.))}
+}
+
+fnote <- "The statistics were obtained from Mann-Kendall trend test, where positive result signifies a positive slope"
+
+tar_read(decom_ssa) %>%
+  subset(.$component %in% c("Original", "Trend") & .$metric != "claim2patient") %>%
+  tibble::tibble() %>%
+  dplyr::group_by(metric, group, component) %>%
+  dplyr::group_modify(~trend::mk.test(.x$value) %>% broom::tidy()) %>%
+  dplyr::ungroup() %>%
+  dplyr::mutate(
+    "Mann-Kendall" = sprintf(
+      "%s (p %s)", prettyRound(statistic, 2), prettyRound(p.value, 3)
+    )
+  ) %>%
+  subset(select = -c(statistic:alternative)) %>%
+  tidyr::pivot_wider(names_from = metric, values_from = `Mann-Kendall`) %>%
+  tidyr::pivot_wider(names_from = component, values_from = eigen:n_claim) %>%
+  set_colnames(c("ATC Group", rep(c("Original", "Trend"), 2))) %>%
+  knitr::kable(longtable = TRUE, booktabs = TRUE) %>%
+  kableExtra::kable_styling(latex_options = "repeat_header") %>%
+  kableExtra::add_header_above(c(" " = 1, "Eigenvector Centrality" = 2, "Prescription Dispensing" = 2)) %>%
+  kableExtra::add_footnote(fnote, notation = "none")
+
+```
 
@@
 #| fig-cap: Time-series decomposition using singular spectrum analysis-based approach
+#| eval: FALSE
 
@@
 
+tar_read(plt_ssa_recon_eigen)[[1]]
+tar_read(plt_ssa_recon_eigen)[[2]]
+tar_read(plt_ssa_recon_eigen)[[3]]
+tar_read(plt_ssa_recon_eigen)[[4]]
+tar_read(plt_ssa_recon_eigen)[[5]]
+tar_read(plt_ssa_recon_eigen)[[6]]
+tar_read(plt_ssa_recon_eigen)[[7]]
+tar_read(plt_ssa_recon_eigen)[[8]]
+tar_read(plt_ssa_recon_eigen)[[9]]
+tar_read(plt_ssa_recon_eigen)[[10]]
+tar_read(plt_ssa_recon_eigen)[[11]]
+tar_read(plt_ssa_recon_eigen)[[12]]
+tar_read(plt_ssa_recon_eigen)[[13]]
+tar_read(plt_ssa_recon_eigen)[[14]]
+tar_read(plt_ssa_recon_eigen)[[15]]
+tar_read(plt_ssa_recon_eigen)[[16]]
+tar_read(plt_ssa_recon_eigen)[[17]]
+tar_read(plt_ssa_recon_eigen)[[18]]
+tar_read(plt_ssa_recon_eigen)[[19]]
+tar_read(plt_ssa_recon_eigen)[[20]]
+tar_read(plt_ssa_recon_eigen)[[21]]
+tar_read(plt_ssa_recon_eigen)[[22]]
+tar_read(plt_ssa_recon_eigen)[[23]]
+tar_read(plt_ssa_recon_eigen)[[24]]
+
 ```

### 2025-07-10 docs/supplementary.tex
Finalize the first draft

@@
 
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \usepackage{longtable}
@@
 
-\normalpapersize
-
 \subsection{Time-series decomposition of medication dispensing
@@
 
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
+\caption{Reconstructed time series data using the SSA-based approach}
 
@@
 
-\begin{figure}[H]
+\normalpapersize
 
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-3.pdf}
+\begin{longtable}{lllll}
 
-}
+\caption{\label{tbl-trend}Trend of medication uses alongside its measure
+of relative importance}
 
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
+\tabularnewline
 
-\end{figure}%
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Eigenvector Centrality} & \multicolumn{2}{c}{Prescription Dispensing} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
+ATC Group & Original & Trend & Original & Trend\\
+\midrule
+\endfirsthead
+\multicolumn{5}{@{}l}{\textit{(continued)}}\\
+\toprule
+ATC Group & Original & Trend & Original & Trend\\
+\midrule
+\endhead
 
-\begin{figure}[H]
+\endfoot
+\bottomrule
+\endlastfoot
+Alimentary and metabolism & 18.63 (p <0.001) & 24.05 (p <0.001) & 11.11 (p <0.001) & 23.8 (p <0.001)\\
+Blood & 17.02 (p <0.001) & 24.06 (p <0.001) & 13.24 (p <0.001) & 24.02 (p <0.001)\\
+Cardiovascular & 18.11 (p <0.001) & 24.06 (p <0.001) & 14.39 (p <0.001) & 23.19 (p <0.001)\\
+Dermatologicals & 3.47 (p 0.001) & 9.83 (p <0.001) & -0.1 (p 0.919) & -2.54 (p 0.011)\\
+Genitourinary & -0.37 (p 0.714) & -1.27 (p 0.204) & -3 (p 0.003) & -11.57 (p <0.001)\\
+\addlinespace
+Systemic hormonal & -11.44 (p <0.001) & -20.17 (p <0.001) & 5.36 (p <0.001) & 13.01 (p <0.001)\\
+Systemic anti-infectives & -7.25 (p <0.001) & -12.64 (p <0.001) & -7.3 (p <0.001) & -12.25 (p <0.001)\\
+Antineoplastics & 1.22 (p 0.224) & 3.58 (p <0.001) & 8.86 (p <0.001) & 18.52 (p <0.001)\\
+Musculoskeletal & -6.92 (p <0.001) & -13.76 (p <0.001) & -6.6 (p <0.001) & -14.98 (p <0.001)\\
+Anesthetic & -1.27 (p 0.204) & -10.01 (p <0.001) & -8.17 (p <0.001) & -19.57 (p <0.001)\\
+\addlinespace
+Analgesics & -14.12 (p <0.001) & -22.7 (p <0.001) & -2.97 (p 0.003) & -4.62 (p <0.001)\\
+Antiepileptics & -15.08 (p <0.001) & -24.07 (p <0.001) & -7.31 (p <0.001) & -17.78 (p <0.001)\\
+Antiparkinson & -9.09 (p <0.001) & -23.07 (p <0.001) & 4.27 (p <0.001) & 18.66 (p <0.001)\\
+Antipsychotics & -9.36 (p <0.001) & -17.68 (p <0.001) & 6.51 (p <0.001) & 18.26 (p <0.001)\\
+Anxiolytics & -13.49 (p <0.001) & -20.76 (p <0.001) & -4.77 (p <0.001) & -9.75 (p <0.001)\\
+\addlinespace
+Hypnotics and sedatives & -16.68 (p <0.001) & -24.06 (p <0.001) & 0.13 (p 0.898) & 0.58 (p 0.563)\\
+Antidepressants & 8.06 (p <0.001) & 15.65 (p <0.001) & 9.43 (p <0.001) & 21.52 (p <0.001)\\
+Psychostimulants & 11.2 (p <0.001) & 23.93 (p <0.001) & 13.75 (p <0.001) & 23.85 (p <0.001)\\
+Antidementia & -0.71 (p 0.477) & -4.24 (p <0.001) & 2.57 (p 0.01) & 1.43 (p 0.153)\\
+Other nervous system drugs & -7.97 (p <0.001) & -6.6 (p <0.001) & -5.85 (p <0.001) & -6.96 (p <0.001)\\
+\addlinespace
+Antiparasitics & 0.38 (p 0.706) & 7.99 (p <0.001) & 4.81 (p <0.001) & 13.23 (p <0.001)\\
+Respiratory & -2.57 (p 0.01) & -5.72 (p <0.001) & -0.28 (p 0.778) & -3.53 (p <0.001)\\
+Sensory & 12.14 (p <0.001) & 21.08 (p <0.001) & 8.15 (p <0.001) & 23.46 (p <0.001)\\
+Others & -0.87 (p 0.385) & 3.77 (p <0.001) & -12.18 (p <0.001) & -14.55 (p <0.001)\\*
 
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-4.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-5.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-6.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-7.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-8.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-9.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-10.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-11.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-12.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-13.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-14.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-15.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-16.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-17.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-18.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-19.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-20.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-21.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-22.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-23.pdf}
-
-}
-
-\caption{Time-series decomposition using singular spectrum
-analysis-based approach}
-
-\end{figure}%
+\end{longtable}
 

### 2025-07-10 _targets.R

@@ -327,9 +327,9 @@ list(
   tar_map(
     unlist = TRUE,
     values = tibble::tibble(
-      "varname" = c("n_claim", "eigen"), "scales" = c("free_y", "fixed")
+      "varname" = c("n_claim", "eigen")
     ),
-    tar_target(plt_dot_recon, vizDot(ts_recon, y = varname, scales = scales, nrow = 4))
+    tar_target(plt_dot_recon, vizDot(ts_recon, y = varname, scales = "free_y", nrow = 4))
   ),
 
   # Compare time-series models and produce a model evaluation table
@@ -367,6 +367,7 @@ list(
   tar_quarto(report_spectral, "docs", profile = "spectral", priority = 0),
   tar_quarto(article, "docs/article.qmd"),
   tar_quarto(supplementary, "docs/supplementary.qmd"),
+  tar_quarto(cover_letter_ije, "docs/submission/cover-letter-ije.md"),
   tar_quarto(readme, "README.qmd", priority = 0)
 
 )

### 2025-07-26 docs/article.qmd
Finalize the IJE draft

@@
       cite-style: numbername
+      highlights:
+        - Multi-class co-prescription was over ten times more common than same-class use in both antidepressant and anxiolytic users.
+        - Seven highly central drug classes link psychiatric medications with chronic disease treatments, indicating key roles in co-prescription networks.
+        - Network analysis reveals prescribing hubs not detectable through traditional drug utilization methods.
+        - Findings align with Dutch clinical guidelines promoting multi-class use in anxiety and monotherapy in depression management.
+        - Co-prescription patterns reflect underlying multimorbidity, highlighting the complexity of psychiatric and chronic illness care.
     output-file: iadb-network-analysis.pdf
@@
 
-Mathematically, a simple undirected graph $\mathcal{G}$ is a pair $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, where $\mathcal{V} = \left(1, \dots, n \right)$ is the set of nodes and $\mathcal{E} = \left(\{i, j\} \ | \ i, j \in \mathcal{V}, \ i \neq j \right)$ is the finite set of edges with $\{i, j\} = \{j, i\}$.
-The adjacency matrix $A \in \{0, 1\}^{n \times n}$ of a simple undirected graph $\mathcal{G}$ with $\mathcal{V}$ nodes is a square symmetric matrix of dimension $n \times n$ defined as @eq-graph-theory, with $A_{ij} = A_{ji}$ for all $i, j \in \mathcal{V}$ where $i \neq j$.
-For each day $t = \left(1, \dots, T \right)$ and each individual $p = \left(1, \dots, P \right)$, the adjacency matrix represented a simple undirected graph [@estrada2012structure].
+Mathematically, a simple undirected graph $\mathcal{G}$ is a pair $\mathcal{G} = \left(\mathcal{V}, \mathcal{E}\right)$, where $\mathcal{V} = \left(1, \dots, n \right)$ is the set of nodes and $\mathcal{E} = \left(\{i, j\} \ | \ i, j \in \mathcal{V}, \ i \neq j \right)$ is the finite set of edges.
+The adjacency matrix $A \in \{0, 1\}^{n \times n}$ of a simple undirected graph $\mathcal{G}$ is a square symmetric matrix of dimension $n \times n$ defined as:
 
@@
 
-In a DPN, the node set $\mathcal{V} = \{\mathcal{v}_1, \mathcal{v}_2, \dots, \mathcal{v}_n\}$ represents a finite set of $n$ medications.
-Additionally, $\mathcal{E}$ is a finite set of edges, where each edge is a pair of nodes that corresponds to a co-prescription.
-In an undirected graph, the order of $i, j$ does not matter.
-Typically, undirected graphs do not contain self connections, $\{\mathcal{v}_i, \mathcal{v}_i\} \notin \mathcal{E}$ [j].
+with elements $A_{ij} = A_{ji}$, for all $i, j \in \mathcal{V}$ where $i \neq j$ [@estrada2012structure].
+
+In our setting, drug co-prescriptions from a single individual $p$ on a specific day $t$ are encoded in a simple undirected graph $\mathcal{G}^p(t)=\left(\mathcal{V}, \mathcal{E}^p\left(t\right)\right)$ with $n \times n$ adjacency matrix ${A^p}\left(t\right)$.
+In these daily observed individual-level networks, the node set $\mathcal{V}$ corresponds to a set of $n$ medication classes according to the ATC classification, and the edge set $\mathcal{E}^p\left(t\right)$ contains edges that indicate the concurrent use of pairs of medications for a particular individual $p$ on a given day $t$.
 
@@
 We defined high and low eigenvector centrality relative to the expected value $\frac{1}{n}$, based on the null model of uniform connectivity (see "Determining relative importance").
-This study focused on eigenvector centrality to evaluate which medications have a significant influence on how antidepressants and anxiolytics are prescribed.
-@eq-eigen-centrality outlines the calculation of eigenvector centrality; $c_i$ and $c_j$ are the centralities of node $\mathcal{v}_i$ and $\mathcal{v}_j$, respectively; $\lambda$ is the eigenvalue; $A_{ji}$ is an element on row $j$ and column $i$ from an adjacency matrix $A$, representing the connection between node $\mathcal{v}_j$ and $\mathcal{v}_i$.
+This study focused on eigenvector centrality to evaluate which medications have a significant influence on the prescription of antidepressants and anxiolytics.
+@eq-eigen-centrality outlines the calculation of eigenvector centrality; $c_i$ and $c_j$ are the centralities of nodes $\mathcal{v}_i$ and $\mathcal{v}_j$, respectively, with $i, j \in \mathcal{V}$; $\lambda$ is the eigenvalue; $A_{ji}\left(t\right)$ is an element on row $j$ and column $i$ from an adjacency matrix $A\left(t\right)$, representing the connection between node $\mathcal{v}_j$ and $\mathcal{v}_i$ with $i, j \in \mathcal{V}$.
 
 $$
-\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} A_{ji} \cdot c_j
+\displaystyle c_i\left(t\right) = \frac{1}{\lambda} \sum_{j \neq i} A_{ji}\left(t\right) \cdot c_j\left(t\right)
 $$ {#eq-eigen-centrality}
@@
 The cyclical patterns are detailed in the supplementary material section S2.1.
-Seasonality was explored as dependencies at daily and weekly lags and further described in the supplementary material section S2.2.
+Seasonality was explored as dependencies at daily and weekly lags and further described in the supplementary material section S2.2 and S2.3.
 
@@
 
-Additional decomposition results for other medication classes are presented in the supplementary section S2.3.
+Additional decomposition results for other medication classes are presented in the supplementary section S2.4.
 Broadly antidepressants exhibited a steady increasing trend over time, while anxiolytics showed a gradual decline both in dispensing frequency and eigenvector centrality.
@@
 
+# Funding {-}
+
+This work was supported by The Indonesia Endowment Funds for Education (LPDP) in the form of a PhD scholarship to AL with Grant Agreement Number 0007457/PHA/D/2/lpdp2022 (26 July 2025).
+
 # References

### 2025-07-26 docs/exec-summary/_preprocessing.qmd
Finalize the IJE draft

@@
 
-At the individual level, each patient's daily prescription record at time $t$ was encoded into a square matrix $A_t^{(p)}$, where rows and columns represent medication classes according to the ATC classification.
-An off-diagonal entry $A_{t_{ij}}^{(p)} = 1$ indicates that medication classes $i$ and $j$ were co-prescribed on the same day for individual $p$, while a diagonal entry $A_{t_{ii}}^{(p)} = 1$ captures the presence of a single prescription of medication $i$.
-To derive the population-level DPN, all individual-level daily prescription matrix $A^{(p)}$ were aggregated by computing their element-wise sum.
+Assume an observational study where $P$ individuals indexed by $p$, $p=1,\dots,P$ are followed for each day $t$, $t=1, \dots, T$ for a total period of $T$ days.
+To derive the population-level DPN on each day $t$ with adjacency matrix $A_t$, the individual-level daily prescription matrices $A^{p}\left(t\right)$ were aggregated by computing their element-wise sum, that is,
 
-$$A_t = \displaystyle \sum_i A_t^{(p)}$$ {#eq-DPN}
+$$
+\displaystyle \sum_{p=1}^P A^{p}\left(t\right), \ \text{where} \ A\left(t\right) \in \ \mathbb{Z}_+^{n\times n}.
+$$ {#eq-DPN}
 
-The population matrix $A_t$ captures the frequency of co-prescriptions (off-diagonal) and single prescriptions (diagonal) across the dataset at the specified time $t$.
-Each element $A_{t_{ij}}$ in the matrix was interpreted as the number of patients being prescribed with medication classes $i$ and $j$ on the same day $t$.
-$A_t$ was represented as a weighted undirected graph, where each node corresponds to a medication class and edges reflect co-prescription frequencies.
+The matrix $A\left(t\right)$ captures the population frequency of co-prescriptions (off-diagonal) and single prescriptions (diagonal) in the data at
+
+the specified time $t$.
+Each element $A_{ij}\left(t\right)$ in the matrix was interpreted as the number of patients being prescribed medication classes $i$ and $j$, with $i,j\in \mathcal{V}$, on the same day $t$.
+
+The population-level DPN is then a weighted undirected graph $\mathcal{G}\left(t\right) = \left(\mathcal{V}, \mathcal{E}\left(t\right)\right)$ observed over $T$ discrete time points $t=1,\dots,T$, where:
+- $\mathcal{V}$ is the fixed set of $n$ nodes,
+- $\mathcal{E}_t \subseteq \{ \{i, j\} : i, j \in \mathcal{V}, i \neq j \}$ is the edge set at time $t$.
+
+The population-level DPN at time $t$ is fully described by its symmetric weighted adjacency matrix $A\left(t\right) \in \mathbb{Z}_+^{n \times n}$, which is defined as:
+
+$$
+{A}_{ij}\left(t\right) =
+\begin{cases}
+w_{t,ij} > 0 & \text{if } \{i, j\} \in \mathcal{E}\left(t\right), \\
+0 & \text{otherwise},
+\end{cases}
+\quad \text{with } {A}\left(t\right) = {{A}\left(t\right)}^\top.
+$$
+
 In the original work of DPN, all defined daily dose (DDD) were assumed equal to 1, allowing for applying raw counts as the edge weights.
@@
 
-$$\omega_j = \frac{1}{\frac{\omega_B}{3} \sqrt{2 \pi}} e^{-\frac{1}{2}\left(\frac{DDD - \omega_B}{\omega_B/3}\right)^2}$$ {#eq-weighted-DDD}
+$$\omega_j = \frac{1}{\sigma \sqrt{2 \pi}} e^{-\frac{\left(DDD_j - 1\right)}{2\sigma^2}^2}$$ {#eq-weighted-DDD}
 

### 2025-07-26 docs/exec-summary/_source-data.qmd
Finalize the IJE draft

@@
 
-This analysis includes daily medication dispensing from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.
+This analysis includes daily drug administration from a static cohort of adults aged 18 to 65 years and prescribed anxiolytics or antidepressants at least once in the period 2018-2022.

### 2025-07-26 _targets.R

@@ -367,7 +367,7 @@ list(
   tar_quarto(report_spectral, "docs", profile = "spectral", priority = 0),
   tar_quarto(article, "docs/article.qmd"),
   tar_quarto(supplementary, "docs/supplementary.qmd"),
-  tar_quarto(cover_letter_ije, "docs/submission/cover-letter-ije.md"),
+  tar_quarto(cover_letter_ije, "docs/submission/IJE/cover-letter-ije.md"),
   tar_quarto(readme, "README.qmd", priority = 0)
 
 )

### 2025-09-22 docs/article.qmd
Finalize submission to GEPI

@@
     include-in-header:
-      file: _header.tex
+      - file: _header.tex
+      - text: |
+          \newpageafter{author}
     journal:
-      name: International Journal of Epidemiology
+      name: Global Epidemiology
       formatting: review
@@
 #| fig-height: 12
-#| fig-pos: H
 #| fig-cap: Time-series decomposition of antidepressants dispensing data using singular spectrum analysis-based approach
@@
 
+# Author Contributions {-}
+
+**AL**: Conceptualization, Methodology, Formal analysis, Visualization, Writing - original draft, Project administration.
+**SB**: Methodology, Writing - review and editing.
+**EH**: Writing - review and editing.
+**JHB**: Data curation, Investigation, Project administration.
+**FJ**: Conceptualization, Supervision, Writing - original draft, Writing - review and editing.
+**TLF**: Conceptualization, Supervision, Methodology, Writing - original draft, Writing - review and editing.
+
 # Funding {-}

### 2025-09-22 docs/submission/GEPI/manuscript/article.tex
Finalize submission to GEPI

--- 2025-07-08 docs/articleSB.tex
@@
 \documentclass[
-  authoryear,
+  number,
   review]{elsarticle}
@@
 \makeatother
+\journal{Global Epidemiology}
 
 \usepackage[]{natbib}
-\bibliographystyle{elsarticle-harv}
+\bibliographystyle{elsarticle-num-names}
 \usepackage{bookmark}
@@
 \hypersetup{
-  pdftitle={A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands from 2018 to 2022},
-  pdfauthor={Aly Lamuri; Spyros Balafas; Eelko Hak; Jens H. Bos; Frederike Jörg; Talitha L. Feenstra},
-  pdfkeywords={Graph Theory, Prescription Registry, Polypharmacy, Mental
-Health, Public Health Monitoring},
+  pdftitle={A temporal network analysis of drug co-prescription during antidepressants and anxiolytics dispensing in the Netherlands from 2018 to 2022},
+  pdfkeywords={Graph Theory, Prescription
+Registry, Co-prescription, Mental Health, Public Health Monitoring},
   colorlinks=true,
@@
 \begin{frontmatter}
-\title{A temporal network analysis of drug co-prescription around
-antidepressants and anxiolytics uses in the Netherlands from 2018 to
-2022}
-\author[1,2]{Aly Lamuri%
-\corref{cor1}%
-}
- \ead{a.l.m.lamuri.murdani@rug.nl} 
-\author[1]{Spyros Balafas%
-%
-}
-
-\author[1]{Eelko Hak%
-%
-}
-
-\author[1]{Jens H. Bos%
-%
-}
-
-\author[1,3]{Frederike Jörg%
-%
-}
-
-\author[1]{Talitha L. Feenstra%
-%
-}
-
-\affiliation[1]{organization={University of
-Groningen},city={Groningen},country={Netherlands},countrysep={,},postcodesep={}}
-\affiliation[2]{organization={University of
-Indonesia},city={Depok},country={Indonesia},countrysep={,},postcodesep={}}
-\affiliation[3]{organization={University Medical Centre
-Groningen},city={Groningen},country={Netherlands},countrysep={,},postcodesep={}}
-
-\cortext[cor1]{Corresponding author}
+\title{A temporal network analysis of drug co-prescription during
+antidepressants and anxiolytics dispensing in the Netherlands from 2018
+to 2022}
 
@@
 \textbf{Methods:} We utilized the IADB.nl database, including
-prescriptions from 128 Dutch pharmacies (2018--2022). A closed cohort of
+prescriptions from 128 Dutch pharmacies (2018--2022). A cohort of
 patients prescribed antidepressants/anxiolytics was extracted.
@@
 co-prescriptions. Eigenvector centrality (\(c_e\)) quantified relative
-nodal importance. Weekly-aggregated data included prescriptions
-(\(n_c\)), number of patients, claim-to-patient ratio, and eigenvector
-centrality. Singular spectrum analysis decomposed trends.
-
-\textbf{Results:} Antidepressants (ATC \texttt{N06A}, \(c_e\): 0.09,
-\(n_c\): 28,993) and anxiolytics (\texttt{N05B}, \(c_e\): 0.04, \(n_c\):
-14,061) had high eigenvector centrality, indicating frequent
-co-prescription. Additional high-centrality groups included medications
-for alimentary and metabolism (\texttt{A01-A16}), blood
-(\texttt{B01-B06}), cardiovascular (\texttt{C01-C10}), analgesics
-(\texttt{N02}), and respiratory (\texttt{R01-R07}).
-
-\textbf{Discussion:} DPNs reveal key polypharmacy patterns.
+nodal importance. Weekly-aggregated data included number of dispensing
+(\(n_c\)) and eigenvector centrality, which were decomposed using a
+singular-spectrum approach.
+
+\textbf{Results:} Antidepressants (\(c_e\): 0.09, \(n_c\): 28,993) and
+anxiolytics (\(c_e\): 0.05, \(n_c\): 14,061) had high eigenvector
+centrality, demonstrating frequent co-prescription. Other ATC groups
+with high centrality included those for the alimentary tract and
+metabolism (\texttt{A01-A16}), blood and blood-forming organs
+(\texttt{B01-B06}), cardiovascular system (\texttt{C01-C10}),
+respiratory system (\texttt{R01-R07}), and analgesics (\texttt{N02}).
+
+\textbf{Discussion:} DPNs revealed key co-prescription patterns.
 High-centrality medications highlight potential targets for drug
-monitoring. This approach aids in identifying influential medications
-and refining prescribing oversight.
+monitoring, such as identifying co-prescription trends that may warrant
+evaluation for safety, appropriateness, or policy oversight. This
+approach aids in identifying influential medications and refining
+prescribing oversight.
 \end{abstract}
@@
     Graph Theory \sep Prescription
-Registry \sep Polypharmacy \sep Mental Health \sep 
+Registry \sep Co-prescription \sep Mental Health \sep 
     Public Health Monitoring
@@
 
-The complexity of health-related phenomena has led to the growing application of network analysis in medicine and epidemiology \citep{Luke2007,Miglio2021}.
-Graph theory provides the mathematical foundation for network analysis, offering an approach to study the relationships among the entities of a complex system.
-The early implementations of network analysis focused primarily on transmission, social, and organizational networks.
-More recently, \citet{Cavallo2012} introduced drug prescription networks (DPNs) to model population-level drug prescription data.
-\citet{Bazzoni2015} formalized the term, emphasizing its utility in understanding polypharmacy.
-
-Polypharmacy is defined as a patient with at least two concurrent medications.
-With a prevalence between 13-90\%, polypharmacy in psychiatry manifests itself in five categories, namely same-class, multiclass, adjunctive, augmentation, and total polypharmacy \citep{Shrivastava2013}.
-Same-class polypharmacy is the use
-of multiple drugs of the same class. Multiclass polypharmacy is
-the use of multiple medications of different classes indicated for the
-same cluster of symptoms. Adjunctive polypharmacy is the use of additional
-medications to treat side effects of other medications. Augmentation
-polypharmacy is the use of full-dose and sub-dose medications from a
-different class for the same symptom cluster. Finally, total
-polypharmacy is the total count of all medications used by a patient, psychopharmaca and other classes as well \citep{Shrivastava2013}. For
-policy makers, differences in the definition of polypharmacy pose a challenge in
-designing a monitoring system \citep{Sirois2016}. DPN can capture
-the complex relationships of a system that can vary over time, which is
-very relevant for drugs prescribed for mental disorders.
-
-A DPN for an individual on a given day can be formalized as a simple undirected graph where medications correspond to nodes, and edges connecting pairs of nodes represent co-prescription relationships between medications.
-Typically, simple undirected graphs are represented by a square symmetric matrix with zeros on the diagonal called the adjacency matrix \citep{estrada2012structure}.
-In the adjacency matrix of the individual-level DPN, nonzero off-diagonal elements correspond to two medications being co-prescribed on a given day.
-
-A population-level DPN on a given day can be constructed from individual-level DPNs through matrix addition of the corresponding adjacency matrices \citep{Cavallo2012}.
-A DPN at the population level on a given day is then formulated as a weighted undirected graph, which is characterized by a weighted adjacency matrix with weights equal to the counts of medication co-prescription occurrences.
-Therefore, analyzing the structural characteristics of a DPN over time using both local (medication-level) and global (network-level) graph measures offers valuable insights into co-prescription dynamics and can deepen our understanding of polypharmacy.
+The complexity of health-related phenomena has led to the growing
+application of network analysis in medicine and epidemiology
+\citep{Luke2007, Miglio2021}. Graph theory provides the mathematical
+foundation for network analysis, offering an approach to study the
+relationships among the entities of a complex system. The early
+implementations of network analysis focused primarily on transmission,
+social, and organizational networks. More recently, \citet{Cavallo2012}
+introduced drug prescription networks (DPNs) to model population-level
+drug prescription data. \citet{Bazzoni2015} formalized the term,
+emphasizing its utility in understanding polypharmacy.
+
+Psychiatric polypharmacy is defined as a patient with at least two
+concurrent psychiatric medications \citep{Shrivastava2013}. With a
+prevalence between 13-90\%, psychiatric polypharmacy manifests in five
+categories, namely same-class, multi-class, adjunctive, augmentation,
+and total polypharmacy \citep{Shrivastava2013}. Same-class polypharmacy
+is the use of multiple medications from the same class. Multi-class
+polypharmacy is the use of multiple medications from different classes
+indicated for the same symptom cluster. Adjunctive polypharmacy is the
+use of additional medications to treat side effects due to other
+medications. Augmentation polypharmacy is the use of full-dose and
+sub-dose medications from a different class for the same symptom
+cluster. Finally, total polypharmacy is the overall number of
+medications a patient uses, including those prescribed for multiple
+psychiatric symptom clusters as well as for comorbid non-psychiatric
+conditions \citep{Shrivastava2013}. For policymakers, differences in
+defining polypharmacy pose a challenge to design an effective monitoring
+system \citep{Sirois2016}. Such monitoring is essential to identify
+prevalent co-prescription pattern that may impact treatment
+appropriateness and healthcare policy development.
+
+A DPN is a graphical representation where medications correspond to
+nodes, and edges represent co-prescription relationships between them.
+Typically, simple undirected graphs are represented by a square
+symmetric adjacency matrix \(A\), where each nonzero element \(A_{ij}\)
+indicates that medications \(i\) and \(j\) were co-prescribed on a given
+day. A population-level DPN can be constructed by aggregating individual
+patient networks through matrix addition \citep{Cavallo2012}. Analyzing
+the structural characteristics of a DPN using both local
+(medication-level) and global (network-level) graph measures provides
+insights into co-prescription dynamics.
+
+A DPN for an individual on a given day can be formalized as a simple
+undirected graph where medications correspond to nodes, and edges
+connecting pairs of nodes represent co-prescription relationships
+between medications \citep{Cavallo2012}. Typically, simple undirected
+graphs are represented by a square symmetric matrix with zeros on the
+diagonal called the adjacency matrix \citep{estrada2012structure}. In
+the adjacency matrix of the individual-level DPN, nonzero off-diagonal
+elements correspond to two medications being co-prescribed on a given
+day.
+
+A population-level DPN on a given day can be constructed from
+individual-level DPNs through matrix addition of the corresponding
+adjacency matrices \citep{Cavallo2012}. A DPN at the population level on
+a given day is then formulated as a weighted undirected graph, which is
+characterized by a weighted adjacency matrix with weights equal to the
+counts of medication co-prescription occurrences. Therefore, analyzing
+the structural characteristics of a DPN over time using both local
+(medication-level) and global (network-level) graph measures offers
+valuable insights into co-prescription dynamics and can deepen our
+understanding of polypharmacy.
 
 Local network statistics, such as node centrality measures, quantify the
-importance of a drug in polypharmacy patterns \citep{Askar2021}.
-Addressing concerns about standardized polypharmacy indicators raised by \citet{Sirois2016} and \citet{Delara2022}, we highlight eigenvector centrality as a key measure for identifying drugs frequently prescribed alongside other influential drugs.
-Thus, high eigenvector centrality suggests frequent co-prescription with commonly used medications, reflecting co-prescribing trends.
-Based on previous studies \citep{Cavallo2012, Bazzoni2015}, we hypothesize that eigenvector centrality serves as a meaningful quantitative indicator of polypharmacy.
-Therefore, this study aims to assess the structural characteristics of temporal DPNs, focusing on the role of eigenvector centrality in identifying influential medications and prescribing patterns in mental health treatments.
+importance of a medication in polypharmacy patterns \citep{Askar2021}.
+Addressing concerns about standardized polypharmacy indicators raised by
+\citet{Sirois2016} and \citet{Delara2022}, we highlight eigenvector
+centrality as a key measure of a medication's connection to highly
+prescribed drugs. A high eigenvector centrality suggests frequent
+co-prescription with commonly used medications, reflecting prescribing
+trends. Building on prior studies \citep{Cavallo2012, Bazzoni2015}, we
+hypothesize that eigenvector centrality serves as a meaningful
+quantitative indicator of polypharmacy. Therefore, this study aimed to
+assess the structural characteristics of temporal DPNs, focusing on the
+role of eigenvector centrality in identifying associated medications in
+adult patients prescribed for antidepressants or anxiolytics.
 
@@
 
-\subsection{Source of data}\label{source-of-data}
-
-The data used in this study are exported from IADB.nl, a dynamic pharmacy database containing prescription data from 1994, which continues to grow expansively.
-The database covers approximately 120 community pharmacies serving over one million patients and was accessed on the 20\textsuperscript{th}of September, 2023.
-All patients are recorded in the database, regardless of health care insurance, where prescription rates, age, and gender can be generalizable to represent the Netherlands \citep{Visser2013}.
-The database offers a longitudinal record, where each individual has a uniquely anonymized tracking identifier.
-All records contain fields on the date of drug dispensing, its quantity, dose regimen, number of days prescribed, prescribing physicians, and the Anatomical Therapeutic Chemical (ATC) code.
-Except for the over the counter drugs and medication dispensed during hospitalization, other medication records for each patient are complete, mainly due to high patient-pharmacy commitment in the Netherlands.
-This analysis includes daily medication claims from a static cohort of adults aged 18-65 years old and prescribed for anxiolytics or antidepressants at least once in the time span from 2018 to 2022.
+\subsection{Source of data and study
+population}\label{source-of-data-and-study-population}
+
+All data in this study originated from the University of Groningen
+IADB.nl, a dynamic pharmacy database containing prescription data since
+1994 which still grows expansively. The database covers approximately
+128 community pharmacies serving over one million patients and was
+accessed on the 20\textsuperscript{th}of September, 2023. All patients
+are recorded in the database, irrespective of health care insurance,
+where the prescription rates, age, and gender are generalizable to
+represent the Netherlands \citep{Visser2013}. The database offers a
+longitudinal record, where each individual has a uniquely anonymized
+tracking identifier. All records contain fields on the date of
+medication dispensing, its quantity, dose regimen, number of days
+prescribed, prescribing physicians, and the Anatomical Therapeutic
+Chemical (ATC) code. Except for the over the counter drugs and
+medication dispensed during hospitalization, all medication records for
+each patient are complete, mainly due to high patient-pharmacy
+commitment in the Netherlands.
+
+This analysis includes daily drug administration from a static cohort of
+adults aged 18 to 65 years and prescribed anxiolytics or antidepressants
+at least once in the period 2018-2022.
 
@@
 Mathematically, a simple undirected graph \(\mathcal{G}\) is a pair
-\(\mathcal{G} = (\mathcal{V}, \mathcal{E})\), where \(\mathcal{V}=\left(1,\dots,n \right)\) is the finite set of nodes and \(\mathcal{E}=\left(\{i,j\} \ |\ i,j\in \mathcal{V},\ i\neq j \right)\) is the finite set of edges with \(\{i,j\}=\{j,i\}\).
-The adjacency matrix $A\in \{0,1\}^{n\times n}$ of a simple undirected graph \(\mathcal{G}\) with \(|\mathcal{V}|=n\) nodes, is a square symmetric matrix of dimension \(n\times n\) defined as, \[
+\(\mathcal{G} = \left(\mathcal{V}, \mathcal{E}\right)\), where
+\(\mathcal{V} = \left(1, \dots, n \right)\) is the set of nodes and
+\(\mathcal{E} = \left(\{i, j\} \ | \ i, j \in \mathcal{V}, \ i \neq j \right)\)
+is the finite set of edges. The adjacency matrix
+\(A \in \{0, 1\}^{n \times n}\) of a simple undirected graph
+\(\mathcal{G}\) is a square symmetric matrix of dimension \(n \times n\)
+defined as:
+
+\begin{equation}\phantomsection\label{eq-graph-theory}{
 A_{ij} = 
 \begin{cases}
-1 & \text{if } \{i, j\} \in \mathcal{E} \\
+1 & \text{if} \{i, j\} \in \mathcal{E} \\
 0 & \text{otherwise}
 \end{cases}
-\] with \( A_{ij} = A_{ji} \), for all \( i, j \in  \mathcal{V}\) where $i\neq j$.
-For each day $t$,$t=1,\dots,T$ and each individual $p$, $p=1,\dots,P$ we the adjacency matrix of a simple undirected graph
-
-In a DPN, the
-node set
-\(\mathcal{V} = \{\mathcal{v}_1, \mathcal{v}_2, \dots, \mathcal{v}_n\}\)
-represents a finite set of \(n\) medications. Additionally,
-\(\mathcal{E}\) is a finite set of edges, where each edge is a pair of
-nodes that corresponds to a co-prescription. In an undirected graph, the
-order of \(i, j\) does not matter. Typically, undirected graphs do not
-contain self connections,
-\(\{\mathcal{v}_i, \mathcal{v}_i\} \notin \mathcal{E}\)
-\citep{estrada2012structure}.
-
-A graph can be represented as an adjacency matrix \(A\). The adjacency
-matrix \(A\) has dimensions of \(|\mathcal{V}| \times |\mathcal{V}|\),
-where \(|\mathcal{V}|\) is the number of nodes in a graph. Each element
-of \(a_{ij}\) is the edge, where in an unweighted graph, \(a_{ij} = 1\)
-if a connection exists between \(\mathcal{v}_i\) and \(\mathcal{v}_j\),
-and \(a_{ij} = 0\) otherwise. In a weighted graph, \(a_{ij}\) can take
-any real value (\(a_{ij} \in \mathbb{R}\)) depending on the application
-\citep{estrada2012structure}.
-
-\subsection{Data pre-processing}\label{data-pre-processing}
-
-Daily medication claims are represented as tabular data where each row
-corresponds to an individual patient's prescriptions. The data was
-transformed into a square matrix summarizing co-prescriptions and single
-prescriptions to construct a graph-based representation. The rows and
-columns of the matrix represent groups of medications, while each matrix
-element indicates the frequency of a specific prescription pattern.
-Elements in the off-diagonal positions represent co-prescriptions
-between two medications, while diagonal elements represent single
-prescriptions. This matrix can be interpreted as a graph, where each
-medication is a node, and the edges represent co-prescription
-frequencies. The weight of the edge is derived from the number of daily
-claims. Originally, all defined daily doses (DDD) were assumed to equal
-1, leading to straightforward edge weights based on raw counts. However,
-since not all medications have DDD values of 1, this assumption could
-lead to inaccurate representations. To address this, weights were
-adjusted using the density of a normal distribution. The expected value
-(\(\mu\)) was set to 1 to prioritize DDD = 1, and the standard deviation
-(\(\sigma\)) was set to \(\frac{1}{3}\) to allow for a gradual reduction
-in weight as DDD deviates from 1.
-
-\begin{equation}\phantomsection\label{eq-weighted-DDD}{\omega = \frac{1}{\frac{\omega_B}{3} \sqrt{2 \pi}} e^{-\frac{1}{2}\left(\frac{DDD - \omega_B}{\omega_B/3}\right)^2}}\end{equation}
-
-\colorbox{yellow}{What is $\omega_B$ in the formula? Where is $\mu$ that you mention in the text above?}
-\colorbox{yellow}{What is the index $B$ in the formula?}\\
-\colorbox{yellow}{Why $\mu$ was set to 1? That is the maximum ddd right?}
+}\end{equation}
+
+with elements \(A_{ij} = A_{ji}\), for all \(i, j \in \mathcal{V}\)
+where \(i \neq j\) \citep{estrada2012structure}.
+
+In our setting, drug co-prescriptions from a single individual \(p\) on
+a specific day \(t\) are encoded in a simple undirected graph
+\(\mathcal{G}^p(t)=\left(\mathcal{V}, \mathcal{E}^p\left(t\right)\right)\)
+with \(n \times n\) adjacency matrix \({A^p}\left(t\right)\). In these
+daily observed individual-level networks, the node set \(\mathcal{V}\)
+corresponds to a set of \(n\) medication classes according to the ATC
+classification, and the edge set \(\mathcal{E}^p\left(t\right)\)
+contains edges that indicate the concurrent use of pairs of medications
+for a particular individual \(p\) on a given day \(t\).
+
+\subsection{Data pre-processing to build the data
+matrix}\label{data-pre-processing-to-build-the-data-matrix}
+
+Assume an observational study where \(P\) individuals indexed by \(p\),
+\(p=1,\dots,P\) are followed for each day \(t\), \(t=1, \dots, T\) for a
+total period of \(T\) days. To derive the population-level DPN on each
+day \(t\) with adjacency matrix \(A_t\), the individual-level daily
+prescription matrices \(A^{p}\left(t\right)\) were aggregated by
+computing their element-wise sum, that is,
+
+\begin{equation}\phantomsection\label{eq-DPN}{
+\displaystyle \sum_{p=1}^P A^{p}\left(t\right), \ \text{where} \ A\left(t\right) \in \ \mathbb{Z}_+^{n\times n}.
+}\end{equation}
+
+The matrix \(A\left(t\right)\) captures the population frequency of
+co-prescriptions (off-diagonal) and single prescriptions (diagonal) in
+the data at
+
+the specified time \(t\). Each element \(A_{ij}\left(t\right)\) in the
+matrix was interpreted as the number of patients being prescribed
+medication classes \(i\) and \(j\), with \(i,j\in \mathcal{V}\), on the
+same day \(t\).
+
+The population-level DPN is then a weighted undirected graph
+\(\mathcal{G}\left(t\right) = \left(\mathcal{V}, \mathcal{E}\left(t\right)\right)\)
+observed over \(T\) discrete time points \(t=1,\dots,T\), where: -
+\(\mathcal{V}\) is the fixed set of \(n\) nodes, -
+\(\mathcal{E}_t \subseteq \{ \{i, j\} : i, j \in \mathcal{V}, i \neq j \}\)
+is the edge set at time \(t\).
+
+The population-level DPN at time \(t\) is fully described by its
+symmetric weighted adjacency matrix
+\(A\left(t\right) \in \mathbb{Z}_+^{n \times n}\), which is defined as:
+
+\[
+{A}_{ij}\left(t\right) =
+\begin{cases}
+w_{t,ij} > 0 & \text{if } \{i, j\} \in \mathcal{E}\left(t\right), \\
+0 & \text{otherwise},
+\end{cases}
+\quad \text{with } {A}\left(t\right) = {{A}\left(t\right)}^\top.
+\]
+
+In the original work of DPN, all defined daily dose (DDD) were assumed
+equal to 1, allowing for applying raw counts as the edge weights.
+However, since not all medications have DDD = 1, this assumption could
+lead to inaccurate representations. To enhance the accuracy of edge
+weights, we introduced a weighting function to adjust the contribution
+of each co-prescription. Specifically, each co-prescribed medication
+class was assigned a weight \(\omega_j\) based on its DDD value using a
+Gaussian kernel centered at the baseline weight \(\omega_B = 1\), i.e.,
+the expected DDD, with standard deviation \(\sigma = \frac{1}{3}\) to
+allow for a gradual reduction in weight as DDD deviates from 1.
+
+\begin{equation}\phantomsection\label{eq-weighted-DDD}{\omega_j = \frac{1}{\sigma \sqrt{2 \pi}} e^{-\frac{\left(DDD_j - 1\right)}{2\sigma^2}^2}}\end{equation}
+
+The edge weight between medication classes \(i\) and \(j\) was computed
+as the average of their individual weights:
 
@@
 
-\colorbox{yellow}{The terms $n_{i,j}$, $\omega_1$, $\omega_2$, etc are not defined somewhere.}\\
-\colorbox{yellow}{Having nonzero diagonal is not a usual network representation.}\\
-\colorbox{yellow}{What happens to your centrality measures if you set the diagonal equal to zero?}\\
-\colorbox{yellow}{I would expect a simpler network structure.}
-\begin{center}
-    \colorbox{yellow}{Proposal:}
-\end{center}
-\colorbox{yellow}{For a given day and individual there is an edge with weight equal to 1}\\
-\colorbox{yellow}{if there are nonzero ddds in the corresponding pair of drugs.}\\
+This weighting approach scaled the edge weight that deviate
+substantially from the standard \(\omega_B = 1\), improving
+comparability across medication classes. To remain consistent with
+standard network representations and avoid confounding self-loops, the
+diagonal elements were omitted.
 
@@
 identify influential medications and narrow down high-impact medications
-for drug monitoring. This study focused on eigenvector centrality to
-evaluate which medications have a significant influence on how
-antidepressants and anxiolytics are prescribed.
-Equation~\ref{eq-eigen-centrality} outlines the calculation of
-eigenvector centrality; \(c_i\) and \(c_j\) are the centralities of node
-\(\mathcal{v}_i\) and \(\mathcal{v}_j\), respectively; \(\lambda\) is
-the eigenvalue; \(a_{ji}\) is an element on row \(j\) and column \(i\)
-from an adjacency matrix \(A\), representing the connection between node
-\(\mathcal{v}_j\) and \(\mathcal{v}_i\).
+for drug monitoring. We defined high and low eigenvector centrality
+relative to the expected value \(\frac{1}{n}\), based on the null model
+of uniform connectivity (see ``Determining relative importance''). This
+study focused on eigenvector centrality to evaluate which medications
+have a significant influence on the prescription of antidepressants and
+anxiolytics. Equation~\ref{eq-eigen-centrality} outlines the calculation
+of eigenvector centrality; \(c_i\) and \(c_j\) are the centralities of
+nodes \(\mathcal{v}_i\) and \(\mathcal{v}_j\), respectively, with
+\(i, j \in \mathcal{V}\); \(\lambda\) is the eigenvalue;
+\(A_{ji}\left(t\right)\) is an element on row \(j\) and column \(i\)
+from an adjacency matrix \(A\left(t\right)\), representing the
+connection between node \(\mathcal{v}_j\) and \(\mathcal{v}_i\) with
+\(i, j \in \mathcal{V}\).
 
 \begin{equation}\phantomsection\label{eq-eigen-centrality}{
-\displaystyle c_i = \frac{1}{\lambda} \sum_{j \neq i} a_{ji} \cdot c_j
+\displaystyle c_i\left(t\right) = \frac{1}{\lambda} \sum_{j \neq i} A_{ji}\left(t\right) \cdot c_j\left(t\right)
 }\end{equation}
@@
 and monthly intervals for analysis. It includes four metrics: daily
-medication claims, daily patients, claim-to-patient ratio, and
-eigenvector centrality. For each metric, a univariate descriptive
+prescription dispensing, daily patients, dispensing-to-patient ratio,
+and eigenvector centrality. For each metric, a univariate descriptive
 analysis was performed, reporting the mean, median, standard deviation,
@@
 
-\subsubsection{Summarizing polypharmacy}\label{summarizing-polypharmacy}
-
-This study explored same-class, multi-class, and total polypharmacy. The
-summary statistics were based on prescription-day data aggregated at the
-population level over the year. Prescription-day is the number of
-medications dispensed on a given day. For example, if seven medications
-are prescribed for one day, it accounts for 7 prescription-days. The
-mean and standard deviation represent the average number of
-prescription-days per person for any polypharmacy regimen.
+\subsubsection{Summarizing
+co-prescription}\label{summarizing-co-prescription}
+
+This study explored same-class, multi-class, and total co-prescription
+categories. These three groups were selected as they can be directly
+inferred from medication dispensing data aggregated at the population
+level over the year. The statistics were summarized as prescription-day,
+defined as the number of medications dispensed on a given day. For
+example, seven medications prescribed for one day account for 7
+prescription-days. The mean and standard deviation represented the
+average number of prescription-days per person for any co-prescription
+regimen.
+
+Although five polypharmacy categories were described by
+\citet{Shrivastava2013}, augmentation and adjunctive polypharmacy
+require clinical context such as diagnoses to determine the rationale
+for combined prescriptions, which is not available in our data source.
+Therefore, focusing on the three categories that rely solely on
+medication class information is the most reasonable approach for this
+study.
 
@@
 Since the sum of all eigenvector centralities \(c_i\) in equation
-\ref{eq-eigen-centrality} is equal to one, a network with similarly
-connected nodes will have an eigenvector centrality \(c_i\) =
-\(\frac{1}{n}\) for each node, where \(n\) is the number of nodes. The
-value of \(c_i = \frac{1}{n}\) is the expected eigenvector centrality in
-a densely connected network where the occurrence of an edge
-\(\{\mathcal{v}_i, \mathcal{v}_j\} \in \mathcal{E}\) has the same
-probability for all nodes. Per the central limit theorem, the value
-\(\frac{1}{n}\) can be parameterized as a mean of a normal distribution,
-where all instances of eigenvector centrality will follow the
-distribution, \(c_i \sim \mathcal{N}(\mu, \sigma)\). A one-sample
-Student's T-test was performed to assess how much each eigenvector
-centrality differs from the expected values. As such, eigenvector
-centrality greater than \(\frac{1}{n}\) can be considered high, and the
-value below it can be considered low. The p-values was corrected for a
-type-I error using Bonferroni method.
+\ref{eq-eigen-centrality} equals 1, the expected eigenvector centrality
+for each node in a uniformly connected network is \(\frac{1}{n}\), where
+\(n\) is the total number of nodes. In such a network, each node has an
+equal probability of being connected to any other, and thus no node is
+more ``influential'' than another. This expected value value,
+\(\frac{1}{n}\), serves as a baseline under a null model of uniform
+connectivity. Assuming eigenvector centrality scores approximately
+follow a normal distribution, we applied a one-sample Student's T-test
+with Bonferroni correction to assess how much each eigenvector
+centrality differs from the expected values. Nodes with \(c_i\) greater
+than \(\frac{1}{n}\) were categorized as having high eigenvector
+centrality, and those below the expected value were considered low.
 
@@
 antidepressants or anxiolytics within five years of data extraction.
-Table~\ref{tbl-overview-patient} captures the dynamics of the population
-from 2018 to 2022. The ratio of male to female only varied slightly, and
-the average age steadily increased over the year. These findings imply
-that the population demography stays relatively stable overtime without
-any indication of sudden changes.
+Table~\ref{tbl-overview-patient} captures the demographical dynamics of
+the population from 2018 to 2022. The ratio of male to female only
+varied slightly, and the average age steadily increased over the year.
+These findings imply that the population demography stays relatively
+stable overtime without any indication of sudden changes.
 
@@
 
-\subsection{Weekly variation of medication
-dispensing}\label{weekly-variation-of-medication-dispensing}
-
-The highest average of medication dispensing occurred on Monday, with an
-average of 7,222 {[}SD: 999.79{]}. Meanwhile, the lowest average of
-medication dispensing occurred on Saturday, with an average of 2,808
-{[}SD: 174.08{]} dispensing. A large margin of difference between the
-highest and lowest average number of dispensing implies daily variation
-and cyclicality, where it peaks on Monday, starts declining afterwards,
-and is at the lowest during weekends, as shown in
-Table~\ref{tbl-overview-daily}. The cyclical patterns are detailed in
-the supplementary material section S2.1.
+\subsection{Cyclicality and seasonality of medication
+dispensing}\label{cyclicality-and-seasonality-of-medication-dispensing}
+
+Visual inspection of daily dispensing volumes revealed consistent weekly
+cycles. Dispensing peaked on Monday, with an average of 7,222 {[}SD:
+999.79{]} and dropped to its lowest on Saturday, with an average of
+2,808 {[}SD: 174.08{]} dispensing. The variation between weekends and
+weekdays showed a regular and repeating structure in the data. There was
+a large margin of difference between the highest and lowest average
+number of prescription dispensed, with a peak on Monday, followed by a
+decline throughout the week and the lowest levels occurring during
+weekends, as shown in Table~\ref{tbl-overview-daily}. The cyclical
+patterns are detailed in the supplementary material section S2.1.
+Seasonality was explored as dependencies at daily and weekly lags and
+further described in the supplementary material section S2.2 and S2.3.
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 2.66in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Number\ of\ Dispensing}}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 2.66in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Number\ of\ Prescriptions\ Dispensed}}}} \\
 
@@
 
-\subsection{Polypharmacy in the
-population}\label{polypharmacy-in-the-population}
-
-Table~\ref{tbl-res-poly} outlines the type of polypharmacy in the
-population. Two statistics are reported in Table~\ref{tbl-res-poly}: the
-sum and the mean with its standard deviation. The sum indicates the
-total prescription-days of polypharmacy within a year. Thus, we can read
-the findings as follow:
+\subsection{Co-prescription in the
+population}\label{co-prescription-in-the-population}
+
+Table~\ref{tbl-res-poly} outlines the type of co-prescription in the
+population and reports two statistics: the sum and the mean with its
+standard deviation. The sum indicates the total prescription-days of
+co-prescription within a year, and the mean with its standard deviation
+represents the average number of co-prescription days per person. For
+example, in 2018, same-class co-prescription of antidepressants occurred
+for a total of 73,528 prescription-days across the population, with an
+average of 0.06 prescription-days per person, interpreted as:
 
 \begin{quote}
-``In 2018, same-class polypharmacy of antidepressants occurred for a
-total of 73,528 prescription-days across the population, with an average
-of 0.06 prescription-days per person. For every 100 people prescribed
-with antidepressants, there were approximately 6 days in total during
-which same-class polypharmacy regimens occurred.''
+``For every 100 people treated with antidepressants, there were
+approximately 6 days in total during which same-class co-prescription
+regimens occurred.''
 \end{quote}
 
+While these average numbers per person may appear low, they are not
+intended to reflect the absolute epidemiological importance of
+co-prescriptions. Instead, prescription-days serve as a relative metric
+to compare the extent of co-prescription across categories and over
+time. For instance, Table~\ref{tbl-res-poly} shows that multi-class
+polypharmacy generally exhibits higher prescription-day values than
+same-class polypharmacy among individuals prescribed antidepressants.
+Therefore, prescription-day counts should be interpreted in the context
+of relative prescribing patterns, rather than as a direct indicator of
+epidemiological significance.
+
 \global\setlength{\Oldarrayrulewidth}{\arrayrulewidth}
@@
 \caption{\label{tbl-res-poly}Summary statistics of different psychiatric
-polypharmacy categories}
+co-prescription categories}
 
@@
 
-\multicolumn{2}{>{\raggedright}m{\dimexpr 1.1in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.42in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Population\ Level}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.42in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Per\ Person\ (Mean\ [SD])}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.42in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Total\ Polypharmacy}}}} \\
+\multicolumn{2}{>{\raggedright}m{\dimexpr 1.1in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.42in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Population\ Level}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.42in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Per\ Person\ (Mean\ [SD])}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.42in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Total\ Co-prescription}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{3}}}}} \\
 
@@
 
-\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{The\ total\ occurrence\ of\ polypharmacy\ on\ the\ population\ level/perscription-day}}}} \\
-
-\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{The\ expected\ occurrence\ of\ polypharmacy\ per\ person/perscription-day}}}} \\
-
-\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Prescription\ day\ is\ defined\ as\ the\ number\ of\ dispensed\ medication\ per\ day}}}} \\
+\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{The\ total\ occurrence\ of\ co-prescription\ on\ the\ population\ level/prescription-day.}}}} \\
+
+\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{The\ expected\ occurrence\ of\ co-prescription\ per\ person/prescription-day.}}}} \\
+
+\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{3}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{The\ overall\ number\ of\ medications\ a\ patient\ uses,\ including\ those\ prescribed\ for\ multiple\ psychiatric\ symptom\ clusters\ as\ well\ as\ for\ comorbid\ non-psychiatric\ conditions.}}}} \\
+
+\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Prescription\ day\ is\ defined\ as\ the\ number\ of\ dispensed\ medication\ per\ day.}}}} \\
+
+\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Multi-class\ co-prescription\ is\ defined\ as\ the\ co-prescription\ of\ medications\ from\ different\ ATC\ classification.}}}} \\
 
@@
 For brevity, Figure~\ref{fig-ssa} only depicts the decomposition result
-of antidepressants dispensing over the years. SSA-based decomposition
+of antidepressants dispensed over the years. SSA-based decomposition
 separates the trend from its harmonics, as shown in the lower half of
@@
 trend, F1, and F2 were used to reconstruct the time series. The largest
-graph in Figure~\ref{fig-ssa} represents the reconstructed time-series
-(green line) and its original data points (gray line). Other
-decomposition results are reported in the supplementary file section
-S2.2.
-
-\begin{figure}[H]
+panel in Figure~\ref{fig-ssa} displays the reconstructed time-series
+(green line) overlaid on the original data points (gray line).
+
+Additional decomposition results for other medication classes are
+presented in the supplementary section S2.4. Broadly antidepressants
+exhibited a steady increasing trend over time, while anxiolytics showed
+a gradual decline both in dispensing frequency and eigenvector
+centrality. Notably, the decomposition made long-term directional
+patterns more discernible across all medication classes, emphasizing the
+utility of SSA in isolating interpretable temporal dynamics from complex
+dispensing data. These decomposed trends provides the reconstructed data
+for the subsequent analysis.
+
+\begin{figure}
 
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{article_files/figure-pdf/fig-ssa-1.pdf}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{fig-ssa-1.pdf}
 
@@
 Figure~\ref{fig-hi-eigen} and Table~\ref{tbl-desc}. Notably, highly
-dispensed medications generally had high eigenvector centrality, which
-aligns with the theoretical expectations from
-Equation~\ref{eq-eigen-centrality}. However, despite a higher number of
-dispensing (6,108,776 vs 5,492,900), antidepressants had lower
-eigenvector centrality than medications for the respiratory system
-(8.94e-02 {[}SD: 1.99e-03{]} vs 8.95e-02 {[}SD: 3.39e-03{]}). A similar
-pattern was observed for anxiolytics, which had more dispensing than
-analgesics (2,644,309 vs 2,557,528) but lower eigenvector centrality
-(4.43e-02 {[}SD: 4.36e-03{]} vs 4.99e-02 {[}SD: 4.26e-03{]}).
+dispensed medications generally had high eigenvector centrality,
+consistent with the theoretical expectations from
+Equation~\ref{eq-eigen-centrality}. However, this relationship was not
+strictly proportional. For example, although antidepressants had a
+higher number of prescription dispensed compared to medications for the
+respiratory system (6,108,776 vs 5,492,900), they exhibited lower
+eigenvector centrality (9.48e-02 {[}SD: 2.24e-03{]} vs 9.53e-02 {[}SD:
+2.21e-03{]}). A similar pattern was observed for anxiolytics, which had
+more dispensing than analgesics (2,644,309 vs 2,557,528) but lower
+eigenvector centrality (5.25e-02 {[}SD: 4.13e-03{]} vs 5.84e-02 {[}SD:
+3.94e-03{]}). These discrepancies show that higher centrality scores
+capture more than just a high dispensing volume.
 
@@
 
-\begin{longtable}[c]{|p{1.57in}|p{0.74in}|p{1.16in}|p{1.16in}|p{1.16in}}
+\begin{longtable}[c]{|p{1.57in}|p{0.75in}|p{1.16in}|p{1.16in}|p{1.16in}}
 
@@
 
-\multicolumn{2}{>{\centering}m{\dimexpr 2.31in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 3.49in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ [SD]}}}} \\
+\multicolumn{2}{>{\raggedright}m{\dimexpr 2.32in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 3.49in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ [SD]}}}} \\
 
@@
 
-\multicolumn{1}{>{\centering}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Dispensing}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Centrality}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{DDD}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Weight}}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Dispensing}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Centrality}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{DDD}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Weight}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}} \\
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Alimentary\ and\ metabolism}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{11,512,424}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.07e-01\ [6.07e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.97e-01\ [3.26e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.28e-01\ [2.06e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Cardiovascular}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9,778,030}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.91e-01\ [1.01e-02]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.38e-01\ [3.05e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.92e-01\ [2.00e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Respiratory}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5,492,900}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.95e-02\ [3.39e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.55e-01\ [3.25e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.70e-01\ [2.15e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidepressants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6,108,776}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.94e-02\ [1.99e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.36e-01\ [3.09e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.92e-01\ [2.03e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Blood}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,908,944}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.27e-02\ [5.29e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.93e-01\ [3.91e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.78e-01\ [2.13e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Analgesics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,557,528}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.99e-02\ [4.26e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.23e-01\ [2.60e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.16e-01\ [1.66e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anxiolytics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,644,309}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.43e-02\ [4.36e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.63e-01\ [2.88e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.35e-01\ [1.73e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Dermatologicals}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,086,095}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.37e-02\ [1.20e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.08e-01\ [3.39e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.62e-01\ [2.09e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Musculoskeletal}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,449,535}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.26e-02\ [1.36e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.59e-01\ [3.26e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.10e-01\ [2.11e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Systemic\ hormonal}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,602,716}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.13e-02\ [1.61e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.97e-01\ [2.76e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.55e-01\ [1.66e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antipsychotics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,473,609}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.08e-02\ [3.38e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.04e-01\ [2.65e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.10e-01\ [1.69e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Genitourinary}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,099,833}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.81e-02\ [8.79e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.46e-01\ [3.69e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.29e-01\ [2.12e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Hypnotics\ and\ sedatives}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,467,752}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.71e-02\ [2.92e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.31e-01\ [3.16e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.49e-01\ [2.09e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiepileptics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,078,266}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.65e-02\ [2.42e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.29e-01\ [2.52e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.25e-01\ [1.66e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Systemic\ anti-infectives}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{734,706}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.63e-02\ [1.25e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.34e-01\ [3.23e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.64e-01\ [2.21e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antineoplastics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{449,030}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.17e-03\ [3.65e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.13e-01\ [3.01e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.49e-01\ [2.05e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Other\ nervous\ system\ drugs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{362,624}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.81e-03\ [9.30e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.23e-01\ [3.16e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.78e-01\ [1.93e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiparkinson}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{306,541}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.80e-03\ [4.93e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.53e-01\ [2.21e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.74e-01\ [1.37e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Psychostimulants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{459,207}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.16e-03\ [6.27e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.20e-01\ [3.13e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.74e-01\ [1.90e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Sensory}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{196,513}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.66e-03\ [4.64e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.66e-01\ [2.87e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.37e-01\ [1.80e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiparasitics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{88,760}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.24e-03\ [9.37e-05]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.24e-01\ [2.53e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.72e-01\ [1.65e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anesthetic}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{39,455}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.76e-04\ [1.54e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.45e-01\ [4.47e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.39e-01\ [2.31e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Others}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{18,157}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.37e-04\ [3.90e-05]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.55e-01\ [2.73e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.37e-01\ [1.77e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidementia}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.74in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9,937}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.58e-04\ [3.59e-05]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.80e-01\ [2.85e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.87e-01\ [2.02e-01]}}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Alimentary\ and\ metabolism}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{11,512,424}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.59e-01\ [5.00e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.97e-01\ [3.26e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.28e-01\ [2.06e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Cardiovascular}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9,778,030}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.50e-01\ [6.87e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.38e-01\ [3.05e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.92e-01\ [2.00e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Respiratory}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5,492,900}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9.53e-02\ [2.21e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.55e-01\ [3.25e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.70e-01\ [2.15e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidepressants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6,108,776}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9.48e-02\ [2.24e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.36e-01\ [3.09e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.92e-01\ [2.03e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Blood}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,908,944}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.87e-02\ [5.64e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.93e-01\ [3.91e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.78e-01\ [2.13e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Analgesics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,557,528}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.84e-02\ [3.94e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.23e-01\ [2.60e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.16e-01\ [1.66e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anxiolytics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,644,309}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.25e-02\ [4.13e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.63e-01\ [2.88e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.35e-01\ [1.73e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Dermatologicals}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,086,095}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.03e-02\ [1.34e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.08e-01\ [3.39e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.62e-01\ [2.09e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Musculoskeletal}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,449,535}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.95e-02\ [1.52e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.59e-01\ [3.26e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.10e-01\ [2.11e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Systemic\ hormonal}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,602,716}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.80e-02\ [1.71e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.97e-01\ [2.76e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.55e-01\ [1.66e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antipsychotics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,473,609}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.70e-02\ [3.20e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.04e-01\ [2.65e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.10e-01\ [1.69e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Genitourinary}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,099,833}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.39e-02\ [9.53e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.46e-01\ [3.69e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.29e-01\ [2.12e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Hypnotics\ and\ sedatives}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,467,752}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.37e-02\ [3.23e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.31e-01\ [3.16e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.49e-01\ [2.09e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Systemic\ anti-infectives}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{734,706}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.07e-02\ [1.47e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.34e-01\ [3.23e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.64e-01\ [2.21e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiepileptics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,078,266}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.06e-02\ [2.73e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.29e-01\ [2.52e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.25e-01\ [1.66e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antineoplastics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{449,030}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.03e-02\ [4.68e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.13e-01\ [3.01e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.49e-01\ [2.05e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Other\ nervous\ system\ drugs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{362,624}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.79e-03\ [1.08e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.23e-01\ [3.16e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.78e-01\ [1.93e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiparkinson}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{306,541}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.17e-03\ [5.64e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.53e-01\ [2.21e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.74e-01\ [1.37e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Psychostimulants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{459,207}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.56e-03\ [8.26e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.20e-01\ [3.13e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.74e-01\ [1.90e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Sensory}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{196,513}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.36e-03\ [5.91e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.66e-01\ [2.87e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.37e-01\ [1.80e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiparasitics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{88,760}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.61e-03\ [1.20e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.24e-01\ [2.53e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.72e-01\ [1.65e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anesthetic}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{39,455}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.15e-03\ [2.15e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.45e-01\ [4.47e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.39e-01\ [2.31e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Others}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{18,157}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.94e-04\ [4.86e-05]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.55e-01\ [2.73e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.37e-01\ [1.77e-01]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidementia}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9,937}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.00e-04\ [4.76e-05]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.80e-01\ [2.85e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.87e-01\ [2.02e-01]}}}} \\
 
@@
 
+\multicolumn{5}{>{\raggedright}m{\dimexpr 5.81in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Defined\ Daily\ Dose,\ representing\ the\ assumed\ average\ maintenance\ dose\ per\ day\ for\ a\ drug\ used\ for\ its\ main\ indication\ in\ adults\ (WHO\ definition).}}}} \\
+
+\multicolumn{5}{>{\raggedright}m{\dimexpr 5.81in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Edge\ weight\ assigned\ to\ each\ medication\ class\ in\ the\ drug\ prescription\ network,\ reflecting\ the\ strength\ of\ co-prescription\ connections\ (see\ Methods:\ Data\ pre-processing\ to\ build\ the\ data\ matrix).}}}} \\
+
 \end{longtable}
@@
 
-\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{article_files/figure-pdf/fig-hi-eigen-1.pdf}
+\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{fig-hi-eigen-1.pdf}
 
@@
 \caption{\label{fig-hi-eigen}Clusters of medication with a significant
-influence on how antidepressants and anxiolytics are prescribed}
+co-prescription patterns on antidepressants and anxiolytics dispensing}
 
@@
 This network analysis of dispensing data in individuals using
-antidepressants or anxiolytics revealed distinct polypharmacy patterns
-between these groups. While same-class polypharmacy was more common
-among antidepressant users, multi-class polypharmacy predominated among
+antidepressants or anxiolytics revealed distinct co-prescription
+patterns. While same-class co-prescription was more common among
+antidepressant users, multi-class co-prescription predominated among
 those receiving anxiolytics. Notably, in both groups, multi-class
-polypharmacy was at least ten times more prevalent than same-class
-polypharmacy. Seven medication classes exhibited high eigenvector
+co-prescription was at least ten times more prevalent than same-class
+co-prescription. Seven medication classes exhibited high eigenvector
 centrality, indicating their strong influence on co-prescription
@@
 Their centrality suggests that they play a role in structuring
-multi-class polypharmacy, either as standard co-prescriptions due to
-clinical guidelines or as necessary adjuncts in managing comorbidities.
-
-Our findings align with previous research showing that antidepressants
-and anxiolytics are frequently co-prescribed with other medications
-\citep{Shrivastava2013}, and that multi-class regimens contribute most
-to psychopharmaca polypharmacy \citep{de2004polypharmacy}. Furthermore,
-there have been established bidirectional associations between
-depression/anxiety and chronic illnesses \citep{qi2024longitudinal}.
-Conditions such as diabetes mellitus, thyroid disorders, and asthma have
-been linked to an increased risk of depression \citep{jang2024temporal}.
-The need for long-term pharmacological management further drives
-co-prescription patterns. Additionally, chronic illness-related anxiety
-can contribute to heightened prescribing of anxiolytics
-\citep{lebel2020health}. This underscores the interconnected nature of
-psychopharmaca prescribing patterns and highlights the complexity of
-medication management in these populations.
+multi-class co-prescription, either as standard co-prescriptions due to
+clinical guidelines or as necessary adjuncts in managing comorbidities
+or side effects, e.g., ATC \texttt{A} class. These findings align with
+the theoretical basis of eigenvector centrality, which incorporates not
+only the frequency of a node but also the influence of its connections.
+Accordingly, medications with high dispensing volume may have lower
+centrality if they are co-prescribed with less central or sparsely
+connected drug classes.
+
+The predomination of multi-class co-prescription among anxiolytics
+recipients is consistent with the recommendations in the Dutch College
+of General Practitioner (\emph{Nederlands Huisartsen Genootschap}/NHG)
+\citep{NHG2019Anxiety}. Specifically, the NHG guideline for anxiety
+disorders advises short-term benzodiazepine use, limited to two to four
+weeks, as an adjunct to Selective Serotonin Reuptake Inhibitors (SSRIs)
+during treatment initiation. In contrast, the NHG guideline for
+depressive disorders recommends initiating pharmacotherapy with a single
+SSRI and discourages the combination of multiple antidepressants
+\citep{NHG2023Depression}. Therefore, the higher rate of multi-class
+co-prescription observed among anxiolytic users is consistent with
+evidence-based clinical practice, rather than an artifact of sampling or
+measurement methods.
+
+Our findings also align with previous research showing that
+antidepressants and anxiolytics are frequently co-prescribed with other
+medications \citep{Shrivastava2013}, and that multi-class regimens
+contribute most to psychopharmaca polypharmacy
+\citep{de2004polypharmacy}. Additionally, our study offers a more
+granular view of these patterns by characterizing their network
+properties. By distinguishing between same-class and multi-class
+co-prescriptions and evaluating medication centrality, we discover that
+certain drug classes function as hubs within the prescribing landscape.
+These characteristics likely reflect the underlying burden of
+multimorbidity in the population, where the bidirectional associations
+between depression/anxiety and chronic illnesses is well established
+\citep{qi2024longitudinal}. Conditions such as diabetes mellitus,
+thyroid disorders, and asthma have been linked to an increased risk of
+depression \citep{jang2024temporal}. The need for long-term
+pharmacological management further drives co-prescription patterns.
+Additionally, chronic illness-related anxiety can contribute to
+heightened prescribing of anxiolytics \citep{lebel2020health}. This
+underscores the interconnected nature of psychopharmaca prescribing
+patterns and highlights the complexity of medication management in these
+populations.
 
@@
 the identification of central medication classes that influence
-polypharmacy patterns. The high centrality of certain medication classes
-suggests they serve as critical connectors in treatment regimens,
-providing the basis for further monitoring and evaluation.
+co-prescription patterns. The high centrality of certain medication
+classes suggests they serve as critical connectors in treatment
+regimens, providing the basis for further monitoring and evaluation.
 
@@
 certain medication classes suggests that they play a pivotal role in
-multi-class polypharmacy, likely due to their involvement in managing
+multi-class co-prescription, likely due to their involvement in managing
 both psychiatric and non-psychiatric conditions. As such, network
-analysis is a suitable approach for generating hypothesis, which has
-also been thoroughly discussed by \citet{Askar2021}.
+analysis is a suitable approach for generating hypotheses for further
+causal or predictive studies, which has also been thoroughly discussed
+by \citet{Askar2021}.
 
@@
 behaviors. These insights can reveal important trends in medication use,
-which can be useful to public health monitoring. By capturing the
-complexity of drug prescription relationships, DPN holds significant
-potential to improve decision-making in both clinical and administrative
-contexts.
+which can be useful to pharmaceutical reviews and public health
+monitoring. By capturing the complexity of drug prescription
+relationships, DPN holds significant potential to improve
+decision-making in both clinical and administrative contexts.
 
@@
 should adopt a more fine-grained ATC classification to identify specific
-medications driving polypharmacy patterns within the currently
+medications driving co-prescription patterns within the currently
 identified seven medication classes. A more granular approach could
 reveal whether certain drugs disproportionately contribute to
-multi-class polypharmacy and whether these prescribing trends vary
+multi-class co-prescription and whether these prescribing trends vary
 across patient demographics or healthcare settings. Such insights could
@@
 
-This study utilized DPN to evaluate the influence of specific medication
-classes on prescribing patterns of antidepressants and anxiolytics. By
-focusing on co-prescription patterns, we identified seven medication
-classes with significant eigenvector centrality, reflecting their
-critical role in polypharmacy regimens for individuals using anxiolytics
-and antidepressants. This study highlights the potential of
-network-based approaches to narrow down high-impact medications for
-further evaluation.
+This study demonstrates the utility of DPN in uncovering the patterns of
+co-prescriptions among antidepressants and anxiolytics recipients. We
+found that multi-class regimens were markedly more prevalent,
+particularly among anxiolytic users, consistent with clinical
+guidelines. Moreover, we identified seven highly central medication
+classes that act as hubs in the prescribing network, linking psychiatric
+medications to the management of chronic somatic conditions. These
+findings emphasize the role of multimorbidity in shaping co-prescription
+behaviors and highlight the importance of these seven classes in both
+psychiatric care and broader chronic disease management. Our study
+contributes a network-based perspective to drug utilization research,
+offering an alternative approach to identifying high-impact medication
+classes that warrant further monitoring and future investigation.
+
+\section*{Author Contributions}\label{author-contributions}
+\addcontentsline{toc}{section}{Author Contributions}
+
+\textbf{AL}: Conceptualization, Methodology, Formal analysis,
+Visualization, Writing - original draft, Project administration.
+\textbf{SB}: Methodology, Writing - review and editing. \textbf{EH}:
+Writing - review and editing. \textbf{JHB}: Data curation,
+Investigation, Project administration. \textbf{FJ}: Conceptualization,
+Supervision, Writing - original draft, Writing - review and editing.
+\textbf{TLF}: Conceptualization, Supervision, Methodology, Writing -
+original draft, Writing - review and editing.
+
+\section*{Funding}\label{funding}
+\addcontentsline{toc}{section}{Funding}
+
+This work was supported by The Indonesia Endowment Funds for Education
+(LPDP) in the form of a PhD scholarship to AL with Grant Agreement
+Number 0007457/PHA/D/2/lpdp2022 (26 July 2025).
 

### 2025-09-22 docs/supplementary.tex
Finalize submission to GEPI

@@
   pdftitle={Supplementary: A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands from 2018 to 2022},
-  pdfauthor={Aly Lamuri; Spyros Balafas; Eelko Hak; Jens H. Bos; Frederike Jörg; Talitha L. Feenstra},
   colorlinks=true,
@@
 Netherlands from 2018 to 2022}
-\author{Aly Lamuri \and Spyros Balafas \and Eelko Hak \and Jens H.
-Bos \and Frederike Jörg \and Talitha L. Feenstra}
+\author{}
 \date{}

### 2025-09-22 _targets.R

@@ -367,7 +367,7 @@ list(
   tar_quarto(report_spectral, "docs", profile = "spectral", priority = 0),
   tar_quarto(article, "docs/article.qmd"),
   tar_quarto(supplementary, "docs/supplementary.qmd"),
-  tar_quarto(cover_letter_ije, "docs/submission/IJE/cover-letter-ije.md"),
+  tar_quarto(cover_letter_ije, "docs/submission/cover-letter.md"),
   tar_quarto(readme, "README.qmd", priority = 0)
 
 )

### 2025-12-05 _targets.R
Provide a ridge plot to compre subgroup differences

@@ -63,6 +63,7 @@ list(
   tar_target(res_tbl_poly, catResPoly(res_tbl_poly_Antidepressants, res_tbl_poly_Anxiolytics, start_year = 2018)),
 
   # Describe the summary statistics
+  tar_target(dispensing_by_year, table(tbl_iadb$year)),
   tar_target(res_tbl_overview, overviewData(tbl_concat)),
   tar_target(res_tbl_stat, summarizeStat(tbl_concat)),
   tar_target(res_tbl_patient, readr::read_csv("data/processed/iadb-desc/patient.csv")),
@@ -322,6 +323,175 @@ list(
   # Generate reconstructed time series based on trend + 2 oscillating functions
   tar_target(ts_recon, genReconTs(decom_ssa, n = 2)),
   tar_target(res_recon_stat, mergeReconSummary(ts_recon, res_tbl_stat)),
+
+  # Preparation for subgroup analyses
+  tar_map(
+    values = tidyr::expand_grid(subgroup = c("is_old", "is_poly"), indicator = c(TRUE, FALSE)),
+    tar_target(sub_tbl_iadb, tbl_iadb %>% subset(.[[subgroup]] == indicator)),
+    tar_group_select(tbl_iadb_by_date, sub_tbl_iadb, by = c("month", "year", subgroup)),
+    tar_target(
+      tbl_iadb_split_date,
+      iterby(tbl_iadb_by_date, "startdat", splitAtc, "atcs"),
+      pattern   = map(tbl_iadb_by_date),
+      iteration = "vector"
+    ),
+
+    tar_target(
+      iadb_graph,
+      lapply(tbl_iadb_split_date, mkGraph),
+      pattern   = map(tbl_iadb_split_date),
+      iteration = "list",
+      priority  = 0
+    ),
+
+    # Create a time-series object based on the calculated metrics
+    tar_target(
+      iadb_metrics,
+      lapply(iadb_graph, function(branch) {
+        lapply(branch, getMetrics) %>% combineMetrics()
+      }) %>%
+        {do.call(rbind, .)}
+    ),
+
+    tar_target(
+      iadb_stats, lapply(tbl_iadb_split_date, fieldSummary) %>% combineMetrics()
+    ),
+
+    tar_target(ts_week, mergeTS(iadb_metrics, iadb_stats, covid_date = covid_date, type = "week")),
+
+    # Fit SSA models to the subgroups then reconstruct the data
+    tar_map(
+      unlist = FALSE,
[…]

### 2025-12-05 src/R/clean.R

@@ -238,3 +238,23 @@ cleanDose <- function(atc_tbl, period = NULL) {
   return(res)
 }
 
+combineSubgroup <- function(tbl_list) {
+  #' Combine Subgroup
+  #'
+  #' Combine time-series data frame obtained from subgroup analyses.
+  #'
+  #' @param tbl_list A named list containing similarly constructed data frame
+  #' @return A concatenated data frame for visualization
+
+  res <- names(tbl_list) |>
+    lapply(\(id) {
+      sub_tbl <- tbl_list[[id]] |>
+        tibble::tibble() |>
+        dplyr::select(date, group, eigen, n_claim, hi_eigen) |>
+        dplyr::mutate("sub" = id)
+      return(sub_tbl)
+    }) %>%
+    {do.call(rbind, .)}
+
+  return(res)
+}

### 2025-12-05 src/R/parse.R

@@ -23,9 +23,13 @@ readIADB <- function(filepath, ...) {
   #' @return An indexed tibble data frame
   coltype = "cDDci"
   tbl <- vroom::vroom(filepath, delim = ";", col_types = coltype, ...) %>%
-    tibble::add_column(
-      "month" = format(.$startdat, "%m"),
-      "year"  = format(.$startdat, "%y")
+    dplyr::mutate(
+      "month"    = format(startdat, "%m"),
+      "year"     = format(startdat, "%y"),
+      "duration" = stopdat - startdat,
+      "count"    = strsplit(atcs, ",") |> sapply(length),
+      "is_poly"  = (duration >= 30 & count >= 5),
+      "is_old"   = (age >= 65)
     )
   
   return(tbl)
@@ -116,7 +120,10 @@ splitAtc <- function(tbl, atcs) {
     anopat   <- entry[1]
     startdat <- entry[2]
     stopdat  <- entry[3]
-    atc      <- entry[4]
+    gender   <- entry[5]
+    atc      <- entry[6]
+    is_poly  <- entry[11]
+    is_old   <- entry[12]
 
     atc   %<>% as.character() %>% strsplit(split = ",") %>% unlist()
     label  <- gsub(x = atc, ";.*", "")
@@ -125,13 +132,16 @@ splitAtc <- function(tbl, atcs) {
       as.numeric()
 
     tbl <- tibble::tibble(
-      "label" = label,
-      "dose"  = dose,
-      "n"     = 1,
-      "N"     = N,
-      "id"    = anopat,
-      "date"  = startdat,
-      "end"   = stopdat
+      "label"   = label,
+      "dose"    = dose,
+      "n"       = 1,
+      "N"       = N,
+      "id"      = anopat,
+      "date"    = startdat,
+      "end"     = stopdat,
+      "gender"  = gender,
+      "is_poly" = is_poly,
+      "is_old"  = is_old
     ) %>%
       groupAtc() %>%
       subset(.$label != "")
@@ -210,4 +220,3 @@ catIADB <- function(fpath) {
 
   return(tbl)
 }
-

### 2025-12-05 src/R/visualize.R

@@ -404,7 +404,7 @@ vizReconSsa <- function(tidy_recon, ...) {
     scale_color_manual(
       name = "",
       values = c("Original Data" = colors$black, "Reconstructed Series" = colors$green),
-      guide = guide_legend(override.aes = aes(fill = NA))
+      guide = guide_legend(override.aes = list(fill = NA))
     ) +
     ggpubr::theme_pubclean() +
     theme(
@@ -541,9 +541,9 @@ vizEigenBox <- function(ts_clust, ...) {
     ggpubr::theme_pubclean() +
     labs(x = "", y = "") +
     scale_x_continuous(expand = c(0, 0)) +
-    scale_fill_manual(values = c("grey60", colors$green)) +
-    scale_color_manual(values = c("grey60", colors$green)) +
-    scale_alpha_manual(values = c(0.5, 0.7)) +
+    scale_fill_manual(values = c("FALSE" = "grey60", "TRUE" = colors$green)) +
+    scale_color_manual(values = c("FALSE" = "grey60", "TRUE" = colors$green)) +
+    scale_alpha_manual(values = c("FALSE" = 0.5, "TRUE" = 0.7)) +
     theme(axis.ticks = element_blank())
 
   return(plt)
@@ -593,6 +593,159 @@ vizReconResult <- function(ts, ts_recon, ...) {
   plt1 <- vizDot(ts, ...)
   plt2 <- vizDot(ts_recon, ...)
   plt  <- ggpubr::ggarrange(plt1, plt2, nrow = 1, align = "v")
+
+  return(plt)
+}
+
+addRidge <- function(tbl, alpha, add_interval = FALSE, ...) {
+  #' Visualize the Legend Box
+  #'
+  #' Generate a legend box to aid in interpreting eigenvector centrality ridge
+  #' plot.
+  #'
+  #' @param tbl A data frame object
+  #' @param alpha Transparency level
+  #' @param add_interval A boolean indicating whether to add `stat_interval`
+  #' @return A GGPlot2 layer
+  require("ggplot2")
+  require("ggdist")
+  require("ggtext")
+
+  layer <- stat_halfeye(
+    data = tbl,
+    inherit.aes = FALSE,
+    alpha = alpha,
+    normalize = "xy",
+    fill_type = "segments",
+    interval_size_range = c(0, 0),
+    aes(
+      x = eigen,
+      y = group,
+      ...
+    )
+  )
+
+  if (add_interval) {
+    layers <- list(
+      layer,
[…]

### 2025-12-10 _targets.R
Generate ridge plot to visualize high eigenvector centrality

@@ -492,6 +492,7 @@ list(
 
   # Generate a ridge plot of high eigenvector centrality in the population and subgroups
   tar_target(plt_hi_eigen_ridge, vizEigenRidge(tbl_combined)),
+  tar_target(plt_hi_eigen_ridge_plain, vizEigenRidge(tbl_combined, add_interval = FALSE)),
 
   # Plot the reconstructed time-series
   tar_map(
@@ -529,12 +530,12 @@ list(
   tar_quarto(abstract_eupha, "docs/abstract/eupha.qmd"),
   tar_quarto(abstract_ispor, "docs/abstract/ispor.qmd"),
   tar_quarto(abstract_short, "docs/abstract/short.qmd"),
-  tar_quarto(report, "docs", profile = "report", extra_files = "docs/exec-summary", priority = 0),
+  #tar_quarto(report, "docs", profile = "report", extra_files = "docs/exec-summary", priority = 0),
   tar_quarto(summary, "docs", profile = "summary", priority = 0),
   tar_quarto(report_descriptive, "docs", profile = "descriptive", priority = 0),
   tar_quarto(report_arima, "docs", profile = "arima", priority = 0),
   tar_quarto(report_seasonality, "docs", profile = "seasonality", priority = 0),
-  tar_quarto(report_spectral, "docs", profile = "spectral", priority = 0),
+  #tar_quarto(report_spectral, "docs", profile = "spectral", priority = 0),
   tar_quarto(article, "docs/article.qmd"),
   tar_quarto(supplementary, "docs/supplementary.qmd"),
   tar_quarto(cover_letter_ije, "docs/submission/cover-letter.md"),

### 2025-12-10 src/R/clean.R

@@ -258,3 +258,19 @@ combineSubgroup <- function(tbl_list) {
 
   return(res)
 }
+
+clamp <- function(x, minval = 0, maxval = 1) {
+  #' Clamp a Number
+  #'
+  #' Bound the value of a given integer (sigular) into the configured min and
+  #' maximum values.
+  #'
+  #' @param x An integer
+  #' @param minval The minimum allowed value
+  #' @param maxval The maximum allowed value
+  #' @return An integer
+
+  res <- min(max(x, minval), maxval)
+
+  return(res)
+}

### 2025-12-10 src/R/visualize.R

@@ -695,17 +695,21 @@ vizEigenRidgeLegend <- function(sub_tbl, ...) {
   return(plt)
 }
 
-vizEigenRidge <- function(tbl_combined, ...) {
+vizEigenRidge <- function(tbl_combined, add_interval = TRUE, ...) {
   #' Visualize Eigenvector Centrality Ridge Plot
   #'
   #' Generate ridge plot of eigenvector centrality for each medication group.
   #'
   #' @param tbl_combined A combined data frame from all subgroups
+  #' @param add_interval Whether to add the interval indicator below the ridge plot
   #' @return A GGPlot2 object
   require("ggplot2")
   require("ggdist")
   require("ggtext")
   require("patchwork")
+
+  # Bind eigenvector centrality range to [0, 1]
+  tbl_combined$eigen %<>% sapply(clamp)
 
   # Reorder the medication groups based on eigenvector centrality median
   tbl <- tbl_combined |>
@@ -722,14 +726,14 @@ vizEigenRidge <- function(tbl_combined, ...) {
   # Generate the plot
   plt_main <- ggplot(tbl_all, aes(x = eigen, y = group)) +
     geom_vline(xintercept = 1/24, linetype = 2, color = "grey60") +
-    addRidge(tbl_subgroup, alpha = 0.2, fill = sub) +
-    addRidge(tbl_all, alpha = 0.8, add_interval = TRUE) +
-    scale_x_continuous(expand = c(0, 0)) +
+    addRidge(tbl_subgroup, alpha = 0.4, fill = sub) +
+    addRidge(tbl_all, alpha = 0.8, add_interval = add_interval) +
+    scale_x_continuous(expand = c(0, 0), transform = "asn") +
     theme_minimal() +
     guides(fill = guide_legend(nrow = 2)) +
     labs(
       title = "The distribution of eigenvector centrality in the population",
-      subtitle = "A high overlap of the distribution indicates similarity of connectedness across the subgroup.",
+      subtitle = "A high overlap of the distribution indicates similarity of connectedness across the subgroups.",
       x = "",
       y = "",
       fill = "Subgroup Distribution: "
@@ -744,8 +748,12 @@ vizEigenRidge <- function(tbl_combined, ...) {
     )
 
   # Combine the main and legend plots
-  plt <- plt_main +
[…]

### 2025-12-10 docs/submission/GEPI/rebuttal-letter.md
Revise the manuscript to address all of the reviewers' comments

---
format: pdf
var:
  date: "10 December 2025"
  journal: "Global Epidemiology"
  editor: "Igor Burstyn, PhD"
  greeting: "Dr. Igor Burstyn"
  manuscript-id: "GEPI-D-25-00113"
in-header: >
  \usepackage{amsmath}
  \usepackage{amssymb}
---

\pagenumbering{gobble}

Aly Lamuri  
University of Groningen

{{< meta var.editor >}}  
{{< meta var.journal >}}

{{< meta var.date >}}

**Dear {{< meta var.greeting >}},**

Thank you for the opportunity to revise and resubmit our original research article entitled *"A temporal network analysis of drug co-prescription during antidepressants and anxiolytics dispensing in the Netherlands from 2018 to 2022"* (Manuscript ID: **{{< meta var.manuscript-id >}}**). We would like to express our gratitude for the reviewers for their constructive feedback, which has been invaluable in enhancing the quality of our manuscript. Below, we provide detailed responses to each comment. All revision in the manuscript are highlighted and noted by page and line numbers.

## Reviewer 1

**Comment 1:**  
The study was performed based on a pharmacy database. The authors should introduce more details about the prescription behavior of local patients. for example, the main route of obtaining drugs, hospital or pharmacy?

**Response:**  
We appreciate the reviewer’s suggestion to clarify prescription behaviors in our study context. The primary route of medication dispensing in our setting is through community pharmacies based on physician's prescription, which constitute the main data source for this study. The database does not include records of in-hospital medication dispensing or over-the-counter (OTC) medications. We have added these details to the section 2.1 (paragraph 1) to provide better context regarding the data source and patient prescription behavior.

**Changes in the manuscript:**

> All data in this study originated from the University of Groningen IADB.nl, a dynamic pharmacy database containing prescription records since 1994. The database covers approximately 128 community pharmacies serving over one million patients and was accessed on the 20^th^ of September 2023. In the Netherlands, the primary route of obtaining prescription medications is through community pharmacies, as physicians issue prescriptions that are almost exclusively dispensed in these settings. Consequently, the database provides a comprehensive longitudinal record for each individual, supported by high patient-pharmacy commitment. All patients are recorded in the database, irrespective of health care insurance, where the prescription rates, age, and gender are generalizable to represent the Netherlands. Each record includes the dispensing date, quantity, dose regimen, number of days prescribed, prescribing physician, and the corresponding Anatomical Therapeutic Chemical (ATC) code. Medication dispensed during hospitalization and over-the-counter drugs are not captured, but prescription medication records in community pharmacies are otherwise complete.

**Comment 2:**  
Was the full information of database used? Or only part? This should be specified in the methods.

**Response:**  
We thank the reviewer for this important clarification request. Only a subset of the database was used for this analysis. Specifically, we extracted anonymized patient identifiers, prescription start and end dates, and ATC codes. Other individual-level variables that is not required to build DPN were not requested to follow the internal regulation of research data management. We have now clarified this in the section 2.1 (paragraph 2) of the revised manuscript.

**Changes in the manuscript:**

> This analysis includes daily drug administration from a static cohort of adults aged 18 to 65 years and prescribed anxiolytics or antidepressants at least once in the period 2018-2022. For this study, only a subset of the database was used to construct the DPN: anonymized patient identifiers, age, prescription start and end dates, and ATC codes. No additional individual-level data were included to align with internal research data management regulations. Other demographic or clinical information available in the database was not extracted.

**Comment 3:**  
The expected $C_e$ should be provided, or no comparison can be made.

**Response:**  
We thank the reviewer for pointing out this clarification. The expected $C_e$ value was implicitly represented as $\frac{1}{n}$, where $n$ denotes the total number of medication classes. In our case, $n$ = 24, and therefore the expected $C_e$ equals $\frac{1}{24}$. We have now explicitly stated this in the section 2.5.5 to ensure clarity and facilitate comparison.

**Changes in the manuscript:**

> Since the sum of all eigenvector centralities $c_i$ in equation 5 equals 1, the expected eigenvector centrality $C_e$ for each node in a uniformly connected network is $\frac{1}{n}$, where $n$ is 24, representing the total number of nodes. In such a network, each node has an equal probability of being connected to any other, and thus no node is more "influential" than another. This expected value value, $\frac{1}{n}$, serves as a baseline under a null model of uniform connectivity. Assuming eigenvector centrality scores approximately follow a normal distribution, we applied a one-sample Student's T-test with Bonferroni correction to assess how much each eigenvector centrality differs from the expected values. Nodes with $c_i$ greater than $\frac{1}{n}$ were categorized as having high eigenvector centrality, and those below the expected value were considered low.

**Comment 4:**  
There was COVID 19 epidemic in 2020. Would this influence the dispensing volume?

**Response:**  
We appreciate the reviewer’s thoughtful question. Based on our data, the COVID-19 pandemic did not substantially affect the overall dispensing volume. The total number of prescriptions remained relatively stable across the study period: 2018 – 2,215,195; 2019 – 2,279,405; 2020 – 2,279,204; 2021 – 2,224,839; and 2022 – 2,151,496. These figures indicate no significant deviation in dispensing trends during 2020. We have added this information to the section 3.1 for completeness.

**Changes in the manuscript:**

> IADB recorded 149,071 patients with at least one dispensing of antidepressants or anxiolytics within five years of data extraction. Table 1 captures the demographical dynamics of the population from 2018 to 2022. The ratio of male to female only varied slightly, and the average age steadily increased over the year. These findings imply that the population demography stays relatively stable overtime without any indication of sudden changes. Importantly, the COVID-19 pandemic in 2020 did not substantially influence dispensing volumes because the community pharmacy remained in service, as a part of nationwide policy. There was no significant disruption in prescription trends during and after the pandemic, with an average of 2,230,028 in annual dispensing (SD: 47,478, IQR: 64,009).

**Comment 5:**  
Figure 1. more detailed caption should be provided to better read the figure.

**Response:**  
We appreciate the reviewer’s suggestion. We have revised and expanded the Figure 1 caption to provide clearer descriptions of the figure elements and to facilitate interpretation. The updated caption now reads as follows:

**Changes in the manuscript:**

> Figure 1. Singular spectrum analysis (SSA)-based decomposition of antidepressant dispensing volumes 2018-2022. The SSA separates the original time-series into the overall trend, residuals, and 25 oscillatory components (F1-F25). The green line represents the reconstructed time-series using the trend component along with the first two oscillatory functions (F1 and F2), highlighting the primary pattern in dispensing over time.

**Comment 6:**  
Figure 2. What does the vertical dash line represent?

**Response:**  
We thank the reviewer for this question. The vertical dashed line in Figure 2 represents the expected Ce value, which equals 1/24 in our analysis (corresponding to the total of 24 medication classes). We have clarified this in the figure caption in the revised manuscript.

**Changes in the manuscript:**

> Figure 2. Clusters of medications showing significant co-prescription patterns for antidepressnts and anxiolytics. The vertical dashed line indicates the expected eigenvector centrality, calculated as 1/24. This line provides a reference for identifying medication classes with eigenvector centrality exceeding the threshold.

# Reviewer 2

**Comment 1:**  
Age-stratified analysis (e.g., $< 65$ vs. $\geq 65$ years) Older adults tend to have more comorbidities and are therefore at higher risk of polypharmacy. Conducting a subgroup analysis based on age—such as $<65$ vs. $\geq 65$ years—could provide further clinical insight. Comparing DPN structures across age strata might reveal different co-prescription dynamics within high-risk populations.

Consider defining a polypharmacy subgroup prior to DPN analysis In many epidemiological and clinical studies, polypharmacy has been defined as the concurrent use of five or more medications for at least 30 days. Identifying a subgroup based on such a definition and then applying DPN analysis specifically to that cohort might help elucidate drug-drug association patterns in a clinically significant context.

**Response:**  
We thank the reviewer for these valuable suggestions regarding subgroup analyses. We agree that both age-stratified and polypharmacy-based subgroup analyses are important for understanding differential co-prescription patterns among high-risk populations. As described in Section 2.5.6 of the Methods and reported in Section 3.5 (paragraph 2 and 3), we conducted the subgroup analyses feasible within the constraints of our dataset and study design. These results have been presented in the revised manuscript for clarity.

**Changes in the manuscript:**

- Section 2.5.6:

  > Subgroup analyses were conducted by first categorizing the population into two age groups: $< 65$ and $\geq 65$ years. The second categorization was based on general polypharmacy, defined a receiving $\geq 5$ medications for at least 30 consecutive days. These subgroup classifications were combined to form three comparison pairs: $< 65$ vs. $\geq 65$ years; non-polypharmacy vs. polypharmacy; and the non-polypharmacy group aged $< 65$ years vs. the polypharmacy group aged $\geq 65$ years. A DPN was generated for each subgroup to calculate its respective eigenvector centrality.

- Section 3.5, paragraph 2 and 3:

  > The distribution of eigenvector centralities exhibited a central peak at intermediate values and heavy tails at both extremes, reflecting the temporal fluctuations of node influence. This pattern arose from the recursive nature of eigenvector centrality, where each node's importance depends on the importance of its neighbors. Aggregating centrality value over time captures the evolving dynamics of the network, where nodes occasionally attain a relatively higher or lower centrality. In contrast, the width of the distribution remained relatively stable, indicating that many co-prescription connections persisted consistently over time.
  > 
  > The eigenvector centrality patterns shown in Figure 2 also highlight the distribution of several subgroups, each distinguished by color. Most subgroup distribution largely overlapped with the general population, represented by the gray density curves. However, two subgroups consistently diverged from this overall pattern: the polypharmacy group and the subset of polypharmacy patiens aged $\geq 65$ years. These subgroups exhibited higher eigenvector centralities across four medication classes, demonstrating a more tightly connected co-prescription patterns within these groups. In addition, the $\geq 65$ years subgroup showed elevated eigenvector centralities in three medication classes, although its magnitude was smaller than that observed in the broader polypharmacy population.

**Comment 2:**  
Abbreviations used in tables and figures (e.g., SD, IQR, ACF, PACF) should be fully spelled out at first use or included in the respective footnotes.

**Response:**  
We thank the reviewer for this suggestion. All abbreviations have now been fully spelled out at first use in the main text, tables, figures, and the supplementary material to ensure clarity for readers.

**Changes in the supplementary:**

> Exploration on seasonality was done on detrended daily and weekly data by generating seasonal plots and calculating the autocorrelation (ACF) and partial autocorrelation function (PACF). Seasonal plots were generated for weekly and yearly pattern by using daily and weekly data, respectively.  To generate the seasonal plots, the data was first deconstructed based on its period. For daily data, the weekly period was used; while for monthly data, the yearly period was used. The weekly period was obtained by creating an ordered value formatted as year - week, e.g. `2018 - W01`. Similarly, monthly period was obtained by creating an ordered value formatted as year - month, e.g. `2018 - M01`. We then grouped the series by its deconstructed period and visually examine seasonality as overlapping pattern in most periods. To substantiate the findings, ACF and PACF plots were used to check on statistical significance of a given pattern.

Once again, we appreciate the feedback and have made the necessary revisions to improve our work. We hope that our revised manuscript meets your expectations.

Sincerely,  
Aly Lamuri, PhD Candidate

**On behalf of other co-authors:**  
Spyros Balafas  
Eelko Hak  
Jens H. Bos  
Frederike Jörg  
Talitha L. Feenstra

### 2025-12-10 docs/article.qmd
Track files for bidirectional synchronization with Overleaf
Update documentation to reflect the recent env and dependencies changes
Revise the manuscript to address all of the reviewers' comments

@@
 
-pkgs <- c("targets", "magrittr")
+pkgs <- c("targets", "magrittr", "ggplot2", "knitr")
 pkgs_load <- sapply(pkgs, library, character.only = TRUE)
@@
 Eigenvector centrality is helpful to identify influential medications and narrow down high-impact medications for drug monitoring.
-We defined high and low eigenvector centrality relative to the expected value $\frac{1}{n}$, based on the null model of uniform connectivity (see "Determining relative importance").
+We defined high and low eigenvector centrality relative to the expected value $C_e = \frac{1}{n}$, based on the null model of uniform connectivity (see "Determining relative importance").
 This study focused on eigenvector centrality to evaluate which medications have a significant influence on the prescription of antidepressants and anxiolytics.
@@
 The extracted trend, residuals, and oscillatory components were evaluated visually and statistically, with Mann-Kendall trend tests applied to assess long-term changes.
-A complete documentation of this approach and its rationale was included in the supplementary file section S1.1.
+A complete documentation of this approach and its rationale was included in the supplementary file section S1.2.
 
@@
 
-Since the sum of all eigenvector centralities $c_i$ in equation [-@eq-eigen-centrality] equals 1, the expected eigenvector centrality for each node in a uniformly connected network is $\frac{1}{n}$, where $n$ is the total number of nodes.
+Since the sum of all eigenvector centralities $c_i$ in equation [-@eq-eigen-centrality] equals 1, the expected eigenvector centrality $C_e$ for each node in a uniformly connected network is $\frac{1}{n}$, where $n$ is 24, representing the total number of nodes.
 In such a network, each node has an equal probability of being connected to any other, and thus no node is more "influential" than another.
-This expected value value, $\frac{1}{n}$, serves as a baseline under a null model of uniform connectivity.
+This expected value, $\frac{1}{n}$, serves as a baseline under a null model of uniform connectivity.
 Assuming eigenvector centrality scores approximately follow a normal distribution, we applied a one-sample Student's T-test with Bonferroni correction to assess how much each eigenvector centrality differs from the expected values.
 Nodes with $c_i$ greater than $\frac{1}{n}$ were categorized as having high eigenvector centrality, and those below the expected value were considered low.
+
+### Subgroup analysis
+
+Subgroup analyses were conducted by first categorizing the population into two age groups: $< 65$ and $\geq 65$ years [@Uddin2022].
+The second categorization was based on general polypharmacy, defined a receiving $\geq 5$ medications for at least 30 consecutive days [@nicholson2024prevalence].
+These subgroup classifications were combined to form three comparison pairs: $< 65$ vs.
+$\geq 65$ years; non-polypharmacy vs.
+polypharmacy; and the non-polypharmacy group aged $< 65$ years vs.
+the polypharmacy group aged $\geq 65$ years.
+A DPN was generated for each subgroup to calculate its respective eigenvector centrality.
 
@@
 
-IADB recorded `r n_patient` patients having at least one dispensing of antidepressants or anxiolytics within five years of data extraction.
+IADB recorded `r n_patient` patients with at least one dispensing of antidepressants or anxiolytics within five years of data extraction.
 @tbl-overview-patient captures the demographical dynamics of the population from 2018 to 2022.
@@
 These findings imply that the population demography stays relatively stable overtime without any indication of sudden changes.
+Importantly, the COVID-19 pandemic in 2020 did not substantially influence dispensing volumes because the community pharmacy remained in service, as a part of nationwide policy.
+There was no significant disruption in prescription trends during and after the pandemic, with an average of 2,230,028 in annual dispensing (standard deviation/SD: 47,478, interquartile range/IQR: 64,009).
 
@@
     top       = TRUE
+  ) |>
+  flextable::footnote(
+    i = 1,
+    j = 5,
+    ref_symbols = "1",
+    part = "header",
+    value = flextable::as_paragraph("SD: Standard Deviation")
   ) |>
@@
     top       = TRUE
+  ) |>
+  flextable::footnote(
+    i = 2,
+    j = c(2, 3),
+    ref_symbols = c("1", "2"),
+    part = "header",
+    value = flextable::as_paragraph(
+      c(
+        "SD: Standard Deviation",
+        "IQR: Interquartile Range"
+      )
+    )
   ) |>
@@
         "The total occurrence of co-prescription on the population level/prescription-day.",
-        "The expected occurrence of co-prescription per person/prescription-day.",
+        "SD: Standard Deviation; The expected occurrence of co-prescription per person/prescription-day.",
         "The overall number of medications a patient uses, including those prescribed for multiple psychiatric symptom clusters as well as for comorbid non-psychiatric conditions.",
@@
 #| fig-height: 12
-#| fig-cap: Time-series decomposition of antidepressants dispensing data using singular spectrum analysis-based approach
+#| fig-cap: Singular spectrum analysis (SSA)-based decomposition of antidepressant dispensing volumes 2018-2022.
+The SSA separates the original time-series into the overall trend, residuals, and 25 oscillatory components (F1-F25).
+The green line represents the reconstructed time-series using the trend component, F1, and F2, highlighting the primary pattern in the series.
 
@@
 
+The distribution of eigenvector centralities exhibited a central peak at intermediate values and heavy tails at both extremes, reflecting the temporal fluctuations of node influence.
+This pattern arose from the recursive nature of eigenvector centrality, where each node's importance depended on the importance of its neighbors.
+Aggregating centrality value over time captured the evolving dynamics of the network, where nodes occasionally attained a relatively higher or lower centrality.
+In contrast, the width of the distribution remained relatively stable, indicating that many co-prescription connections persisted consistently over time.
+
+The eigenvector centrality patterns shown in @fig-hi-eigen also highlight the distribution of several subgroups, each distinguished by color.
+Most subgroup distribution largely overlapped with the general population, represented by the gray density curves.
+However, two subgroups consistently diverged from this overall pattern: the polypharmacy group and the subset of polypharmacy patients aged $\geq 65$ years.
+These subgroups exhibited higher eigenvector centralities across four medication classes, demonstrating a more tightly connected co-prescription patterns within these groups.
+In addition, the $\geq 65$ years subgroup showed elevated eigenvector centralities in three medication classes, although its magnitude was smaller than that observed in the broader polypharmacy population.
+
 ```{r tbl-desc}
@@
   flextable::footnote(
-    i = 2,
-    j = c(4, 5),
-    ref_symbols = c("1", "2"),
+    i = c(1, 2, 2),
+    j = c(3, 4, 5),
+    ref_symbols = c("1", "2", "3"),
     part = "header",
@@
       c(
+        "SD: Standard Deviation",
         "Defined Daily Dose, representing the assumed average maintenance dose per day for a drug used for its main indication in adults (WHO definition).",
@@
 ```{r fig-hi-eigen}
-#| fig-cap: Clusters of medication with a significant co-prescription patterns on antidepressants and anxiolytics dispensing
+#| fig-cap: Clusters of medications showing significant co-prescription patterns for antidepressnts and anxiolytics.
+The vertical dashed line indicates the expected eigenvector centrality, calculated as 1/24.
+This line provides a reference for identifying medication classes with eigenvector centrality exceeding the threshold.
 #| fig-width: 9
@@
 
-tar_read(plt_hi_eigen_box)
+tar_read(plt_hi_eigen_ridge_plain)
 

### 2025-12-10 docs/exec-summary/_seasonality.qmd
Draft an initial report using Elsevier template
Revise the manuscript to address all of the reviewers' comments

--- 2024-02-12 docs/exec-summary/seasonality.qmd
@@
+::: {.content-visible unless-meta="in.article"}
 ### Exploring seasonality in the dataset
+:::
 
-Exploration on seasonality was done on detrended daily, weekly, and monthly data by generating seasonal plots and calculating the autocorrelation (ACF) and partial autocorrelation function (PACF).
-Seasonal plots were generated for weekly and yearly pattern by using daily and monthly data, respectively.
+Exploration on seasonality was done on detrended daily and weekly data by generating seasonal plots and calculating the autocorrelation (ACF) and partial autocorrelation function (PACF).
+Seasonal plots were generated for weekly and yearly pattern by using daily and weekly data, respectively.
 To generate the seasonal plots, the data was first deconstructed based on its period.
-For daily data, the weekly period was used; while for monthly data, the yearly period was used.
+For daily data, the weekly period was used; while for weekly data, the yearly period was used.
 The weekly period was obtained by creating an ordered value formatted as year - week, e.g.

### 2025-12-10 docs/exec-summary/_source-data.qmd
Revise the manuscript to address all of the reviewers' comments

@@
 
-All data in this study originated from the University of Groningen IADB.nl, a dynamic pharmacy database containing prescription data since 1994 which still grows expansively.
-The database covers approximately 128 community pharmacies serving over one million patients and was accessed on the 20^th^of September, 2023.
+All data in this study originated from the University of Groningen IADB.nl, a dynamic pharmacy database containing prescription records since 1994.
+The database covers approximately 128 community pharmacies serving over one million patients and was accessed on the 20^th^ of September 2023.
+In the Netherlands, the primary route of obtaining prescription medications is through community pharmacies, as physicians issue prescriptions that are almost exclusively dispensed in these settings.
+Consequently, the database provides a comprehensive longitudinal record for each individual, supported by high patient-pharmacy commitment.
 All patients are recorded in the database, irrespective of health care insurance, where the prescription rates, age, and gender are generalizable to represent the Netherlands [@Visser2013].
-The database offers a longitudinal record, where each individual has a uniquely anonymized tracking identifier.
-All records contain fields on the date of medication dispensing, its quantity, dose regimen, number of days prescribed, prescribing physicians, and the Anatomical Therapeutic Chemical (ATC) code.
-Except for the over the counter drugs and medication dispensed during hospitalization, all medication records for each patient are complete, mainly due to high patient-pharmacy commitment in the Netherlands.
+Each record includes the dispensing date, quantity, dose regimen, number of days prescribed, prescribing physician, and the corresponding Anatomical Therapeutic Chemical (ATC) code.
+Medication dispensed during hospitalization and over-the-counter drugs are not captured, but prescription medication records in community pharmacies are otherwise complete.
 
 This analysis includes daily drug administration from a static cohort of adults aged 18 to 65 years and prescribed anxiolytics or antidepressants at least once in the period 2018-2022.
+For this study, only a subset of the database was used to construct the DPN: anonymized patient identifiers, age, prescription start and end dates, and ATC codes.
+No additional individual-level data were included to align with internal research data management regulations.
+Other demographic or clinical information available in the database was not extracted.

### 2025-12-10 docs/submission/GEPI/rebuttal-letter.md
Resolve comments and suggestions to the rebuttal letter

@@
 Thank you for the opportunity to revise and resubmit our original research article entitled *"A temporal network analysis of drug co-prescription during antidepressants and anxiolytics dispensing in the Netherlands from 2018 to 2022"* (Manuscript ID: **{{< meta var.manuscript-id >}}**).
-We would like to express our gratitude for the reviewers for their constructive feedback, which has been invaluable in enhancing the quality of our manuscript.
-Below, we provide detailed responses to each comment.
-All revision in the manuscript are highlighted and noted by page and line numbers.
+We would like to express our gratitude for the reviewers for their constructive feedback, which has been important in enhancing the quality of our manuscript.
+Attached, please find detailed responses to each comment.
+All revisions in the manuscript are highlighted and noted by page and line numbers.
+
+Yours sincerely,  
+Aly Lamuri, PhD Candidate
+
+**On behalf of other co-authors:**  
+Spyros Balafas  
+Eelko Hak  
+Jens H. Bos  
+Frederike Jörg  
+Talitha L. Feenstra
+
+\newpage
+
+We thank both reviewers for their constructive feedback.
 
@@
 We appreciate the reviewer’s suggestion to clarify prescription behaviors in our study context.
-The primary route of medication dispensing in our setting is through community pharmacies based on physician's prescription, which constitute the main data source for this study.
+The primary route of medication dispensing in our setting is through community pharmacies based on physician's prescriptions.
+Community pharmacy dispensings constitute the main data source for this study.
 The database does not include records of in-hospital medication dispensing or over-the-counter (OTC) medications.
@@
 **Response:**  
-We thank the reviewer for this important clarification request.
+We agree this could be clarified.
 Only a subset of the database was used for this analysis.
 Specifically, we extracted anonymized patient identifiers, prescription start and end dates, and ATC codes.
-Other individual-level variables that is not required to build DPN were not requested to follow the internal regulation of research data management.
-We have now clarified this in the section 2.1 (paragraph 2) of the revised manuscript.
+Other individual-level variables that are not required to build DPN were not requested to follow the internal regulation of research data management and to satisfy data minimization requirements.
+We have now clarified this in section 2.1 (paragraph 2) of the revised manuscript.
 
@@
 For this study, only a subset of the database was used to construct the DPN: anonymized patient identifiers, age, prescription start and end dates, and ATC codes.
-No additional individual-level data were included to align with internal research data management regulations.
+No additional individual-level data were included to align with internal research data management regulations and general data minimization requirements.
 Other demographic or clinical information available in the database was not extracted.
@@
 These figures indicate no significant deviation in dispensing trends during 2020.
-We have added this information to the section 3.1 for completeness.
+We have added this information to section 3.1 for completeness and explain this is as expected, since pharmacies stayed operational during the pandemic.
 
@@
 **Response:**  
-We appreciate the reviewer’s suggestion.
+Thank you for this suggestion.
 We have revised and expanded the Figure 1 caption to provide clearer descriptions of the figure elements and to facilitate interpretation.
@@
 **Response:**  
-We thank the reviewer for this question.
-The vertical dashed line in Figure 2 represents the expected Ce value, which equals 1/24 in our analysis (corresponding to the total of 24 medication classes).
+Indeed this has to be clarified.
+The vertical dashed line in Figure 2 represents the expected $C_e$ value, which equals $\frac{1}{24}$ in our analysis (corresponding to the total of 24 medication classes).
 We have clarified this in the figure caption in the revised manuscript.
@@
 We agree that both age-stratified and polypharmacy-based subgroup analyses are important for understanding differential co-prescription patterns among high-risk populations.
-As described in Section 2.5.6 of the Methods and reported in Section 3.5 (paragraph 2 and 3), we conducted the subgroup analyses feasible within the constraints of our dataset and study design.
-These results have been presented in the revised manuscript for clarity.
+As described in Section 2.5.6 of the Methods and reported in Section 3.5 (paragraph 2 and 3), we conducted the additional  subgroup analyses that were feasible within the constraints of our dataset and study design.
+These results have been added to the  revised manuscript and inform on age and polypharmacy specific results.
 
@@
 **Response:**  
-We thank the reviewer for this suggestion.
 All abbreviations have now been fully spelled out at first use in the main text, tables, figures, and the supplementary material to ensure clarity for readers.
@@
 Once again, we appreciate the feedback and have made the necessary revisions to improve our work. We hope that our revised manuscript meets your expectations.
-
-Sincerely,  
-Aly Lamuri, PhD Candidate
-
-**On behalf of other co-authors:**  
-Spyros Balafas  
-Eelko Hak  
-Jens H. Bos  
-Frederike Jörg  
-Talitha L. Feenstra

### 2025-12-10 docs/submission/GEPI/rebuttal-letter.md
Incorporate suggestions by Prof. Frederike and Prof. Talitha

@@
   journal: "Global Epidemiology"
-  editor: "Igor Burstyn, PhD"
-  greeting: "Dr. Igor Burstyn"
+  editor: "Assoc. Prof. Igor Burstyn, PhD"
+  greeting: "Professor Igor Burstyn"
   manuscript-id: "GEPI-D-25-00113"
@@
 Yours sincerely,
+
+\vspace{3em}
+
 Aly Lamuri, PhD Candidate
@@
 
-\newpage
+\pagebreak
 
@@
 Specifically, we extracted anonymized patient identifiers, prescription start and end dates, and ATC codes.
-Other individual-level variables that are not required to build DPN were not requested to follow the internal regulation of research data management and to satisfy data minimization requirements.
+Other individual-level variables that are not required to build DPN were not requested to satisfy data minimization requirements.
 We have now clarified this in section 2.1 (paragraph 2) of the revised manuscript.
@@
 For this study, only a subset of the database was used to construct the DPN: anonymized patient identifiers, age, prescription start and end dates, and ATC codes.
-No additional individual-level data were included to align with internal research data management regulations and general data minimization requirements.
+No additional individual-level data were included to align general data minimization requirements.
 Other demographic or clinical information available in the database was not extracted.
@@
 **Response:**  
-We thank the reviewer for pointing out this clarification.
+We thank the reviewer for requesting this clarification.
 The expected $C_e$ value was implicitly represented as $\frac{1}{n}$, where $n$ denotes the total number of medication classes.
@@
 In such a network, each node has an equal probability of being connected to any other, and thus no node is more "influential" than another.
-This expected value value, $\frac{1}{n}$, serves as a baseline under a null model of uniform connectivity.
+This expected value, $\frac{1}{24}$, serves as a baseline under a null model of uniform connectivity.
 Assuming eigenvector centrality scores approximately follow a normal distribution, we applied a one-sample Student's T-test with Bonferroni correction to assess how much each eigenvector centrality differs from the expected values.
-Nodes with $c_i$ greater than $\frac{1}{n}$ were categorized as having high eigenvector centrality, and those below the expected value were considered low.
+Nodes with $c_i$ greater than $\frac{1}{24}$ were categorized as having high eigenvector centrality, and those below the expected value were considered low.
 
@@
 Based on our data, the COVID-19 pandemic did not substantially affect the overall dispensing volume.
-The total number of prescriptions remained relatively stable across the study period: 2018 – 2,215,195; 2019 – 2,279,405; 2020 – 2,279,204; 2021 – 2,224,839; and 2022 – 2,151,496.
-These figures indicate no significant deviation in dispensing trends during 2020.
+The total number of prescriptions for all medication classes remained relatively stable across the study period: 2018 – 2,215,195; 2019 – 2,279,405; 2020 – 2,279,204; 2021 – 2,224,839; and 2022 – 2,151,496.
+These figures indicate no significant deviation in dispensing trends for all medications during 2020.
 We have added this information to section 3.1 for completeness and explain this is as expected, since pharmacies stayed operational during the pandemic.
@@
 These findings imply that the population demography stays relatively stable overtime without any indication of sudden changes.
-Importantly, the COVID-19 pandemic in 2020 did not substantially influence dispensing volumes because the community pharmacy remained in service, as a part of nationwide policy.
-There was no significant disruption in prescription trends during and after the pandemic, with an average of 2,230,028 in annual dispensing (SD: 47,478, IQR: 64,009).
+Importantly, the COVID-19 pandemic in 2020 did not substantially influence dispensing volumes because the community pharmacy remained in service as a part of nationwide policy.
+There was no significant disruption in prescription trends during and after the pandemic, with an average of 2,230,028 in annual dispensing for all medication classes (SD: 47,478, IQR: 64,009).
 
@@
 To substantiate the findings, ACF and PACF plots were used to check on statistical significance of a given pattern.
-
-Once again, we appreciate the feedback and have made the necessary revisions to improve our work. We hope that our revised manuscript meets your expectations.

### 2025-12-10 docs/article.qmd
Incorporate suggestions by Prof. Frederike and Prof. Talitha

@@
 In such a network, each node has an equal probability of being connected to any other, and thus no node is more "influential" than another.
-This expected value, $\frac{1}{n}$, serves as a baseline under a null model of uniform connectivity.
+This expected value, $\frac{1}{24}$, serves as a baseline under a null model of uniform connectivity.
 Assuming eigenvector centrality scores approximately follow a normal distribution, we applied a one-sample Student's T-test with Bonferroni correction to assess how much each eigenvector centrality differs from the expected values.
-Nodes with $c_i$ greater than $\frac{1}{n}$ were categorized as having high eigenvector centrality, and those below the expected value were considered low.
+Nodes with $c_i$ greater than $\frac{1}{24}$ were categorized as having high eigenvector centrality, and those below the expected value were considered low.
 
@@
 These findings imply that the population demography stays relatively stable overtime without any indication of sudden changes.
-Importantly, the COVID-19 pandemic in 2020 did not substantially influence dispensing volumes because the community pharmacy remained in service, as a part of nationwide policy.
-There was no significant disruption in prescription trends during and after the pandemic, with an average of 2,230,028 in annual dispensing (standard deviation/SD: 47,478, interquartile range/IQR: 64,009).
+Importantly, the COVID-19 pandemic in 2020 did not substantially influence dispensing volumes because the community pharmacy remained in service as a part of nationwide policy.
+There was no significant disruption in prescription trends during and after the pandemic, with an average of 2,230,028 in annual dispensing for all medication classes (standard deviation/SD: 47,478, interquartile range/IQR: 64,009).
 
@@
 #| fig-cap: Singular spectrum analysis (SSA)-based decomposition of antidepressant dispensing volumes 2018-2022.
-The SSA separates the original time-series into the overall trend, residuals, and 25 oscillatory components (F1-F25).
+The SSA separated the original time-series into the overall trend, residuals, and 25 oscillatory components (F1-F25).
 The green line represents the reconstructed time-series using the trend component, F1, and F2, highlighting the primary pattern in the series.

### 2025-12-15 docs/submission/GEPI/rebuttal-letter.md
Track the revision and its diff

@@
 
+Numerical expressions such as "9.48e-02" are more commonly formatted as "9.48e-2" in standard scientific notation; adopting a consistent style may improve readability.
+
 **Response:**  
 All abbreviations have now been fully spelled out at first use in the main text, tables, figures, and the supplementary material to ensure clarity for readers.
+Moreover, we also revised the supplementary to include the definition of ACF and PACF, also the rationale for using these approaches.
+All scientific notations have been standardized and formatted as "9.48e-2."
 

### 2025-12-15 docs/submission/GEPI/manuscript-revision-01/article.tex
Track the revision and its diff

--- 2025-09-22 docs/submission/GEPI/manuscript/article.tex
@@
+% Options for packages loaded elsewhere
 % Options for packages loaded elsewhere
@@
   review]{elsarticle}
-
+\usepackage{xcolor}
 \usepackage{amsmath,amssymb}
+\setcounter{secnumdepth}{5}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
@@
 \makeatother
-\usepackage{xcolor}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{5}
 % Make \paragraph and \subparagraph free-standing
@@
 
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{longtable,booktabs,array}
 \usepackage{calc} % for calculating minipage widths
@@
 \makeatother
+
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\usepackage[]{natbib}
+\bibliographystyle{elsarticle-num-names}
 
@@
 \journal{Global Epidemiology}
-
-\usepackage[]{natbib}
-\bibliographystyle{elsarticle-num-names}
 \usepackage{bookmark}
-
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
   pdftitle={A temporal network analysis of drug co-prescription during antidepressants and anxiolytics dispensing in the Netherlands from 2018 to 2022},
+  pdfauthor={Aly Lamuri; Spyros Balafas; Eelko Hak; Jens H. Bos; Frederike Jörg; Talitha L. Feenstra},
   pdfkeywords={Graph Theory, Prescription
@@
 All data in this study originated from the University of Groningen
-IADB.nl, a dynamic pharmacy database containing prescription data since
-1994 which still grows expansively. The database covers approximately
-128 community pharmacies serving over one million patients and was
-accessed on the 20\textsuperscript{th}of September, 2023. All patients
-are recorded in the database, irrespective of health care insurance,
-where the prescription rates, age, and gender are generalizable to
-represent the Netherlands \citep{Visser2013}. The database offers a
-longitudinal record, where each individual has a uniquely anonymized
-tracking identifier. All records contain fields on the date of
-medication dispensing, its quantity, dose regimen, number of days
-prescribed, prescribing physicians, and the Anatomical Therapeutic
-Chemical (ATC) code. Except for the over the counter drugs and
-medication dispensed during hospitalization, all medication records for
-each patient are complete, mainly due to high patient-pharmacy
-commitment in the Netherlands.
+IADB.nl, a dynamic pharmacy database containing prescription records
+since 1994. The database covers approximately 128 community pharmacies
+serving over one million patients and was accessed on the
+20\textsuperscript{th} of September 2023. In the Netherlands, the
+primary route of obtaining prescription medications is through community
+pharmacies, as physicians issue prescriptions that are almost
+exclusively dispensed in these settings. Consequently, the database
+provides a comprehensive longitudinal record for each individual,
+supported by high patient-pharmacy commitment. All patients are recorded
+in the database, irrespective of health care insurance, where the
+prescription rates, age, and gender are generalizable to represent the
+Netherlands \citep{Visser2013}. Each record includes the dispensing
+date, quantity, dose regimen, number of days prescribed, prescribing
+physician, and the corresponding Anatomical Therapeutic Chemical (ATC)
+code. Medication dispensed during hospitalization and over-the-counter
+drugs are not captured, but prescription medication records in community
+pharmacies are otherwise complete.
 
@@
 adults aged 18 to 65 years and prescribed anxiolytics or antidepressants
-at least once in the period 2018-2022.
+at least once in the period 2018-2022. For this study, only a subset of
+the database was used to construct the DPN: anonymized patient
+identifiers, age, prescription start and end dates, and ATC codes. No
+additional individual-level data were included to align with general
+data minimization requirements. Other demographic or clinical
+information available in the database was not extracted.
 
@@
 for drug monitoring. We defined high and low eigenvector centrality
-relative to the expected value \(\frac{1}{n}\), based on the null model
-of uniform connectivity (see ``Determining relative importance''). This
-study focused on eigenvector centrality to evaluate which medications
-have a significant influence on the prescription of antidepressants and
-anxiolytics. Equation~\ref{eq-eigen-centrality} outlines the calculation
-of eigenvector centrality; \(c_i\) and \(c_j\) are the centralities of
-nodes \(\mathcal{v}_i\) and \(\mathcal{v}_j\), respectively, with
-\(i, j \in \mathcal{V}\); \(\lambda\) is the eigenvalue;
-\(A_{ji}\left(t\right)\) is an element on row \(j\) and column \(i\)
-from an adjacency matrix \(A\left(t\right)\), representing the
-connection between node \(\mathcal{v}_j\) and \(\mathcal{v}_i\) with
+relative to the expected value \(C_e = \frac{1}{n}\), based on the null
+model of uniform connectivity (see ``Determining relative importance'').
+This study focused on eigenvector centrality to evaluate which
+medications have a significant influence on the prescription of
+antidepressants and anxiolytics. Equation~\ref{eq-eigen-centrality}
+outlines the calculation of eigenvector centrality; \(c_i\) and \(c_j\)
+are the centralities of nodes \(\mathcal{v}_i\) and \(\mathcal{v}_j\),
+respectively, with \(i, j \in \mathcal{V}\); \(\lambda\) is the
+eigenvalue; \(A_{ji}\left(t\right)\) is an element on row \(j\) and
+column \(i\) from an adjacency matrix \(A\left(t\right)\), representing
+the connection between node \(\mathcal{v}_j\) and \(\mathcal{v}_i\) with
 \(i, j \in \mathcal{V}\).
@@
 
-Exploration on seasonality was done on detrended daily, weekly, and
-monthly data by generating seasonal plots and calculating the
-autocorrelation (ACF) and partial autocorrelation function (PACF).
-Seasonal plots were generated for weekly and yearly pattern by using
-daily and monthly data, respectively. To generate the seasonal plots,
-the data was first deconstructed based on its period. For daily data,
-the weekly period was used; while for monthly data, the yearly period
-was used. The weekly period was obtained by creating an ordered value
-formatted as year - week, e.g.~\texttt{2018\ -\ W01}. Similarly, monthly
+Exploration on seasonality was done on detrended daily and weekly data
+by generating seasonal plots and calculating the autocorrelation (ACF)
+and partial autocorrelation function (PACF). Seasonal plots were
+generated for weekly and yearly pattern by using daily and weekly data,
+respectively. To generate the seasonal plots, the data was first
+deconstructed based on its period. For daily data, the weekly period was
+used; while for weekly data, the yearly period was used. The weekly
 period was obtained by creating an ordered value formatted as year -
-month, e.g.~\texttt{2018\ -\ M01}. We then grouped the series by its
+week, e.g.~\texttt{2018\ -\ W01}. Similarly, monthly period was obtained
+by creating an ordered value formatted as year - month,
+e.g.~\texttt{2018\ -\ M01}. We then grouped the series by its
 deconstructed period and visually examine seasonality as overlapping
@@
 documentation of this approach and its rationale was included in the
-supplementary file section S1.1.
+supplementary file section S1.2.
 
@@
 \ref{eq-eigen-centrality} equals 1, the expected eigenvector centrality
-for each node in a uniformly connected network is \(\frac{1}{n}\), where
-\(n\) is the total number of nodes. In such a network, each node has an
-equal probability of being connected to any other, and thus no node is
-more ``influential'' than another. This expected value value,
-\(\frac{1}{n}\), serves as a baseline under a null model of uniform
-connectivity. Assuming eigenvector centrality scores approximately
-follow a normal distribution, we applied a one-sample Student's T-test
-with Bonferroni correction to assess how much each eigenvector
-centrality differs from the expected values. Nodes with \(c_i\) greater
-than \(\frac{1}{n}\) were categorized as having high eigenvector
-centrality, and those below the expected value were considered low.
+\(C_e\) for each node in a uniformly connected network is
+\(\frac{1}{n}\), where \(n\) is 24, representing the total number of
+nodes. In such a network, each node has an equal probability of being
+connected to any other, and thus no node is more ``influential'' than
+another. This expected value, \(\frac{1}{24}\), serves as a baseline
+under a null model of uniform connectivity. Assuming eigenvector
+centrality scores approximately follow a normal distribution, we applied
+a one-sample Student's T-test with Bonferroni correction to assess how
+much each eigenvector centrality differs from the expected values. Nodes
+with \(c_i\) greater than \(\frac{1}{24}\) were categorized as having
+high eigenvector centrality, and those below the expected value were
+considered low.
+
+\subsubsection{Subgroup analysis}\label{subgroup-analysis}
+
+Subgroup analyses were conducted by first categorizing the population
+into two age groups: \(< 65\) and \(\geq 65\) years \citep{Uddin2022}.
+The second categorization was based on general polypharmacy, defined a
+receiving \(\geq 5\) medications for at least 30 consecutive days
+\citep{nicholson2024prevalence}. These subgroup classifications were
+combined to form three comparison pairs: \(< 65\) vs.~\(\geq 65\) years;
+non-polypharmacy vs.~polypharmacy; and the non-polypharmacy group aged
+\(< 65\) years vs.~the polypharmacy group aged \(\geq 65\) years. A DPN
+was generated for each subgroup to calculate its respective eigenvector
+centrality.
 
@@
 
-IADB recorded 149,071 patients having at least one dispensing of
+IADB recorded 149,071 patients with at least one dispensing of
 antidepressants or anxiolytics within five years of data extraction.
@@
 These findings imply that the population demography stays relatively
-stable overtime without any indication of sudden changes.
+stable overtime without any indication of sudden changes. Importantly,
+the COVID-19 pandemic in 2020 did not substantially influence dispensing
+volumes because the community pharmacy remained in service as a part of
+nationwide policy. There was no significant disruption in prescription
+trends during and after the pandemic, with an average of 2,230,028 in
+annual dispensing for all medication classes (standard deviation/SD:
+47,478, interquartile range/IQR: 64,009).
 
@@
 
-\begin{longtable}[c]{|p{0.43in}|p{0.94in}|p{0.94in}|p{0.59in}|p{0.85in}|p{0.85in}}
+\begin{longtable}[c]{|p{0.75in}|p{0.94in}|p{0.94in}|p{0.75in}|p{0.85in}|p{0.85in}}
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 2.47in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Number\ of\ Patients\ (\%)}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.7in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ Age\ (SD)}}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 2.63in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Number\ of\ Patients\ (\%)}}}} & \multicolumn{2}{>{\centering}m{\dimexpr 1.7in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ Age\ (SD)}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}} \\
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Year}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Male}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Female}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Total}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Male}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Female}}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Year}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Male}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Female}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Total}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Male}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Female}}}} \\
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2018}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,164\ (36.6\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{73,124\ (63.4\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{115,288}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.72\ (12.33)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.02\ (12.80)}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2019}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,427\ (36.7\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{73,109\ (63.3\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{115,536}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{49.26\ (12.62)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.54\ (13.02)}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2020}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,010\ (36.6\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{72,700\ (63.4\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{114,710}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{49.77\ (12.79)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{49.15\ (13.16)}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2021}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,016\ (36.7\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{72,532\ (63.3\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{114,548}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{50.15\ (13.04)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{49.55\ (13.42)}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.43in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2022}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{39,464\ (36.7\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{67,930\ (63.3\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.59in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{107,394}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{50.82\ (13.12)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{50.38\ (13.50)}}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2018}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,164\ (36.6\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{73,124\ (63.4\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{115,288}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.72\ (12.33)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.02\ (12.80)}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2019}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,427\ (36.7\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{73,109\ (63.3\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{115,536}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{49.26\ (12.62)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{48.54\ (13.02)}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2020}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,010\ (36.6\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{72,700\ (63.4\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{114,710}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{49.77\ (12.79)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{49.15\ (13.16)}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2021}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{42,016\ (36.7\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{72,532\ (63.3\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{114,548}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{50.15\ (13.04)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{49.55\ (13.42)}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2022}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{39,464\ (36.7\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.94in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{67,930\ (63.3\%)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{107,394}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{50.82\ (13.12)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.85in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{50.38\ (13.50)}}}} \\
 
 \ascline{1.5pt}{666666}{1-6}
+
+\multicolumn{6}{>{\raggedright}m{\dimexpr 5.08in+10\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{SD:\ Standard\ Deviation}}}} \\
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Day}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ (SD)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Median\ (IQR)}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.84in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Range}}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Day}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ (SD)}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.91in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Median\ (IQR)}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.84in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Range}}}} \\
 
@@
 \ascline{1.5pt}{666666}{1-4}
+
+\multicolumn{4}{>{\raggedright}m{\dimexpr 3.41in+6\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{SD:\ Standard\ Deviation}}}} \\
+
+\multicolumn{4}{>{\raggedright}m{\dimexpr 3.41in+6\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{IQR:\ Interquartile\ Range}}}} \\
 
@@
 
-\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{The\ expected\ occurrence\ of\ co-prescription\ per\ person/prescription-day.}}}} \\
+\multicolumn{8}{>{\raggedright}m{\dimexpr 5.35in+14\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{SD:\ Standard\ Deviation;\ The\ expected\ occurrence\ of\ co-prescription\ per\ person/prescription-day.}}}} \\
 
@@
 
-\caption{\label{fig-ssa}Time-series decomposition of antidepressants
-dispensing data using singular spectrum analysis-based approach}
+\caption{\label{fig-ssa}Singular spectrum analysis (SSA)-based
+decomposition of antidepressant dispensing volumes 2018-2022. The SSA
+separated the original time-series into the overall trend, residuals,
+and 25 oscillatory components (F1-F25). The green line represents the
+reconstructed time-series using the trend component, F1, and F2,
+highlighting the primary pattern in the series.}
 
@@
 respiratory system (6,108,776 vs 5,492,900), they exhibited lower
-eigenvector centrality (9.48e-02 {[}SD: 2.24e-03{]} vs 9.53e-02 {[}SD:
-2.21e-03{]}). A similar pattern was observed for anxiolytics, which had
+eigenvector centrality (9.48e-2 {[}SD: 2.24e-3{]} vs 9.53e-2 {[}SD:
+2.21e-3{]}). A similar pattern was observed for anxiolytics, which had
 more dispensing than analgesics (2,644,309 vs 2,557,528) but lower
-eigenvector centrality (5.25e-02 {[}SD: 4.13e-03{]} vs 5.84e-02 {[}SD:
-3.94e-03{]}). These discrepancies show that higher centrality scores
+eigenvector centrality (5.25e-2 {[}SD: 4.13e-3{]} vs 5.84e-2 {[}SD:
+3.94e-3{]}). These discrepancies show that higher centrality scores
 capture more than just a high dispensing volume.
+
+The distribution of eigenvector centralities exhibited a central peak at
+intermediate values and heavy tails at both extremes, reflecting the
+temporal fluctuations of node influence. This pattern arose from the
+recursive nature of eigenvector centrality, where each node's importance
+depended on the importance of its neighbors. Aggregating centrality
+value over time captured the evolving dynamics of the network, where
+nodes occasionally attained a relatively higher or lower centrality. In
+contrast, the width of the distribution remained relatively stable,
+indicating that many co-prescription connections persisted consistently
+over time.
+
+The eigenvector centrality patterns shown in Figure~\ref{fig-hi-eigen}
+also highlight the distribution of several subgroups, each distinguished
+by color. Most subgroup distribution largely overlapped with the general
+population, represented by the gray density curves. However, two
+subgroups consistently diverged from this overall pattern: the
+polypharmacy group and the subset of polypharmacy patients aged
+\(\geq 65\) years. These subgroups exhibited higher eigenvector
+centralities across four medication classes, demonstrating a more
+tightly connected co-prescription patterns within these groups. In
+addition, the \(\geq 65\) years subgroup showed elevated eigenvector
+centralities in three medication classes, although its magnitude was
+smaller than that observed in the broader polypharmacy population.
 
@@
 
-\multicolumn{2}{>{\raggedright}m{\dimexpr 2.32in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 3.49in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ [SD]}}}} \\
+\multicolumn{2}{>{\raggedright}m{\dimexpr 2.32in+2\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{3}{>{\centering}m{\dimexpr 3.49in+4\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Mean\ [SD]}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}} \\
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Dispensing}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Centrality}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{DDD}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Weight}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Dispensing}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Centrality}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{DDD}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Weight}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{3}}}}} \\
 
@@
 
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Alimentary\ and\ metabolism}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{11,512,424}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.59e-01\ [5.00e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.97e-01\ [3.26e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.28e-01\ [2.06e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Cardiovascular}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9,778,030}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.50e-01\ [6.87e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.38e-01\ [3.05e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.92e-01\ [2.00e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Respiratory}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5,492,900}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9.53e-02\ [2.21e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.55e-01\ [3.25e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.70e-01\ [2.15e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidepressants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6,108,776}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9.48e-02\ [2.24e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.36e-01\ [3.09e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.92e-01\ [2.03e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Blood}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,908,944}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.87e-02\ [5.64e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.93e-01\ [3.91e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.78e-01\ [2.13e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Analgesics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,557,528}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.84e-02\ [3.94e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.23e-01\ [2.60e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.16e-01\ [1.66e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anxiolytics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,644,309}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.25e-02\ [4.13e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.63e-01\ [2.88e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.35e-01\ [1.73e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Dermatologicals}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,086,095}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.03e-02\ [1.34e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.08e-01\ [3.39e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.62e-01\ [2.09e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Musculoskeletal}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,449,535}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.95e-02\ [1.52e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.59e-01\ [3.26e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.10e-01\ [2.11e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Systemic\ hormonal}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,602,716}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.80e-02\ [1.71e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.97e-01\ [2.76e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.55e-01\ [1.66e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antipsychotics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,473,609}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.70e-02\ [3.20e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.04e-01\ [2.65e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.10e-01\ [1.69e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Genitourinary}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,099,833}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.39e-02\ [9.53e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.46e-01\ [3.69e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.29e-01\ [2.12e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Hypnotics\ and\ sedatives}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,467,752}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.37e-02\ [3.23e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.31e-01\ [3.16e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.49e-01\ [2.09e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Systemic\ anti-infectives}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{734,706}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.07e-02\ [1.47e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.34e-01\ [3.23e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.64e-01\ [2.21e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiepileptics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,078,266}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.06e-02\ [2.73e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.29e-01\ [2.52e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.25e-01\ [1.66e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antineoplastics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{449,030}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.03e-02\ [4.68e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.13e-01\ [3.01e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.49e-01\ [2.05e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Other\ nervous\ system\ drugs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{362,624}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.79e-03\ [1.08e-03]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.23e-01\ [3.16e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.78e-01\ [1.93e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiparkinson}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{306,541}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.17e-03\ [5.64e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.53e-01\ [2.21e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.74e-01\ [1.37e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Psychostimulants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{459,207}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.56e-03\ [8.26e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.20e-01\ [3.13e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.74e-01\ [1.90e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Sensory}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{196,513}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.36e-03\ [5.91e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.66e-01\ [2.87e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.37e-01\ [1.80e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiparasitics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{88,760}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.61e-03\ [1.20e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.24e-01\ [2.53e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.72e-01\ [1.65e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anesthetic}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{39,455}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.15e-03\ [2.15e-04]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.45e-01\ [4.47e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.39e-01\ [2.31e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Others}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{18,157}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.94e-04\ [4.86e-05]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.55e-01\ [2.73e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.37e-01\ [1.77e-01]}}}} \\
-
-\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidementia}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9,937}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.00e-04\ [4.76e-05]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.80e-01\ [2.85e-01]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.87e-01\ [2.02e-01]}}}} \\
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Alimentary\ and\ metabolism}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{11,512,424}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.59e-1\ [5.00e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.97e-1\ [3.26e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.28e-1\ [2.06e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Cardiovascular}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9,778,030}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.50e-1\ [6.87e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.38e-1\ [3.05e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.92e-1\ [2.00e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Respiratory}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5,492,900}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9.53e-2\ [2.21e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.55e-1\ [3.25e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.70e-1\ [2.15e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidepressants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6,108,776}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9.48e-2\ [2.24e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.36e-1\ [3.09e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.92e-1\ [2.03e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Blood}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,908,944}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.87e-2\ [5.64e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.93e-1\ [3.91e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.78e-1\ [2.13e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Analgesics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,557,528}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.84e-2\ [3.94e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.23e-1\ [2.60e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.16e-1\ [1.66e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anxiolytics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,644,309}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.25e-2\ [4.13e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.63e-1\ [2.88e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.35e-1\ [1.73e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Dermatologicals}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,086,095}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.03e-2\ [1.34e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.08e-1\ [3.39e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.62e-1\ [2.09e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Musculoskeletal}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,449,535}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.95e-2\ [1.52e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.59e-1\ [3.26e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.10e-1\ [2.11e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Systemic\ hormonal}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,602,716}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.80e-2\ [1.71e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.97e-1\ [2.76e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.55e-1\ [1.66e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antipsychotics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,473,609}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.70e-2\ [3.20e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.04e-1\ [2.65e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.10e-1\ [1.69e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Genitourinary}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2,099,833}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.39e-2\ [9.53e-4]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.46e-1\ [3.69e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.29e-1\ [2.12e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Hypnotics\ and\ sedatives}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,467,752}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.37e-2\ [3.23e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.31e-1\ [3.16e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.49e-1\ [2.09e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Systemic\ anti-infectives}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{734,706}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.07e-2\ [1.47e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.34e-1\ [3.23e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.64e-1\ [2.21e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiepileptics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1,078,266}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.06e-2\ [2.73e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.29e-1\ [2.52e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.25e-1\ [1.66e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antineoplastics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{449,030}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.03e-2\ [4.68e-4]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.13e-1\ [3.01e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.49e-1\ [2.05e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Other\ nervous\ system\ drugs}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{362,624}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{8.79e-3\ [1.08e-3]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.23e-1\ [3.16e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.78e-1\ [1.93e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiparkinson}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{306,541}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.17e-3\ [5.64e-4]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.53e-1\ [2.21e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.74e-1\ [1.37e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Psychostimulants}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{459,207}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.56e-3\ [8.26e-4]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.20e-1\ [3.13e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.74e-1\ [1.90e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Sensory}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{196,513}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{3.36e-3\ [5.91e-4]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.66e-1\ [2.87e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.37e-1\ [1.80e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antiparasitics}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{88,760}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.61e-3\ [1.20e-4]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{5.24e-1\ [2.53e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.72e-1\ [1.65e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Anesthetic}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{39,455}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{1.15e-3\ [2.15e-4]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.45e-1\ [4.47e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.39e-1\ [2.31e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Others}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{18,157}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.94e-4\ [4.86e-5]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{4.55e-1\ [2.73e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.37e-1\ [1.77e-1]}}}} \\
+
+\multicolumn{1}{>{\raggedright}m{\dimexpr 1.57in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Antidementia}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 0.75in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{9,937}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{2.00e-4\ [4.76e-5]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{6.80e-1\ [2.85e-1]}}}} & \multicolumn{1}{>{\centering}m{\dimexpr 1.16in+0\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{7.87e-1\ [2.02e-1]}}}} \\
 
@@
 
-\multicolumn{5}{>{\raggedright}m{\dimexpr 5.81in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Defined\ Daily\ Dose,\ representing\ the\ assumed\ average\ maintenance\ dose\ per\ day\ for\ a\ drug\ used\ for\ its\ main\ indication\ in\ adults\ (WHO\ definition).}}}} \\
-
-\multicolumn{5}{>{\raggedright}m{\dimexpr 5.81in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Edge\ weight\ assigned\ to\ each\ medication\ class\ in\ the\ drug\ prescription\ network,\ reflecting\ the\ strength\ of\ co-prescription\ connections\ (see\ Methods:\ Data\ pre-processing\ to\ build\ the\ data\ matrix).}}}} \\
+\multicolumn{5}{>{\raggedright}m{\dimexpr 5.81in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{1}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{SD:\ Standard\ Deviation}}}} \\
+
+\multicolumn{5}{>{\raggedright}m{\dimexpr 5.81in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{2}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Defined\ Daily\ Dose,\ representing\ the\ assumed\ average\ maintenance\ dose\ per\ day\ for\ a\ drug\ used\ for\ its\ main\ indication\ in\ adults\ (WHO\ definition).}}}} \\
+
+\multicolumn{5}{>{\raggedright}m{\dimexpr 5.81in+8\tabcolsep}}{\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{\textsuperscript{3}}}}\textcolor[HTML]{000000}{\fontsize{7}{7}\selectfont{\global\setmainfont{DejaVu Sans}{Edge\ weight\ assigned\ to\ each\ medication\ class\ in\ the\ drug\ prescription\ network,\ reflecting\ the\ strength\ of\ co-prescription\ connections\ (see\ Methods:\ Data\ pre-processing\ to\ build\ the\ data\ matrix).}}}} \\
 
@@
 
-\caption{\label{fig-hi-eigen}Clusters of medication with a significant
-co-prescription patterns on antidepressants and anxiolytics dispensing}
+\caption{\label{fig-hi-eigen}Clusters of medications showing significant
+co-prescription patterns for antidepressnts and anxiolytics. The
+vertical dashed line indicates the expected eigenvector centrality,
+calculated as 1/24. This line provides a reference for identifying
+medication classes with eigenvector centrality exceeding the threshold.}
 

### 2025-12-15 docs/submission/GEPI/supplementary-revision-01/supplementary.tex
Track the revision and its diff

--- 2025-09-22 docs/supplementary.tex
@@
   numbers=noendperiod]{scrartcl}
-
+\usepackage{xcolor}
+\usepackage[inner=2cm,outer=3cm,top=2cm,bottom=2.5cm]{geometry}
 \usepackage{amsmath,amssymb}
+\setcounter{secnumdepth}{3}
 \usepackage{iftex}
@@
 \makeatother
-\usepackage{xcolor}
-\usepackage[inner=2cm,outer=3cm,top=2cm,bottom=2.5cm]{geometry}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{3}
 % Make \paragraph and \subparagraph free-standing
@@
 \makeatother
+
 % definitions for citeproc citations
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
@@
 \makeatother
-
 \usepackage{bookmark}
-
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 \date{}
-
 \begin{document}
@@
 \section{Methods}\label{methods}
+
+\subsection{Exploring seasonality in the
+dataset}\label{exploring-seasonality-in-the-dataset}
+
+Exploration on seasonality was done on detrended daily and weekly data
+by generating seasonal plots and calculating the autocorrelation (ACF)
+and partial autocorrelation function (PACF). Seasonal plots were
+generated for weekly and yearly pattern by using daily and weekly data,
+respectively. To generate the seasonal plots, the data was first
+deconstructed based on its period. For daily data, the weekly period was
+used; while for weekly data, the yearly period was used. The weekly
+period was obtained by creating an ordered value formatted as year -
+week, e.g.~\texttt{2018\ -\ W01}. Similarly, monthly period was obtained
+by creating an ordered value formatted as year - month,
+e.g.~\texttt{2018\ -\ M01}. We then grouped the series by its
+deconstructed period and visually examine seasonality as overlapping
+pattern in most periods. To substantiate the findings, ACF and PACF
+plots were used to check on statistical significance of a given pattern.
 
@@
 
-\begin{longtable}{lllll}
+\begin{longtable}[t]{lllll}
 
